### 2018-07-23 mnras_template.tex
starting repo

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Danielle Skinner et al.]{
Danielle Skinner,$^{1}$\thanks{E-mail: drenniks@gatech.edu}
John H. Wise,$^{1}$
\\
% List of institutions
$^{1}$Center for Relativistic Astrophysics, Georgia Institute of Technology, Atlanta, GA 30332, USA\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2018}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

All papers should start with an Introduction section, which sets the work
in context, cites relevant earlier studies in the field by \citet{Others2013},
and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.

\section{Methods, Observations, Simulations etc.}

Normally the next section describes the techniques the authors used.
It is frequently split into subsections, such as Section~\ref{sec:maths} below.

\subsection{Maths}
\label{sec:maths} % used for referring to this section from elsewhere

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
e.g. Table~\ref{tab:example_table}.

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{example}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \label{fig:example_figure}
\end{figure}

% Example table
\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
Others S., 2012, Journal of Interesting Stuff, 17, 198
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2018-08-21 paper.tex
creating empty paper.tex

--- 2018-07-23 mnras_template.tex
@@
-% mnras_template.tex
+% paper.tex
 %
@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+\section{Methods/Cosmological Simulations}
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{Others2013},
-and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.
+\section{Results}
 
-\section{Methods, Observations, Simulations etc.}
-
-Normally the next section describes the techniques the authors used.
-It is frequently split into subsections, such as Section~\ref{sec:maths} below.
-
-\subsection{Maths}
-\label{sec:maths} % used for referring to this section from elsewhere
-
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
-
-\begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
-\end{equation}
-
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
-
-\subsection{Figures and tables}
-
-Figures and tables should be placed at logical positions in the text. Don't
-worry about the exact layout, which will be handled by the publishers.
-
-Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
-e.g. Table~\ref{tab:example_table}.
-
-% Example figure
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{example}
-    \caption{This is an example figure. Captions appear below each figure.
-	Give enough detail for the reader to understand what they're looking at,
-	but leave detailed discussion to the main body of the text.}
-    \label{fig:example_figure}
-\end{figure}
-
-% Example table
-\begin{table}
-	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\label{tab:example_table}
-	\begin{tabular}{lccr} % four columns, alignment for each
-		\hline
-		A & B & C & D\\
-		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
-		\hline
-	\end{tabular}
-\end{table}
+\section{Discussion}
 
@@
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
-
 \section*{Acknowledgements}
-
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
 
@@
 
-\section{Some extra material}
-
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-08-23 paper.tex
removing files
Adding some subsection titles and bullet points (mostly previous work)

@@
 
+\input{macros.tex}
+
 % Please keep new commands to a minimum, and use \newcommand not \def to avoid
@@
 % These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
+%\date{Accepted XXX. Received YYY; in original form ZZZ}
 
@@
 
-\section{Methods/Cosmological Simulations}
+\li Here are some relevant papers that studied the minimum halo mass
+with simulations or ones that developed an analytical model of the
+halo mass.  We will probably cite most of these in the introduction.
+
+\lli Semi-analytic papers: \citep{Tegmark97, Trenti09, Visbal18,
+  Mebane18, Griffen18}
+
+\lli Simulation papers: \citep{Machacek01, Yoshida03, Wise07_UVB,
+  OShea08, Muratov13}
+
+\lli {\it Note:} I looked at which papers cited the \citet{Machacek01}
+paper to look for recent papers.  I didn't find any in the past five
+years that used simulations to study the minimum halo mass.
+
+\section{Methods}
+
+\subsection{Simulation setup}
+
+We used Enzo \citep{Enzo}.
+
+\subsection{Star formation and feedback}
 
@@
 
+\subsection{Population III host halo masses}
+
+\subsection{Multiple stellar systems}
+
+\subsection{Population III stars in atomic cooling halos}
+
 \section{Discussion}
+
+\subsection{Variations in the halo masses at collapse}
+
+\li Halos can form metal-free stars again if their progenitors had
+only formed stars that did not go supernova
+
+\li Dynamical heating \citep{Yoshida03}
+
+\li Temporal fluctuations in the local Lyman-Werner radiation
+
+\subsection{Comparison to previous work}
+
+\li Semi-analytic papers: \citep{Tegmark97, Trenti09, Visbal18,
+  Mebane18, Griffen18}
+
+\li Simulation papers: \citep{Machacek01, Yoshida03, Wise07_UVB,
+  OShea08, Muratov13}
+
+\li We don't have to compare with all of the semi-analytic papers, but
+it will be good to compare with all of the simulation papers.
+
+\subsection{Caveats}
+
+\li Optically-thin Lyman-Werner radiation field from point sources \citep{Schauer17}
+
+\li No streaming velocities that suppresses star formation at very
+high ($z \ga 20$) redshifts \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}
+
+\li Uncertainties from the assumed Pop III initial mass function
 
@@
 
-%\bibliographystyle{mnras}
-%\bibliography{example} % if your bibtex file is called example.bib
+\bibliographystyle{mnras}
+\bibliography{jwise} % if your bibtex file is called example.bib
 
@@
 % This method is tedious and prone to error if you have lots of references
-\begin{thebibliography}{99}
-\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-Others S., 2012, Journal of Interesting Stuff, 17, 198
-\end{thebibliography}
+%\begin{thebibliography}{99}
+%\end{thebibliography}
 

### 2018-08-23 paper.tex
Adding detailed bullet points for the introduction.  Added acknowledgments.

@@
 
-\li Here are some relevant papers that studied the minimum halo mass
-with simulations or ones that developed an analytical model of the
-halo mass.  We will probably cite most of these in the introduction.
+\noindent Here are some relevant papers that studied the minimum halo
+mass with simulations or ones that developed an analytical model of
+the halo mass.  We will probably cite most of these in the
+introduction.
 
@@
 
+\medskip
+\noindent Here are some bullet points to guide the intro's narrative.
+
+\li The first generation of stars transformed a cold and dark universe
+by illuminating and enriching up their neighborhoods with radiation
+and heavy elements.
+
+\li They are metal-free (Population III; Pop III) and are thought to
+be generally massive and thus a substantial fraction will generate
+prodigious amounts of ionizing photons and will end their lives in
+supernovae \citep[e.g.][]{Schaerer02, Heger02}.
+
+\li Once a halo becomes chemically enriched, by definition, it cannot
+form Pop III stars anymore, marking the end of metal-free star
+formation in that pregalactic object.  Numerical studies have shown
+that turbulence within halos can mix metals well down to their
+resolution limit \citep[][and more]{Wise08_Gal, Greif10}.
+
+\li Given the paradigm of hierarchical structure formation, halos grow
+through smooth accretion and successive mergers of smaller halos.  But
+in which halos do these first generations of stars form?  Their
+formation rates and locations are important to constrain because they
+influence the very beginnings of galaxy formation and cosmic
+reionization.
+
+\li Without metals and dust to facilitate efficient radiative cooling,
+Pop III stars rely on \hh{} formation to cool the gas.  These
+molecules are however fragile to dissociation from Lyman-Werner
+(LW) radiation in the energy range 11.2--13.6~eV.
+
+\li Diffuse gas is optically thin to LW radiation, thus a background
+builds over time and can suppress \hh{} formation and thus Pop III
+star formation.  Furthermore, nearby sources of LW radiation can
+dissociate \hh{} in minihalos.
+
+\li Other sources of the suppression of Pop III star formation are
+streaming baryonic velocities, arising from recombination, and
+dynamical heating, occuring during the virialization of halos.
+
+\li Previous work have mainly investigated and established the lower
+limit for a halo to host Pop III stars.  However, subsequent
+simulations have shown that they don't necessarily form at this
+minimum, whereas other physical processes (mentioned above) play a
+role.
+
+\li In this paper, we focus on the distribution of host halo masses,
+not just the minimum, and its dependence on redshift and the LW
+background, augmenting the results from prior work.
+
+\medskip
+\noindent Include the ``typical'' overview of the paper's sections
+last in the introduction.
+
 \section{Methods}
@@
 
-We used Enzo \citep{Enzo}.
+We used \enzo{} \citep{Enzo} and \yt{} \citep{yt_full_paper}.
 
@@
 
+See \citet{Wise14}.
+
 \section{Results}
+
+Temporary list of figures:
+\begin{enumerate}
+\item One
+\item Two
+\end{enumerate}
 
@@
 
+JHW is supported by National Science Foundation grants AST-1614333 and
+OAC-1835213, NASA grant NNX17AG23G, and Hubble theory grant
+HST-AR-14326.  We thank the support staff at Georgia Tech's PACE,
+where we ran this simulation.  The freely available plotting library
+{\sc matplotlib} \citep{matplotlib} was used to construct numerous
+plots within this paper. Computations and analysis described in this
+work were performed using the publicly-available \enzo{} and \yt{}
+codes, which is the product of a collaborative effort of many
+independent scientists from numerous institutions around the world.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-19 paper.tex
Adding list of figures

@@
 \begin{enumerate}
-\item One
-\item Two
+\item Mean Halo Mass vs. Redshift - plotted with Machacek relation - mean\_mass\_errorb\_fix.png
+\item Jlw/J21 total vs. Halo Mass colored by redshift - plotted with Machacek relation - jlw\_mass\_machacek\_total.png
+\item Percentage of Halos Below Machacek - percent\_below\_dz1.png 
+\item Jlw/J21 vs. Halo Mass colored by redshift - plotted with Machacek relation ??  - jlw\_mass\_machacek.png
+\item Halo mass vs. redshift colored by total Jlw - plotted with background Machacek relation ?? - mass\_redshift\_machacek\_clocal.png
+\item SFRD of PopIII Stars - pop3\_SFR\_bar.png
+\item Total # of PopIII Stars vs. Halo mass 2d histogram - tot\#p3\_halomass\_sidehist.png
+\item Total mass of PopIII stars vs. halo mass 2d histogram - plotted with SFE - totp3mass\_halomass\_sidehist.png
+
 \end{enumerate}

### 2018-10-01 paper.tex
Rough methods written

@@
 \usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
+% Depending on your LaTeX fonts installation, you might get better results with 
+% one of these:
 %\usepackage{mathptmx}
@@
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{mathtools}
 
@@
 \input{macros.tex}
+\makeatletter
+\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
+\makeatother
 
@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
+\title[Where Do Pop III Stars Form?]{Where Do Population III Stars Form?}
 
@@
 % List of institutions
-$^{1}$Center for Relativistic Astrophysics, Georgia Institute of Technology, Atlanta, GA 30332, USA\\
+$^{1}$Center for Relativistic Astrophysics, Georgia Institute of Technology, 
+Atlanta, GA 30332, USA\\
 }
@@
 This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
+The abstract should briefly describe the aims, methods, and main results of the 
+paper.
 It should be a single paragraph not more than 250 words (200 words for Letters).
@@
 
+%====================================================================
 \section{Methods}
+%====================================================================
+\subsection{Simulation setup}
+%====================================================================
+This simulation is an expansion of the analysis done on the 
+simulations from Wise et al. (2014, hereafter W14) and Wise et al. 
+(2012b, hereafter W12).
+W12 focused on the role of radiation pressure in simulated halos and W14 was an extension of the W12 paper, specifically looking at the simulation including radiation pressure.
+While the cosmological parameters are updated to the 2013 Planck release \citet{Planck13_Cosmo} for this simulation, much of the physics is the same as W12 and W14.
+For more detailed descriptions, refer to W12 and W14.
 
-\subsection{Simulation setup}
+This simulation was run with an adaptive mesh refinement (AMR) code 
+\enzo{} \citep{Enzo} and \yt{} \citep{yt_full_paper} for visualization.
+\enzo{} uses an N-body adaptive particle-mesh solver \citep{Efstathiou85, Couchman91, BryanNorman1997} to follow the dark matter (DM) dynamics.
+We use the nine-species (H \rom{1}, H \rom{2}, He \rom{1}, He \rom{2}, He \rom{3}, e$^{-}$, H$_{2}$, H$_{2}^{+}$, H$^{-}$) non-equilibrium chemistry model \citep{Abel97, Anninos97}.
 
-We used \enzo{} \citep{Enzo} and \yt{} \citep{yt_full_paper}.
+We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
+resolution. We have a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
+initialized with \music{} \citep{Hahn11_MUSIC} at z = 130 and use the cosmological parameters from the Planck collaboration best fit 
+\citet{Planck13_Cosmo}: $\Omega_{M}$ = 0.3175, $\Omega_{\Lambda}$ = 
+0.6825, $\Omega_{DM}$ = 0.2685, and h = 0.6711, with the variables 
+having their usual definitions. The simulation is run until z = 9.32. In this paper, we focus only on outputs where new Pop III stars are born, from z = 27.23 to 9.39.
 
-\subsection{Star formation and feedback}
+A time-dependent Lyman-Werner (LW) optically thin radiation background is applied in the simulation.
+This was fit in W12 (see Eqn.
+16) and is consistent with the values in \citet{Trenti09_SFR}.
+The background evolution of the specific intensity takes the following form:
+\begin{equation}
+	log_{10}(J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
+\end{equation}
+where (A, B, C, D, E) = (-2.567, 0.4562, - 0.02680, 5.882 $\times$ 10$^{-4}$, - 5.056 $\times$ 10$^{-6}$) and J$_{21}$ is the specific intensity in units of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.
 
-See \citet{Wise14}.
+Adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} is used to evolve the radiation field.
+Centered on each Pop II and Pop III star, we model the H$_{2}$ dissociating radiation field with an optically thin, inverse square profile.
+These LW sources are added on top of the background intensity described above.
+(When to describe how we caculate the total Lyman-Werner flux of the halos?)
+%====================================================================
+\subsection{Star formation}
+%====================================================================
+In this section, we will discuss how we implement Pop III and Pop II 
+star formation. No other types of stars are considered. For further 
+details, refer to W14 and W12.
 
+%====================================================================
+\subsubsection{Pop III Star Formation and Feedback }
+%====================================================================
+The implemented Pop III star formation model is the same as in Wise \& Abel (2008). Each star particle represents a single star, and is formed in a cell when the following criteria are met: 
+\begin{enumerate}
+	\item Z $\leq$ 6.85 $\times$ 10$^{-8}$
+
+	\item particle overdensity of 1 $\times$ 10$^{6}$ 
+		particles/cm$^{3}$
+
+	\item converging gas flow, $\nabla \cdot \mathbf{v_{gas}}$ < 0
+
+	\item molecular hydrogen fraction, f$_{H2}$ > 0.001
+\end{enumerate}
+
+If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.
+The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
+\begin{equation}
+	f(log_{M})dM = M^{-1.3}exp \Big[-\left( \frac{M_{char}}{M}\right)^{1.6} \Big]dM
+\end{equation}
+where M$_{char}$ = 20 M$_{\odot}$.
+This characteristic mass is different from W12 and W14 (would like to find a citation for this number, having a hard time tracking down some John had suggested).
+This results in an exponential cutoff before M$_{char}$ and a Salpeter IMF after.
+Once the cell meets the above criteria and the mass of the star is randomly determined, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
+The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere.
+
+We use the mass-dependent hydrogen ionising Lyman-Werner (LW) luminosities and lifetimes from Schaerer (2002) and a mass-independent photon energy of E$_{ph}$ = 29.6 ev, which is appropriate for the approximately constant surface temperature of Pop III stars, at 10$^{5}$ K.
+A Type II supernova results if the Pop III star dies with a mass between $\leq$ M$_{\ast}$/M$_{\odot}$ $\leq$ 40 M$_{\odot}$.
+A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\ast}$/M$_{\odot}$ $\leq$ 260 M$_{\odot}$.
+Outside of these mass ranges, the Pop III star dies as a black hole.
+In this simulation, no black hole physics are implemented, so the Pop III star simply turns into a dark matter particle.
+From 11 $\leq$ M$_{\ast}$/M$_{\odot}$ < 20 M$_{\odot}$, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg.
+From 20 $\leq$ M$_{\ast}$/M$_{\odot}$ $\leq$ 40 M$_{\odot}$, the star dies as a hypernova with energies taken from \citet{Nomoto06}.
+The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq. 12 of W12.
+
+%====================================================================
+\subsubsection{Pop II  Star Formation and Feedback}
+%====================================================================
+The Pop II star formation model is the same as Wise \& Cen (2009), which is equivalent to the above criteria for Pop III star formation but without the molecular hydrogen fraction requirement, and with a metallicity greater than the above value.
+Star formation is only allowed for gas with temperatures T < 1000 K, to ensure that the volume is cooling.
+Contrary to Pop III stars representing single star particles, Pop II star particles are modelled as clusters of Pop II stars.
+The mass of these clusters is determined from a Salpeter IMF with a minimum mass of M$_{min}$ = 1000 M$_{\odot}$.
+
+The lifetime of these particles is 20 Myr, during which they radiate 6000 hydrogen ionizing photons per stellar baryon.
+The photons exhibit a monochromatic spectrum with an energy of 21.6 eV.
+After living for 4 Myr, the Pop II stars generate supernova energies of 6.8 $\times$ 10$^{48}$ erg s$^{-1}$ M$_{\odot}^{-1}$.
+
+%====================================================================
+\subsection{H2 Shielding}
+%====================================================================
+We use the Sobolev-like approximation from \citet{Wolcott11} to model H2 self-shielding. To determine the H2 shielding factor, the column density of H2 needs to be calculated:
+\begin{equation}
+	N_{H_{2}} = n_{H_{2}}L_{char}
+\end{equation}
+Where n$_{H_{2}}$ is the number density of H2 and L$_{char}$ is a characteristic length over which n$_{H_{2}}$ is assumed to be constant.
+The method employed in this simulation is to define the characteristic length as:
+\begin{equation}
+	L_{char} = \frac{\rho}{|\nabla \rho|}
+\end{equation}
+This Sobolev-like method determines the length over which gas with density $\rho$ is diminished.
+The most accurate, non-ray tracing, method is to use a single Sobolev-like length determined from the mean Sobolev-like length over all directions.
+
+Upon numerically calculating the shielding factor of H2 for simulated protogalaxies, Wolcott-Green et al.
+determine that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures.
+The implemented shielding factor is then (see Eqn.
+10 in \citet{Wolcott11}):
+\begin{equation}
+	\begin{multlined}
+	f_{sh}(N_{H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
+	\end{multlined}
+\end{equation}
+Here, x $\equiv$ N$_{H_{2}}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and b is the Doppler broadening parameter. N$_{H_{2}}$ is then calculated as described above.
+
+%====================================================================
 \section{Results}
-
+%====================================================================
 Temporary list of figures:
 \begin{enumerate}
+\item hmf.png
 \item Mean Halo Mass vs. Redshift - plotted with Machacek relation - mean\_mass\_errorb\_fix.png
@@
 \item SFRD of PopIII Stars - pop3\_SFR\_bar.png
-\item Total # of PopIII Stars vs. Halo mass 2d histogram - tot\#p3\_halomass\_sidehist.png
+\item Total \# of PopIII Stars vs. Halo mass 2d histogram - tot\#p3\_halomass\_sidehist.png
 \item Total mass of PopIII stars vs. halo mass 2d histogram - plotted with SFE - totp3mass\_halomass\_sidehist.png
@@
 
+%====================================================================
 \subsection{Population III host halo masses}
+%====================================================================
 
+%====================================================================
 \subsection{Multiple stellar systems}
+%====================================================================
 
+%====================================================================
 \subsection{Population III stars in atomic cooling halos}
+%====================================================================
 
+%====================================================================
 \section{Discussion}
+%====================================================================
 
+%====================================================================
 \subsection{Variations in the halo masses at collapse}
+%====================================================================
 
@@
 
+%====================================================================
 \subsection{Comparison to previous work}
+%====================================================================
 
@@
 
+%====================================================================
 \subsection{Caveats}
+%====================================================================
 
@@
 
+%====================================================================
 \section{Conclusions}
+%====================================================================
 
+%====================================================================
 \section*{Acknowledgements}
+%====================================================================
 

### 2018-10-02 paper.tex
adding rough introduction -- need to add sources and further details about previous work

@@
 \medskip
-\noindent Here are some bullet points to guide the intro's narrative.
 
-\li The first generation of stars transformed a cold and dark universe
+The first generation of stars transformed a cold and dark universe
 by illuminating and enriching up their neighborhoods with radiation
 and heavy elements.
+The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments is necessary for further star production and chemical enrichment.
+Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today.
+These stars are, by definition, metal-free (Population III; Pop III) and are thought to be generally massive.
+A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
+The supernova will spread the enriched guts of the Pop III star out across it's local environment, providing the area with chemicals the universe has not yet seen.
 
-\li They are metal-free (Population III; Pop III) and are thought to
-be generally massive and thus a substantial fraction will generate
-prodigious amounts of ionizing photons and will end their lives in
-supernovae \citep[e.g.][]{Schaerer02, Heger02}.
+Once a halo becomes chemically enriched by the death of it's Pop III stars, then by definition, it can no longer form more Pop III stars.
+This marks the end of metal-free star formation in that pregalactic object.
+Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation.
+Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10}.
+Stars will continue to form in halos, but with an increase metal abundance, these stars are now labelled as Population II, or Pop II, stars.
+Pop II stars are considered metal-poor, relative to their metal-free Pop III progenitors, and are observable in the universe.
+Understanding the formation and chemical abundance of Pop II stars can provide more evidence and insight for the earlier generation of Pop III stars.
 
-\li Once a halo becomes chemically enriched, by definition, it cannot
-form Pop III stars anymore, marking the end of metal-free star
-formation in that pregalactic object.  Numerical studies have shown
-that turbulence within halos can mix metals well down to their
-resolution limit \citep[][and more]{Wise08_Gal, Greif10}.
+Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos.
+But in which halos do these first generations of stars form?
+Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization.
+Learning about their host halos can also guide future telescopic surveys to observe Pop III galaxies which may lead to direct observational evidence for Pop III stars.
+Without metals and dust to facilitate efficient radiative cooling, Pop III stars rely on \hh{} formation to cool the gas.
+These molecules are however fragile to dissociation from Lyman-Werner (LW) radiation in the energy range 11.2--13.6~eV, through the Soloman process :
+\begin{equation}
+	H_{2} + \gamma \rightarrow  H + H
+\end{equation}
+Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, prohibiting Pop III star formation.
+Furthermore, nearby sources of LW radiation can dissociate \hh{} in minihalos.
+This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding.
+Halos with an \hh{} column density of N$_{H_{2}}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons, giving the halo a chance to form Pop III stars.
+Other sources of the suppression of Pop III star formation are streaming baryonic velocities, arising from recombination, and dynamical heating, occuring during the virialization of halos.
 
-\li Given the paradigm of hierarchical structure formation, halos grow
-through smooth accretion and successive mergers of smaller halos.  But
-in which halos do these first generations of stars form?  Their
-formation rates and locations are important to constrain because they
-influence the very beginnings of galaxy formation and cosmic
-reionization.
+Previous work have mainly investigated and established the lower limit for a halo to host Pop III stars, or for a halo to collapse.
+However, subsequent simulations have shown that they don't necessarily form at this minimum due to other physical processes (mentioned above) playing a role.
 
-\li Without metals and dust to facilitate efficient radiative cooling,
-Pop III stars rely on \hh{} formation to cool the gas.  These
-molecules are however fragile to dissociation from Lyman-Werner
-(LW) radiation in the energy range 11.2--13.6~eV.
-
-\li Diffuse gas is optically thin to LW radiation, thus a background
-builds over time and can suppress \hh{} formation and thus Pop III
-star formation.  Furthermore, nearby sources of LW radiation can
-dissociate \hh{} in minihalos.
-
-\li Other sources of the suppression of Pop III star formation are
-streaming baryonic velocities, arising from recombination, and
-dynamical heating, occuring during the virialization of halos.
-
-\li Previous work have mainly investigated and established the lower
-limit for a halo to host Pop III stars.  However, subsequent
-simulations have shown that they don't necessarily form at this
-minimum, whereas other physical processes (mentioned above) play a
-role.
-
-\li In this paper, we focus on the distribution of host halo masses,
-not just the minimum, and its dependence on redshift and the LW
-background, augmenting the results from prior work.
-
-\medskip
-\noindent Include the ``typical'' overview of the paper's sections
-last in the introduction.
+In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background, augmenting results from prior work.
+We aim to provide further insight into the host halos of Pop III stars.
+In \S 2 the methods of the simulation, implementation of star formation, feedback, and \hh{} self-shielding is described.
+In \S 3 we present the results of our analysis.
+In \S 4 we discuss the results in more detail and compare with previous work.
+In \S 5 we conclude our discussion with a summary of our results and the implications therein.
 

### 2018-10-10 paper.tex
adding figures/captions and rough introduction

@@
 %%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
+%====================================================================
 \section{Introduction}
-
-\noindent Here are some relevant papers that studied the minimum halo
-mass with simulations or ones that developed an analytical model of
-the halo mass.  We will probably cite most of these in the
-introduction.
-
-\lli Semi-analytic papers: \citep{Tegmark97, Trenti09, Visbal18,
-  Mebane18, Griffen18}
-
-\lli Simulation papers: \citep{Machacek01, Yoshida03, Wise07_UVB,
-  OShea08, Muratov13}
-
-\lli {\it Note:} I looked at which papers cited the \citet{Machacek01}
-paper to look for recent papers.  I didn't find any in the past five
-years that used simulations to study the minimum halo mass.
-
-\medskip
+%====================================================================
 
@@
 A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
-The supernova will spread the enriched guts of the Pop III star out across it's local environment, providing the area with chemicals the universe has not yet seen.
+The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.
 
-Once a halo becomes chemically enriched by the death of it's Pop III stars, then by definition, it can no longer form more Pop III stars.
+Once a halo becomes chemically enriched by the death of its Pop III stars, then by definition, it can no longer form more Pop III stars.
 This marks the end of metal-free star formation in that pregalactic object.
@@
 Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10}.
-Stars will continue to form in halos, but with an increase metal abundance, these stars are now labelled as Population II, or Pop II, stars.
-Pop II stars are considered metal-poor, relative to their metal-free Pop III progenitors, and are observable in the universe.
-Understanding the formation and chemical abundance of Pop II stars can provide more evidence and insight for the earlier generation of Pop III stars.
+Stars will continue to form in halos, but with an increased metal abundance, these stars are now labelled as metal-enriched stars.
+These stars still are considered metal-poor, relative to the solar abundance, and are observable in the universe.
+Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.
 
@@
 Learning about their host halos can also guide future telescopic surveys to observe Pop III galaxies which may lead to direct observational evidence for Pop III stars.
+Previous studies have investigated the possibility of finding Pop III systems.
+\citep{Trenti09} found that metal-free halos may still be able to form at $z \approx$ 6, which offer the best chance at observing such primordial systems.
+Given a certain rate of Pop III supernova per year, large sky surveys, such as the Large Synoptic Survey Telescope (LSST), should be able to detect the very luminous supernova.
+Unless the metal-free systems are particularly efficient at forming Pop III stars (star formation efficiences > 10$^{-2}$), the upcoming James Webb Space Telescope (JWST) will not be able to detect such systems.
+
+Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars.
+\citep{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15.
+In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time.
+\citep{Visbal18} came up with a semi-analytic model for the formation of Pop III stars and the transition from Pop III to metal-enriched stars.
+They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing espcape fraction, leads to large differencies in the star formation history of Pop III and metal-enriched stars.
+This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.
+
 Without metals and dust to facilitate efficient radiative cooling, Pop III stars rely on \hh{} formation to cool the gas.
-These molecules are however fragile to dissociation from Lyman-Werner (LW) radiation in the energy range 11.2--13.6~eV, through the Soloman process :
-\begin{equation}
-	H_{2} + \gamma \rightarrow  H + H
+These molecules are however fragile to dissociation from Lyman-Werner (LW) radiation in the energy range 11.2--13.6~eV, through the Solomon process \citep{Field66, Stecher67}.
+This is a two-step process through which H$_{2}$ is excited to a higher state, H$_{2}^{\ast}$, via absorption of a LW photon:
+\begin{equation} \label{Solomon1}
+	H_{2} + \gamma \rightarrow  H_{2}^{\ast}
 \end{equation}
+This excited state then has a probability of dissociating into two hydrogen atoms:
+\begin{equation} \label{Solomon2}
+	H_{2}^{\ast} \rightarrow H + H
+\end{equation}
+
 Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, prohibiting Pop III star formation.
-Furthermore, nearby sources of LW radiation can dissociate \hh{} in minihalos.
+Furthermore, nearby sources of LW radiation can boost the intensity above the background value which facilitates further \hh{} dissociation in minihalos.
 This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding.
@@
 Previous work have mainly investigated and established the lower limit for a halo to host Pop III stars, or for a halo to collapse.
-However, subsequent simulations have shown that they don't necessarily form at this minimum due to other physical processes (mentioned above) playing a role.
+However, subsequent simulations have shown that they do not necessarily form at this minimum due to the aforementioned physical processes playing a role.
+\citep{Mebane18} used a semi-analytic model of early star formation and found that the LW background coming from the rapidly increasing supply of Pop III stars becomes responsible for suppressing Pop III star formation.
+Pop III supernova feedback is another key process which can allow Pop III stars to continue to form, as long as the metals are ejected from the host halo.
+\citep{Griffen18} also find that the LW background can significantly suppress the amount of potential sites for Pop III star formation.
+
+Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation.
+\citep{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
+They derive a simple analytic expression for the mass threshold of halos given a particular LW flux.
+We will compare our results with this relation in future sections.
+\citep{yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
+In fact, \citep{Wise07_UVB} found that central shocks drives \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$.
+They find that \hh{} cooling is always a dominant process, even in large LW background fluxes.
+Assisting this result, \citep{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, indicating that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
 
@@
 %====================================================================
-This simulation is an expansion of the analysis done on the 
-simulations from Wise et al. (2014, hereafter W14) and Wise et al. 
-(2012b, hereafter W12).
-W12 focused on the role of radiation pressure in simulated halos and W14 was an extension of the W12 paper, specifically looking at the simulation including radiation pressure.
-While the cosmological parameters are updated to the 2013 Planck release \citet{Planck13_Cosmo} for this simulation, much of the physics is the same as W12 and W14.
-For more detailed descriptions, refer to W12 and W14.
-
 This simulation was run with an adaptive mesh refinement (AMR) code 
-\enzo{} \citep{Enzo} and \yt{} \citep{yt_full_paper} for visualization.
+\enzo{} \citep{Enzo} and analyzed with the toolkit, \yt{} \citep{yt_full_paper}.
 \enzo{} uses an N-body adaptive particle-mesh solver \citep{Efstathiou85, Couchman91, BryanNorman1997} to follow the dark matter (DM) dynamics.
-We use the nine-species (H \rom{1}, H \rom{2}, He \rom{1}, He \rom{2}, He \rom{3}, e$^{-}$, H$_{2}$, H$_{2}^{+}$, H$^{-}$) non-equilibrium chemistry model \citep{Abel97, Anninos97}.
+We use the nine-species (\hi, \hii, \hei, \heii, \heiii, e$^{-}$, H$_{2}$, H$_{2}^{+}$, H$^{-}$) non-equilibrium chemistry model \citep{Abel97, Anninos97}.
+This simulation is similar to the RP simulation in
+\citet[hereafter W12]{Wise12_RP}, but with updated cosmological and Pop III parameters, and the inclusion of \hh{} shielding.
 
@@
 resolution. We have a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
-initialized with \music{} \citep{Hahn11_MUSIC} at z = 130 and use the cosmological parameters from the Planck collaboration best fit 
+initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and use the cosmological parameters from the Planck collaboration best fit 
 \citet{Planck13_Cosmo}: $\Omega_{M}$ = 0.3175, $\Omega_{\Lambda}$ = 
 0.6825, $\Omega_{DM}$ = 0.2685, and h = 0.6711, with the variables 
-having their usual definitions. The simulation is run until z = 9.32. In this paper, we focus only on outputs where new Pop III stars are born, from z = 27.23 to 9.39.
+having their usual definitions.
+The simulation is run until $z$ = 9.32, when it becomes too computationally expensive to continue.
+At this point, 20\% of the volume is ionized.
+In this paper, we focus only on outputs where new Pop III stars are born, from $z$ = 27.23 to 9.39.
 
-A time-dependent Lyman-Werner (LW) optically thin radiation background is applied in the simulation.
-This was fit in W12 (see Eqn.
+A time-dependent LW optically thin radiation background is applied in the simulation.
+This was fit in W12 (see their Eq.
 16) and is consistent with the values in \citet{Trenti09_SFR}.
 The background evolution of the specific intensity takes the following form:
-\begin{equation}
-	log_{10}(J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
+\begin{equation} \label{LWbg}
+	\log_{10}(J_{LW}/J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
 \end{equation}
-where (A, B, C, D, E) = (-2.567, 0.4562, - 0.02680, 5.882 $\times$ 10$^{-4}$, - 5.056 $\times$ 10$^{-6}$) and J$_{21}$ is the specific intensity in units of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.
+where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.
 
 Adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} is used to evolve the radiation field.
-Centered on each Pop II and Pop III star, we model the H$_{2}$ dissociating radiation field with an optically thin, inverse square profile.
+Centered on each metal-enriched and Pop III star, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile.
 These LW sources are added on top of the background intensity described above.
-(When to describe how we caculate the total Lyman-Werner flux of the halos?)
 %====================================================================
@@
 %====================================================================
-In this section, we will discuss how we implement Pop III and Pop II 
-star formation. No other types of stars are considered. For further 
-details, refer to W14 and W12.
+In this section, we will discuss how we implement Pop III and metal-enriched star formation.
+We do not consider the formation and feedback from stellar remnants or asymptotic giant branch (AGB) stars.
+For further details, we refer the reader to W12.
 
@@
 \begin{enumerate}
-	\item Z $\leq$ 6.85 $\times$ 10$^{-8}$
+	\item a metallicity Z $\leq$ 5 $\times$ 10$^{-6}$ Z$_{\odot}$
 
-	\item particle overdensity of 1 $\times$ 10$^{6}$ 
-		particles/cm$^{3}$
+	\item a gas number density n > 10$^{6}$ cm$^{-3}$
 
@@
 
-	\item molecular hydrogen fraction, f$_{H2}$ > 0.001
+	\item molecular hydrogen fraction, f$_{\rm H2}$ > 10$^{-3}$
 \end{enumerate}
@@
 The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
-\begin{equation}
-	f(log_{M})dM = M^{-1.3}exp \Big[-\left( \frac{M_{char}}{M}\right)^{1.6} \Big]dM
+\begin{equation} \label{IMF}
+	f(\log M)dM = M^{-1.3} \exp \Big[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \Big]dM
 \end{equation}
-where M$_{char}$ = 20 M$_{\odot}$.
+where M$_{\rm char}$ = 20 M$_{\odot}$.
 This characteristic mass is different from W12 and W14 (would like to find a citation for this number, having a hard time tracking down some John had suggested).
 This results in an exponential cutoff before M$_{char}$ and a Salpeter IMF after.
-Once the cell meets the above criteria and the mass of the star is randomly determined, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
+Once the cell meets the above criteria and the mass of the star is randomly determined from Eq.
+3, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
 The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere.
 
-We use the mass-dependent hydrogen ionising Lyman-Werner (LW) luminosities and lifetimes from Schaerer (2002) and a mass-independent photon energy of E$_{ph}$ = 29.6 ev, which is appropriate for the approximately constant surface temperature of Pop III stars, at 10$^{5}$ K.
-A Type II supernova results if the Pop III star dies with a mass between $\leq$ M$_{\ast}$/M$_{\odot}$ $\leq$ 40 M$_{\odot}$.
-A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\ast}$/M$_{\odot}$ $\leq$ 260 M$_{\odot}$.
+We use the mass-dependent hydrogen ionising LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K.
+A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\ast}$/M$_{\odot}$ $\leq$ 40 M$_{\odot}$.
+A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 260 M$_{\odot}$.
 Outside of these mass ranges, the Pop III star dies as a black hole.
-In this simulation, no black hole physics are implemented, so the Pop III star simply turns into a dark matter particle.
-From 11 $\leq$ M$_{\ast}$/M$_{\odot}$ < 20 M$_{\odot}$, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg.
-From 20 $\leq$ M$_{\ast}$/M$_{\odot}$ $\leq$ 40 M$_{\odot}$, the star dies as a hypernova with energies taken from \citet{Nomoto06}.
-The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq. 12 of W12.
+In this simulation, no black hole physics are implemented, so the Pop III star simply turns into a collisionless particle.
+From 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20 M$_{\odot}$, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg.
+From 20 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40 M$_{\odot}$, the star dies as a hypernova with energies taken from \citet{Nomoto06}.The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq.
+12 of W12.
 
@@
 The Pop II star formation model is the same as Wise \& Cen (2009), which is equivalent to the above criteria for Pop III star formation but without the molecular hydrogen fraction requirement, and with a metallicity greater than the above value.
-Star formation is only allowed for gas with temperatures T < 1000 K, to ensure that the volume is cooling.
-Contrary to Pop III stars representing single star particles, Pop II star particles are modelled as clusters of Pop II stars.
-The mass of these clusters is determined from a Salpeter IMF with a minimum mass of M$_{min}$ = 1000 M$_{\odot}$.
+Star formation is only allowed for gas with temperatures $T$ < 1000 K, to ensure that the volume is cold and collapsing.
+Contrary to Pop III stars representing single star particles, metal-enriched star particles are modelled as clusters of stars.
+We enforce a minimum mass of M$_{min}$ = 1000 M$_{\odot}$ for these star particles.
 
-The lifetime of these particles is 20 Myr, during which they radiate 6000 hydrogen ionizing photons per stellar baryon.
-The photons exhibit a monochromatic spectrum with an energy of 21.6 eV.
-After living for 4 Myr, the Pop II stars generate supernova energies of 6.8 $\times$ 10$^{48}$ erg s$^{-1}$ M$_{\odot}^{-1}$.
+The lifetime of these particles is 20 Myr, during which they radiate 6000 hydrogen ionising photons per stellar baryon, or 1.13 $\times$ 10$^{46}$ photons s$^{-1}$ M$_{\odot}^{-1}$, which is appropriate for a Salpeter IMF.
+Their spectra are approximated with a monochromatic spectrum with an energy of 21.6 eV at a constant luminosity.
+After living for 4 Myr, the stars generate supernova energies of 6.8 $\times$ 10$^{48}$ erg s$^{-1}$ M$_{\odot}^{-1}$.
 
 %====================================================================
-\subsection{H2 Shielding}
+\subsection{\hh{} Shielding}
 %====================================================================
-We use the Sobolev-like approximation from \citet{Wolcott11} to model H2 self-shielding. To determine the H2 shielding factor, the column density of H2 needs to be calculated:
-\begin{equation}
-	N_{H_{2}} = n_{H_{2}}L_{char}
+We use the Sobolev-like approximation from \citet{Wolcott11} to model \hh{} self-shielding. To determine the \hh{} shielding factor, the column density of \hh{} needs to be calculated:
+\begin{equation} \label{Nh2}
+	N_{H_{2}} = n_{H_{2}}L_{\rm char}
 \end{equation}
-Where n$_{H_{2}}$ is the number density of H2 and L$_{char}$ is a characteristic length over which n$_{H_{2}}$ is assumed to be constant.
+Where n$_{H_{2}}$ is the number density of \hh{} and L$_{\rm char}$ is a characteristic length over which n$_{H_{2}}$ is assumed to be constant.
 The method employed in this simulation is to define the characteristic length as:
-\begin{equation}
-	L_{char} = \frac{\rho}{|\nabla \rho|}
+\begin{equation} \label{Lchar}
+	L_{\rm char} = \frac{\rho}{|\nabla \rho|}
 \end{equation}
 This Sobolev-like method determines the length over which gas with density $\rho$ is diminished.
-The most accurate, non-ray tracing, method is to use a single Sobolev-like length determined from the mean Sobolev-like length over all directions.
+The most accurate, non-ray tracing, method is to use a single Sobolev-like length determined from the mean Sobolev-like length over all cartesian directions.
 
@@
 determine that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures.
-The implemented shielding factor is then (see Eqn.
+The implemented shielding factor is then (see Eq.
 10 in \citet{Wolcott11}):
-\begin{equation}
+\begin{equation} \label{shield}
 	\begin{multlined}
@@
 \end{equation}
-Here, x $\equiv$ N$_{H_{2}}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and b is the Doppler broadening parameter. N$_{H_{2}}$ is then calculated as described above.
+Here, x $\equiv$ N$_{H_{2}}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. N$_{H_{2}}$ is then calculated as described above.
 
@@
 %====================================================================
-Temporary list of figures:
+Possible other figures:
 \begin{enumerate}
-\item hmf.png
-\item Mean Halo Mass vs. Redshift - plotted with Machacek relation - mean\_mass\_errorb\_fix.png
-\item Jlw/J21 total vs. Halo Mass colored by redshift - plotted with Machacek relation - jlw\_mass\_machacek\_total.png
-\item Percentage of Halos Below Machacek - percent\_below\_dz1.png 
 \item Jlw/J21 vs. Halo Mass colored by redshift - plotted with Machacek relation ??  - jlw\_mass\_machacek.png
 \item Halo mass vs. redshift colored by total Jlw - plotted with background Machacek relation ?? - mass\_redshift\_machacek\_clocal.png
-\item SFRD of PopIII Stars - pop3\_SFR\_bar.png
-\item Total \# of PopIII Stars vs. Halo mass 2d histogram - tot\#p3\_halomass\_sidehist.png
-\item Total mass of PopIII stars vs. halo mass 2d histogram - plotted with SFE - totp3mass\_halomass\_sidehist.png
+\end{enumerate}
 
-\end{enumerate}
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/hmf.png}
+    \caption{Halo mass function of the last output of the simulation at $z$ = 9.3.
+The thick line is the analytic Sheth-Tormen mass function.
+The distribution of halo masses matches well with Sheth-Tormen until about 10$^{5}$ M$_{\odot}$.}
+    \label{fig:hmf}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.png}
+    \caption{For halos hosting new Pop III stars, the mean halo mass is plotted versus redshift, in bins of $\Delta z$ = 1.
+The Machacek et al.
+minimum mass threshold is plotted for the constant LW background given in Eq.
+\ref{LWbg}.
+The mean halo masses fall below the relation until a redshift of 12.5, at which point the mean halo masses rise above the relation.}
+    \label{fig:mean_mass}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/jlw_mass_machacek_total.png}
+    \caption{The average LW background for host halos of new Pop III stars is plotted versus the host halo mass, colored by redshift.
+The Machacek et al.
+relation is plotted given the background LW in Eq.
+\ref{LWbg}.
+Almost all halos fall below the relation, across a range of redshifts.
+A few halos (or possibly a single halo) allow Pop III stars to form at a low halo mass in a very high LW background.
+There are a few halos that have Pop III stars forming at later times and at high halo masses.}
+    \label{fig:jlw_mass_machacek}{}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/percent_below_dz1.png}
+    \caption{The percentage of halos that form Pop III stars below the minimum mass threshold from \citet{Machacek01}, in bins of $\Delta z$ = 1.
+As seen in \ref{fig:jlw_mass_machacek}, almost all halos form below the mass threshold.}
+    \label{fig:percent_below_dz1}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.png}
+    \caption{The star formation rate density of Pop III stars. It peaks at a redshift of 20, and slowly falls off.}
+    \label{fig:pop3_SFR_bar}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/totnump3_halomass_sidehist.png}
+    \caption{Total number of Pop III stars in halos hosting new Pop III stars versus halo mass.
+A median number of four Pop III stars form in a single halo, with some forming as many as 16 Pop III stars.}
+    \label{fig:totnump3_halomass_sidehist}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/totp3mass_halomass_sidehist.png}
+    \caption{Total mass of Pop III stars in halos hosting new Pop III stars versus halo mass.
+Lines of constant star formation efficiencies are overplotted.
+Most halos form Pop III stars at efficiencies between 10$^{-3}$ and 10$^{-4}$.}
+    \label{fig:totp3mass_halomass_sidehist}
+\end{figure}
 

### 2018-10-10 paper.tex
updating previous commit -- changing citation

@@
 Previous studies have investigated the possibility of finding Pop III systems.
-\citep{Trenti09} found that metal-free halos may still be able to form at $z \approx$ 6, which offer the best chance at observing such primordial systems.
+\citet{Trenti09} found that metal-free halos may still be able to form at $z \approx$ 6, which offer the best chance at observing such primordial systems.
 Given a certain rate of Pop III supernova per year, large sky surveys, such as the Large Synoptic Survey Telescope (LSST), should be able to detect the very luminous supernova.
@@
 Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars.
-\citep{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15.
+\citet{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15.
 In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time.
-\citep{Visbal18} came up with a semi-analytic model for the formation of Pop III stars and the transition from Pop III to metal-enriched stars.
+\citet{Visbal18} came up with a semi-analytic model for the formation of Pop III stars and the transition from Pop III to metal-enriched stars.
 They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing espcape fraction, leads to large differencies in the star formation history of Pop III and metal-enriched stars.
@@
 However, subsequent simulations have shown that they do not necessarily form at this minimum due to the aforementioned physical processes playing a role.
-\citep{Mebane18} used a semi-analytic model of early star formation and found that the LW background coming from the rapidly increasing supply of Pop III stars becomes responsible for suppressing Pop III star formation.
+\citet{Mebane18} used a semi-analytic model of early star formation and found that the LW background coming from the rapidly increasing supply of Pop III stars becomes responsible for suppressing Pop III star formation.
 Pop III supernova feedback is another key process which can allow Pop III stars to continue to form, as long as the metals are ejected from the host halo.
-\citep{Griffen18} also find that the LW background can significantly suppress the amount of potential sites for Pop III star formation.
+\citet{Griffen18} also find that the LW background can significantly suppress the amount of potential sites for Pop III star formation.
 
 Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation.
-\citep{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
+\citet{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
 They derive a simple analytic expression for the mass threshold of halos given a particular LW flux.
 We will compare our results with this relation in future sections.
-\citep{yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
-In fact, \citep{Wise07_UVB} found that central shocks drives \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$.
+\citet{yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
+In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$.
 They find that \hh{} cooling is always a dominant process, even in large LW background fluxes.
-Assisting this result, \citep{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, indicating that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
+Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
 

### 2018-10-10 paper.tex
Fixing case of a bibtex entry/cite

@@
 We will compare our results with this relation in future sections.
-\citet{yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
+\citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
 In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$.

### 2018-10-24 paper.tex
update to paper: new figures, added results

--- 2018-10-10 paper.tex
@@
 \usepackage{mathtools}
-
+\usepackage{hyperref}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the 
-paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+We perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Population III stars, using the adaptive mesh refinement code \enzo{}.
+We investigate the distribution of host halo masses and its relationship to the Lyman-Werner background intensity.
+In our sample of 697 host halos, we find that 84\% of them have masses below the Machacek et al.
+(2001) relation because of the inclusion of \hh{} self-shielding.
+In our simulation above a redshift of 12.5, the mean halo mass is time-independent and ~10$^{5.8}$ M$_{\odot}$.
+Afterwards, it steadily rises above the Machacek et al.
+relation to a mean value of ~10$^{6.6}$ M$_{\odot}$.
+Most of these halos form multiple Population III stars, with a median number of four, up to a maximum of 16.
+We also find that a few halos do form stars below the Machacek et al.
+relation but in a high Lyman-Werner radiation field with values up to ~50 J$_{21}$.
+Our results suggest that Population III star formation may be less affected by Lyman-Werner radiation feedback than previously thought and that Population III multiple systems are common.
 \end{abstract}
@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3
+star formation -- methods:numerical -- cosmology
 \end{keywords}
@@
 Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10}.
-Stars will continue to form in halos, but with an increased metal abundance, these stars are now labelled as metal-enriched stars.
+Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars.
 These stars still are considered metal-poor, relative to the solar abundance, and are observable in the universe.
@@
 Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation.
-\citet{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
-They derive a simple analytic expression for the mass threshold of halos given a particular LW flux.
+\citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
+They derive a simple analytic expression for the mass threshold of halos given a particular LW flux:
+\begin{equation} \label{mthresh}
+	M_{TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{LW}}{10^{-21}} \right)^{.47}
+\end{equation}
 We will compare our results with this relation in future sections.
@@
 %====================================================================
-The implemented Pop III star formation model is the same as in Wise \& Abel (2008). Each star particle represents a single star, and is formed in a cell when the following criteria are met: 
+The implemented Pop III star formation model is the same as in \citet{Wise08_Gal}. Each star particle represents a single star, and is formed in a cell when the following criteria are met: 
 \begin{enumerate}
@@
 \end{equation}
-where M$_{\rm char}$ = 20 M$_{\odot}$.
+where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}.
 This characteristic mass is different from W12 and W14 (would like to find a citation for this number, having a hard time tracking down some John had suggested).
@@
 %====================================================================
-Possible other figures:
-\begin{enumerate}
-\item Jlw/J21 vs. Halo Mass colored by redshift - plotted with Machacek relation ??  - jlw\_mass\_machacek.png
-\item Halo mass vs. redshift colored by total Jlw - plotted with background Machacek relation ?? - mass\_redshift\_machacek\_clocal.png
-\end{enumerate}
+In this section, we will present the distribution of host halo masses of Pop III stars, the relation between the mass distribution and the LW background radiation, and the distribution of various Pop III properties.
+
+%====================================================================
+\subsection{Population III host halo masses}
+%====================================================================
+To ensure that our box is representative of a typical piece of the universe, the numerical halo mass function is plotted along with the analytic Sheth-Tormen mass function at $z$ = 9.3 in Fig.
+\ref{fig:hmf}.
+The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve lower mass halos.
 
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/hmf.png}
+	\includegraphics[width=\columnwidth]{images/hmf.pdf}
     \caption{Halo mass function of the last output of the simulation at $z$ = 9.3.
-The thick line is the analytic Sheth-Tormen mass function.
+The thick, black line is the analytic Sheth-Tormen mass function.
 The distribution of halo masses matches well with Sheth-Tormen until about 10$^{5}$ M$_{\odot}$.}
@@
 
+As mentioned previously, Pop III stars form in our simulation only between 27.23 $\leq z \geq$ 9.39.
+During this time frame, a total of 697 Pop III stars form.
+The corresponding star formation rate density can be seen in Figure \ref{fig:pop3_SFR_bar}.
+To determine the host halos of new Pop III stars, the halo finding code, \rockstar{} \citep{rockstar}, is used.
+The mass determined by \rockstar{} is the dark matter mass, so to get the baryonic mass of the halos, we multiply the masses by $\Omega_{M}$/$\Omega_{DM}$.
+The baryonic mass is subsequently used in our analysis.
+The center and virial radius of each halo is also pulled from \rockstar{}.
+A small percentage of Pop III stars do not form in a halo found by \rockstar{}.
+Assuming that Pop III stars should be forming in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star as an approximation.
+The LW background intensity is calculated by summing up the LW intensity coming from each radiating star particle outside the virial radius of the host halo.
+This is then added to the constant LW background implemented in the simulation (Eq.
+\ref{LWbg}).
+
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.png}
-    \caption{For halos hosting new Pop III stars, the mean halo mass is plotted versus redshift, in bins of $\Delta z$ = 1.
-The Machacek et al.
-minimum mass threshold is plotted for the constant LW background given in Eq.
-\ref{LWbg}.
-The mean halo masses fall below the relation until a redshift of 12.5, at which point the mean halo masses rise above the relation.}
-    \label{fig:mean_mass}
+	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.png}
+    \caption{The star formation rate density of Pop III stars. It peaks at a redshift of 20, and slowly falls off.}
+    \label{fig:pop3_SFR_bar}
 \end{figure}
 
+Binning the data in $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted against the redshift bins in Figure \ref{fig:mean_mass}.
+Equation \ref{mthresh} is plotted using the LW background intensity in Eq.
+\ref{LWbg}.
+Notably, the mean halo mass falls well below the relation until $z$ = 12.5.
+Below the mass threshold, the mean halo mass is 10$^{5.89}$ M$_{\odot}$, and rises to 10$^{6.6}$ M$_{\odot}$ after $z$ = 12.5.
+The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation.
+\hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at early times.
+In the analysis done in M01, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times.
+Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts.
+Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[e.g.]{yoshida03, Ricotti01, Glover01, Hartwig15}.
+
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/jlw_mass_machacek_total.png}
+	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
+    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus redshift.
+The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass.
+The error bars indicate the 15.1\% and 84.1\% percentiles.
+Plotted along the right hand side is the percentage of halos that fall below the M01 mass threshold, also plotted along redshift.
+The M01 mass threshold (Eq.
+\ref{mthresh}), is plotted for the constant LW background in Eq.
+\ref{LWbg}.
+Almost all halos fall below the M01 relation, until $z$ = 12.5, when the mean halo mass rises above the relation.}
+    \label{fig:mean_mass}
+\end{figure},
+
+The LW background intensity is plotted versus the halo mass for each host Pop III halo in our dataset in Figure \ref{fig:jlw_mass_machacek}.
+Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq.
+\ref{mthresh}) for the given LW background (Eq.
+\ref{LWbg}) is also plotted.
+We see that almost all halos form below the M01 threshold.
+There are also a few halos that form in very high J$_{LW}$, below the relation.
+It should be noted that there may be duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient.
+The grouped points in the higher end of J$_{LW}$ may be representative of such halos.
+We find that 84\% of the halos forming new Pop III stars lie below the M01 mass threshold.
+
+%====================================================================
+\subsection{Multiple stellar systems}
+%====================================================================
+
+We can also look at the number of Pop III stars and the total mass of Pop III stars per halo.
+The number of Pop III stars per halo is plotted against the halo mass in Figure \ref{fig:totnump3_halomass_sidehist} as a 2D-histogram.
+The histogram of the number of Pop III stars is projected on the right.
+We find that a median number of four Pop III stars form per halo, with a maximum of 16 Pop III stars forming per halo.
+Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multi-Pop III stars to form in a single system.
+The total mass of Pop III stars per halo is plotted against halo mass in \autoref{fig:totp3mass_halomass_sidehist}.
+The histogram of the total Pop III mass is projected on the right.
+Lines of constant star formation efficiency are overplotted.
+We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/jlw_mass_machacek_total.pdf}
     \caption{The average LW background for host halos of new Pop III stars is plotted versus the host halo mass, colored by redshift.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/percent_below_dz1.png}
-    \caption{The percentage of halos that form Pop III stars below the minimum mass threshold from \citet{Machacek01}, in bins of $\Delta z$ = 1.
-As seen in \ref{fig:jlw_mass_machacek}, almost all halos form below the mass threshold.}
-    \label{fig:percent_below_dz1}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.png}
-    \caption{The star formation rate density of Pop III stars. It peaks at a redshift of 20, and slowly falls off.}
-    \label{fig:pop3_SFR_bar}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{images/totnump3_halomass_sidehist.png}
+	\includegraphics[width=\columnwidth]{images/totnump3_halomass_sidehist.pdf}
     \caption{Total number of Pop III stars in halos hosting new Pop III stars versus halo mass.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/totp3mass_halomass_sidehist.png}
+	\includegraphics[width=\columnwidth]{images/totp3mass_halomass_sidehist.pdf}
     \caption{Total mass of Pop III stars in halos hosting new Pop III stars versus halo mass.
@@
 \end{figure}
-
-%====================================================================
-\subsection{Population III host halo masses}
-%====================================================================
-
-%====================================================================
-\subsection{Multiple stellar systems}
-%====================================================================
 

### 2018-10-24 paper.tex

@@
 Given a certain rate of Pop III supernova per year, large sky surveys, such as the Large Synoptic Survey Telescope (LSST), should be able to detect the very luminous supernova.
-Unless the metal-free systems are particularly efficient at forming Pop III stars (star formation efficiences > 10$^{-2}$), the upcoming James Webb Space Telescope (JWST) will not be able to detect such systems.
+Unless the metal-free systems are particularly efficient at forming Pop III stars (star formation efficiencies > 10$^{-2}$), the upcoming James Webb Space Telescope (JWST) will not be able to detect such systems.
 
@@
 \citet{Visbal18} came up with a semi-analytic model for the formation of Pop III stars and the transition from Pop III to metal-enriched stars.
-They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing espcape fraction, leads to large differencies in the star formation history of Pop III and metal-enriched stars.
+They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing escape fraction, leads to large differences in the star formation history of Pop III and metal-enriched stars.
 This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.
@@
 \citet{yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
+In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$.
+They find that \hh{} cooling is always a dominant process, even in large LW background fluxes.
+Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
+
+Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation.
+\citet{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
+They derive a simple analytic expression for the mass threshold of halos given a particular LW flux.
+We will compare our results with this relation in future sections.
+\citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
 In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$.

### 2018-10-24 paper.tex
removing files

@@
 Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts.
-Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[e.g.]{yoshida03, Ricotti01, Glover01, Hartwig15}.
+Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
 
@@
     \label{fig:mean_mass}
-\end{figure},
+\end{figure}
 

### 2019-02-04 paper.tex
Went through comparison papers and made a list of important results for each paper.

@@
 and heavy elements.
-The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments is necessary for further star production and chemical enrichment.
+The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments are necessary for further star production and chemical enrichment.
 Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today.
-These stars are, by definition, metal-free (Population III; Pop III) and are thought to be generally massive.
+These stars are, by definition, metal-free (Population III; Pop III) and are thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}.
 A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
@@
 Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars.
-These stars still are considered metal-poor, relative to the solar abundance, and are observable in the universe.
+These stars still are metal-poor, having metallicities of 10$^{-6}$ - 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to PopIII stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}.
 Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.
@@
 Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization.
-Learning about their host halos can also guide future telescopic surveys to observe Pop III galaxies which may lead to direct observational evidence for Pop III stars.
+Learning about their host halos can also guide future telescopic surveys to observe Pop III galaxies which may lead to their direct observational evidence.
 Previous studies have investigated the possibility of finding Pop III systems.
-\citet{Trenti09} found that metal-free halos may still be able to form at $z \approx$ 6, which offer the best chance at observing such primordial systems.
-Given a certain rate of Pop III supernova per year, large sky surveys, such as the Large Synoptic Survey Telescope (LSST), should be able to detect the very luminous supernova.
-Unless the metal-free systems are particularly efficient at forming Pop III stars (star formation efficiencies > 10$^{-2}$), the upcoming James Webb Space Telescope (JWST) will not be able to detect such systems.
+For example, \citet{Trenti09} found that metal-free halos may still be able to form at $z \approx$ 6, which offer the best chance at observing such primordial systems.
+They find that, given a certain rate of Pop III supernova per year, large sky surveys, such as the Large Synoptic Survey Telescope (LSST), should be able to detect the very luminous supernova.
+\citet{Trenti09} determine that unless the metal-free systems are particularly efficient at forming Pop III stars (star formation efficiencies > 10$^{-2}$), the upcoming James Webb Space Telescope (JWST) will not be able to detect such systems.
 
@@
 In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time.
-\citet{Visbal18} came up with a semi-analytic model for the formation of Pop III stars and the transition from Pop III to metal-enriched stars.
+\citet{Visbal18} devised a semi-analytic model for the formation of Pop III stars and the transition to metal-enriched stars.
 They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing escape fraction, leads to large differences in the star formation history of Pop III and metal-enriched stars.
@@
 
-Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, prohibiting Pop III star formation.
+Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, delaying Pop III star formation.
 Furthermore, nearby sources of LW radiation can boost the intensity above the background value which facilitates further \hh{} dissociation in minihalos.
 This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding.
-Halos with an \hh{} column density of N$_{H_{2}}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons, giving the halo a chance to form Pop III stars.
-Other sources of the suppression of Pop III star formation are streaming baryonic velocities, arising from recombination, and dynamical heating, occuring during the virialization of halos.
+Halos with an \hh{} column density of N$_{H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars.
+Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12,OLeary12}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}.
 
@@
 \citet{Mebane18} used a semi-analytic model of early star formation and found that the LW background coming from the rapidly increasing supply of Pop III stars becomes responsible for suppressing Pop III star formation.
-Pop III supernova feedback is another key process which can allow Pop III stars to continue to form, as long as the metals are ejected from the host halo.
 \citet{Griffen18} also find that the LW background can significantly suppress the amount of potential sites for Pop III star formation.
@@
 \citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
-In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$.
-They find that \hh{} cooling is always a dominant process, even in large LW background fluxes.
-Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
-
-Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation.
-\citet{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
-They derive a simple analytic expression for the mass threshold of halos given a particular LW flux.
-We will compare our results with this relation in future sections.
-\citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
-In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$.
+In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 J$_{21}$.
 They find that \hh{} cooling is always a dominant process, even in large LW background fluxes.
@@
 We aim to provide further insight into the host halos of Pop III stars.
-In \S 2 the methods of the simulation, implementation of star formation, feedback, and \hh{} self-shielding is described.
+In \S 2 the methods of the simulation, implementation of star formation, feedback, and \hh{} self-shielding are described.
 In \S 3 we present the results of our analysis.
@@
 %====================================================================
-This simulation was run with an adaptive mesh refinement (AMR) code 
-\enzo{} \citep{Enzo} and analyzed with the toolkit, \yt{} \citep{yt_full_paper}.
+We run and analyze a cosmological simulation with the adaptive mesh refinement (AMR) code \enzo{} \citep{Enzo} and the toolkit \yt{} \citep{yt_full_paper}.
 \enzo{} uses an N-body adaptive particle-mesh solver \citep{Efstathiou85, Couchman91, BryanNorman1997} to follow the dark matter (DM) dynamics.
 We use the nine-species (\hi, \hii, \hei, \heii, \heiii, e$^{-}$, H$_{2}$, H$_{2}^{+}$, H$^{-}$) non-equilibrium chemistry model \citep{Abel97, Anninos97}.
-This simulation is similar to the RP simulation in
-\citet[hereafter W12]{Wise12_RP}, but with updated cosmological and Pop III parameters, and the inclusion of \hh{} shielding.
+This simulation is similar to the RP simulation in \citet[hereafter W12]{Wise12_RP}, but with updated cosmological and Pop III parameters, and the inclusion of \hh{} shielding.
 
 We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
-resolution. We have a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
-initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and use the cosmological parameters from the Planck collaboration best fit 
+resolution. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
+initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and uses the cosmological parameters from the Planck collaboration best fit 
 \citet{Planck13_Cosmo}: $\Omega_{M}$ = 0.3175, $\Omega_{\Lambda}$ = 
@@
 At this point, 20\% of the volume is ionized.
-In this paper, we focus only on outputs where new Pop III stars are born, from $z$ = 27.23 to 9.39.
+We output 918 datasets,  roughly 50,000 yr apart.
+In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.
 
@@
 \begin{equation} \label{LWbg}
-	\log_{10}(J_{LW}/J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
+	\log_{10}(J_{\rm LW}/J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
 \end{equation}
 where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.
-
-Adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} is used to evolve the radiation field.
+We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the radiation field.
 Centered on each metal-enriched and Pop III star, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile.
@@
 %====================================================================
-The implemented Pop III star formation model is the same as in \citet{Wise08_Gal}. Each star particle represents a single star, and is formed in a cell when the following criteria are met: 
+The utilized Pop III star formation model is the same as in \citet{Wise08_Gal}. Each star particle represents a single star, and is formed in a cell when the following criteria are met: 
 \begin{enumerate}
@@
 \begin{equation} \label{IMF}
-	f(\log M)dM = M^{-1.3} \exp \Big[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \Big]dM
+	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
 \end{equation}
 where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}.
-This characteristic mass is different from W12 and W14 (would like to find a citation for this number, having a hard time tracking down some John had suggested).
-This results in an exponential cutoff before M$_{char}$ and a Salpeter IMF after.
-Once the cell meets the above criteria and the mass of the star is randomly determined from Eq.
-3, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
+This characteristic mass is different from W12 \citep{Hirano17}.
+This results in an exponential cutoff before M$_{\rm char}$ and a power-law IMF after.
+Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
 The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere.
 
-We use the mass-dependent hydrogen ionising LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K.
-A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\ast}$/M$_{\odot}$ $\leq$ 40 M$_{\odot}$.
-A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 260 M$_{\odot}$.
+We use the mass-dependent hydrogen ionizing and LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K.
+A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40.
+A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 260.
 Outside of these mass ranges, the Pop III star dies as a black hole.
 In this simulation, no black hole physics are implemented, so the Pop III star simply turns into a collisionless particle.
-From 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20 M$_{\odot}$, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg.
-From 20 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40 M$_{\odot}$, the star dies as a hypernova with energies taken from \citet{Nomoto06}.The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq.
+When 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg.
+From 20 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40, the star dies as a hypernova with energies taken from \citet{Nomoto06}.
+The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq.
 12 of W12.
@@
 %====================================================================
-The Pop II star formation model is the same as Wise \& Cen (2009), which is equivalent to the above criteria for Pop III star formation but without the molecular hydrogen fraction requirement, and with a metallicity greater than the above value.
+The Pop II star formation model is the same as \citet{Wise09}, which is equivalent to the above criteria for Pop III star formation but without the molecular hydrogen fraction requirement, and with a metallicity greater than the above value.
 Star formation is only allowed for gas with temperatures $T$ < 1000 K, to ensure that the volume is cold and collapsing.
@@
 Their spectra are approximated with a monochromatic spectrum with an energy of 21.6 eV at a constant luminosity.
-After living for 4 Myr, the stars generate supernova energies of 6.8 $\times$ 10$^{48}$ erg s$^{-1}$ M$_{\odot}^{-1}$.
+After living for 4 Myr, the stars begin to return supernova energies of 6.8 $\times$ 10$^{48}$ erg s$^{-1}$ M$_{\odot}^{-1}$ back to their surroundings.
 
 %====================================================================
-\subsection{\hh{} Shielding}
+\subsection{\hh{} Self-Shielding}
 %====================================================================
@@
 \begin{equation} \label{Nh2}
-	N_{H_{2}} = n_{H_{2}}L_{\rm char}
+	N_{H2} = n_{H2}L_{\rm char} \ ,
 \end{equation}
-Where n$_{H_{2}}$ is the number density of \hh{} and L$_{\rm char}$ is a characteristic length over which n$_{H_{2}}$ is assumed to be constant.
+where n$_{H2}$ is the number density of \hh{} and L$_{\rm char}$ is a characteristic length over which n$_{H2}$ is assumed to be constant.
 The method employed in this simulation is to define the characteristic length as:
@@
 This Sobolev-like method determines the length over which gas with density $\rho$ is diminished.
-The most accurate, non-ray tracing, method is to use a single Sobolev-like length determined from the mean Sobolev-like length over all cartesian directions.
+They found that the most accurate, non-ray tracing, method is to use a single Sobolev-like length determined from the mean Sobolev-like length over all Cartesian directions.
 
-Upon numerically calculating the shielding factor of H2 for simulated protogalaxies, Wolcott-Green et al.
+Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al.
 determine that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures.
@@
 	\begin{multlined}
-	f_{sh}(N_{H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
+	f_{\rm sh}(N_{\rm H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
 	\end{multlined}
 \end{equation}
-Here, x $\equiv$ N$_{H_{2}}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. N$_{H_{2}}$ is then calculated as described above.
+Here, x $\equiv$ N$_{H_{2}}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter.
 
@@
 %====================================================================
-To ensure that our box is representative of a typical piece of the universe, the numerical halo mass function is plotted along with the analytic Sheth-Tormen mass function at $z$ = 9.3 in Fig.
-\ref{fig:hmf}.
-The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve lower mass halos.
+To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the numerical halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3.
+The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$50 particles.
 
@@
 
-As mentioned previously, Pop III stars form in our simulation only between 27.23 $\leq z \geq$ 9.39.
+As mentioned previously, Pop III stars form in our simulation only between 27.23 $\geq z \geq$ 9.39.
 During this time frame, a total of 697 Pop III stars form.
 The corresponding star formation rate density can be seen in Figure \ref{fig:pop3_SFR_bar}.
-To determine the host halos of new Pop III stars, the halo finding code, \rockstar{} \citep{rockstar}, is used.
-The mass determined by \rockstar{} is the dark matter mass, so to get the baryonic mass of the halos, we multiply the masses by $\Omega_{M}$/$\Omega_{DM}$.
-The baryonic mass is subsequently used in our analysis.
-The center and virial radius of each halo is also pulled from \rockstar{}.
-A small percentage of Pop III stars do not form in a halo found by \rockstar{}.
-Assuming that Pop III stars should be forming in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star as an approximation.
-The LW background intensity is calculated by summing up the LW intensity coming from each radiating star particle outside the virial radius of the host halo.
+Pop III star formation peaks at a redshift of 20 and slowly decreases.
+The star formation rate density does not fall to zero at the end of the simulation, since Pop III stars were still being produced when the simulation was cut off.
+To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}.
+The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}$/$\Omega_{\rm DM}$.
+The total mass is subsequently used in our analysis.
+We also take the center and virial radius from the \rockstar{} halo catalog.
+A small percentage of Pop III stars do not form in a halo identified by \rockstar{}.
+Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data.
+We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo.
 This is then added to the constant LW background implemented in the simulation (Eq.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.png}
+	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
     \caption{The star formation rate density of Pop III stars. It peaks at a redshift of 20, and slowly falls off.}
@@
 
-Binning the data in $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted against the redshift bins in Figure \ref{fig:mean_mass}.
-Equation \ref{mthresh} is plotted using the LW background intensity in Eq.
+In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted against the redshift bins in Figure \ref{fig:mean_mass}.
+The M01 relation (Equation \ref{mthresh}) is plotted using the LW background intensity in Eq.
 \ref{LWbg}.
-Notably, the mean halo mass falls well below the relation until $z$ = 12.5.
-Below the mass threshold, the mean halo mass is 10$^{5.89}$ M$_{\odot}$, and rises to 10$^{6.6}$ M$_{\odot}$ after $z$ = 12.5.
+Notably, the mean halo mass falls well below the relation, at 10$^{5.89}$ M$_{\odot}$ until $z$ = 12.5, at which point, the mean halo mass rises to 10$^{6.6}$ M$_{\odot}$.
 The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation.
-\hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at early times.
-In the analysis done in M01, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times.
+\hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times.
+In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times.
 Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts.
-Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
+As can be seen by the red solid line in \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation.
+Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
 
@@
 
-The LW background intensity is plotted versus the halo mass for each host Pop III halo in our dataset in Figure \ref{fig:jlw_mass_machacek}.
+The LW background intensity is plotted versus the host halo mass for each Pop III halo in our dataset in Figure \ref{fig:jlw_mass_machacek}.
 Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq.
@@
 We see that almost all halos form below the M01 threshold.
-There are also a few halos that form in very high J$_{LW}$, below the relation.
-It should be noted that there may be duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient.
-The grouped points in the higher end of J$_{LW}$ may be representative of such halos.
-We find that 84\% of the halos forming new Pop III stars lie below the M01 mass threshold.
+There are also a few halos that form Pop III stars in very high J$_{\rm LW}$, below the relation.
+This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 90 pc of each other.
+Star formation can occur in a neighboring halo of a Pop III star whose LW radation does not have ample time to photodissociate enough \hh{} to suppress star formation.
+The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs synchronically, star formation will not be suppressed, so long as they are a suitable distance away from each other.
+As there are only a few data points in this region, this situation may be somewhat rare.
+It should be noted that there may be duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation.
+The grouped points in the higher end of J$_{\rm LW}$ are representative of such halos.
+We find that a total of 84\% of the halos forming Pop III stars lie below the M01 mass threshold over the entire simulation redshift range.
 
@@
 
-We can also look at the number of Pop III stars and the total mass of Pop III stars per halo.
-The number of Pop III stars per halo is plotted against the halo mass in Figure \ref{fig:totnump3_halomass_sidehist} as a 2D-histogram.
-The histogram of the number of Pop III stars is projected on the right.
+We now inspect the number of Pop III stars and the total mass of Pop III stars per halo.
+Figure \ref{fig:totnump3_halomass_sidehist} shows the number of Pop III stars per halo for a given halo mass.
+The histogram of the number of Pop III stars for all masses is projected on the right hand side.
 We find that a median number of four Pop III stars form per halo, with a maximum of 16 Pop III stars forming per halo.
-Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multi-Pop III stars to form in a single system.
-The total mass of Pop III stars per halo is plotted against halo mass in \autoref{fig:totp3mass_halomass_sidehist}.
-The histogram of the total Pop III mass is projected on the right.
+Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo.
+Out of the halos forming Pop III stars, only 16\% of them form single PopIII stars, whereas 54\% form between two and five Pop III stars.
+Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side.
 Lines of constant star formation efficiency are overplotted.
 We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$.
+The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$.
 
@@
 
+\li Tegmark97
+\begin{enumerate}
+	\item They are numerically integrating a set of chemical equations given a model for halo profiles
+	\item Figure 5 shows the minimum virial temperature needed to collapse as a function of 1 + the virial redshift.
+I have plotted the virial temperature of my halos as a function of the redshift (this redshift is not the virial redshift, rather it is the redshift at which the Pop III star forms for that halo).
+I could make a comparison here but I'm not really comparing the same thing.
+It looks some of our halos form in their forbidden shaded regions.
+	\item I could calculate what zvir would be given Tvir
+	\item Figure 6 is similar to the item above
+	\item They find that "\hh{} formation triggers cooling in virialized clouds and allows early formation of low mass objects" (pg. 18)
+	\item They find that ~10$^{5}$ M$_{\odot}$ (baryonic mass) clouds can be virialzed at redshift 30
+\end{enumerate}
+
+\li Trenti09
+\begin{enumerate}
+	\item Individual observation of Pop III stars will likely not happen with upcoming telescopes, although detection of pair instability supernovae may happen with all sky surveys.
+	\item They are investigating the number density of pockets of metal free gas that survive below z = 10
+	\item They use the particle mesh tree code Gadget-2 
+	\item They begin their simulation at a higher redshift, in a larger box (7 h$^{-1}$ Mpc), with a higher mass resolution (3.4 $
+	\times$ 10$^{4}$ M$_{\odot}$) and a higher spatial resolution (0.16 h$^{-1}$ kpc).
+	\item They look between z = 30 and z = 4 and use a friend-of-friend halo finder
+	\item They assume a minimum halo mass that is capable of cooling from Trenti and Stiavelli 2009, this includes LW 
+	\item They also consider metal enrichment coming from nearby supernovaes. They find that even with relativly high wind bubble expansion velocities, metal-free halos can exist until z=5
+	\item Observing Pop III stars with JWST may be possible if their star formation efficiencies were greater than 10$^{-2}$ -- we are not seeing these types of efficiences --> JWST will likely not be able to see these stars
+	\item They say that "the best-case scenario for supernovae detection would be if multiple, very massive Pop III stars formed per halo" -- we are finding that having multiple Pop III stars in a single halo is actually more likely than having only one Pop III star
+	\item They are assuming only a single Pop III star per halo
+	\item Figure 1 shows the minimum halo mass required for cooling and collapse of a metal-free halo in the presence of a LW background. 
+	\item Upon comparing our halo masses with their mass criteria, none of our halos follow their mass trend (see jupyter notebook and https://arxiv.org/pdf/0901.0711.pdf)
+	\item 
+\end{enumerate}
+
+\li Visbal18
+\begin{enumerate}
+	\item They develop a semi-analytic technique to study evolution of Pop III to metal-enriched star formation, using n-body simulations and applying a prescription for Pop III and metal-enriched star formation
+	\item They include LW feedback and metal enrichment from supernovae winds
+	\item They use Gadget-2
+	\item First stars star forming at z=40
+	\item Our Pop III stars are forming in halos that fall below their critical mass value 
+	\item Self-consistent LW background, although does not take into account density fluctuations on scales larger than the box
+	\item They assume a single mass for all Pop III stars (40 msol)
+	\item As they only measure between z=40 and z=20, we can really only compare our peak SFRD with theirs, which does occur at about the same time.
+Our SFRD peaks around z=20 at a value of ~2$\times$10$^{-4}$ and decreases before and after z = 20.
+It looks like we are getting a similar peak value at z=20 for a Pop III SFE of 0.005 (also similar to our SFE).
+Other parameters they consider aren't hitting the same peak value as us at the end of their simulation.
+I think comparing with SFRD here is one of the only things we can directly compare, since they are looking at higher redshifts than we are.
+	\item Streaming velocities have not been included
+\end{enumerate}
+
+\li Mebane 18
+\begin{enumerate}
+	\item Focus only on neutral primordial gas accreting onto a halo and cooling via \hh{} line emission.
+	\item They try to understand how the first generation of Pop III stars persists
+	\item They are looking between z=50 and z=6
+	\item They use the Trac et al. (2015) halo mass function
+	\item They assume star formation occurs once the \hh{} fraction within a halo exceeds a critical value found in Tegmark et al.
+(1997).
+This occurs in small mass halos of about 10$^{5}$ M$_{\odot}$ at z=50
+	\item They self-consistently calculate the LW background which controls the minimum halo mass once stars begint to form
+	\item They make the Pop III IMF a variable
+	\item They have an interesting discussion about whether or not a Pop III star would be able to ionize the surrounding gas in it's birth halo, implying that Pop III stars likely form in isolation (pg.
+5)
+	\item Similar to their findings of the SFRD, our SFRD rapidly increases, then flattens out and decreases.
+Comparing with their Figure 7, our SFRD density seems to approximately match their peak values for particular variables.
+While we have a distinguished peak in our SFRD, they don't have as much of a peak.
+We seem to approximately match their mid mass and high mass Pop III IMF with energy-regulated Pop II star formation.
+	\item Our halo masses for Pop III stars appear to be quite a bit lower than their minimum masses
+	\item It may be worth including the SFRD for Pop II stars so we can compare with this paper further?
+	\item They conclude that the increasing LW background coming from Pop II stars is what halts Pop III star formation
+	\item They say that supernova feedback is one of the most important processes for a single halo: if enough metals are expelled from the halo, Pop III star formation can persist for several generations
+\end{enumerate}
+
+\li Griffen18
+\begin{enumerate}
+	\item They are using the Caterpillar simulations to do their work, specifically looking at Milky Way mass halos - rather large compared to our work
+	\item Looking at their Figure 1, our halos are forming Pop III stars below their minimum halo mass criteria
+	\item They identify Pop III star formation sites beginning at z=26, very similar to when we start seeing Pop III stars
+	\item This paper seems to be focusing on progenitors of Milky Way sized halos.
+As far as Pop III star formation goes, they seem to be getting a somewhat similiar number of potential star forming sites as we have number of Pop III stars (see their Table 2)
+\end{enumerate}
+
 \li Simulation papers: \citep{Machacek01, Yoshida03, Wise07_UVB,
   OShea08, Muratov13}
+
+\li Machacek01
+\begin{enumerate}
+	\item
+\end{enumerate}
+
+\li Yoshida03
+\begin{enumerate}
+	\item They are investigating primoridal star forming sites between redshifts 25 and 30 using Gadget
+	\item They take 64 snapshots from z = 100 to z = 14
+	\item Their Figure 2 and our halo mass vs.
+redshift plot are fairly similar, although we see a wider range of min halo masses for each redshift.
+We also see a bit more of a trend.
+At higher redshifts, our minimum halo mass is sitting at about 4 $\times$ 10$^{6}$ M$_{\odot}$, and steadily rises, although with a fairly large amount of scatter
+	\item I may be able to make a plot similar to Figure 3 once I get YT working properly on Comet (also for Figure 4)
+	\item They do investigate the effects of radiative feedback to various degrees, including the effects of self-shielding
+	\item They start by considering a constand Lyman-Werner background radiation with values J$_{21}$ = 0.01, and 0.1. 
+	\item They find that the mean molecular hydrogen fraction drops by an order of magnitude for J$_{21}$ = 0.01, making primordial gas cooling very inefficient
+	\item When they begin discussing the effects of self-shielding, they note that their prescription for self-shielding assumes a stationary gas, so their results show the maximum effect of self-shielding
+	\item Figure 12 shows that including a LW background does increase the minimum halo mass of halos that host gas clouds compared to the runs where there was no LW background applied.
+When self-shielding is taken into account, the minimum halo mass is lowered compared to the run without self-shielding.
+This figure shows that self-shielding does appear to be an important factor in determining the minimum halo mass that can host Pop III stars
+	\item Once they begin determining early star formation (section 8), they assume a single massive Pop III star for each cold dense gas cloud.
+They also assume the mass of the star to be at least greater than 100 solar masses, but leave this as a parameter.
+	\item They do find that just assuming a minimum-mass model for star-forming clouds over-predicts the values by up to a factor of three
+	\item The first star-forming regions appear at z=32
+	\item Top panel of Figure 15 shows that star-formation is quenched more strongly in the optically thin case than in the self-shielding case
+	\item Figure 16 shows the SFRD including self-shielding for a Pop III star with mass of 100 M$_{\odot}$ and with a mass of 600 M$_{\odot}$.
+This is a somehwat different redshift range than we are looking at, but we can compare peak values.
+Our peak value at z=20 is about 2 $\times$ 10$^{-4}$, whereas their peak value at $\approx$z=21 is 4 $\times$ 10$^{-4}$ for the Pop III star with 100 M$_{\odot}$, and 10$^{-3}$ for the Pop III star with 600 M$_{\odot}$.
+Our peak value matches fairly well with their 100 M$_{\odot}$.
+We also have a much faster rise in star formation than they do.
+I have plotted their function (Eqn.
+23) vs.
+our SFRD
+	\item Coming to their discussion section, they do state that while gas cooling is suppresed for J$_{21}$ > 0.01, when self-shielding is included, primoridial gas efficiently cools for J$_{21}$ = 0.01.
+\end{enumerate}
+
+\li Wise07UVB
+\begin{enumerate}
+	\item Using Enzo to investigate \hh{} cooling
+	\item One of their box sizes matches our box size of 1 comoving MPC
+	\item Self-shielding of LW photons is not included, and they state that they don't expect their results to change significantly by the effect of self-shielding
+	\item There are 14 simulations in this paper, with various LW fluxes, with and without \hh{} cooling. 
+	\item Their Figure 3a shows the halo masses of the most massive halos versus redshift when the halo starts to collapse.
+This figure shows higher masses than what we are seeing during similar redshift ranges
+	\item They find that \hh{} cooling is dominant even when there is a large LW background
+	\item They give a discussion about the effect of local LW sources on Pop III formation and say that these local sources should only affect the timing of nearby star formation instead of the global star formation rate.
+This appears to be similar to what we are finding as we see only a couple instances where Pop III stars are born within close proximity to one another.
+	\item \hh{} formation is possible in the center of high redshift halos with a relatively high LW intensity due to free electrons created in central shocks.
+\end{enumerate}
+
+\li OShea08
+\begin{enumerate}
+	\item They are investigating Pop III formation by varying the strength of the LW background using Enzo
+	\item They find that the LW background does delay collapse of high density gas of the most massive halo, and increases the virial mass.
+They also find that star formation can occur in LW backgrounds as high as J$_{21}$ = 1.
+	\item Their simulation is similar to ours, with a smaller boxseze (0.6 h$^{-1}$ Mpc comoving) and run from z = 99 to when gas collapses in the center of the most massive halo.
+They assume an unevolving LW background with 8 different values, ranging from J$_{LW}$ = 0 to 10$^{-21}$.
+	\item Figures 1 and 2 show the most massive halo when it begins to collapse for J$_{21}$ = 0 and 1. For J$_{21}$ = 0, collapse begins at z = 24, and for J$_{21}$ = 1, collapse begins at z = 17. 
+	\item Figure 3 shows mean halo quantities for the simulations.
+We can compare with the bottom left panel, showing the halo virial mass versus J$_{LW}$, which also has the Machacek relation plotted on it.
+Their halos all lie well above the Machacek relation.
+	\item I may be able to make a figure similar to the top panels of Figure 4 once I get the trace halos to work
+	\item Overall results relevant to our work (I think) are that as the LW background increases, Pop III star formation is delayed and will thus occur in halos with higher masses.
+They also find that Pop III star formation is never suppressed, given the LW values they investigate.
+\end{enumerate}
+
+\li Muratov13
+\begin{enumerate}
+	\item They are using the simulation code ART to investigate how Pop III stars affect their host galaxies. 
+	\item Their simulations include \hh{} formation and dissociation by LW feedback, including self-shielding.
+They have a 1 h$^{-1}$ Mpc comoving box, and two smaller boxes to see the effect of mass resolution.
+They end their simulations at z=9, similar to us.
+	\item They have a similar criteria for Pop III star formation. For our Pop III stars, we require a lower metallicity, and the same molecular hydrogen fraction. 
+	\item They assume the mass of the Pop III star to randomly be either 170 M$_{\odot}$ (PISN) or 100 M$_{\odot}$. 
+	\item They find Pop III stars forming in halos with masses $\geq$ 10$^{6}$ M$_{\odot}$ beginning at z $\approx$ 21.2. 
+	\item Their host halo masses are much larger than our host halo masses. 
+\end{enumerate}
 
@@
 \li No streaming velocities that suppresses star formation at very
-high ($z \ga 20$) redshifts \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}
+high ($z \ga 20$) redshifts \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12} (schauer18 belongs here as well)
 
 \li Uncertainties from the assumed Pop III initial mass function 
-
+,
 %====================================================================

### 2019-02-08 paper.tex
Making a few notation changes`

@@
 Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation.
-Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10}.
+Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10, Smith15}.
 Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars.
@@
 This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding.
-Halos with an \hh{} column density of N$_{H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars.
+Halos with an \hh{} column density of N$_{\rm H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars.
 Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12,OLeary12}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}.
@@
 \begin{equation} \label{mthresh}
-	M_{TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{LW}}{10^{-21}} \right)^{.47}
+	M_{\rm TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{\rm LW}}{10^{-21}} \right)^{.47}
 \end{equation}
 We will compare our results with this relation in future sections.
-\citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation.
+\citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01 J$_{\rm 21}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation.
 In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 J$_{21}$.
@@
 At this point, 20\% of the volume is ionized.
-We output 918 datasets,  roughly 50,000 yr apart.
+We output 918 datasets,  roughly 0.5 Myr apart.
 In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.
@@
 where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.
+
 We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the radiation field.
@@
 
-We use the mass-dependent hydrogen ionizing and LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K.
+We use the mass-dependent hydrogen ionizing and LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{\rm ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K.
 A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40.
@@
 \begin{equation} \label{Nh2}
-	N_{H2} = n_{H2}L_{\rm char} \ ,
+	N_{\rm H2} = n_{\rm H2}L_{\rm char} \ ,
 \end{equation}
-where n$_{H2}$ is the number density of \hh{} and L$_{\rm char}$ is a characteristic length over which n$_{H2}$ is assumed to be constant.
+where n$_{\rm H2}$ is the number density of \hh{} and L$_{\rm char}$ is a characteristic length over which n$_{\rm H2}$ is assumed to be constant.
 The method employed in this simulation is to define the characteristic length as:
@@
 This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 90 pc of each other.
-Star formation can occur in a neighboring halo of a Pop III star whose LW radation does not have ample time to photodissociate enough \hh{} to suppress star formation.
+Star formation can occur in a neighboring halo of a Pop III star whose LW radation does not have ample time to photodissociate enough \hh{} to completely suppress star formation.
 The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs synchronically, star formation will not be suppressed, so long as they are a suitable distance away from each other.
-As there are only a few data points in this region, this situation may be somewhat rare.
+As there are only a few data points in this region, this situation is rare.
 It should be noted that there may be duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation.

### 2019-03-13 paper.tex
Updated plots to remove most massive halos, added discussion about variation of halo masses, and added conclusions from papers about caveats

@@
 (2001) relation because of the inclusion of \hh{} self-shielding.
-In our simulation above a redshift of 12.5, the mean halo mass is time-independent and ~10$^{5.8}$ M$_{\odot}$.
+In our simulation above a redshift of 11.5, the mean halo mass is time-independent and ~10$^{5.9}$ M$_{\odot}$.
 Afterwards, it steadily rises above the Machacek et al.
@@
 We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
-resolution. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
+resolution and a dark matter paticle mass of 2000 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
 initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and uses the cosmological parameters from the Planck collaboration best fit 
@@
 \ref{LWbg}.
-Notably, the mean halo mass falls well below the relation, at 10$^{5.89}$ M$_{\odot}$ until $z$ = 12.5, at which point, the mean halo mass rises to 10$^{6.6}$ M$_{\odot}$.
+Notably, the mean halo mass falls well below the relation, at 10$^{5.9}$ M$_{\odot}$ until $z$ = 11.5, at which point, the mean halo mass rises to 10$^{6.6}$ M$_{\odot}$.
 The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation.
@@
 \ref{LWbg}.
-Almost all halos fall below the M01 relation, until $z$ = 12.5, when the mean halo mass rises above the relation.}
+Almost all halos fall below the M01 relation, until $z$ = 11.5, when the mean halo mass rises above the relation.}
     \label{fig:mean_mass}
@@
 %====================================================================
-\subsection{Population III stars in atomic cooling halos}
-%====================================================================
-
-%====================================================================
 \section{Discussion}
@@
 %====================================================================
-
-\li Halos can form metal-free stars again if their progenitors had
-only formed stars that did not go supernova
-
-\li Dynamical heating \citep{Yoshida03}
-
-\li Temporal fluctuations in the local Lyman-Werner radiation
+The collapse of gas that goes on to form Pop III stars occurs in a wide range of host halo masses across time.
+There are three main reasons why the host halo masses may vary significantly.
+First, a generation of metal-free stars can form if their progenitors had only formed stars that did not go supernova.
+This prevents metals from enriching the environment which would stop metal-free star formation and begin metal-enriched star formation.
+Second, dynamical heating from mergers and accretion can heat the gas within halos and prevent \hh{} regions from cooling.
+This would delay star formation in halos with a large dynamic range at early times (not sure if dynamic range is the right way to say this) \citep{Yoshida03}.
+Finally, temporal fluctuations in the local Lyman-Werner radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool.
+While this may only be a small affect in some halos where the local Lyman-Werner radiation is relatively low, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active Pop III star formation sites.
+The combination of these three processes will determine which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.
 
@@
 
+\li Schauer17
+\begin{enumerate}
+	\item Interested in the LW escape fraction from atomic cooling halos and whether or not shielding due to neutral hydrogen is important to prevent the build up of LW background
+	\item They use radiation-hydrodynamical simulations of the growth of H II regions in the first galaxies using the code ZEUS-MP. Their simulations are one dimensional. 
+	\item Their code follows the same nine chemical species as ours, and follows the growth of cosmological ionisation fronts
+	\item They calculate escape fractions in the near-field (an observer close to at rest with respect to the halo, it is within this range that \hh{} can provide shielding of the LW photons), and the far-field (an observer faraway from the halo, moving with a large velocity with respect to the halo)
+	\item They are looking at two halos with masses 10$^{7}$ and 10$^{8}$ solar masses, so already much higher than the halos hosting Pop III stars in our simulation.
+Their halos have stellar populations at the center.
+They vary different parameters of the stellar population, including SFEs and their IMF.
+	\item They find that the LW escape fraction depends on the ionisation front. If a halo is fully ionised, all photons escape.
+	\item In the near-field, for SFEs greater than 0.5\% and with a Salpeter IMF ranging from 50 to 500 Msol, the ionisation front overwhelms the halo and the gas remains ioinsed
+	\item If the spectrum weakens over time, recombination starts from the outside in and the halo becomes optically-thick.
+	\item If the ionisation front is slowly moving, the LW escape fraction can vary over a wide range. Molecular hydrogen abundance is enhanced and suppresses the LW background.
+	\item In the far-field, LW escape fractions are larger than in the near-field.
+Neutral hydrogen can shield here since "Lyman lines of Hbeta and higher, that lie in side the LW range, become very broad".
+	\item In general, they find that the LW escape fraction in these early halos is high.
+They say that unless a protogalaxy forms stars with a low 0.1\% SFE, most LW radiation will escape the halo.
+Our halos have SFEs at a much lower rate than this.
+	\item They say that "the gas present in the host halo of a stellar cluster with 10$^{4}$ to 10$^{6}$ Msol in stars cannot prevent the build-up of the LW background."
+	\item These results inform us that we are overestimating the LW radiation coming from point sources in our simulation.
+If we wanted to account for the reduced escape fraction, we could lower the intensity of our stars, and this would result in more star formation, since the overall LW radiation would be reduced.
+Although this should not significantly change our results.
+\end{enumerate}
+
 \li No streaming velocities that suppresses star formation at very
@@
 
+\li Tselia11
+\begin{enumerate}
+	\item Looking at the effect of streaming velocities on the evolution of the first bound objects in the early universe.
+	\item It was previously found that the effect of streaming velocities leads to power suppression on scales corresponding to the first bound halos and delays formation of the first bound objects
+	\item Their include the relative velocities between dark matter and baryons after recombination as well as a treatment of the variation of the sound speed between recombination and z=200. 
+	\item After applying these new prescriptions, they look at how the characteristic mass scale changes between gas-rich and gas-poor halos
+	\item They find an equation for the filtering mass which provides a boundary between gas-rich and gas-poor halos.
+	\item When there is a high streaming velocity, baryons may not fall into collapsing dark matter halos, and the filtering mass would increase (figure 2)
+	\item The gas fraction in halos significantly decreases in regions where there is a high streaming velocity relative to no streaming velocity (figure 5)
+	\item Relative velocites have a large affect on minihalos
+	\item Streaming velocities significantly suppress gas accretion during halo formation and thus increases the characteristic mass of gas-rich halos at redshifts greater than 10.
+They find the characteristic mass should be around 2 $\times$ 10$^{5}$ M$_{\odot}$ at z=20.
+	\item Streaming velocities also will delay star formation and cause spatial fluctuations, although the suppression affect is about a factor of 1.6 at z=20 since the minimum mass of \hh{} cooling is larger than the chracteristic mass they found.
+There is a factor of 3.3 effect on the gas fraction in starless minihalos.
+These effects grow with redshift
+	\item Streaming velocities is what determines the gas content of halos at high redshifts
+\end{enumerate}
+
+\li Greif11_Delay
+\begin{enumerate}
+	\item Using high resolution moving mesh simulations to show the effects of streaming velocities on the virialization of the first halo and first star formation
+	\item They focus on minihalos where they expect a more pronounced effect
+	\item Using AREPO, three different simulations with a side length of 500 kpc.
+	\item They identify the first minihalos which exceed a virial mass of 5 $\times$ 10$^{5}$ M$_{\odot}$.
+	\item They apply a relative velocity of 3 km s$^{-1}$ at z = 99.
+	\item When a streaming velocity is applied, the gas fractions in their halos are reduced by about 50\%
+	\item Figure 3 shows how the virial mass is increased when a streaming velocity is applied.
+The factor the virial mass is increased by is about 3, which results in a delay of Pop III star formation by $\delta$z $\approx$ 4
+	\item With a streaming velocity, the gas temperature at the virial radius is higher
+	\item The velocity dispersion is also higher with streaming velocities, which means the gas is more turbulent.
+They say that this could lead to a lower mass for Pop III stars than expected since fragmentation is increased
+	\item The nubmer of minihalos that can cool and form stars is reduced in the case of streaming velocities. 
+	\item Overall, gravitational collapse in minihalos is delayed, which means Pop III star formation is delayed, and the increased fragmentation may affect the mass function of the first stars. 
+\end{enumerate}
+
+\li Naoz12
+\begin{enumerate}
+	\item They use simulations to systematically understand the suppression of structure formation due to streaming velocities
+	\item They are using GADGET-2
+	\item They model the streaming velocities as constant throughout their boxes
+	\item They find that the halo number density is a function of the stream velcity. The halo mass function is suppressed for typical streaming velocity values
+	\item There is a 50\% suppression of the total number density of halos for 10$^{6}$ M$_{\odot}$ at z=19 for large streaming velocities
+	\item Where the streaming velocity is high the formation of the first stars and galaxies is delayed
+	\item There appears to be a delay in the formation epoch of gas rich halos
+	\item The position shift of baryons relative to dark matter appears to be erased by z=15
+	\item Streaming velocity will suppress the clumping factor of baryons at lower redshift 
+	\item Overall, the total halo mass function is significantly suppressed. This suppression appears to diminsh at different rates by z=15 for different streaming velocities
+	\item Significantly, they find that for the largest values of their streaming velocity, gas does not accrete onto the dark matter halo sand thus almost all halos below 10$^{6}$ M$_{\odot}$ are empty.
+Formation of the first generation of galaxies should be delayed
+	\item They also find that the reionization process may proceed differently in regions of the universe with different streaming velocities
+\end{enumerate}
+
+\li OLeary12
+\begin{enumerate}
+	\item They are simulating the formation of the first structures between z = 15 and z=200
+	\item They use a different method to model the streaming velocities, namely they use a consistent linear theory to initialize these flows, instead of simply changing the velocity of the gas at the beginning of the simulation
+	\item They are using both GADGET3 and Enzo
+	\item They are spending a fair amount of time in their paper actually comparing the results from GADGET and Enzo
+	\item They initialize their simulations including "the impact of pressure growth and rate of growth modes, temperature fluctuations, correct baryonic and dark matter velocities, and transfer functions that account for the dark matter-baryon velocity differential"
+	\item With some non-zero streaming velicities, halo gas is off center and with lower densities, which delay formation of the first stars
+	\item Maximum gas density can be suppresed by an order of magnitude for halos between 10$^{4}$ and 10$^{6}$ M$_{\odot}$
+	\item Interestingly, they find that the orientation of the filaments to the streaming velocity can tell you something about whether or not a halo has gas
+\end{enumerate}
+
+\li Schauer18
+\begin{enumerate}
+	\item They are looking at streaming velocity effects using the AREPO code
+	\item They run simulations with three different streaming velocities and without the effect of the position shift of the baryons with respect to the dark matter
+	\item A non-zero streaming velocity makes it hard for baryons to fall into dark matter halos.
+Figure 8 shows that for increasing streaming velocities, they baryon fraction in halos is significantly decreased.
+	\item This also means that the halo mass function decreases with increasing streaming velocities as can be seen in Figure 9
+	\item Figure 13 nicely shows that with increasing streaming velocities the halo mass of the first halo to contain cold gas increases. 
+	\item Overall, they find that where the streaming velocity is increased, the minimum halo mass and the average halo mass to include cold, dense gas increases significantly compared to the zero streaming velocity case.
+	\item They find that where the streaming velocity is the highest, star formation occurs in atomic cooling halos
+	\item Increasing the mass threshold for cold gas results in a suppressed star formation rate
+\end{enumerate}
+
 \li Uncertainties from the assumed Pop III initial mass function
-,
+
 %====================================================================
@@
 
-JHW is supported by National Science Foundation grants AST-1614333 and
-OAC-1835213, NASA grant NNX17AG23G, and Hubble theory grant
+JHW is supported by National Science Foundation grants AST-1614333 and OAC-1835213, NASA grant NNX17AG23G, and Hubble theory grant
 HST-AR-14326.  We thank the support staff at Georgia Tech's PACE,

### 2019-03-29 paper.tex
Adding summary of my thoughts on SA model comparison

@@
 
+\noindent\textbf{JHW summary:} In all of these papers, we shouldn't be focusing on the redshift dependence because that is model dependent.
+We should focus on the relationship between the LW background intensity and the halo masses.
+This is the best practice because our cosmological volume is small and cannot capture the cosmic variance.
+The Tegmark+ result is the absolute lowest halo mass for H2 cooling.
+Trenti+ uses a similar argument as them to calculate the minimum mass that is dependent on the LW background that they calculate from their semi-analytic model.
+In this discussion, I wouldn't put emphasis (e.g.
+in comparison with Mebane+) on our Pop III SFRD decreasing at a particular redshift because it's a small box.
+In other studies (like the Renaissance and Wise12+), the Pop III SFRD is pretty flat until some later time.
+None of these semi-analytic models include self-shielding.
+I think it would be worthwhile to make a plot of (minimum) host halo mass and J_LW, comparining our work with others.
+
 \li Tegmark97
@@
 
-\li Greif11_Delay
+\li Greif11\_Delay
 \begin{enumerate}

### 2019-03-29 paper.tex
Adding summary of my thoughts on simulation comparison

@@
 
-\noindent\textbf{JHW summary:} In all of these papers, we shouldn't be focusing on the redshift dependence because that is model dependent.
+\noindent\textbf{JHW summary:} In all of these papers, we shouldn't be focusing on the redshift dependence because that relies on the galaxy/star formation model that has large uncertainties.
 We should focus on the relationship between the LW background intensity and the halo masses.
-This is the best practice because our cosmological volume is small and cannot capture the cosmic variance.
+This is the best thing to do because our cosmological volume is small and cannot capture the cosmic variance.
 The Tegmark+ result is the absolute lowest halo mass for H2 cooling.
@@
 None of these semi-analytic models include self-shielding.
-I think it would be worthwhile to make a plot of (minimum) host halo mass and J_LW, comparining our work with others.
+I think it would be worthwhile to make a plot of (minimum) host halo mass and J\_LW, comparining our work with others.
 
@@
   OShea08, Muratov13}
+
+\noindent\textbf{JHW summary:} Mention that the Trenti+ and Mebane+ results have higher halo masses than the Machacek+ paper, but this is more in-line with the masses found in simulations (e.g.
+Wise+ \& O'Shea).
+We should focus our comparison with Yoshida+ because it includes self-shielding and includes many different halos, whereas Wise+ and O'Shea+ only look at one halo.
+Also, we need to figure out why the Muratov+ results have much higher halo masses even though they include self-shielding.
+Is it a resolution issue or something else?
 

### 2019-03-29 paper.tex
Adding summary of my thoughts on streaming velocities

@@
 
+\noindent\textbf{JHW summary:} We should emphasize your last point for Schauer+ -- that we are overestimating the LW flux in the box.
+
 \li Schauer17
@@
 high ($z \ga 20$) redshifts \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12} (schauer18 belongs here as well)
+
+\noindent\textbf{JHW summary:} Streaming velocities impact the very earliest Pop III host halos because they decrease with the scale factor.
+They delay the formation by increasing the necessary halo mass to overcome the bulk velocity.
+Just like the studies on LW radiation feedback, the simulations only focus on a handful of halos, whereas, Naoz+ gives a good estimate of the minimum mass (their filtering mass; equations 16-18).
+These masses are $2-3 \times 10^5 M_\odot$ and should only be important when the LW flux is small and not suppressing cooling.
+All of the halos in our simulation are more massive than this filtering mass.
+Even if we included streaming velocities, the gas would've fallen into the potential well when the halo exceeds the filtering mass.
+But then it couldn't cool because of the LW background.
+Thus I don't think streaming velocities would affect our results much at all.
 

### 2019-04-02 paper.tex
rough paragraphs for the comparion, caveats, and conclusion section. including a rough comparison plot

@@
 Second, dynamical heating from mergers and accretion can heat the gas within halos and prevent \hh{} regions from cooling.
-This would delay star formation in halos with a large dynamic range at early times (not sure if dynamic range is the right way to say this) \citep{Yoshida03}.
+This would delay star formation in halos at early times \citep{Yoshida03}.
 Finally, temporal fluctuations in the local Lyman-Werner radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool.
@@
 
-\li Semi-analytic papers: \citep{Tegmark97, Trenti09, Visbal18,
-  Mebane18, Griffen18}
+There has been a large amount of work done throughout the literature investigating the relationship between the LW background intensity and halo masses.
+\citet{Tegmark97} numerically integrates a set of chemical equations to calculate the minimum mass a halo must have in order to cool, by considering \hh{} production and cooling rates.
+They conclude that cooling by \hh{} is efficient and leads to the first formation of structures.
+They find a minimum halo mass needed to collapse which depends on the virial temperature of the halo and the virial redshift.
+\citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and find that metal-free halos can exist until z $\approx$ 6 using cosmological simulations and analytical calculations for metal enrichment.
+They also provide some insight into whether or not Pop III supernova rates are high enough within these metal-free halos to allow for the Large Synoptic Survey Telescope to see these regions of the universe.
+They use the minimum halo mass capable of cooling from \citet{Trenti09_SFR} as their halo mass model (see the blue solid line in Figure \ref{fig:compare_JLW_mass}, given our LW background).
+Neither \citet{Trenti09} nor \citet{Tegmark97} include the effects of \hh{} self-shielding, which results in the discrepancy between our data and their mass threshold relationship (Figure \ref{fig:compare_JLW_mass}).
+\citet{Mebane18} use a semi-analytic model of star formation, including a variety of feeback processes, to see for how long Pop III stars will survive for and find that Pop III stars can continue to form until z $\approx$ 6.
+They find a minimum halo mass for hosting Pop III star formation, but with the caveat that they do not include \hh{} self-shielding.
+The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations (Wise+ \& O'Shea -- put references here).
+It should be noted that because our box is fairly small, we cannot capture the cosmic variance, therefore our star formation models have large uncertainties, and we cannot directly compare these results with previous work.
+
+\citet{Yoshida03} uses cosmological simulations to study the formations of primordial star-forming clouds.
+They follow the growth of structure to find where cold gas forms to say something about the formation of the first stars, and how the effects of LW radiation may affect these gas clouds.
+Importantly, they include self-shielding within halos.
+In their series of simulations, they find a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12).
+They find that in the presence of a LW background of J$_{21}$ = 0.01, the minimum halo mass does increase compared to their runs where no LW background is applied.
+When self-shielding is taken into account, they see these halo masses decrease, falling closer to what the minimum halo masses were in the case where there was no LW background.
+They find that self-shielding does appear to be an efficient mechanism for primordial gas cooling.
+In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses across redshifts, ranging from 10$^{5.4}$ M$_{\odot}$ to 10$^{7.1}$ M$_{\odot}$.
+While our halos never experience a LW intensity as low as 0.01, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see red X in Figure \ref{fig:compare_JLW_mass}).
+\citet{Wise07_UVB} uses cosmological simulations to investigate \hh{} cooling in a LW background.
+They find that \hh{} cooling is dominant even when there is a large LW background present.
+They do not include self-shielding, and subsequently find halo masses at their collapse that closely match M01 (see pink stars in Figure \ref{fig:compare_JLW_mass}).
+Their J$_{LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
+\citet{OShea08} uses cosmological simulations to investivate Pop III star formation in various LW backgrounds.
+They find that due to an increased LW background, there is a delay in star formation, and thus there is an increase in the halo masses at collapse.
+They also ignore self-shielding in their calculations, which can again account for the increased halo masses they are finding compared to this work, as can be seen in Figure \ref{fig:compare_JLW_mass}.
+Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/compare_JLW_mass.pdf}
+    \caption{The average LW intensity normalized by J21 versus the halo mass for this work and a variety of other works.
+The black solid line is from M01, blue solid line from \citet{Trenti09_SFR}, red x from \citet{Yoshida03}, brown plus from \citet{OShea08}, pink stars from \citet{Wise07_UVB}.
+J$_{LW}$ = 0 for the various sources is plotted here at J$_{LW}$/J$_{21}$ = 10$^{-4}$}
+    \label{fig:compare_JLW_mass}
+\end{figure}
+
+%====================================================================
+\subsection{Caveats}
+%====================================================================
+
+There are a few caveats to this work that should be noted.
+Work done by \citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo.
+In our work, we allow all LW photons to escape the halo.
+Since we are not accounting for the reduced escape fraction within our halos, we are overestimatng the LW radiation coming from point sources in our simulation.
+We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results.
+We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}.
+Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with redshift.
+Pop III star formation is delayed by increasing the halo  mass needed to overcome the bulk velocity.
+Often in the literature, streaming velocities are only studied for a few halos.
+But \citep{Naoz13} estimates the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be see in Figure \ref{fig:compare_JLW_mass}.
+These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the halos in our simulation.
+\citep{Naoz13} mention that at the largest streaming velocity, their simulations don't match expected value due to a small sample size of high mass halos.
+If we included streaming velocities, the gas would've already fallen into the dark matter potential well when the halo exceeds this characteristic mass.
+Because of this, streaming velocities would likely not affect our results.
+Finally, there is the obvious caveat of the unknown Pop III initial mass function (IMF).
+Like with any work done trying to model Pop III star formation, an IMF must be chosen.
+Therefore, we have uncertainties coming from the assumed Pop III IMF.
+
+\
+\
+\
+\
 
@@
 
-\li Tegmark97
-\begin{enumerate}
-	\item They are numerically integrating a set of chemical equations given a model for halo profiles
-	\item Figure 5 shows the minimum virial temperature needed to collapse as a function of 1 + the virial redshift.
-I have plotted the virial temperature of my halos as a function of the redshift (this redshift is not the virial redshift, rather it is the redshift at which the Pop III star forms for that halo).
-I could make a comparison here but I'm not really comparing the same thing.
-It looks some of our halos form in their forbidden shaded regions.
-	\item I could calculate what zvir would be given Tvir
-	\item Figure 6 is similar to the item above
-	\item They find that "\hh{} formation triggers cooling in virialized clouds and allows early formation of low mass objects" (pg. 18)
-	\item They find that ~10$^{5}$ M$_{\odot}$ (baryonic mass) clouds can be virialzed at redshift 30
-\end{enumerate}
-
-\li Trenti09
-\begin{enumerate}
-	\item Individual observation of Pop III stars will likely not happen with upcoming telescopes, although detection of pair instability supernovae may happen with all sky surveys.
-	\item They are investigating the number density of pockets of metal free gas that survive below z = 10
-	\item They use the particle mesh tree code Gadget-2 
-	\item They begin their simulation at a higher redshift, in a larger box (7 h$^{-1}$ Mpc), with a higher mass resolution (3.4 $
-	\times$ 10$^{4}$ M$_{\odot}$) and a higher spatial resolution (0.16 h$^{-1}$ kpc).
-	\item They look between z = 30 and z = 4 and use a friend-of-friend halo finder
-	\item They assume a minimum halo mass that is capable of cooling from Trenti and Stiavelli 2009, this includes LW 
-	\item They also consider metal enrichment coming from nearby supernovaes. They find that even with relativly high wind bubble expansion velocities, metal-free halos can exist until z=5
-	\item Observing Pop III stars with JWST may be possible if their star formation efficiencies were greater than 10$^{-2}$ -- we are not seeing these types of efficiences --> JWST will likely not be able to see these stars
-	\item They say that "the best-case scenario for supernovae detection would be if multiple, very massive Pop III stars formed per halo" -- we are finding that having multiple Pop III stars in a single halo is actually more likely than having only one Pop III star
-	\item They are assuming only a single Pop III star per halo
-	\item Figure 1 shows the minimum halo mass required for cooling and collapse of a metal-free halo in the presence of a LW background. 
-	\item Upon comparing our halo masses with their mass criteria, none of our halos follow their mass trend (see jupyter notebook and https://arxiv.org/pdf/0901.0711.pdf)
-	\item 
-\end{enumerate}
-
-\li Visbal18
-\begin{enumerate}
-	\item They develop a semi-analytic technique to study evolution of Pop III to metal-enriched star formation, using n-body simulations and applying a prescription for Pop III and metal-enriched star formation
-	\item They include LW feedback and metal enrichment from supernovae winds
-	\item They use Gadget-2
-	\item First stars star forming at z=40
-	\item Our Pop III stars are forming in halos that fall below their critical mass value 
-	\item Self-consistent LW background, although does not take into account density fluctuations on scales larger than the box
-	\item They assume a single mass for all Pop III stars (40 msol)
-	\item As they only measure between z=40 and z=20, we can really only compare our peak SFRD with theirs, which does occur at about the same time.
-Our SFRD peaks around z=20 at a value of ~2$\times$10$^{-4}$ and decreases before and after z = 20.
-It looks like we are getting a similar peak value at z=20 for a Pop III SFE of 0.005 (also similar to our SFE).
-Other parameters they consider aren't hitting the same peak value as us at the end of their simulation.
-I think comparing with SFRD here is one of the only things we can directly compare, since they are looking at higher redshifts than we are.
-	\item Streaming velocities have not been included
-\end{enumerate}
-
-\li Mebane 18
-\begin{enumerate}
-	\item Focus only on neutral primordial gas accreting onto a halo and cooling via \hh{} line emission.
-	\item They try to understand how the first generation of Pop III stars persists
-	\item They are looking between z=50 and z=6
-	\item They use the Trac et al. (2015) halo mass function
-	\item They assume star formation occurs once the \hh{} fraction within a halo exceeds a critical value found in Tegmark et al.
-(1997).
-This occurs in small mass halos of about 10$^{5}$ M$_{\odot}$ at z=50
-	\item They self-consistently calculate the LW background which controls the minimum halo mass once stars begint to form
-	\item They make the Pop III IMF a variable
-	\item They have an interesting discussion about whether or not a Pop III star would be able to ionize the surrounding gas in it's birth halo, implying that Pop III stars likely form in isolation (pg.
-5)
-	\item Similar to their findings of the SFRD, our SFRD rapidly increases, then flattens out and decreases.
-Comparing with their Figure 7, our SFRD density seems to approximately match their peak values for particular variables.
-While we have a distinguished peak in our SFRD, they don't have as much of a peak.
-We seem to approximately match their mid mass and high mass Pop III IMF with energy-regulated Pop II star formation.
-	\item Our halo masses for Pop III stars appear to be quite a bit lower than their minimum masses
-	\item It may be worth including the SFRD for Pop II stars so we can compare with this paper further?
-	\item They conclude that the increasing LW background coming from Pop II stars is what halts Pop III star formation
-	\item They say that supernova feedback is one of the most important processes for a single halo: if enough metals are expelled from the halo, Pop III star formation can persist for several generations
-\end{enumerate}
-
-\li Griffen18
-\begin{enumerate}
-	\item They are using the Caterpillar simulations to do their work, specifically looking at Milky Way mass halos - rather large compared to our work
-	\item Looking at their Figure 1, our halos are forming Pop III stars below their minimum halo mass criteria
-	\item They identify Pop III star formation sites beginning at z=26, very similar to when we start seeing Pop III stars
-	\item This paper seems to be focusing on progenitors of Milky Way sized halos.
-As far as Pop III star formation goes, they seem to be getting a somewhat similiar number of potential star forming sites as we have number of Pop III stars (see their Table 2)
-\end{enumerate}
-
-\li Simulation papers: \citep{Machacek01, Yoshida03, Wise07_UVB,
-  OShea08, Muratov13}
-
 \noindent\textbf{JHW summary:} Mention that the Trenti+ and Mebane+ results have higher halo masses than the Machacek+ paper, but this is more in-line with the masses found in simulations (e.g.
@@
 
-\li Machacek01
-\begin{enumerate}
-	\item
-\end{enumerate}
-
-\li Yoshida03
-\begin{enumerate}
-	\item They are investigating primoridal star forming sites between redshifts 25 and 30 using Gadget
-	\item They take 64 snapshots from z = 100 to z = 14
-	\item Their Figure 2 and our halo mass vs.
-redshift plot are fairly similar, although we see a wider range of min halo masses for each redshift.
-We also see a bit more of a trend.
-At higher redshifts, our minimum halo mass is sitting at about 4 $\times$ 10$^{6}$ M$_{\odot}$, and steadily rises, although with a fairly large amount of scatter
-	\item I may be able to make a plot similar to Figure 3 once I get YT working properly on Comet (also for Figure 4)
-	\item They do investigate the effects of radiative feedback to various degrees, including the effects of self-shielding
-	\item They start by considering a constand Lyman-Werner background radiation with values J$_{21}$ = 0.01, and 0.1. 
-	\item They find that the mean molecular hydrogen fraction drops by an order of magnitude for J$_{21}$ = 0.01, making primordial gas cooling very inefficient
-	\item When they begin discussing the effects of self-shielding, they note that their prescription for self-shielding assumes a stationary gas, so their results show the maximum effect of self-shielding
-	\item Figure 12 shows that including a LW background does increase the minimum halo mass of halos that host gas clouds compared to the runs where there was no LW background applied.
-When self-shielding is taken into account, the minimum halo mass is lowered compared to the run without self-shielding.
-This figure shows that self-shielding does appear to be an important factor in determining the minimum halo mass that can host Pop III stars
-	\item Once they begin determining early star formation (section 8), they assume a single massive Pop III star for each cold dense gas cloud.
-They also assume the mass of the star to be at least greater than 100 solar masses, but leave this as a parameter.
-	\item They do find that just assuming a minimum-mass model for star-forming clouds over-predicts the values by up to a factor of three
-	\item The first star-forming regions appear at z=32
-	\item Top panel of Figure 15 shows that star-formation is quenched more strongly in the optically thin case than in the self-shielding case
-	\item Figure 16 shows the SFRD including self-shielding for a Pop III star with mass of 100 M$_{\odot}$ and with a mass of 600 M$_{\odot}$.
-This is a somehwat different redshift range than we are looking at, but we can compare peak values.
-Our peak value at z=20 is about 2 $\times$ 10$^{-4}$, whereas their peak value at $\approx$z=21 is 4 $\times$ 10$^{-4}$ for the Pop III star with 100 M$_{\odot}$, and 10$^{-3}$ for the Pop III star with 600 M$_{\odot}$.
-Our peak value matches fairly well with their 100 M$_{\odot}$.
-We also have a much faster rise in star formation than they do.
-I have plotted their function (Eqn.
-23) vs.
-our SFRD
-	\item Coming to their discussion section, they do state that while gas cooling is suppresed for J$_{21}$ > 0.01, when self-shielding is included, primoridial gas efficiently cools for J$_{21}$ = 0.01.
-\end{enumerate}
-
-\li Wise07UVB
-\begin{enumerate}
-	\item Using Enzo to investigate \hh{} cooling
-	\item One of their box sizes matches our box size of 1 comoving MPC
-	\item Self-shielding of LW photons is not included, and they state that they don't expect their results to change significantly by the effect of self-shielding
-	\item There are 14 simulations in this paper, with various LW fluxes, with and without \hh{} cooling. 
-	\item Their Figure 3a shows the halo masses of the most massive halos versus redshift when the halo starts to collapse.
-This figure shows higher masses than what we are seeing during similar redshift ranges
-	\item They find that \hh{} cooling is dominant even when there is a large LW background
-	\item They give a discussion about the effect of local LW sources on Pop III formation and say that these local sources should only affect the timing of nearby star formation instead of the global star formation rate.
-This appears to be similar to what we are finding as we see only a couple instances where Pop III stars are born within close proximity to one another.
-	\item \hh{} formation is possible in the center of high redshift halos with a relatively high LW intensity due to free electrons created in central shocks.
-\end{enumerate}
-
-\li OShea08
-\begin{enumerate}
-	\item They are investigating Pop III formation by varying the strength of the LW background using Enzo
-	\item They find that the LW background does delay collapse of high density gas of the most massive halo, and increases the virial mass.
-They also find that star formation can occur in LW backgrounds as high as J$_{21}$ = 1.
-	\item Their simulation is similar to ours, with a smaller boxseze (0.6 h$^{-1}$ Mpc comoving) and run from z = 99 to when gas collapses in the center of the most massive halo.
-They assume an unevolving LW background with 8 different values, ranging from J$_{LW}$ = 0 to 10$^{-21}$.
-	\item Figures 1 and 2 show the most massive halo when it begins to collapse for J$_{21}$ = 0 and 1. For J$_{21}$ = 0, collapse begins at z = 24, and for J$_{21}$ = 1, collapse begins at z = 17. 
-	\item Figure 3 shows mean halo quantities for the simulations.
-We can compare with the bottom left panel, showing the halo virial mass versus J$_{LW}$, which also has the Machacek relation plotted on it.
-Their halos all lie well above the Machacek relation.
-	\item I may be able to make a figure similar to the top panels of Figure 4 once I get the trace halos to work
-	\item Overall results relevant to our work (I think) are that as the LW background increases, Pop III star formation is delayed and will thus occur in halos with higher masses.
-They also find that Pop III star formation is never suppressed, given the LW values they investigate.
-\end{enumerate}
-
-\li Muratov13
-\begin{enumerate}
-	\item They are using the simulation code ART to investigate how Pop III stars affect their host galaxies. 
-	\item Their simulations include \hh{} formation and dissociation by LW feedback, including self-shielding.
-They have a 1 h$^{-1}$ Mpc comoving box, and two smaller boxes to see the effect of mass resolution.
-They end their simulations at z=9, similar to us.
-	\item They have a similar criteria for Pop III star formation. For our Pop III stars, we require a lower metallicity, and the same molecular hydrogen fraction. 
-	\item They assume the mass of the Pop III star to randomly be either 170 M$_{\odot}$ (PISN) or 100 M$_{\odot}$. 
-	\item They find Pop III stars forming in halos with masses $\geq$ 10$^{6}$ M$_{\odot}$ beginning at z $\approx$ 21.2. 
-	\item Their host halo masses are much larger than our host halo masses. 
-\end{enumerate}
-
-\li We don't have to compare with all of the semi-analytic papers, but
-it will be good to compare with all of the simulation papers.
-
-%====================================================================
-\subsection{Caveats}
-%====================================================================
-
-\li Optically-thin Lyman-Werner radiation field from point sources \citep{Schauer17}
-
 \noindent\textbf{JHW summary:} We should emphasize your last point for Schauer+ -- that we are overestimating the LW flux in the box.
-
-\li Schauer17
-\begin{enumerate}
-	\item Interested in the LW escape fraction from atomic cooling halos and whether or not shielding due to neutral hydrogen is important to prevent the build up of LW background
-	\item They use radiation-hydrodynamical simulations of the growth of H II regions in the first galaxies using the code ZEUS-MP. Their simulations are one dimensional. 
-	\item Their code follows the same nine chemical species as ours, and follows the growth of cosmological ionisation fronts
-	\item They calculate escape fractions in the near-field (an observer close to at rest with respect to the halo, it is within this range that \hh{} can provide shielding of the LW photons), and the far-field (an observer faraway from the halo, moving with a large velocity with respect to the halo)
-	\item They are looking at two halos with masses 10$^{7}$ and 10$^{8}$ solar masses, so already much higher than the halos hosting Pop III stars in our simulation.
-Their halos have stellar populations at the center.
-They vary different parameters of the stellar population, including SFEs and their IMF.
-	\item They find that the LW escape fraction depends on the ionisation front. If a halo is fully ionised, all photons escape.
-	\item In the near-field, for SFEs greater than 0.5\% and with a Salpeter IMF ranging from 50 to 500 Msol, the ionisation front overwhelms the halo and the gas remains ioinsed
-	\item If the spectrum weakens over time, recombination starts from the outside in and the halo becomes optically-thick.
-	\item If the ionisation front is slowly moving, the LW escape fraction can vary over a wide range. Molecular hydrogen abundance is enhanced and suppresses the LW background.
-	\item In the far-field, LW escape fractions are larger than in the near-field.
-Neutral hydrogen can shield here since "Lyman lines of Hbeta and higher, that lie in side the LW range, become very broad".
-	\item In general, they find that the LW escape fraction in these early halos is high.
-They say that unless a protogalaxy forms stars with a low 0.1\% SFE, most LW radiation will escape the halo.
-Our halos have SFEs at a much lower rate than this.
-	\item They say that "the gas present in the host halo of a stellar cluster with 10$^{4}$ to 10$^{6}$ Msol in stars cannot prevent the build-up of the LW background."
-	\item These results inform us that we are overestimating the LW radiation coming from point sources in our simulation.
-If we wanted to account for the reduced escape fraction, we could lower the intensity of our stars, and this would result in more star formation, since the overall LW radiation would be reduced.
-Although this should not significantly change our results.
-\end{enumerate}
-
-\li No streaming velocities that suppresses star formation at very
-high ($z \ga 20$) redshifts \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12} (schauer18 belongs here as well)
 
@@
 These masses are $2-3 \times 10^5 M_\odot$ and should only be important when the LW flux is small and not suppressing cooling.
-All of the halos in our simulation are more massive than this filtering mass.
+All of the halos in our simulation are more massive than {}this filtering mass.
 Even if we included streaming velocities, the gas would've fallen into the potential well when the halo exceeds the filtering mass.
@@
 
-\li Tselia11
-\begin{enumerate}
-	\item Looking at the effect of streaming velocities on the evolution of the first bound objects in the early universe.
-	\item It was previously found that the effect of streaming velocities leads to power suppression on scales corresponding to the first bound halos and delays formation of the first bound objects
-	\item Their include the relative velocities between dark matter and baryons after recombination as well as a treatment of the variation of the sound speed between recombination and z=200. 
-	\item After applying these new prescriptions, they look at how the characteristic mass scale changes between gas-rich and gas-poor halos
-	\item They find an equation for the filtering mass which provides a boundary between gas-rich and gas-poor halos.
-	\item When there is a high streaming velocity, baryons may not fall into collapsing dark matter halos, and the filtering mass would increase (figure 2)
-	\item The gas fraction in halos significantly decreases in regions where there is a high streaming velocity relative to no streaming velocity (figure 5)
-	\item Relative velocites have a large affect on minihalos
-	\item Streaming velocities significantly suppress gas accretion during halo formation and thus increases the characteristic mass of gas-rich halos at redshifts greater than 10.
-They find the characteristic mass should be around 2 $\times$ 10$^{5}$ M$_{\odot}$ at z=20.
-	\item Streaming velocities also will delay star formation and cause spatial fluctuations, although the suppression affect is about a factor of 1.6 at z=20 since the minimum mass of \hh{} cooling is larger than the chracteristic mass they found.
-There is a factor of 3.3 effect on the gas fraction in starless minihalos.
-These effects grow with redshift
-	\item Streaming velocities is what determines the gas content of halos at high redshifts
-\end{enumerate}
-
-\li Greif11\_Delay
-\begin{enumerate}
-	\item Using high resolution moving mesh simulations to show the effects of streaming velocities on the virialization of the first halo and first star formation
-	\item They focus on minihalos where they expect a more pronounced effect
-	\item Using AREPO, three different simulations with a side length of 500 kpc.
-	\item They identify the first minihalos which exceed a virial mass of 5 $\times$ 10$^{5}$ M$_{\odot}$.
-	\item They apply a relative velocity of 3 km s$^{-1}$ at z = 99.
-	\item When a streaming velocity is applied, the gas fractions in their halos are reduced by about 50\%
-	\item Figure 3 shows how the virial mass is increased when a streaming velocity is applied.
-The factor the virial mass is increased by is about 3, which results in a delay of Pop III star formation by $\delta$z $\approx$ 4
-	\item With a streaming velocity, the gas temperature at the virial radius is higher
-	\item The velocity dispersion is also higher with streaming velocities, which means the gas is more turbulent.
-They say that this could lead to a lower mass for Pop III stars than expected since fragmentation is increased
-	\item The nubmer of minihalos that can cool and form stars is reduced in the case of streaming velocities. 
-	\item Overall, gravitational collapse in minihalos is delayed, which means Pop III star formation is delayed, and the increased fragmentation may affect the mass function of the first stars. 
-\end{enumerate}
-
-\li Naoz12
-\begin{enumerate}
-	\item They use simulations to systematically understand the suppression of structure formation due to streaming velocities
-	\item They are using GADGET-2
-	\item They model the streaming velocities as constant throughout their boxes
-	\item They find that the halo number density is a function of the stream velcity. The halo mass function is suppressed for typical streaming velocity values
-	\item There is a 50\% suppression of the total number density of halos for 10$^{6}$ M$_{\odot}$ at z=19 for large streaming velocities
-	\item Where the streaming velocity is high the formation of the first stars and galaxies is delayed
-	\item There appears to be a delay in the formation epoch of gas rich halos
-	\item The position shift of baryons relative to dark matter appears to be erased by z=15
-	\item Streaming velocity will suppress the clumping factor of baryons at lower redshift 
-	\item Overall, the total halo mass function is significantly suppressed. This suppression appears to diminsh at different rates by z=15 for different streaming velocities
-	\item Significantly, they find that for the largest values of their streaming velocity, gas does not accrete onto the dark matter halo sand thus almost all halos below 10$^{6}$ M$_{\odot}$ are empty.
-Formation of the first generation of galaxies should be delayed
-	\item They also find that the reionization process may proceed differently in regions of the universe with different streaming velocities
-\end{enumerate}
-
-\li OLeary12
-\begin{enumerate}
-	\item They are simulating the formation of the first structures between z = 15 and z=200
-	\item They use a different method to model the streaming velocities, namely they use a consistent linear theory to initialize these flows, instead of simply changing the velocity of the gas at the beginning of the simulation
-	\item They are using both GADGET3 and Enzo
-	\item They are spending a fair amount of time in their paper actually comparing the results from GADGET and Enzo
-	\item They initialize their simulations including "the impact of pressure growth and rate of growth modes, temperature fluctuations, correct baryonic and dark matter velocities, and transfer functions that account for the dark matter-baryon velocity differential"
-	\item With some non-zero streaming velicities, halo gas is off center and with lower densities, which delay formation of the first stars
-	\item Maximum gas density can be suppresed by an order of magnitude for halos between 10$^{4}$ and 10$^{6}$ M$_{\odot}$
-	\item Interestingly, they find that the orientation of the filaments to the streaming velocity can tell you something about whether or not a halo has gas
-\end{enumerate}
-
-\li Schauer18
-\begin{enumerate}
-	\item They are looking at streaming velocity effects using the AREPO code
-	\item They run simulations with three different streaming velocities and without the effect of the position shift of the baryons with respect to the dark matter
-	\item A non-zero streaming velocity makes it hard for baryons to fall into dark matter halos.
-Figure 8 shows that for increasing streaming velocities, they baryon fraction in halos is significantly decreased.
-	\item This also means that the halo mass function decreases with increasing streaming velocities as can be seen in Figure 9
-	\item Figure 13 nicely shows that with increasing streaming velocities the halo mass of the first halo to contain cold gas increases. 
-	\item Overall, they find that where the streaming velocity is increased, the minimum halo mass and the average halo mass to include cold, dense gas increases significantly compared to the zero streaming velocity case.
-	\item They find that where the streaming velocity is the highest, star formation occurs in atomic cooling halos
-	\item Increasing the mass threshold for cold gas results in a suppressed star formation rate
-\end{enumerate}
-
-\li Uncertainties from the assumed Pop III initial mass function
-
 %====================================================================
@@
 %====================================================================
+In this work, we presented the analysis of the host halo mass distribution of Pop III stars and how it relates to the LW background radiation.
+We find that Pop III stars are forming in halos with a mean mass of $10^{5.9} M_\odot$ until $z = 11.5$, which falls well below the M01 relation due to \hh{} self-shielding.
+The mean halo mass then rises above the M01 to a mean value of $10^{6.6} M_\odot$ due to the domination of LW radiation throughout our simulation box produced by metal-enriched stars.
+As we compare with the literature, we appear to have much lower halo masses than those that do not include \hh{} self-shielding, so it appears that this is an important process that is often ignored in calculations.
+We also see that there doesn't appear to be a correlation between the average LW intensity with a halo and the halo mass.
+Therefore, the LW intensity may not be as indicative of which halos may form Pop III stars as previously thought.
+Pop III stars are often assumed to form in isolation, but we are finding that most of our halos are forming multiple Pop III stars, with a median number of four Pop III stars in a single halo, up to a maximum of 16 Pop III stars.
 

### 2019-04-02 paper.tex
added rough paragraphs for the comparison, caveat, and conclusion sections. also included rough comparison plot

@@
 Often in the literature, streaming velocities are only studied for a few halos.
-But \citep{Naoz13} estimates the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be see in Figure \ref{fig:compare_JLW_mass}.
+But \citet{Naoz13} estimates the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be see in Figure \ref{fig:compare_JLW_mass}.
 These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the halos in our simulation.
-\citep{Naoz13} mention that at the largest streaming velocity, their simulations don't match expected value due to a small sample size of high mass halos.
+\citet{Naoz13} mention that at the largest streaming velocity, their simulations don't match expected value due to a small sample size of high mass halos.
 If we included streaming velocities, the gas would've already fallen into the dark matter potential well when the halo exceeds this characteristic mass.

### 2019-04-11 paper.tex
Revising halo variation discussion

@@
 %====================================================================
-The collapse of gas that goes on to form Pop III stars occurs in a wide range of host halo masses across time.
-There are three main reasons why the host halo masses may vary significantly.
-First, a generation of metal-free stars can form if their progenitors had only formed stars that did not go supernova.
-This prevents metals from enriching the environment which would stop metal-free star formation and begin metal-enriched star formation.
-Second, dynamical heating from mergers and accretion can heat the gas within halos and prevent \hh{} regions from cooling.
-This would delay star formation in halos at early times \citep{Yoshida03}.
+Previous studies have focused on the minimum halo mass of Pop III hosts as a function of Lymer-Werner intensity and often in halos up to an order of magnitude greater than the mininum.
+We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation.
+There are three main causes of this significant variation in mass.
+First, a fraction of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.
+Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs.
+Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.
+Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently \hh{} cooling.
+This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situtation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}.
 Finally, temporal fluctuations in the local Lyman-Werner radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool.
-While this may only be a small affect in some halos where the local Lyman-Werner radiation is relatively low, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active Pop III star formation sites.
-The combination of these three processes will determine which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.
+While this may only be a small effect in some halos where the local Lyman-Werner radiation flucutations is relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.
+In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.
+The combination of these three processes determines which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.
 

### 2019-04-18 paper.tex
Updated paper and figures

@@
 As mentioned previously, Pop III stars form in our simulation only between 27.23 $\geq z \geq$ 9.39.
-During this time frame, a total of 697 Pop III stars form.
+During this time frame, a total of 688 Pop III stars form.
 The corresponding star formation rate density can be seen in Figure \ref{fig:pop3_SFR_bar}.
@@
 The star formation rate density does not fall to zero at the end of the simulation, since Pop III stars were still being produced when the simulation was cut off.
+The SFRD plotted here is particular for our box.
+Due to the small size of our box, we are unable to capture all of the cosmic variance.
+Therefore the SFRD is likely to change depending on the size and initial conditions of the box.
 To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}.
@@
 	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
-    \caption{The star formation rate density of Pop III stars. It peaks at a redshift of 20, and slowly falls off.}
+    \caption{The star formation rate density of Pop III stars.
+It peaks at a redshift of 20, and slowly falls off.
+Note that metal-enriched star formation continually increases throughout time, although that is not plotted here.}
     \label{fig:pop3_SFR_bar}
@@
 
-In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted against the redshift bins in Figure \ref{fig:mean_mass}.
+In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}.
+The median for each bin is plotted as an x, and the 15.9\% and 84.1\% are plotted below and above the mean, respectively.
 The M01 relation (Equation \ref{mthresh}) is plotted using the LW background intensity in Eq.
@@
 Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts.
+Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
 As can be seen by the red solid line in \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation.
-Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
+The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times.
+This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars.
 
@@
 The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass.
-The error bars indicate the 15.1\% and 84.1\% percentiles.
+The error bars indicate the 15.9\% and 84.1\% percentiles.
 Plotted along the right hand side is the percentage of halos that fall below the M01 mass threshold, also plotted along redshift.
@@
 \ref{LWbg}) is also plotted.
-We see that almost all halos form below the M01 threshold.
+We see again that almost all halos form below the M01 threshold.
 There are also a few halos that form Pop III stars in very high J$_{\rm LW}$, below the relation.
@@
 We find that a total of 84\% of the halos forming Pop III stars lie below the M01 mass threshold over the entire simulation redshift range.
+We also do not see a clear relationship between the LW intensity and the host halo mass.
+This may be showing that the LW intensity is not as great an indicator of which halo will be allowed to for a Pop III star as previously thought.
 
@@
 Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo.
-Out of the halos forming Pop III stars, only 16\% of them form single PopIII stars, whereas 54\% form between two and five Pop III stars.
+Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars.
+It should be noted that these halos aren't necessarily forming all of the Pop III stars at once.
+The number of Pop III stars that form within a halo is indicative of the star formation history of that halo.
 Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side.
@@
 %====================================================================
-Previous studies have focused on the minimum halo mass of Pop III hosts as a function of Lymer-Werner intensity and often in halos up to an order of magnitude greater than the mininum.
+Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity.
+Pop III stars often form in halos up to an order of magnitude greater than the mininum.
 We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation.
@@
 Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.
-Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently \hh{} cooling.
+Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}.
 This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situtation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}.
-Finally, temporal fluctuations in the local Lyman-Werner radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool.
-While this may only be a small effect in some halos where the local Lyman-Werner radiation flucutations is relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.
+Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool.
+While this may only be a small effect in some halos where the local LW radiation flucutations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.
 In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.
@@
 There has been a large amount of work done throughout the literature investigating the relationship between the LW background intensity and halo masses.
-\citet{Tegmark97} numerically integrates a set of chemical equations to calculate the minimum mass a halo must have in order to cool, by considering \hh{} production and cooling rates.
+\citet{Tegmark97} numerically integrated a chemical network to calculate the minimum mass a halo must have in order to cool, by considering \hh{} formation and cooling rates.
 They conclude that cooling by \hh{} is efficient and leads to the first formation of structures.
-They find a minimum halo mass needed to collapse which depends on the virial temperature of the halo and the virial redshift.
-\citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and find that metal-free halos can exist until z $\approx$ 6 using cosmological simulations and analytical calculations for metal enrichment.
+They found a minimum halo mass needed to collapse which depends on the virial temperature of the halo and the virial redshift.
+At $z = 20$, this minimum halo mass is $4 \times 10^{6} M_{\odot}$.
+\citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and found that metal-free halos can exist until z $\approx$ 6 using cosmological simulations and analytical calculations for metal enrichment.
 They also provide some insight into whether or not Pop III supernova rates are high enough within these metal-free halos to allow for the Large Synoptic Survey Telescope to see these regions of the universe.
-They use the minimum halo mass capable of cooling from \citet{Trenti09_SFR} as their halo mass model (see the blue solid line in Figure \ref{fig:compare_JLW_mass}, given our LW background).
-Neither \citet{Trenti09} nor \citet{Tegmark97} include the effects of \hh{} self-shielding, which results in the discrepancy between our data and their mass threshold relationship (Figure \ref{fig:compare_JLW_mass}).
-\citet{Mebane18} use a semi-analytic model of star formation, including a variety of feeback processes, to see for how long Pop III stars will survive for and find that Pop III stars can continue to form until z $\approx$ 6.
-They find a minimum halo mass for hosting Pop III star formation, but with the caveat that they do not include \hh{} self-shielding.
-The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations (Wise+ \& O'Shea -- put references here).
-It should be noted that because our box is fairly small, we cannot capture the cosmic variance, therefore our star formation models have large uncertainties, and we cannot directly compare these results with previous work.
+They used the minimum halo mass capable of cooling via \hh{} from \citet{Trenti09_SFR} as one part of their halo mass model (see the blue solid line in Figure \ref{fig:compare_JLW_mass}, given our LW background).
+Neither \citet{Trenti09} nor \citet{Tegmark97} included the effects of \hh{} self-shielding, which can explain the discrepancy between our data and their mass threshold relationship (Figure \ref{fig:compare_JLW_mass}).
+\citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6.
+They found a minimum halo mass for hosting Pop III star formation, but with the caveat that they did not include \hh{} self-shielding.
+They found that when Pop III stars contribute to the LW background, the minimum halo mass for Pop III star formation is $4 \times 10^{6} M_{\odot}$ as $z = 20$, similar to results from \citet{Tegmark97}.
+The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations (see \citet{Wise07_UVB, OShea08}).
+It should be noted that because our box is fairly small, we cannot capture the cosmic variance of rare halos and galaxies.
+For example, at late times, a single galaxy dominates the LW radiation field, and drives up the host halo masses.
+However, we would expect this to happen at different times in other cosmological volumes.
+Therefore, we cannot directly compare the time dependence, however, a comparison as a function of LW intensity is still valid.
 
-\citet{Yoshida03} uses cosmological simulations to study the formations of primordial star-forming clouds.
-They follow the growth of structure to find where cold gas forms to say something about the formation of the first stars, and how the effects of LW radiation may affect these gas clouds.
-Importantly, they include self-shielding within halos.
-In their series of simulations, they find a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12).
-They find that in the presence of a LW background of J$_{21}$ = 0.01, the minimum halo mass does increase compared to their runs where no LW background is applied.
-When self-shielding is taken into account, they see these halo masses decrease, falling closer to what the minimum halo masses were in the case where there was no LW background.
-They find that self-shielding does appear to be an efficient mechanism for primordial gas cooling.
+\citet{Yoshida03} used cosmological simulations to study the formation of primordial star-forming clouds.
+They followed the growth of structure to find where gas cools and condenses which would form the first stars, and how the effects of LW radiation may affect these gas clouds.
+Importantly, they included \hh{} self-shielding within halos.
+In a series of simulations, they found a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12).
+They found that in the presence of a LW background of J$_{21}$ = 0.01, the minimum halo mass at $1.5 \times 10^{6} M_{\odot}$.
+When \hh{} self-shielding is taken into account along with a LW background, they see these halo masses decrease to $9 \times 10^{6} M_{\odot}$.
+This value lies close to the case where there is no LW background applied, where the minimum halo mass is $7 \times 10^{5} M_{\odot}$.
+They find that \hh{} self-shielding does appear to be an efficient mechanism for primordial gas cooling.
 In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses across redshifts, ranging from 10$^{5.4}$ M$_{\odot}$ to 10$^{7.1}$ M$_{\odot}$.
-While our halos never experience a LW intensity as low as 0.01, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see red X in Figure \ref{fig:compare_JLW_mass}).
-\citet{Wise07_UVB} uses cosmological simulations to investigate \hh{} cooling in a LW background.
-They find that \hh{} cooling is dominant even when there is a large LW background present.
-They do not include self-shielding, and subsequently find halo masses at their collapse that closely match M01 (see pink stars in Figure \ref{fig:compare_JLW_mass}).
+While our halos never experience a LW intensity as low as 0.01, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}) (this may change !!!
+).
+\citet{Wise07_UVB} used cosmological simulations to investigate \hh{} cooling in a LW background.
+They found that \hh{} cooling is dominant even when there is a large LW background present.
+They included dynamical heating but did not include self-shielding, and subsequently found halo masses at their collapse that lie well above the M01 relation (see red open triangles in Figure \ref{fig:compare_JLW_mass}).
 Their J$_{LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
-\citet{OShea08} uses cosmological simulations to investivate Pop III star formation in various LW backgrounds.
-They find that due to an increased LW background, there is a delay in star formation, and thus there is an increase in the halo masses at collapse.
-They also ignore self-shielding in their calculations, which can again account for the increased halo masses they are finding compared to this work, as can be seen in Figure \ref{fig:compare_JLW_mass}.
+\citet{OShea08} used cosmological simulations to investivate Pop III star formation in various LW backgrounds.
+They found that due to an increased LW background, there is a delay in star formation, and thus there is an increase in the halo masses at collapse.
+They also ignored \hh{} self-shielding in their calculations and included dynamical heating, which can again account for the increased halo masses they found compared to this work, as can be seen in Figure \ref{fig:compare_JLW_mass} (open green squares).
+Their halo masses are similar to the results of \citet{Wise07_UVB}.
 Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
@@
     \caption{The average LW intensity normalized by J21 versus the halo mass for this work and a variety of other works.
-The black solid line is from M01, blue solid line from \citet{Trenti09_SFR}, red x from \citet{Yoshida03}, brown plus from \citet{OShea08}, pink stars from \citet{Wise07_UVB}.
-J$_{LW}$ = 0 for the various sources is plotted here at J$_{LW}$/J$_{21}$ = 10$^{-4}$}
+The black solid line is from M01, blue solid line from \citet{Trenti09_SFR}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.
+J$_{LW}$ = 0 for the various sources is plotted here at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
+The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.}
     \label{fig:compare_JLW_mass}
@@
 
-There are a few caveats to this work that should be noted.
-Work done by \citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo.
+There are a few minor shortenings to this work that should be noted.
+\citet{Schauer17} investigated the escape fraction of LW photons in the near-and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo.
+In the near-field with an outbreaking ionisation front, they find that the LW escape fraction is greater than 95\%.
+But when the ionisation front is slowly moving, they found that the LW escape fraction can range from 3\% to 88\%.
+In general, they find that the LW escape fractions in the far-field are higher than 75\%.
 In our work, we allow all LW photons to escape the halo.
 Since we are not accounting for the reduced escape fraction within our halos, we are overestimatng the LW radiation coming from point sources in our simulation.
-We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results.
+We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results as we find little dependence on LW intensity.
 We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}.
-Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with redshift.
-Pop III star formation is delayed by increasing the halo  mass needed to overcome the bulk velocity.
+Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with time.
+Pop III star formation is delayed by an average of $\delta z = 4$ by increasing the halo mass needed to overcome the bulk velocity by about a factor of three \citep{Greif11_Delay}.
+The streaming velocities will generally result in lower gas densities within halos as well as an offset of the peak density from the center of the halo \citep{OLeary12}.
 Often in the literature, streaming velocities are only studied for a few halos.
-But \citet{Naoz13} estimates the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be see in Figure \ref{fig:compare_JLW_mass}.
-These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the halos in our simulation.
-\citet{Naoz13} mention that at the largest streaming velocity, their simulations don't match expected value due to a small sample size of high mass halos.
-If we included streaming velocities, the gas would've already fallen into the dark matter potential well when the halo exceeds this characteristic mass.
+But \citet{Naoz13} estimated the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be seen in Figure \ref{fig:compare_JLW_mass} (see shaded bands).
+These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the star forming halos in our simulation.
+\citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass halos.
+If we had included streaming velocities, the gas would have already fallen into the dark matter potential well when the halo exceeds this characteristic mass.
 Because of this, streaming velocities would likely not affect our results.
-Finally, there is the obvious caveat of the unknown Pop III initial mass function (IMF).
-Like with any work done trying to model Pop III star formation, an IMF must be chosen.
-Therefore, we have uncertainties coming from the assumed Pop III IMF.
-
-\
-\
-\
-\
-
-\noindent\textbf{JHW summary:} In all of these papers, we shouldn't be focusing on the redshift dependence because that relies on the galaxy/star formation model that has large uncertainties.
-We should focus on the relationship between the LW background intensity and the halo masses.
-This is the best thing to do because our cosmological volume is small and cannot capture the cosmic variance.
-The Tegmark+ result is the absolute lowest halo mass for H2 cooling.
-Trenti+ uses a similar argument as them to calculate the minimum mass that is dependent on the LW background that they calculate from their semi-analytic model.
-In this discussion, I wouldn't put emphasis (e.g.
-in comparison with Mebane+) on our Pop III SFRD decreasing at a particular redshift because it's a small box.
-In other studies (like the Renaissance and Wise12+), the Pop III SFRD is pretty flat until some later time.
-None of these semi-analytic models include self-shielding.
-I think it would be worthwhile to make a plot of (minimum) host halo mass and J\_LW, comparining our work with others.
-
-\noindent\textbf{JHW summary:} Mention that the Trenti+ and Mebane+ results have higher halo masses than the Machacek+ paper, but this is more in-line with the masses found in simulations (e.g.
-Wise+ \& O'Shea).
-We should focus our comparison with Yoshida+ because it includes self-shielding and includes many different halos, whereas Wise+ and O'Shea+ only look at one halo.
-Also, we need to figure out why the Muratov+ results have much higher halo masses even though they include self-shielding.
-Is it a resolution issue or something else?
-
-\noindent\textbf{JHW summary:} We should emphasize your last point for Schauer+ -- that we are overestimating the LW flux in the box.
-
-\noindent\textbf{JHW summary:} Streaming velocities impact the very earliest Pop III host halos because they decrease with the scale factor.
-They delay the formation by increasing the necessary halo mass to overcome the bulk velocity.
-Just like the studies on LW radiation feedback, the simulations only focus on a handful of halos, whereas, Naoz+ gives a good estimate of the minimum mass (their filtering mass; equations 16-18).
-These masses are $2-3 \times 10^5 M_\odot$ and should only be important when the LW flux is small and not suppressing cooling.
-All of the halos in our simulation are more massive than {}this filtering mass.
-Even if we included streaming velocities, the gas would've fallen into the potential well when the halo exceeds the filtering mass.
-But then it couldn't cool because of the LW background.
-Thus I don't think streaming velocities would affect our results much at all.
+Finally, there is the obvious caveat of the unknown Pop III IMF.
+Like with any work done assuming a Pop III IMF, uncertainties about metal enrichment, multiplicity, total stellar mass, ionization rates, supernova rates, and the amount of black holes produced are introduced into our results.
 

### 2019-05-06 paper.tex
Adding two new plots, a new subsection, and adjusted some text.

@@
 %====================================================================
-The utilized Pop III star formation model is the same as in \citet{Wise08_Gal}. Each star particle represents a single star, and is formed in a cell when the following criteria are met: 
+The utilized Pop III star formation model is the same as in \citet{Wise08_Gal}. Each star particle represents a single massive star, and is formed in a cell when the following criteria are met: 
 \begin{enumerate}
@@
 The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere.
+In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}, we are only tracking massive Pop III star formation.
 
@@
 %====================================================================
+\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
+%====================================================================
+To demonstrate how the shielding factor can affect the column density of \hh{}, we can examine $N_{\rm H2}$ to the core as a function of halo mass for an isothermal halo, with a constant \hh{} fraction.
+The total number of \hh{} molecules within the halo is given by
+\begin{equation} \label{numberh2}
+	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
+\end{equation}
+where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c}$ is the critical density.
+The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$:
+\begin{equation} \label{columnh2}
+	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
+\end{equation}
+Here, $f_{c} = 10^{-2}$ and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$.
+For $z = 15$ and $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, Figure \ref{fig:H2_column_mass} shows the \hh{} column density as a function of halo mass.
+As the shielding factor is increases, the column density can effectively increase by an order of magnitude.
+The effect of the shielding factor on the column density of \hh{} within a halo is critical in understanding how LW feedback might affect these halos.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/H2_column_mass.pdf}
+    \caption{\hh{} column density versus halo mass for varying shielding factors.
+At f$_{\rm H2}$ = $10^{-4}$, the shielding factor is equal to one and thus acts as the case where shielding is not applied to the halo.}
+    \label{fig:H2_column_mass}
+\end{figure}
+%====================================================================
 \section{Results}
@@
 
-%====================================================================
-\subsection{Population III host halo masses}
-%====================================================================
-To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the numerical halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3.
+To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3.
 The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$50 particles.
@@
 Therefore the SFRD is likely to change depending on the size and initial conditions of the box.
+
+%====================================================================
+\subsection{Population III host halo masses}
+%====================================================================
  To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}.
@@
 In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}.
-The median for each bin is plotted as an x, and the 15.9\% and 84.1\% are plotted below and above the mean, respectively.
-The M01 relation (Equation \ref{mthresh}) is plotted using the LW background intensity in Eq.
-\ref{LWbg}.
+The median for each bin is by an x, and the 15.9\% and 84.1\% are plotted below and above the mean, respectively.
+The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq.
+\ref{LWbg} is shown as the black solid line.
 Notably, the mean halo mass falls well below the relation, at 10$^{5.9}$ M$_{\odot}$ until $z$ = 11.5, at which point, the mean halo mass rises to 10$^{6.6}$ M$_{\odot}$.
@@
 The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times.
+This galaxy has a halo mass of $10^{8.5} M_{\odot}$, a total stellar mass of $10^{6.5} M_{\odot}$, and has a peak Pop III SFR of $10^{-3.5} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $10^{-1.3}$ at $\approx$ 500 Myr.
 This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars.
+This increase in the LW background can also be seen in Figure \ref{fig:JLW_xe_mass}, where by the end of the simulation, the LW background rises to greater than 1 $J_{21}$.
 
@@
 
-The LW background intensity is plotted versus the host halo mass for each Pop III halo in our dataset in Figure \ref{fig:jlw_mass_machacek}.
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/JLW_xe_mass.pdf}
+    \caption{For the entire box, the average mass weighted LW background and the fraction of the volume ionized above 10\% versus time.
+Temperature projections are shown at the points indicated by the arrows.}
+    \label{fig:JLW_xe_mass}
+\end{figure}
+
+The LW background intensity versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}.
 Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq.
 \ref{mthresh}) for the given LW background (Eq.
-\ref{LWbg}) is also plotted.
-We see again that almost all halos form below the M01 threshold.
+\ref{LWbg}) is the solid black line.
+We see again that almost all halos form Pop III stars below the M01 threshold.
 There are also a few halos that form Pop III stars in very high J$_{\rm LW}$, below the relation.
-This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 90 pc of each other.
-Star formation can occur in a neighboring halo of a Pop III star whose LW radation does not have ample time to photodissociate enough \hh{} to completely suppress star formation.
+This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 100 pc of each other.
+Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation.
 The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs synchronically, star formation will not be suppressed, so long as they are a suitable distance away from each other.
 As there are only a few data points in this region, this situation is rare.
-It should be noted that there may be duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation.
+It should be noted that there are duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation.
 The grouped points in the higher end of J$_{\rm LW}$ are representative of such halos.
@@
 We now inspect the number of Pop III stars and the total mass of Pop III stars per halo.
-Figure \ref{fig:totnump3_halomass_sidehist} shows the number of Pop III stars per halo for a given halo mass.
+Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses < $1 M_{\odot}$.
+Figure \ref{fig:totnump3_halomass_sidehist} shows the number of Pop III stars per halo for a given halo mass, just after star formation.
 The histogram of the number of Pop III stars for all masses is projected on the right hand side.
@@
 It should be noted that these halos aren't necessarily forming all of the Pop III stars at once.
+For example, a halo can form stars again if it din't host a supernova.
 The number of Pop III stars that form within a halo is indicative of the star formation history of that halo.
+At the end of the simulation, Figure \ref{fig:final_redshift_Np3_mass} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star.
+The red line shows the median number of Pop III stars for each halo mass bin.
 Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side.
@@
     \label{fig:totnump3_halomass_sidehist}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/final_redshift_Np3_mass.pdf}
+    \caption{Total number of Pop III stars in all halos versus halo mass at the end of the simulation, at $z = 9$. The red line indicates the median number of Pop III stars in each halo mass bin.}
+    \label{fig:final_redshift_Np3_mass}
 \end{figure}
@@
 J$_{LW}$ = 0 for the various sources is plotted here at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
-The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.}
+The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
+For each band, the maximum halo mass occurs at $z = 15$.
+For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$, the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.}
     \label{fig:compare_JLW_mass}

### 2019-05-06 paper.tex
Adjusting Yoshida data

@@
 In a series of simulations, they found a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12).
-They found that in the presence of a LW background of J$_{21}$ = 0.01, the minimum halo mass at $1.5 \times 10^{6} M_{\odot}$.
-When \hh{} self-shielding is taken into account along with a LW background, they see these halo masses decrease to $9 \times 10^{6} M_{\odot}$.
-This value lies close to the case where there is no LW background applied, where the minimum halo mass is $7 \times 10^{5} M_{\odot}$.
+They found that in the presence of a LW background of J$_{21}$ = 0.01, the minimum halo mass is $7 \times 10^{5} M_{\odot}$.
+When \hh{} self-shielding is taken into account along with a LW background, they see their minimum halo mass decrease to $4.5 \times 10^{5} M_{\odot}$.
+This value lies close to the case where there is no LW background applied, where the minimum halo mass is $3.5 \times 10^{5} M_{\odot}$.
 They find that \hh{} self-shielding does appear to be an efficient mechanism for primordial gas cooling.
 In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses across redshifts, ranging from 10$^{5.4}$ M$_{\odot}$ to 10$^{7.1}$ M$_{\odot}$.
-While our halos never experience a LW intensity as low as 0.01, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}) (this may change !!!
-).
+While our halos never experience a LW intensity as low as 0.01, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}).
 \citet{Wise07_UVB} used cosmological simulations to investigate \hh{} cooling in a LW background.

### 2019-05-07 paper.tex
Added P3 spread in creation time plot, as well it's description within the results. Adjusted a few other things here and there.

@@
 Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars.
-These stars still are metal-poor, having metallicities of 10$^{-6}$ - 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to PopIII stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}.
+These stars still are metal-poor, having metallicities of 10$^{-6}$ - 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}.
 Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.
@@
 The simulation is run until $z$ = 9.32, when it becomes too computationally expensive to continue.
-At this point, 20\% of the volume is ionized.
+At this point, about 20\% of the volume is over 10\% ionized.
 We output 918 datasets,  roughly 0.5 Myr apart.
@@
 The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere.
-In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}, we are only tracking massive Pop III star formation.
+In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}.
+We are only tracking massive Pop III star formation.
 
@@
 Contrary to Pop III stars representing single star particles, metal-enriched star particles are modelled as clusters of stars.
-We enforce a minimum mass of M$_{min}$ = 1000 M$_{\odot}$ for these star particles.
+We enforce a minimum mass of M$_{\rm min}$ = 1000 M$_{\odot}$ for these star particles.
 
@@
 \end{equation}
-where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c}$ is the critical density.
-The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$:
+where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$ is the critical density.
+The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$ with $f_{c} = 10^{-2}$:
 \begin{equation} \label{columnh2}
@@
 \end{equation}
-Here, $f_{c} = 10^{-2}$ and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$.
 For $z = 15$ and $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, Figure \ref{fig:H2_column_mass} shows the \hh{} column density as a function of halo mass.
-As the shielding factor is increases, the column density can effectively increase by an order of magnitude.
+Here, the shielding factor is simply $f = 10^{\rm x} / f_{\rm H2}$, and is multiplied to the column density, effectively adjusting the \hh{} fraction within the halo.
+As the shielding factor increases, the column density can effectively increase by an order of magnitude.
 The effect of the shielding factor on the column density of \hh{} within a halo is critical in understanding how LW feedback might affect these halos.
+(More needs to be said here.
+I'd like to make it more clear about why the shielding factor changes, one way or the other, and the effects of that change.
+I don't think the plot shows exactly what we want.)
 
@@
 To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3.
-The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$50 particles.
+The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles.
 
@@
     \caption{The star formation rate density of Pop III stars.
-It peaks at a redshift of 20, and slowly falls off.
-Note that metal-enriched star formation continually increases throughout time, although that is not plotted here.}
+The SFRD peaks at a redshift of 20, and slowly falls off.
+Note that metal-enriched star formation continually increases throughout time, although that is not plotted here.
+Due to the small box size of our simulation, this SFRD is particular for our box, and would change for larger, or smaller box sizes.}
     \label{fig:pop3_SFR_bar}
@@
 In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}.
-The median for each bin is by an x, and the 15.9\% and 84.1\% are plotted below and above the mean, respectively.
+The median for each bin is represented by an x, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively.
 The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq.
@@
 The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass.
-The error bars indicate the 15.9\% and 84.1\% percentiles.
-Plotted along the right hand side is the percentage of halos that fall below the M01 mass threshold, also plotted along redshift.
+The error bars indicate the 15.9 and 84.1 percentiles.
+The right hand side shows the percentage of halos that fall below the M01 mass threshold as a function of redshift.
 The M01 mass threshold (Eq.
@@
 We also do not see a clear relationship between the LW intensity and the host halo mass.
-This may be showing that the LW intensity is not as great an indicator of which halo will be allowed to for a Pop III star as previously thought.
+This may be showing that the LW intensity is not as great an indicator of which halo will be allowed to form a Pop III star as previously thought.
 
@@
 The number of Pop III stars that form within a halo is indicative of the star formation history of that halo.
-At the end of the simulation, Figure \ref{fig:final_redshift_Np3_mass} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star.
-The red line shows the median number of Pop III stars for each halo mass bin.
 Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side.
@@
 The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$.
+
+At the end of the simulation, Figure \ref{fig:final_redshift_Np3_mass} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star.
+The red line shows the median number of Pop III stars for each halo mass bin.
+At low masses, the number of Pop III stars per halo sits around 2 Pop III stars, and quickly rises once the halo mass reaches $10^{7} M_{\odot}$.
+We can also look at the spread in creation times of these Pop III stars per halo, shown in Figure \ref{fig:p3spread_mass}.
+The halos that have a zero spread in their Pop III creation time, meaning the Pop III stars formed at the same time, lie at $10^{-3}$ Myr.
+The red line indicates the median spread in creation times for each halo mass bin.
+There are two groups within this plot.
+The first group contains halos that form their Pop III stars in a spread of < 10 Myr, with a median spread of about $10^{-1}$ Myr.
+The second group contains halos that form their Pop III stars in a spread of > 10 Myr, with a median spread of about 100 Myr.
+The second group represents typically larger mass halos that have acquired older Pop III stars by the end of the simulation through their long merger history.
+These halos have acquired these Pop III stars from outside halos, accounting for the large spread in Pop III creation time as well as the increased number of Pop III stars, as seen in Figure \ref{fig:final_redshift_Np3_mass}.
 
@@
 \begin{figure}
+	\includegraphics[width=\columnwidth]{images/totp3mass_halomass_sidehist.pdf}
+    \caption{Total mass of Pop III stars in halos hosting new Pop III stars versus halo mass.
+Lines of constant star formation efficiencies are overplotted.
+Most halos form Pop III stars at efficiencies between 10$^{-3}$ and 10$^{-4}$.}
+    \label{fig:totp3mass_halomass_sidehist}
+\end{figure}
+
+\begin{figure}
 	\includegraphics[width=\columnwidth]{images/final_redshift_Np3_mass.pdf}
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/totp3mass_halomass_sidehist.pdf}
-    \caption{Total mass of Pop III stars in halos hosting new Pop III stars versus halo mass.
-Lines of constant star formation efficiencies are overplotted.
-Most halos form Pop III stars at efficiencies between 10$^{-3}$ and 10$^{-4}$.}
-    \label{fig:totp3mass_halomass_sidehist}
+	\includegraphics[width=\columnwidth]{images/p3spread_mass.pdf}
+    \caption{The spread in Pop III creation times per halo versus halo mass at the end of the simulation.
+The red line indicates the median spread in creation times for each halo mass bin.
+There are two groups that appear in this plot, halos that have a spread of less than 10 Myr, representing halos that form Pop III stars quickly, and halos that have a spread of greater than 10 Myr, representing larger mass halos that acquire old Pop III stars through mergers.}
+    \label{fig:p3spread_mass}
 \end{figure}

### 2019-05-08 paper.tex
Making adjustments discussed on 05/08/19.

@@
 \usepackage{hyperref}
+\usepackage{subcaption}
+\usepackage{caption}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-For $z = 15$ and $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, Figure \ref{fig:H2_column_mass} shows the \hh{} column density as a function of halo mass.
-Here, the shielding factor is simply $f = 10^{\rm x} / f_{\rm H2}$, and is multiplied to the column density, effectively adjusting the \hh{} fraction within the halo.
-As the shielding factor increases, the column density can effectively increase by an order of magnitude.
-The effect of the shielding factor on the column density of \hh{} within a halo is critical in understanding how LW feedback might affect these halos.
-(More needs to be said here.
-I'd like to make it more clear about why the shielding factor changes, one way or the other, and the effects of that change.
-I don't think the plot shows exactly what we want.)
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{images/H2_column_mass.pdf}
-    \caption{\hh{} column density versus halo mass for varying shielding factors.
-At f$_{\rm H2}$ = $10^{-4}$, the shielding factor is equal to one and thus acts as the case where shielding is not applied to the halo.}
-    \label{fig:H2_column_mass}
-\end{figure}
+For $z = 15$ and $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, ... 
 %====================================================================
@@
 The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles.
+By the end of the simulation, over 10\% of the box is ionized over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.
 
@@
     \label{fig:hmf}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/JLW_xe_mass.pdf}
+    \caption{For the entire box, the average mass weighted LW background and the fraction of the volume ionized above 10\% versus time.
+Temperature projections are shown at the points indicated by the arrows.}
+    \label{fig:JLW_xe_mass}
 \end{figure}
@@
 Therefore the SFRD is likely to change depending on the size and initial conditions of the box.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
+    \caption{The star formation rate density of Pop III stars.
+The SFRD peaks at a redshift of 20, and slowly falls off.
+Note that metal-enriched star formation continually increases throughout time, although that is not plotted here.
+Due to the small box size of our simulation, this SFRD is particular for our box, and would change for larger, or smaller box sizes.}
+    \label{fig:pop3_SFR_bar}
+\end{figure}
 
@@
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
-    \caption{The star formation rate density of Pop III stars.
-The SFRD peaks at a redshift of 20, and slowly falls off.
-Note that metal-enriched star formation continually increases throughout time, although that is not plotted here.
-Due to the small box size of our simulation, this SFRD is particular for our box, and would change for larger, or smaller box sizes.}
-    \label{fig:pop3_SFR_bar}
-\end{figure}
-
 In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}.
@@
 \ref{LWbg} is shown as the black solid line.
-Notably, the mean halo mass falls well below the relation, at 10$^{5.9}$ M$_{\odot}$ until $z$ = 11.5, at which point, the mean halo mass rises to 10$^{6.6}$ M$_{\odot}$.
+Notably, the mean halo mass falls well below the relation, at $7.7 \times 10^{5}$ M$_{\odot}$ until $z$ = 11.5, at which point, the mean halo mass rises to $3.7 \times 10^{6}$ M$_{\odot}$.
 The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation.
@@
 The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times.
-This galaxy has a halo mass of $10^{8.5} M_{\odot}$, a total stellar mass of $10^{6.5} M_{\odot}$, and has a peak Pop III SFR of $10^{-3.5} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $10^{-1.3}$ at $\approx$ 500 Myr.
+This galaxy has a halo mass of $3.6 \times 10^{8} M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $5.4 \ times 10^{-2}$ at $\approx$ 500 Myr.
 This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars.
@@
 	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
-    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus redshift.
+    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus time.
 The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass.
@@
 \ref{LWbg}.
-Almost all halos fall below the M01 relation, until $z$ = 11.5, when the mean halo mass rises above the relation.}
+Almost all halos fall below the M01 relation, until $\approx$ 380 Myr, when the mean halo mass rises above the relation.}
     \label{fig:mean_mass}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{images/JLW_xe_mass.pdf}
-    \caption{For the entire box, the average mass weighted LW background and the fraction of the volume ionized above 10\% versus time.
-Temperature projections are shown at the points indicated by the arrows.}
-    \label{fig:JLW_xe_mass}
 \end{figure}
@@
 We can also look at the spread in creation times of these Pop III stars per halo, shown in Figure \ref{fig:p3spread_mass}.
-The halos that have a zero spread in their Pop III creation time, meaning the Pop III stars formed at the same time, lie at $10^{-3}$ Myr.
+The halos that have a zero spread in their Pop III creation time, meaning the Pop III stars formed at the same time, lie at $10^{-2}$ Myr.
 The red line indicates the median spread in creation times for each halo mass bin.
@@
 
-\begin{figure}
+\begin{figure*}
+	\centering
+	\begin{subfigure}{.5\textwidth}
+  		\centering
   		\includegraphics[width=\columnwidth]{images/totnump3_halomass_sidehist.pdf}
-    \caption{Total number of Pop III stars in halos hosting new Pop III stars versus halo mass.
-A median number of four Pop III stars form in a single halo, with some forming as many as 16 Pop III stars.}
+  		\caption{Total number of Pop III stars in halos hosting new Pop III stars versus halo mass at the instance of star formation.}
   		\label{fig:totnump3_halomass_sidehist}
-\end{figure}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+  		\centering
+  		\includegraphics[width=\columnwidth]{images/final_redshift_Np3_mass.pdf}
+  		\caption{Total number of Pop III stars in all halos versus halo mass at the end of the simulation, at $z \approx 9$.}
+  		\label{fig:final_redshift_Np3_mass}
+	\end{subfigure}
+	\caption{The number of Pop III stars per halo versus halo mass at the instance of Pop III star formation and the final redshift.
+On the left, a Pop III star will form in a halo which contains a median number of four Pop III stars, with some containing as many as 16 Pop III stars.
+On the right, the red line indicates the median number of Pop III stars in each halo mass bin.}
+\end{figure*}
 
@@
     \label{fig:totp3mass_halomass_sidehist}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{images/final_redshift_Np3_mass.pdf}
-    \caption{Total number of Pop III stars in all halos versus halo mass at the end of the simulation, at $z = 9$. The red line indicates the median number of Pop III stars in each halo mass bin.}
-    \label{fig:final_redshift_Np3_mass}
 \end{figure}

### 2019-05-13 paper.tex
Adding shielding calculation, adjustments to abstract, conclusion, title

@@
 % Keep the title short and informative.
-\title[Where Do Pop III Stars Form?]{Where Do Population III Stars Form?}
+\title[Where Do Pop III Stars Form?]{Where Do Population III Stars Form? The Effects of Radiative Feedback and Self-Shielding on the Host Halo Mass Distribution}
 
@@
 \begin{abstract}
-We perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Population III stars, using the adaptive mesh refinement code \enzo{}.
+The formation of Population III (Pop III) stars is a critical step in the evolution of the early universe.
+To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place is crucial to understand.
+One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, which can destroy \hh{}, a necessary ingredient for the cooling and creation of Pop III stars.
+\hh{} self-shielding can alleviate the effect the LW background has on the \hh{} within halos, and is a process which is often neglected throughout the literature.
+In this work, we perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Population III stars, using the adaptive mesh refinement code \enzo{}.
 We investigate the distribution of host halo masses and its relationship to the Lyman-Werner background intensity.
-In our sample of 697 host halos, we find that 84\% of them have masses below the Machacek et al.
-(2001) relation because of the inclusion of \hh{} self-shielding.
-In our simulation above a redshift of 11.5, the mean halo mass is time-independent and ~10$^{5.9}$ M$_{\odot}$.
-Afterwards, it steadily rises above the Machacek et al.
-relation to a mean value of ~10$^{6.6}$ M$_{\odot}$.
-Most of these halos form multiple Population III stars, with a median number of four, up to a maximum of 16.
-We also find that a few halos do form stars below the Machacek et al.
-relation but in a high Lyman-Werner radiation field with values up to ~50 J$_{21}$.
+In our simulation above a redshift of 11.5, the mean halo mass is time-independent and $7.7 \times 10^{5} M_{\odot}$.
+Afterwards, it steadily rises to a mean value of $3.7 \times 10^{6} M_{\odot}$, due to the increased LW background coming from a massive galaxy actively forming stars.
+Compared to the literature, our halos form Pop III stars at much lower masses due tot eh inclusion of \hh{} self-shielding.
+Most halos form multiple Population III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation.
+We also find that a few halos do form stars in a high Lyman-Werner radiation field with values up to ~50 J$_{21}$.
 Our results suggest that Population III star formation may be less affected by Lyman-Werner radiation feedback than previously thought and that Population III multiple systems are common.
-\end{abstract}
+\end{abstract}{}
 
@@
 Here, x $\equiv$ N$_{H_{2}}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter.
+This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding.
 
@@
 %====================================================================
-To demonstrate how the shielding factor can affect the column density of \hh{}, we can examine $N_{\rm H2}$ to the core as a function of halo mass for an isothermal halo, with a constant \hh{} fraction.
+To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ to the core as a function of halo mass for an isothermal halo, with a constant \hh{} fraction, and use Equation \ref{shield} to calculate the shielding factor.
 The total number of \hh{} molecules within the halo is given by
@@
 where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$ is the critical density.
-The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$ with $f_{c} = 10^{-2}$:
+The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$:
 \begin{equation} \label{columnh2}
@@
 \end{equation}
-For $z = 15$ and $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, ... 
+
+For $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, a typical \hh{} fraction of $f_{\rm H2} = 10^{-4}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, and redshift.
+Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively.
+The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$.
+At each redshift, all halo masses, and each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum.
+The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background.
+Smaller mass halos can then form Pop III stars since \hh{} will stick around in the halo for a longer amount of time.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/shield_mass.pdf}
+    \caption{Shielding factor as a function of halo mass.
+Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$.
+For these parameters, and assuming the Doppler broadening parameter equals the circular velocity, the shielding factor is almost zero, implying maximum shielding.}
+    \label{fig:shield_mass}
+\end{figure}
 %====================================================================
@@
 \ref{LWbg} is shown as the black solid line.
-Notably, the mean halo mass falls well below the relation, at $7.7 \times 10^{5}$ M$_{\odot}$ until $z$ = 11.5, at which point, the mean halo mass rises to $3.7 \times 10^{6}$ M$_{\odot}$.
+Notably, the mean halo mass falls well below the relation, at $7.7 \times 10^{5}$ M$_{\odot}$ until $\approx$ 380 Myr, at which point, the mean halo mass rises to $3.7 \times 10^{6}$ M$_{\odot}$.
 The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation.
@@
 The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times.
-This galaxy has a halo mass of $3.6 \times 10^{8} M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $5.4 \ times 10^{-2}$ at $\approx$ 500 Myr.
+This galaxy has a halo mass of $3.6 \times 10^{8} M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $5.4 \times 10^{-2}$ at $\approx$ 500 Myr.
 This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars.
@@
 Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses < $1 M_{\odot}$.
-Figure \ref{fig:totnump3_halomass_sidehist} shows the number of Pop III stars per halo for a given halo mass, just after star formation.
+The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation.
 The histogram of the number of Pop III stars for all masses is projected on the right hand side.
@@
 
-At the end of the simulation, Figure \ref{fig:final_redshift_Np3_mass} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star.
+At the end of the simulation, the right panel of Figure \ref{fig:num_p3} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star.
 The red line shows the median number of Pop III stars for each halo mass bin.
@@
 The second group represents typically larger mass halos that have acquired older Pop III stars by the end of the simulation through their long merger history.
-These halos have acquired these Pop III stars from outside halos, accounting for the large spread in Pop III creation time as well as the increased number of Pop III stars, as seen in Figure \ref{fig:final_redshift_Np3_mass}.
+These halos have acquired these Pop III stars from outside halos, accounting for the large spread in Pop III creation time as well as the increased number of Pop III stars, as seen in the right panel of Figure \ref{fig:num_p3}.
 
@@
   \centering
-	\begin{subfigure}{.5\textwidth}
-  		\centering
-  		\includegraphics[width=\columnwidth]{images/totnump3_halomass_sidehist.pdf}
-  		\caption{Total number of Pop III stars in halos hosting new Pop III stars versus halo mass at the instance of star formation.}
-  		\label{fig:totnump3_halomass_sidehist}
-	\end{subfigure}%
-	\begin{subfigure}{.5\textwidth}
-  		\centering
-  		\includegraphics[width=\columnwidth]{images/final_redshift_Np3_mass.pdf}
-  		\caption{Total number of Pop III stars in all halos versus halo mass at the end of the simulation, at $z \approx 9$.}
-  		\label{fig:final_redshift_Np3_mass}
-	\end{subfigure}
-	\caption{The number of Pop III stars per halo versus halo mass at the instance of Pop III star formation and the final redshift.
-On the left, a Pop III star will form in a halo which contains a median number of four Pop III stars, with some containing as many as 16 Pop III stars.
-On the right, the red line indicates the median number of Pop III stars in each halo mass bin.}
+  \includegraphics[width=0.48\textwidth]{images/totnump3_halomass_sidehist.pdf}
+  \hfill
+  \includegraphics[width=0.48\textwidth]{images/final_redshift_Np3_mass.pdf}
+  \caption{The number of Pop III stars per halo versus halo mass at the instance of Pop III star formation (left) and the final redshift (right).
+At the instance of formation, Pop III stars will form in a halo which contains a median number of four Pop III stars, with some containing as many as 16 Pop III stars.
+On the right, the red line indicates the median number of Pop III stars in each halo mass bin.
+By the end of the simulation, high mass halos contain a large number of Pop III stars due to their long merger history with smaller halos hosting Pop III stars.}
+  \label{fig:num_p3}
 \end{figure*}
@@
 In this work, we presented the analysis of the host halo mass distribution of Pop III stars and how it relates to the LW background radiation.
-We find that Pop III stars are forming in halos with a mean mass of $10^{5.9} M_\odot$ until $z = 11.5$, which falls well below the M01 relation due to \hh{} self-shielding.
-The mean halo mass then rises above the M01 to a mean value of $10^{6.6} M_\odot$ due to the domination of LW radiation throughout our simulation box produced by metal-enriched stars.
-As we compare with the literature, we appear to have much lower halo masses than those that do not include \hh{} self-shielding, so it appears that this is an important process that is often ignored in calculations.
-We also see that there doesn't appear to be a correlation between the average LW intensity with a halo and the halo mass.
+We find that Pop III stars are forming in halos with a mean mass of $7.7 \times 10^{5}$ M$_{\odot}$, which falls well below the M01 relation due to \hh{} self-shielding, until $\approx$ 380 Myr, at which point the mean halo mass rises above the M01 relation to a mean value of $3.7 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive halo in the simulation box.
+As we compare with the literature, we see much lower halo masses hosting Pop III stars due to the inclusion of \hh{} shielding.
+It appears that this is an important process that is often ignored in calculations.
+We also see that there doesn't appear to be a correlation between the average LW intensity within a halo and the halo mass.
 Therefore, the LW intensity may not be as indicative of which halos may form Pop III stars as previously thought.
-Pop III stars are often assumed to form in isolation, but we are finding that most of our halos are forming multiple Pop III stars, with a median number of four Pop III stars in a single halo, up to a maximum of 16 Pop III stars.
+Pop III stars are often assumed to form in isolation, but we find that most of our halos are forming multiple Pop III stars, with a median number of four Pop III stars in a single halo, up to a maximum of 16 Pop III stars.
+By the end of the simulation, halos with masses > $10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos.
+This results in these high mass halos containing multiple Pop III stars, both young and old.
+
+Our results provide another piece of the Pop III puzzle.
+With the inclusion of \hh{} self-shielding, we find Pop III stars forming in smaller mass halos than previously predicted and not necessarily in isolation.
+The assumptions often made about the formation of Pop III stars appear to break down when important processes are taken into account, and restrictions about their formation are lifted.
+Further work needs to be done to determine why some halos form Pop III stars and others don't, to provide further insight about the formation process of these stars and thus how they will affect their surrounding galactic environment.
 

### 2019-05-13 paper.tex
Tiny abstract adjustment

@@
 The formation of Population III (Pop III) stars is a critical step in the evolution of the early universe.
-To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place is crucial to understand.
+To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place needs to be determined.
 One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, which can destroy \hh{}, a necessary ingredient for the cooling and creation of Pop III stars.

### 2019-05-13 paper.tex
Okay, one more tiny adjustment to the abstract

@@
 In this work, we perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Population III stars, using the adaptive mesh refinement code \enzo{}.
-We investigate the distribution of host halo masses and its relationship to the Lyman-Werner background intensity.
+We investigate the distribution of host halo masses and its relationship to the LW background intensity.
 In our simulation above a redshift of 11.5, the mean halo mass is time-independent and $7.7 \times 10^{5} M_{\odot}$.
 Afterwards, it steadily rises to a mean value of $3.7 \times 10^{6} M_{\odot}$, due to the increased LW background coming from a massive galaxy actively forming stars.
-Compared to the literature, our halos form Pop III stars at much lower masses due tot eh inclusion of \hh{} self-shielding.
-Most halos form multiple Population III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation.
-We also find that a few halos do form stars in a high Lyman-Werner radiation field with values up to ~50 J$_{21}$.
-Our results suggest that Population III star formation may be less affected by Lyman-Werner radiation feedback than previously thought and that Population III multiple systems are common.
+Compared to the literature, our halos form Pop III stars at much lower masses due to the inclusion of \hh{} self-shielding.
+Most halos form multiple Pop III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation.
+We also find that a few halos do form stars in a high LW radiation field with values up to ~50 J$_{21}$.
+Our results suggest that Pop III star formation may be less affected by LW radiation feedback than previously thought and that Pop III multiple systems are common.
 \end{abstract}{}

### 2019-05-16 paper.tex
Removing unused (sub)caption packages
Adjustments to abstract, conclusion and figures.

@@
 \hh{} self-shielding can alleviate the effect the LW background has on the \hh{} within halos, and is a process which is often neglected throughout the literature.
-In this work, we perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Population III stars, using the adaptive mesh refinement code \enzo{}.
+In this work, we perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Pop III stars, using the adaptive mesh refinement code \enzo{}.
 We investigate the distribution of host halo masses and its relationship to the LW background intensity.
-In our simulation above a redshift of 11.5, the mean halo mass is time-independent and $7.7 \times 10^{5} M_{\odot}$.
-Afterwards, it steadily rises to a mean value of $3.7 \times 10^{6} M_{\odot}$, due to the increased LW background coming from a massive galaxy actively forming stars.
 Compared to the literature, our halos form Pop III stars at much lower masses due to the inclusion of \hh{} self-shielding.
+We see no relationship between the LW intensity and host halo mass.
 Most halos form multiple Pop III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation.
-We also find that a few halos do form stars in a high LW radiation field with values up to ~50 J$_{21}$.
 Our results suggest that Pop III star formation may be less affected by LW radiation feedback than previously thought and that Pop III multiple systems are common.
@@
 
-For $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, a typical \hh{} fraction of $f_{\rm H2} = 10^{-4}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, and redshift.
+For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, a typical \hh{} fraction of $f_{\rm H2} = 10^{-4}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, and redshift.
 Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively.
@@
 %====================================================================
-In this work, we presented the analysis of the host halo mass distribution of Pop III stars and how it relates to the LW background radiation.
-We find that Pop III stars are forming in halos with a mean mass of $7.7 \times 10^{5}$ M$_{\odot}$, which falls well below the M01 relation due to \hh{} self-shielding, until $\approx$ 380 Myr, at which point the mean halo mass rises above the M01 relation to a mean value of $3.7 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive halo in the simulation box.
-As we compare with the literature, we see much lower halo masses hosting Pop III stars due to the inclusion of \hh{} shielding.
-It appears that this is an important process that is often ignored in calculations.
-We also see that there doesn't appear to be a correlation between the average LW intensity within a halo and the halo mass.
-Therefore, the LW intensity may not be as indicative of which halos may form Pop III stars as previously thought.
-Pop III stars are often assumed to form in isolation, but we find that most of our halos are forming multiple Pop III stars, with a median number of four Pop III stars in a single halo, up to a maximum of 16 Pop III stars.
-By the end of the simulation, halos with masses > $10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos.
+In this work, we presented the analysis of the host halo mass distribution of Pop III stars and how it relates to the LW background radiation. From our results, we conclude the following:
+
+\begin{itemize}
+	\item We find that Pop III stars are forming in halos with a mean mass of $7.7 \times 10^{5}$ M$_{\odot}$, which falls well below the M01 relation, until $\approx$ 380 Myr, at which point the mean halo mass rises above the M01 relation to a mean value of $3.7 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive halo in the simulation box.
+	\item Including \hh{} self-shielding results in lower mass halos forming Pop III stars as compared with the literature.
+	\item There does not appear to be a strict correlation between LW intensity within a halo and the halo mass.
+LW intensity within a halo may not be as indicative of which halos may form Pop III stars as previously thought.
+	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
+	\item By the end of the simulation, halos with masses > $10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos.
 This results in these high mass halos containing multiple Pop III stars, both young and old.
+\end{itemize}
 
 Our results provide another piece of the Pop III puzzle.
-With the inclusion of \hh{} self-shielding, we find Pop III stars forming in smaller mass halos than previously predicted and not necessarily in isolation.
-The assumptions often made about the formation of Pop III stars appear to break down when important processes are taken into account, and restrictions about their formation are lifted.
-Further work needs to be done to determine why some halos form Pop III stars and others don't, to provide further insight about the formation process of these stars and thus how they will affect their surrounding galactic environment.
+With the inclusion of \hh{} self-shielding, we find Pop III stars forming in smaller mass halos than previously predicted.
+These smaller mass halos provide more sites for Pop III star formation, and therefore, more metal-enrichment within halos.
+We also find that Pop III stars don't have to form in isolation, in fact, they are more likely to form in a halo that has already formed multiple other Pop III stars.
+Since these stars are generally very massive, and are likely to produce stellar mass black holes, they may be gravitational wave candidates detected through LIGO.
+While we do not see any relationship between the LW intensity and Pop III host halo mass,  in order to determine exactly how the LW intensity influences the host halo mass, a more systematic approach needs to be taken.
+
+The assumptions often made about the formation of Pop III stars appear to break down when important processes are taken into account and restrictions about their formation are lifted.
+Further work needs to be done to determine why some halos form Pop III stars and others don't, to provide insight about the formation process of these stars and thus how they will affect their surrounding galactic environment.
+The effect of the LW intensity on host halo mass needs to be systematically investigated to determine whether or not this background radiation really has a profound effect on Pop III formation or not.
+The possibility of halos hosting multiple Pop III stars provides another avenue for observation with LIGO detecting gravitational waves coming from solar mass black holes produced from Pop III stars.
+The exact detection signature of these gravitational waves is a topic which also needs to be studied further.
 

### 2019-05-17 paper.tex
Adding shielding plot, fixed reference problem

@@
 \usepackage{hyperref}
-\usepackage{subcaption}
-\usepackage{caption}
+%\usepackage{subcaption}
+%\usepackage{caption}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The first generation of stars transformed a cold and dark universe
+%The first generation of stars transformed a cold and dark universe
 by illuminating and enriching up their neighborhoods with radiation
@@
 The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$.
-At each redshift, all halo masses, and each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum.
+Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.
+At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum.
 The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background.
 Smaller mass halos can then form Pop III stars since \hh{} will stick around in the halo for a longer amount of time.
+We also see that for column densities at just under $10^{17} cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} at relatively low column densities.
 
@@
 Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$.
-For these parameters, and assuming the Doppler broadening parameter equals the circular velocity, the shielding factor is almost zero, implying maximum shielding.}
+For these parameters, and assuming the Doppler broadening parameter equals the circular velocity, the shielding factor is almost zero, implying maximum shielding.
+The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s.
+}
     \label{fig:shield_mass}
@@
 There are a few halos that have Pop III stars forming at later times and at high halo masses.}
-    \label{fig:jlw_mass_machacek}{}
+    \label{fig:jlw_mass_machacek}
 \end{figure}

### 2019-05-28 paper.tex
Addressing edits from John's paper-JHW-28May.pdf

@@
 To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place needs to be determined.
-One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, which can destroy \hh{}, a necessary ingredient for the cooling and creation of Pop III stars.
-\hh{} self-shielding can alleviate the effect the LW background has on the \hh{} within halos, and is a process which is often neglected throughout the literature.
-In this work, we perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Pop III stars, using the adaptive mesh refinement code \enzo{}.
+One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, that destroys \hh{}, a necessary coolant in the creation of Pop III stars.
+Self-shielding can alleviate the effect the LW background has on the \hh{} within halos.
+In this work, we perform a cosmological simulation to study the birthplaces of Pop III stars, using the adaptive mesh refinement code \textsc{Enzo}.
 We investigate the distribution of host halo masses and its relationship to the LW background intensity.
-Compared to the literature, our halos form Pop III stars at much lower masses due to the inclusion of \hh{} self-shielding.
+Compared to previous work, halos form Pop III stars at much lower masses, up to a factor of a few, due to the inclusion of \hh{} self-shielding.
 We see no relationship between the LW intensity and host halo mass.
@@
 
-%The first generation of stars transformed a cold and dark universe
+The first generation of stars transformed a cold and dark universe
 by illuminating and enriching up their neighborhoods with radiation
@@
 Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation.
-Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10, Smith15}.
+Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep{Wise08_Gal, Greif10, Smith15}.
 Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars.
-These stars still are metal-poor, having metallicities of 10$^{-6}$ - 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}.
+These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}.
 Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.
-
-Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos.
-But in which halos do these first generations of stars form?
-Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization.
-Learning about their host halos can also guide future telescopic surveys to observe Pop III galaxies which may lead to their direct observational evidence.
-Previous studies have investigated the possibility of finding Pop III systems.
-For example, \citet{Trenti09} found that metal-free halos may still be able to form at $z \approx$ 6, which offer the best chance at observing such primordial systems.
-They find that, given a certain rate of Pop III supernova per year, large sky surveys, such as the Large Synoptic Survey Telescope (LSST), should be able to detect the very luminous supernova.
-\citet{Trenti09} determine that unless the metal-free systems are particularly efficient at forming Pop III stars (star formation efficiencies > 10$^{-2}$), the upcoming James Webb Space Telescope (JWST) will not be able to detect such systems.
-
-Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars.
-\citet{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15.
-In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time.
-\citet{Visbal18} devised a semi-analytic model for the formation of Pop III stars and the transition to metal-enriched stars.
-They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing escape fraction, leads to large differences in the star formation history of Pop III and metal-enriched stars.
-This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.
 
@@
 
+Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos.
+But in which halos do these first generations of stars form?
+Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization.
+Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars.
+\citet{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15.
+In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time.
+\citet{Visbal18} devised a semi-analytic model for the formation of Pop III stars and the transition to metal-enriched stars.
+They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing escape fraction, leads to large differences in the star formation history of Pop III and metal-enriched stars.
+This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.
+
 Previous work have mainly investigated and established the lower limit for a halo to host Pop III stars, or for a halo to collapse.
@@
 \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
-They derive a simple analytic expression for the mass threshold of halos given a particular LW flux:
+They fit a simple analytic expression for the mass threshold of halos given a particular LW flux:
 \begin{equation} \label{mthresh}
-	M_{\rm TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{\rm LW}}{10^{-21}} \right)^{.47}
+	M_{\rm TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{\rm LW}}{10^{-21}} \right)^{0.47} .
 \end{equation}
@@
 They find that \hh{} cooling is always a dominant process, even in large LW background fluxes.
-Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
+\citet{OShea08} also find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
 
@@
 %====================================================================
-We run and analyze a cosmological simulation with the adaptive mesh refinement (AMR) code \enzo{} \citep{Enzo} and the toolkit \yt{} \citep{yt_full_paper}.
-\enzo{} uses an N-body adaptive particle-mesh solver \citep{Efstathiou85, Couchman91, BryanNorman1997} to follow the dark matter (DM) dynamics.
+We run and analyze a cosmological simulation with the adaptive mesh refinement (AMR) code \textsc{Enzo} \citep{Enzo} and the toolkit \yt{} \citep{yt_full_paper}.
+\textsc{Enzo} uses an N-body adaptive particle-mesh solver \citep{Efstathiou85, Couchman91} to follow the dark matter (DM) dynamics.
 We use the nine-species (\hi, \hii, \hei, \heii, \heiii, e$^{-}$, H$_{2}$, H$_{2}^{+}$, H$^{-}$) non-equilibrium chemistry model \citep{Abel97, Anninos97}.
@@
 We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
-resolution and a dark matter paticle mass of 2000 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
+resolution and a dark matter paticle mass of 2000.54 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
 initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and uses the cosmological parameters from the Planck collaboration best fit 
-\citet{Planck13_Cosmo}: $\Omega_{M}$ = 0.3175, $\Omega_{\Lambda}$ = 
-0.6825, $\Omega_{DM}$ = 0.2685, and h = 0.6711, with the variables 
+\citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 
+0.6825, $\Omega_{\rm DM}$ = 0.2685, and h = 0.6711, with the variables 
 having their usual definitions.
@@
 where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.
-
-We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the radiation field.
-Centered on each metal-enriched and Pop III star, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile.
+This form gives a maximum of $J_{\rm LW}/J_{21} = 0.85$ at a redshift of 13.5 and quickly and continually declines for higher redshifts.
+We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the ionizing radiation field.
+Centered on each metal-enriched and Pop III star particle, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile.
 These LW sources are added on top of the background intensity described above.
@@
 %====================================================================
-In this section, we will discuss how we implement Pop III and metal-enriched star formation.
+In this section, we briefly discuss our implementation of Pop III and metal-enriched star formation.
 We do not consider the formation and feedback from stellar remnants or asymptotic giant branch (AGB) stars.
@@
 %====================================================================
-The utilized Pop III star formation model is the same as in \citet{Wise08_Gal}. Each star particle represents a single massive star, and is formed in a cell when the following criteria are met: 
+The utilized Pop III star formation model is the same as in \citet{Wise08_Gal} but with updated parameters.
+Each star particle represents a single massive star, and is formed in a cell when the following criteria are met:
 \begin{enumerate}
@@
 where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}.
-This characteristic mass is different from W12 \citep{Hirano17}.
+This characteristic mass is different from the W12 choice of 100 M$_{\odot}$.
 This results in an exponential cutoff before M$_{\rm char}$ and a power-law IMF after.
@@
 
-The lifetime of these particles is 20 Myr, during which they radiate 6000 hydrogen ionising photons per stellar baryon, or 1.13 $\times$ 10$^{46}$ photons s$^{-1}$ M$_{\odot}^{-1}$, which is appropriate for a Salpeter IMF.
+The lifetime of these particles is 20 Myr, during which they radiate 6000 hydrogen ionising photons per stellar baryon, or 1.13 $\times$ 10$^{46}$ photons s$^{-1}$ M$_{\odot}^{-1}$, which is appropriate for a Salpeter IMF \citep{Schaerer03}.
 Their spectra are approximated with a monochromatic spectrum with an energy of 21.6 eV at a constant luminosity.
@@
 \begin{equation} \label{Lchar}
-	L_{\rm char} = \frac{\rho}{|\nabla \rho|}
+	L_{\rm char} = \frac{\rho}{|\nabla \rho|} \ . 
 \end{equation}
@@
 Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al.
-determine that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures.
+determined that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures.
 The implemented shielding factor is then (see Eq.
@@
 \end{equation}
-Here, x $\equiv$ N$_{H_{2}}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter.
+Here, x $\equiv$ N$_{\rm H2}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter.
 This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding.
@@
 %====================================================================
-To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ to the core as a function of halo mass for an isothermal halo, with a constant \hh{} fraction, and use Equation \ref{shield} to calculate the shielding factor.
-The total number of \hh{} molecules within the halo is given by
+To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a constant \hh{} fraction, and use Equation \ref{shield} to calculate the shielding factor.
+The \hh{} molecule number density within the halo is given by
 \begin{equation} \label{numberh2}
@@
 The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background.
-Smaller mass halos can then form Pop III stars since \hh{} will stick around in the halo for a longer amount of time.
-We also see that for column densities at just under $10^{17} cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} at relatively low column densities.
+Smaller mass halos can then form Pop III stars since \hh{} will survive in the halo for a longer amount of time.
+We also see that for column densities at just under $10^{17} \rm cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} at relatively low column densities.
 
@@
 The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles.
-By the end of the simulation, over 10\% of the box is ionized over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.
+After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box.
+These stars either become black holes or supernova at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
+Metal-enriched star formation begins to take place as soon as enough metals are present within a halo.
+In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place.
+By the end of the simulation, 20\% of the box is ionized over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.
 
@@
 
-As mentioned previously, Pop III stars form in our simulation only between 27.23 $\geq z \geq$ 9.39.
-During this time frame, a total of 688 Pop III stars form.
+In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39.
 The corresponding star formation rate density can be seen in Figure \ref{fig:pop3_SFR_bar}.
-Pop III star formation peaks at a redshift of 20 and slowly decreases.
+Pop III star formation peaks at $1.9 \times 10^{-4}$ at $z = 21.3$ and slowly decreases.
 The star formation rate density does not fall to zero at the end of the simulation, since Pop III stars were still being produced when the simulation was cut off.
@@
 \ref{LWbg} is shown as the black solid line.
-Notably, the mean halo mass falls well below the relation, at $7.7 \times 10^{5}$ M$_{\odot}$ until $\approx$ 380 Myr, at which point, the mean halo mass rises to $3.7 \times 10^{6}$ M$_{\odot}$.
+Notably, the mean halo mass falls well below the relation, at $7.7 \times 10^{5}$ M$_{\odot}$ until $z = 15$ (270 Myr), at which point, the mean halo mass rises to $3.7 \times 10^{6}$ M$_{\odot}$.
 The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation.
-\hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times.
+\hh{} shielding allows for halos to cool at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times.
 In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times.
-Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts.
+Interestingly, a full radiation hydrodyanmics simulation, such as ours, does not produce identical results as M01 predicts.
 Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
@@
 The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times.
-This galaxy has a halo mass of $3.6 \times 10^{8} M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $5.4 \times 10^{-2}$ at $\approx$ 500 Myr.
+This galaxy has a halo mass of $3.6 \times 10^{8} \rm M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} \rm M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4} \rm M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $5.4 \times 10^{-2}$ at $\approx$ 500 Myr.
 This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars.
@@
 \end{figure}
+
+%====================================================================
+\subsection{Lyman-Werner background for Pop III host halos}
+%====================================================================
 
@@
 
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/jlw_mass_machacek_total.pdf}
+    \caption{The average LW background for host halos of new Pop III stars is plotted versus the host halo mass, colored by redshift.
+The Machacek et al.
+relation is plotted given the background LW in Eq.
+\ref{LWbg}.
+Almost all halos fall below the relation, across a range of redshifts.
+A few halos (or possibly a single halo) allow Pop III stars to form at a low halo mass in a very high LW background.
+There are a few halos that have Pop III stars forming at later times and at high halo masses.}
+    \label{fig:jlw_mass_machacek}
+\end{figure}
+
 %====================================================================
@@
 Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars.
-It should be noted that these halos aren't necessarily forming all of the Pop III stars at once.
-For example, a halo can form stars again if it din't host a supernova.
+It should be noted that these halos are not necessarily forming all of the Pop III stars at once.
+For example, a halo can form stars again if it did not host a supernova.
 The number of Pop III stars that form within a halo is indicative of the star formation history of that halo.
@@
 The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$.
+Note that the mass of the Pop III stars depends on the chosen IMF.
 
@@
 These halos have acquired these Pop III stars from outside halos, accounting for the large spread in Pop III creation time as well as the increased number of Pop III stars, as seen in the right panel of Figure \ref{fig:num_p3}.
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{images/jlw_mass_machacek_total.pdf}
-    \caption{The average LW background for host halos of new Pop III stars is plotted versus the host halo mass, colored by redshift.
-The Machacek et al.
-relation is plotted given the background LW in Eq.
-\ref{LWbg}.
-Almost all halos fall below the relation, across a range of redshifts.
-A few halos (or possibly a single halo) allow Pop III stars to form at a low halo mass in a very high LW background.
-There are a few halos that have Pop III stars forming at later times and at high halo masses.}
-    \label{fig:jlw_mass_machacek}
-\end{figure}
 
@@
 Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity.
-Pop III stars often form in halos up to an order of magnitude greater than the mininum.
+However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the mininum.
 We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation.
@@
 At $z = 20$, this minimum halo mass is $4 \times 10^{6} M_{\odot}$.
-\citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and found that metal-free halos can exist until z $\approx$ 6 using cosmological simulations and analytical calculations for metal enrichment.
-They also provide some insight into whether or not Pop III supernova rates are high enough within these metal-free halos to allow for the Large Synoptic Survey Telescope to see these regions of the universe.
+\citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and found that metal-free halos can exist until z $\approx$ 6 using cosmological simulations and an analytical model for metal enrichment.
+They also provide some insight into whether or not Pop III supernova rates are high enough within these metal-free halos to allow for the LSST to see these regions of the universe.
 They used the minimum halo mass capable of cooling via \hh{} from \citet{Trenti09_SFR} as one part of their halo mass model (see the blue solid line in Figure \ref{fig:compare_JLW_mass}, given our LW background).
@@
 They found that when Pop III stars contribute to the LW background, the minimum halo mass for Pop III star formation is $4 \times 10^{6} M_{\odot}$ as $z = 20$, similar to results from \citet{Tegmark97}.
-The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations (see \citet{Wise07_UVB, OShea08}).
+The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations \citet[see][]{Wise07_UVB, OShea08}.
 It should be noted that because our box is fairly small, we cannot capture the cosmic variance of rare halos and galaxies.
@@
 They found that in the presence of a LW background of J$_{21}$ = 0.01, the minimum halo mass is $7 \times 10^{5} M_{\odot}$.
-When \hh{} self-shielding is taken into account along with a LW background, they see their minimum halo mass decrease to $4.5 \times 10^{5} M_{\odot}$.
+When \hh{} self-shielding is taken into account along with a LW background, their minimum halo mass decreases to $4.5 \times 10^{5} M_{\odot}$.
 This value lies close to the case where there is no LW background applied, where the minimum halo mass is $3.5 \times 10^{5} M_{\odot}$.
 They find that \hh{} self-shielding does appear to be an efficient mechanism for primordial gas cooling.
-In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses across redshifts, ranging from 10$^{5.4}$ M$_{\odot}$ to 10$^{7.1}$ M$_{\odot}$.
+In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses across redshifts, ranging from $2.8 \times 10^{5}$ M$_{\odot}$ to $1.4 \times 10^{7}$ M$_{\odot}$.
 While our halos never experience a LW intensity as low as 0.01, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}).
@@
 They found that \hh{} cooling is dominant even when there is a large LW background present.
-They included dynamical heating but did not include self-shielding, and subsequently found halo masses at their collapse that lie well above the M01 relation (see red open triangles in Figure \ref{fig:compare_JLW_mass}).
+They did not include self-shielding and subsequently found halo masses at their collapse that lie well above the M01 relation (see red open triangles in Figure \ref{fig:compare_JLW_mass}).
 Their J$_{LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
@@
 They found that due to an increased LW background, there is a delay in star formation, and thus there is an increase in the halo masses at collapse.
-They also ignored \hh{} self-shielding in their calculations and included dynamical heating, which can again account for the increased halo masses they found compared to this work, as can be seen in Figure \ref{fig:compare_JLW_mass} (open green squares).
+They also ignored \hh{} self-shielding in their calculations which can again account for the increased halo masses they found compared to this work, as can be seen in Figure \ref{fig:compare_JLW_mass} (open green squares).
 Their halo masses are similar to the results of \citet{Wise07_UVB}.
@@
 
-There are a few minor shortenings to this work that should be noted.
-\citet{Schauer17} investigated the escape fraction of LW photons in the near-and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo.
-In the near-field with an outbreaking ionisation front, they find that the LW escape fraction is greater than 95\%.
-But when the ionisation front is slowly moving, they found that the LW escape fraction can range from 3\% to 88\%.
+There are a few minor shortcomings to this work that should be noted.
+\citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo.
+In the near-field with an ionisation front breaking out of a halo, they find that the LW escape fraction is greater than 95\%.
+But when the ionisation front is contained within the halo, they found that the LW escape fraction can range from 3\% to 88\%.
 In general, they find that the LW escape fractions in the far-field are higher than 75\%.
-In our work, we allow all LW photons to escape the halo.
 Since we are not accounting for the reduced escape fraction within our halos, we are overestimatng the LW radiation coming from point sources in our simulation.
 We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results as we find little dependence on LW intensity.
+
 We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}.
@@
 \begin{itemize}
-	\item We find that Pop III stars are forming in halos with a mean mass of $7.7 \times 10^{5}$ M$_{\odot}$, which falls well below the M01 relation, until $\approx$ 380 Myr, at which point the mean halo mass rises above the M01 relation to a mean value of $3.7 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive halo in the simulation box.
-	\item Including \hh{} self-shielding results in lower mass halos forming Pop III stars as compared with the literature.
+	\item We find that Pop III stars are forming in halos with a mean mass of $7.7 \times 10^{5}$ M$_{\odot}$, which falls well below the M01 relation, until $\approx$ 380 Myr, at which point the mean halo mass rises above the M01 relation to a mean value of $3.7 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
+	\item Including \hh{} self-shielding results in a factor of up to 1.1 lower mass halos compared to M01, forming Pop III stars.
 	\item There does not appear to be a strict correlation between LW intensity within a halo and the halo mass.
@@
 With the inclusion of \hh{} self-shielding, we find Pop III stars forming in smaller mass halos than previously predicted.
-These smaller mass halos provide more sites for Pop III star formation, and therefore, more metal-enrichment within halos.
-We also find that Pop III stars don't have to form in isolation, in fact, they are more likely to form in a halo that has already formed multiple other Pop III stars.
-Since these stars are generally very massive, and are likely to produce stellar mass black holes, they may be gravitational wave candidates detected through LIGO.
+These smaller mass halos provide earlier and additional sites for Pop III star formation, and therefore, more metal-enrichment within halos.
+We also find that Pop III stars do not necessarily have to form in isolation, in fact, they are more likely to form in a halo that has already formed multiple other Pop III stars.
+Since these stars are generally massive and are likely to produce stellar mass black holes, their remnants may be gravitational wave candidates detected through LIGO \citep{Hartwig16}.
+The exact detection signature of these gravitational waves is a topic which needs to be studied further.
 While we do not see any relationship between the LW intensity and Pop III host halo mass,  in order to determine exactly how the LW intensity influences the host halo mass, a more systematic approach needs to be taken.
 
-The assumptions often made about the formation of Pop III stars appear to break down when important processes are taken into account and restrictions about their formation are lifted.
-Further work needs to be done to determine why some halos form Pop III stars and others don't, to provide insight about the formation process of these stars and thus how they will affect their surrounding galactic environment.
-The effect of the LW intensity on host halo mass needs to be systematically investigated to determine whether or not this background radiation really has a profound effect on Pop III formation or not.
-The possibility of halos hosting multiple Pop III stars provides another avenue for observation with LIGO detecting gravitational waves coming from solar mass black holes produced from Pop III stars.
-The exact detection signature of these gravitational waves is a topic which also needs to be studied further.
+The assumptions often made about the formation of Pop III stars, like how they will only form in isolation and how \hh{} self-shielding will not affect formation, appear to break down when self-shielding is taken into account and restrictions about their formation are lifted.
+Further work needs to be done to determine why some halos form Pop III stars and others do not, to provide insight about the formation process of these stars and thus how they will affect their surrounding galactic environment.
+The effect of the LW intensity on host halo mass should be systematically investigated to determine whether or not this background radiation really has a profound effect on Pop III formation or not.
+These primordial objects need to be studied further to assist multi-messenger astronomers in finding these ancient systems.
 

### 2019-05-28 paper.tex
Adding final changes to edits.

@@
 Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars.
-These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}.
+These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18, Ezzeddine19}.
 Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.
@@
 At low masses, the number of Pop III stars per halo sits around 2 Pop III stars, and quickly rises once the halo mass reaches $10^{7} M_{\odot}$.
+\citet{Xu13} found that at $z = 15$, halos with masses at about $10^{7} M_{\odot}$ will contain between 10 and 100 living Pop III stars, with even more remnants.
+While we do not see quite as many Pop III stars, we agree that high mass halos can contain a large amount of Pop III stars.
 We can also look at the spread in creation times of these Pop III stars per halo, shown in Figure \ref{fig:p3spread_mass}.
@@
 Neither \citet{Trenti09} nor \citet{Tegmark97} included the effects of \hh{} self-shielding, which can explain the discrepancy between our data and their mass threshold relationship (Figure \ref{fig:compare_JLW_mass}).
+For a LW background of $J_{LW} / J_{21} = 0.2$, we see halos hosting Pop III stars at $\approx 4 \times 10^{5}$ M$_{\odot}$, while the relation from \citet{Trenti09_SFR} would expect to see minimum halo masses capable of cooling, and thus capable of hosting Pop III stars, at $10^7$ M$_{\odot}$, almost two orders of magnitude larger.
+Since we include \hh{} self-shielding, Pop III stars are allowed to form in smaller mass halos for a given LW background.
 \citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6.

### 2019-05-30 paper.tex
Spelling error
Changing title, adding detail about only analyzing minihalos

@@
 % Keep the title short and informative.
-\title[Where Do Pop III Stars Form?]{Where Do Population III Stars Form? The Effects of Radiative Feedback and Self-Shielding on the Host Halo Mass Distribution}
+\title[Cradles of the first stars]{Cradles of the first stars: self-shielding, halo masses, and multiplicity}
 
@@
 \ref{LWbg}).
+In this work, we only analyze halos below the atomic cooling limit.
 
@@
 In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times.
-Interestingly, a full radiation hydrodyanmics simulation, such as ours, does not produce identical results as M01 predicts.
+Interestingly, a full radiation hydrodynamics simulation, such as ours, does not produce identical results as M01 predicts.
 Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.

### 2019-05-30 paper.tex
Spelling error

@@
 They found a minimum halo mass for hosting Pop III star formation, but with the caveat that they did not include \hh{} self-shielding.
-They found that when Pop III stars contribute to the LW background, the minimum halo mass for Pop III star formation is $4 \times 10^{6} M_{\odot}$ as $z = 20$, similar to results from \citet{Tegmark97}.
+They found that when Pop III stars contribute to the LW background, the minimum halo mass for Pop III star formation is $4 \times 10^{6} M_{\odot}$ at $z = 20$, similar to results from \citet{Tegmark97}.
 The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations \citet[see][]{Wise07_UVB, OShea08}.

### 2019-05-30 paper.tex
Latex adjustment

@@
 They found that when Pop III stars contribute to the LW background, the minimum halo mass for Pop III star formation is $4 \times 10^{6} M_{\odot}$ at $z = 20$, similar to results from \citet{Tegmark97}.
-The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations \citet[see][]{Wise07_UVB, OShea08}.
+The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations \citep[see][]{Wise07_UVB, OShea08}.
 It should be noted that because our box is fairly small, we cannot capture the cosmic variance of rare halos and galaxies.

### 2019-05-30 paper.tex
Fixing Figure 10 caption
Rewording P3 SFRD description and minor changes

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[Danielle Skinner et al.]{
+\author[D. Skinner and J.~H. Wise]{
 Danielle Skinner,$^{1}$\thanks{E-mail: drenniks@gatech.edu}
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2018}
+\pubyear{2019}
 
@@
 We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
-resolution and a dark matter paticle mass of 2000.54 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
-initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and uses the cosmological parameters from the Planck collaboration best fit 
+resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
+initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit 
 \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 
-0.6825, $\Omega_{\rm DM}$ = 0.2685, and h = 0.6711, with the variables 
+0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables 
 having their usual definitions.
-The simulation is run until $z$ = 9.32, when it becomes too computationally expensive to continue.
+The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue.
 At this point, about 20\% of the volume is over 10\% ionized.
@@
 In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39.
-The corresponding star formation rate density can be seen in Figure \ref{fig:pop3_SFR_bar}.
-Pop III star formation peaks at $1.9 \times 10^{-4}$ at $z = 21.3$ and slowly decreases.
-The star formation rate density does not fall to zero at the end of the simulation, since Pop III stars were still being produced when the simulation was cut off.
-The SFRD plotted here is particular for our box.
-Due to the small size of our box, we are unable to capture all of the cosmic variance.
-Therefore the SFRD is likely to change depending on the size and initial conditions of the box.
+The corresponding star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4}$ at $z = 21.3$ and slowly decreases.
+The SFRD sharply declines near the end of the simulation but does not drop to zero.
+Small volumes are subject to cosmic variance, in particular the formation time of the first galaxies, which generates the bulk of the LW radiation background.
+This SFRD is therefore not representative of a cosmological average.
+In particular, it decreases at $z \le 11$ when the most massive galaxy undergoes an extended period of star formation, boosting the local LW radiation field as shown in Figure \ref{fig:JLW_xe_mass}.
+The rates are consistent with other studies \citep[e.g.][]{Xu13, Magg16}, but it is likely to change depending on the particular modes captured by the initial conditions.
 
@@
 	\includegraphics[width=\columnwidth]{images/compare_JLW_mass.pdf}
-    \caption{The average LW intensity normalized by J21 versus the halo mass for this work and a variety of other works.
+    \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works.
 The black solid line is from M01, blue solid line from \citet{Trenti09_SFR}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.

### 2019-05-30 paper.tex
Marking where I will reword things

@@
  To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}.
-The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}$/$\Omega_{\rm DM}$.
+The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$.
 The total mass is subsequently used in our analysis.
@@
 This may be showing that the LW intensity is not as great an indicator of which halo will be allowed to form a Pop III star as previously thought.
+\jhw{will add more to the ending.}
 
@@
 Like with any work done assuming a Pop III IMF, uncertainties about metal enrichment, multiplicity, total stellar mass, ionization rates, supernova rates, and the amount of black holes produced are introduced into our results.
+\jhw{will reword.}
 

### 2019-05-31 paper.tex
Adding more detail to LWB evo

@@
 where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.
-This form gives a maximum of $J_{\rm LW}/J_{21} = 0.85$ at a redshift of 13.5 and quickly and continually declines for higher redshifts.
+This form only varies by a factor of five in $z = 9-25$ and has a maximum of $J_{\rm LW}/J_{21} = 0.97$ at a redshift of 13.5 and slowly declines to 0.60 $J_{21}$ at $z = 9$ when we halt the simulation.
 We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the ionizing radiation field.

### 2019-05-31 paper.tex
Clarifying ending in LW result subsection

@@
 %====================================================================
-\subsection{Lyman-Werner background for Pop III host halos}
+\subsection{Lyman-Werner intensities in Pop III host haloes}
 %====================================================================
@@
 The LW background intensity versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}.
+Because the LW background only varies by a factor of five as Pop III stars form, most points lie within a small intensity range, just below $1~J_{21}$.
 Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq.
@@
 The grouped points in the higher end of J$_{\rm LW}$ are representative of such halos.
+
 We find that a total of 84\% of the halos forming Pop III stars lie below the M01 mass threshold over the entire simulation redshift range.
-We also do not see a clear relationship between the LW intensity and the host halo mass.
-This may be showing that the LW intensity is not as great an indicator of which halo will be allowed to form a Pop III star as previously thought.
-\jhw{will add more to the ending.}
+Given that the background intensity only varies by a factor of five, previous work suggested that most halos should have formed stars around or above the M01 relationship.
+However, we see a large spread in host halo masses, over an order of magnitude, and no clear relationship between the LW intensity and the host halo mass.
+This behavior suggests that the LW intensity is not the primary indicator of the mass at which a metal-free halo collapses.
+\hh{} self-shielding is the main cause behind this conclusion because the internal dynamics and chemo-thermal evolution are now isolated from its large-scale environment and mostly depends on the local conditions within the halo.
 

### 2019-05-31 paper.tex
Rewording end of discussion

@@
 Because of this, streaming velocities would likely not affect our results.
-Finally, there is the obvious caveat of the unknown Pop III IMF.
-Like with any work done assuming a Pop III IMF, uncertainties about metal enrichment, multiplicity, total stellar mass, ionization rates, supernova rates, and the amount of black holes produced are introduced into our results.
-\jhw{will reword.}
+
+Finally with most studies of metal-free stars, there is the caveat of its uncertain IMF that affects the individual stellar luminosities and surface temperatures of the Pop III stars.
+Changes in the IMF could alter the multiplicity and total stellar mass of the system because the radiative feedback from the earlier stars could affect the thermodynamics of other molecular clouds within the same halo.
+Ultimately the IMF determines the fraction of stars going supernova and the metal production in pre-galactic objects that is the root cause of suppressing and ending Pop III star formation in the early universe.
 

### 2019-05-31 paper.tex
Rewording some of the conclusions

@@
 	\item We find that Pop III stars are forming in halos with a mean mass of $7.7 \times 10^{5}$ M$_{\odot}$, which falls well below the M01 relation, until $\approx$ 380 Myr, at which point the mean halo mass rises above the M01 relation to a mean value of $3.7 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
-	\item Including \hh{} self-shielding results in a factor of up to 1.1 lower mass halos compared to M01, forming Pop III stars.
-	\item There does not appear to be a strict correlation between LW intensity within a halo and the halo mass.
-LW intensity within a halo may not be as indicative of which halos may form Pop III stars as previously thought.
+	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.
+Self-shielding creates a disconnect between the LW intensity and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
 	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
-	\item By the end of the simulation, halos with masses > $10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos.
-This results in these high mass halos containing multiple Pop III stars, both young and old.
+	\item By the end of the simulation, halos with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos, resulting galaxies with young and old metal-free stars.
 \end{itemize}
@@
 The assumptions often made about the formation of Pop III stars, like how they will only form in isolation and how \hh{} self-shielding will not affect formation, appear to break down when self-shielding is taken into account and restrictions about their formation are lifted.
-Further work needs to be done to determine why some halos form Pop III stars and others do not, to provide insight about the formation process of these stars and thus how they will affect their surrounding galactic environment.
+Further work needs to be done to determine why some halos form Pop III stars and others do not, to provide insight about the formation process of these stars and thus how they will affect their surrounding pre-galactic environment.
 The effect of the LW intensity on host halo mass should be systematically investigated to determine whether or not this background radiation really has a profound effect on Pop III formation or not.
-These primordial objects need to be studied further to assist multi-messenger astronomers in finding these ancient systems.
+Further constraints on these primordial objects will assist multi-messenger astronomers in identifying these ancient systems.
 

### 2019-05-31 paper.tex
Minor changes.

@@
 % Basic setup. Most papers should leave these options alone.
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib]{mnras}
 
@@
 \author[D. Skinner and J.~H. Wise]{
-Danielle Skinner,$^{1}$\thanks{E-mail: drenniks@gatech.edu}
-John H. Wise,$^{1}$
+Danielle Skinner$^{1}$\thanks{E-mail: drenniks@gatech.edu}
+and John H. Wise$^{1}$
 \\
 % List of institutions
-$^{1}$Center for Relativistic Astrophysics, Georgia Institute of Technology, 
-Atlanta, GA 30332, USA\\
+$^{1}$Center for Relativistic Astrophysics, School of Physics, Georgia Institute of Technology, Atlanta, GA 30332, USA\\
 }

### 2019-06-06 paper.tex
Changes after the final proofreading

@@
 where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.
-This form only varies by a factor of five in $z = 9-25$ and has a maximum of $J_{\rm LW}/J_{21} = 0.97$ at a redshift of 13.5 and slowly declines to 0.60 $J_{21}$ at $z = 9$ when we halt the simulation.
+This form only varies by a factor of five in $z = 9-25$ and has a maximum of $J_{\rm LW}/J_{21} = 0.97$ at a redshift of 13.5 and slowly declines to 0.60 $J_{21}$ at $z = 9.3$ when we halt the simulation.
 We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the ionizing radiation field.
@@
 \end{equation}
-where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$ is the critical density.
+where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 H_{0}^{2} / 8 \pi G (1+z)^3$ is the critical density.
 The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$:
@@
 
-To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3.
+To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$.
 The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles.
@@
 In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place.
-By the end of the simulation, 20\% of the box is ionized over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.
+By the end of the simulation, 20\% of the box has an ionized fraction over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.
 
@@
 The thick, black line is the analytic Sheth-Tormen mass function.
-The distribution of halo masses matches well with Sheth-Tormen until about 10$^{5}$ M$_{\odot}$.}
+The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where halos are captured by 50 particles.}
     \label{fig:hmf}
@@
 \ref{LWbg} is shown as the black solid line.
-Notably, the mean halo mass falls well below the relation, at $7.7 \times 10^{5}$ M$_{\odot}$ until $z = 15$ (270 Myr), at which point, the mean halo mass rises to $3.7 \times 10^{6}$ M$_{\odot}$.
+Notably, the mean halo mass falls well below the relation, at $<10^{6}$ M$_{\odot}$ until $z = 15$ (270 Myr), at which point, the mean halo mass steadily rises above $3 \times 10^{6}$ M$_{\odot}$.
 The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation.
@@
 The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times.
-This galaxy has a halo mass of $3.6 \times 10^{8} \rm M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} \rm M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4} \rm M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $5.4 \times 10^{-2}$ at $\approx$ 500 Myr.
+This galaxy has a halo mass of $3.6 \times 10^{8} \rm M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} \rm M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4}\, \rm M_{\odot} yr^{-1}$ at $z=15$ (250 Myr) and a peak metal enriched SFR of $5.4 \times 10^{-2}\, \rm M_{\odot} yr^{-1}$ at $z=9.5$ (500~Myr).
 This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars.
@@
 Almost all halos fall below the relation, across a range of redshifts.
-A few halos (or possibly a single halo) allow Pop III stars to form at a low halo mass in a very high LW background.
-There are a few halos that have Pop III stars forming at later times and at high halo masses.}
+There are extreme cases where Pop III stars form in small halos located in a very intense LW radiation field or large halos in relatively weak radiation fields.}
     \label{fig:jlw_mass_machacek}
@@
 We now inspect the number of Pop III stars and the total mass of Pop III stars per halo.
-Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses < $1 M_{\odot}$.
+Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses $<1 M_{\odot}$.
 The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation.
@@
 Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo.
-Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars.
+Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars, similar to the radiation hydrodynamic simulations of \citet{Susa13, Susa14}.
 It should be noted that these halos are not necessarily forming all of the Pop III stars at once.
@@
 \subsection{Variations in the halo masses at collapse}
+\label{sec:variations}
 %====================================================================
@@
 They found a minimum halo mass needed to collapse which depends on the virial temperature of the halo and the virial redshift.
-At $z = 20$, this minimum halo mass is $4 \times 10^{6} M_{\odot}$.
+At $z = 15$, this minimum halo mass is $10^{6} M_{\odot}$.
 \citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and found that metal-free halos can exist until z $\approx$ 6 using cosmological simulations and an analytical model for metal enrichment.
@@
 Neither \citet{Trenti09} nor \citet{Tegmark97} included the effects of \hh{} self-shielding, which can explain the discrepancy between our data and their mass threshold relationship (Figure \ref{fig:compare_JLW_mass}).
-For a LW background of $J_{LW} / J_{21} = 0.2$, we see halos hosting Pop III stars at $\approx 4 \times 10^{5}$ M$_{\odot}$, while the relation from \citet{Trenti09_SFR} would expect to see minimum halo masses capable of cooling, and thus capable of hosting Pop III stars, at $10^7$ M$_{\odot}$, almost two orders of magnitude larger.
+For a LW background of $J_{\rm LW} / J_{21} = 0.2$, we see halos hosting Pop III stars down to $4 \times 10^{5}$ M$_{\odot}$, while the relation from \citet{Trenti09_SFR} would expect to see minimum halo masses capable of cooling, and thus capable of hosting Pop III stars, at $10^7$ M$_{\odot}$, almost two orders of magnitude larger.
 Since we include \hh{} self-shielding, Pop III stars are allowed to form in smaller mass halos for a given LW background.
@@
 \citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass halos.
-If we had included streaming velocities, the gas would have already fallen into the dark matter potential well when the halo exceeds this characteristic mass.
-Because of this, streaming velocities would likely not affect our results.
+Our results indicate that halos collapse at larger masses that are not as affected by typical streaming velocities ($<1\sigma_{\rm vbc}$).
+In the evolution of such a halo, it would have started to accumulate gas above these critical masses while also being irradiated by a LW background.
+Afterwards, the collapse will be controled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results.
 
@@
 \begin{itemize}
-	\item We find that Pop III stars are forming in halos with a mean mass of $7.7 \times 10^{5}$ M$_{\odot}$, which falls well below the M01 relation, until $\approx$ 380 Myr, at which point the mean halo mass rises above the M01 relation to a mean value of $3.7 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
+	\item We find that Pop III stars are forming in halos with a mean mass below $10^{6}$ M$_{\odot}$, which falls well below the M01 relation, until $z=15$, at which point the mean halo mass rises above the M01 relation to a mean value of $3 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
 	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.
@@
 
-The assumptions often made about the formation of Pop III stars, like how they will only form in isolation and how \hh{} self-shielding will not affect formation, appear to break down when self-shielding is taken into account and restrictions about their formation are lifted.
+The assumptions often made about the formation of Pop III stars, like how they will only form in isolation and how the LW background mainly determines the collapse mass, appear to break down when self-shielding is taken into account and restrictions about their formation are lifted.
 Further work needs to be done to determine why some halos form Pop III stars and others do not, to provide insight about the formation process of these stars and thus how they will affect their surrounding pre-galactic environment.
-The effect of the LW intensity on host halo mass should be systematically investigated to determine whether or not this background radiation really has a profound effect on Pop III formation or not.
+The effect of the LW intensity on host halo mass should be systematically investigated with \hh{} self-shielding to determine whether or not this background radiation really has a profound effect on Pop III formation or not.
 Further constraints on these primordial objects will assist multi-messenger astronomers in identifying these ancient systems.

### 2019-06-07 paper.tex
Making final changes.

@@
 \begin{keywords}
-star formation -- methods:numerical -- cosmology
+star formation  -- cosmology: first stars -- stars: Population III -- methods: numerical
 \end{keywords}
@@
 
-Once a halo becomes chemically enriched by the death of its Pop III stars, then by definition, it can no longer form more Pop III stars.
+Once a halo becomes chemically enriched by the death of Pop III stars, then by definition, it can no longer form more Pop III stars.
 This marks the end of metal-free star formation in that pregalactic object.
@@
 Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep{Wise08_Gal, Greif10, Smith15}.
-Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars.
-These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18, Ezzeddine19}.
+Stars will continue to form in halos, but with an increased metal abundance.
+These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and can survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18, Ezzeddine19}.
 Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.
 
-Without metals and dust to facilitate efficient radiative cooling, Pop III stars rely on \hh{} formation to cool the gas.
+Without metals and dust to facilitate efficient radiative cooling, Pop III stars rely on \hh{} formation in the gas-phase for cooling.
 These molecules are however fragile to dissociation from Lyman-Werner (LW) radiation in the energy range 11.2--13.6~eV, through the Solomon process \citep{Field66, Stecher67}.
@@
 \citet{Mebane18} used a semi-analytic model of early star formation and found that the LW background coming from the rapidly increasing supply of Pop III stars becomes responsible for suppressing Pop III star formation.
-\citet{Griffen18} also find that the LW background can significantly suppress the amount of potential sites for Pop III star formation.
+\citet{Griffen18} also found that the LW background can significantly suppress the amount of potential sites for Pop III star formation.
 
@@
 \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
-They fit a simple analytic expression for the mass threshold of halos given a particular LW flux:
+They fit a simple analytic expression for the mass threshold of halos given a particular LW intensity J$_{\rm LW}$:
 \begin{equation} \label{mthresh}
@@
 We will compare our results with this relation in future sections.
-\citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01 J$_{\rm 21}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation.
+\citet{Yoshida03} also found that cooling is inefficient in halos with a LW background > 0.01 J$_{\rm 21}$, where J$_{\rm 21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation.
 In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 J$_{21}$.
 They find that \hh{} cooling is always a dominant process, even in large LW background fluxes.
-\citet{OShea08} also find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
+\citet{OShea08} also found that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.
 
@@
 \end{equation}
-where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.
+where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$.
 This form only varies by a factor of five in $z = 9-25$ and has a maximum of $J_{\rm LW}/J_{21} = 0.97$ at a redshift of 13.5 and slowly declines to 0.60 $J_{21}$ at $z = 9.3$ when we halt the simulation.
@@
 This characteristic mass is different from the W12 choice of 100 M$_{\odot}$.
-This results in an exponential cutoff before M$_{\rm char}$ and a power-law IMF after.
+This results in an exponential cutoff below M$_{\rm char}$ and a power-law IMF above.
 Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
@@
 Outside of these mass ranges, the Pop III star dies as a black hole.
-In this simulation, no black hole physics are implemented, so the Pop III star simply turns into a collisionless particle.
+In this simulation, no black hole physics are implemented, so the Pop III star simply turns into an inert collisionless particle.
 When 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg.
@@
 where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 H_{0}^{2} / 8 \pi G (1+z)^3$ is the critical density.
+Here, H$_{0}$ is the Hubble constant, G is the gravitational constant, and z is the redshift.
 The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$:
@@
 Smaller mass halos can then form Pop III stars since \hh{} will survive in the halo for a longer amount of time.
-We also see that for column densities at just under $10^{17} \rm cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} at relatively low column densities.
+We also see that for column densities at just under $10^{17} \rm cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} in relatively low halo masses.
 
@@
 Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$.
-For these parameters, and assuming the Doppler broadening parameter equals the circular velocity, the shielding factor is almost zero, implying maximum shielding.
+For these parameters, and assuming the Doppler broadening parameter equals the circular velocity, the shielding factor is below 1 percent.
 The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s.
@@
 After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box.
-These stars either become black holes or supernova at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
+These stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
 Metal-enriched star formation begins to take place as soon as enough metals are present within a halo.
 In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place.
-By the end of the simulation, 20\% of the box has an ionized fraction over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.
+By the end of the simulation, 20\% of the box has an ionized fraction greater than 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.
 
@@
 In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39.
-The corresponding star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4}$ at $z = 21.3$ and slowly decreases.
+The corresponding star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4} \ \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 21.3$ and slowly decreases.
 The SFRD sharply declines near the end of the simulation but does not drop to zero.
@@
 Note that metal-enriched star formation continually increases throughout time, although that is not plotted here.
-Due to the small box size of our simulation, this SFRD is particular for our box, and would change for larger, or smaller box sizes.}
+Due to the small box size of our simulation, this SFRD is particular for our box.}
     \label{fig:pop3_SFR_bar}
@@
 A small percentage of Pop III stars do not form in a halo identified by \rockstar{}.
-Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data.
+Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$.
 We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo.
@@
 In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}.
-The median for each bin is represented by an x, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively.
+The median for each bin is represented by a cross, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively.
 The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq.
@@
 Interestingly, a full radiation hydrodynamics simulation, such as ours, does not produce identical results as M01 predicts.
-Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
-As can be seen by the red solid line in \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation.
+Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[e.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
+As can be seen by the red solid line in Figure \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation.
 The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times.
-This galaxy has a halo mass of $3.6 \times 10^{8} \rm M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} \rm M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4}\, \rm M_{\odot} yr^{-1}$ at $z=15$ (250 Myr) and a peak metal enriched SFR of $5.4 \times 10^{-2}\, \rm M_{\odot} yr^{-1}$ at $z=9.5$ (500~Myr).
+This galaxy has a halo mass of $3.6 \times 10^{8} \rm M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} \rm M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4}\, \rm M_{\odot}\ yr^{-1}$ at $z=15$ (250 Myr) and a peak metal enriched SFR of $5.4 \times 10^{-2}\, \rm M_{\odot} \ yr^{-1}$ at $z=9.5$ (500~Myr).
 This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars.
@@
 Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation.
-The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs synchronically, star formation will not be suppressed, so long as they are a suitable distance away from each other.
+The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs at about the same time, star formation will not be suppressed, so long as they are a suitable distance away from each other.
 As there are only a few data points in this region, this situation is rare.
@@
 At low masses, the number of Pop III stars per halo sits around 2 Pop III stars, and quickly rises once the halo mass reaches $10^{7} M_{\odot}$.
-\citet{Xu13} found that at $z = 15$, halos with masses at about $10^{7} M_{\odot}$ will contain between 10 and 100 living Pop III stars, with even more remnants.
-While we do not see quite as many Pop III stars, we agree that high mass halos can contain a large amount of Pop III stars.
+\citet{Xu13} found that at $z = 15$, halos with masses at about $10^{7} M_{\odot}$ will contain between 10 and 100 Pop III stellar remnants, similar to our results.
 We can also look at the spread in creation times of these Pop III stars per halo, shown in Figure \ref{fig:p3spread_mass}.
@@
 There are two groups within this plot.
-The first group contains halos that form their Pop III stars in a spread of < 10 Myr, with a median spread of about $10^{-1}$ Myr.
+The first group contains halos that form their Pop III stars in a spread of < 10 Myr, with a median spread of about 0.1 Myr.
 The second group contains halos that form their Pop III stars in a spread of > 10 Myr, with a median spread of about 100 Myr.
@@
 In a series of simulations, they found a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12).
-They found that in the presence of a LW background of J$_{21}$ = 0.01, the minimum halo mass is $7 \times 10^{5} M_{\odot}$.
+They found that in the presence of a LW background of 0.01 J$_{21}$, the minimum halo mass is $7 \times 10^{5} M_{\odot}$.
 When \hh{} self-shielding is taken into account along with a LW background, their minimum halo mass decreases to $4.5 \times 10^{5} M_{\odot}$.
 This value lies close to the case where there is no LW background applied, where the minimum halo mass is $3.5 \times 10^{5} M_{\odot}$.
-They find that \hh{} self-shielding does appear to be an efficient mechanism for primordial gas cooling.
-In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses across redshifts, ranging from $2.8 \times 10^{5}$ M$_{\odot}$ to $1.4 \times 10^{7}$ M$_{\odot}$.
-While our halos never experience a LW intensity as low as 0.01, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}).
+They found that \hh{} self-shielding does appear to be an efficient mechanism enabling primordial gas cooling.
+In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses, ranging from $2.8 \times 10^{5}$ M$_{\odot}$ to $1.4 \times 10^{7}$ M$_{\odot}$.
+While our halos never experience a LW intensity as low as 0.01 J$_{21}$, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}).
 \citet{Wise07_UVB} used cosmological simulations to investigate \hh{} cooling in a LW background.
@@
 They did not include self-shielding and subsequently found halo masses at their collapse that lie well above the M01 relation (see red open triangles in Figure \ref{fig:compare_JLW_mass}).
-Their J$_{LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
+Their J$_{\rm LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
 \citet{OShea08} used cosmological simulations to investivate Pop III star formation in various LW backgrounds.
@@
 The black solid line is from M01, blue solid line from \citet{Trenti09_SFR}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.
-J$_{LW}$ = 0 for the various sources is plotted here at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
+J$_{LW}$ = 0 for the various sources is plotted here at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
 The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
@@
 Finally with most studies of metal-free stars, there is the caveat of its uncertain IMF that affects the individual stellar luminosities and surface temperatures of the Pop III stars.
-Changes in the IMF could alter the multiplicity and total stellar mass of the system because the radiative feedback from the earlier stars could affect the thermodynamics of other molecular clouds within the same halo.
+Changes in the IMF could alter the multiplicity and total stellar mass of the system because the radiative feedback from the earlier stars can affect the thermodynamics of other molecular clouds within the same halo.
 Ultimately the IMF determines the fraction of stars going supernova and the metal production in pre-galactic objects that is the root cause of suppressing and ending Pop III star formation in the early universe.
@@
 	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.
-Self-shielding creates a disconnect between the LW intensity and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
+Self-shielding creates a disconnect between the LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
 	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.

### 2019-06-07 paper.tex
Removing italics.

@@
 \end{equation}
-where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 H_{0}^{2} / 8 \pi G (1+z)^3$ is the critical density.
+where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm H_{0}^{2} / 8 \pi G (1+z)^3$ is the critical density.
 Here, H$_{0}$ is the Hubble constant, G is the gravitational constant, and z is the redshift.

### 2019-06-07 paper.tex
Fixing sentence structure.

@@
 	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
-	\item By the end of the simulation, halos with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos, resulting galaxies with young and old metal-free stars.
+	\item By the end of the simulation, halos with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos, resulting in galaxies with young and old metal-free stars.
 \end{itemize}

### 2019-07-22 sample-response.tex
Adding sample referee responses from Wise+ (2014)

\documentclass[11pt]{article}
%\renewcommand\refname{ }

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}

\input macros.tex

\definecolor{verbgray}{gray}{0.9}
\lstnewenvironment{referee}{%
  \lstset{backgroundcolor=\color{verbgray},
  frame=single,
  framerule=0pt,
  basicstyle=\ttfamily,
  columns=fullflexible}}{}

\begin{document}

\begin{center} 
\bfseries{
\begin{large}
  Response to referee report for manuscript ref. MN-14-0750-MJ
\end{large}
}
\end{center}

\begin{referee}
The authors perform sophisticated galaxy formation simulations in a
fully cosmological context. Using explicit radiative transfer
calculations, the authors can derive, rather than assume, photon
escape fractions of the simulated galaxies and hence consistent
reionization simulations are performed. The authors conclude
low-mass galaxies actually dominate the ionizing photon budget in
the early phase of reionization. The simulations are of high quality
and the conclusions are interesting. The authors have also checked
caveats and done reasonable comparisons with previous works. I
recommend the paper for publication in MN, subject to revisions as
suggested in the below. I request mostly clarifications of a number
of points in the text.
\end{referee}

We thank the referee for his/her review of our work, and we have
addressed the points individually below.  In the manuscript, we have
boldfaced the added text and crossed out the deleted text.  In
addition to these changes below, we have cited Kimm \& Cen (2014) and
Salvadori et al. (2014) in Section 5.3.2 and 5.3.3, respectively,
during the revision process.

\begin{referee}
1 Introduction, 1st para.
"Lyman alpha forest lines imply that"
Please describe a little more precisely.
The authors probably mean the complete Gunn-Peterson
trough in the spectra of QSOs beyond z=6, and they do
not really mean  the IGM temperature inferred from Lyman-a
lines, is this right ?
\end{referee}

We were referring to the Gunn-Peterson trough, not the IGM temperature
in Lyman-a lines.  We have changed that sentence to read,

``First, the transmission fraction of $z \sim 6$ quasar light blueward
of \lya~through the intergalactic medium (IGM) indicates that the
universe was mostly ionised by this epoch.''

\begin{referee}
2 Introduction 2nd para
"which both are too rare"
-> "both of which are too rare" ??
\end{referee}

Fixed.

\begin{referee}
3. Intro, the end of 3rd para.
"but starting at which limiting magnitude?"
Sounds like a conversation.
\end{referee}

This is in the first author's writing style, and we would prefer to
keep this question as originally stated because it leads into the next
paragraph, which answers this exact question.

\begin{referee}
4. Intro. in the middle of 4th para.
"... Lyman-Werner (LW) background".
I find the authors use this term a little carelessly
throughout the manuscript.
With "background", I imagine some uniform cosmic
(large-scale) background, but with
"Lyman-Werner radiation", I think of some external
(nearby) radiation source as well.
In some parts, the authors mean "LW radiation
(including from near-by sources) suppress H2 formation" 
by writing "by LW background".
A related point is the treatment of the global LW background
later in section 2.2. Shouldn't the authors include the global
background in addition to the collective LW photons
from local sources in the simulation box ?
\end{referee}

We treat the LW radiation field as the sum of a time-dependent uniform
background and optically-thin fields from point sources in the
simulation.  This is discussed at the end of Section 2.2.  We agree
with the referee that we should have been more specific about the
terminology concerning soft UV radiation.  We have replaced all
relevant references to a soft UV or LW background with either
``radiation field'', ``external radiation'', or ``intensity''.

\begin{referee}
5. Somewhere in Introduction, perhaps around
6th-8th para, please write that the escape fraction
is intrinsically a quantity of an object, rather than
of a population. Namely, galaxies with the same mass
can have very much different fesc because of complex
structures, dust content etc. It is also very likely
time-dependent even within the active time of a galaxy.
I agree with the authors that it is important to discuss
the mean value of fesc as a function of mass, formation
epoch etc. Nevertheless, fesc is often misused or confused
in the literature, as if it were some global quantity.
\end{referee}

We agree with the referee that this is important to stress to the
readers.  We have added the following sentences to the 6th paragraph,

``Before moving forward, it should be stressed that the UV escape
fraction is an intrinsic quantity for a given galaxy not an entire
population.  Galaxies with the same mass can have very different
escape fractions, arising from, e.g., complex gaseous and stellar
morphologies, dust content, and cosmological mass inflow.
Furthermore, variable star formation rates (SFRs) and the associated
radiative feedback in the ISM can result in an escape fraction that is
highly time-dependent.''

\begin{referee}
6. Section 2.1
This is not really a comment in a referee report,
but I just wonder why the authors still use GRAFIC
when more useful ones are available such as MUSIC.
\end{referee}

This is a fair question, and the answer isn't obvious to someone
outside our collaboration.  When we started this project in mid-2010,
MUSIC was not fully tested, thus we used GRAFIC for the initial
conditions.  The simulations in the \textit{Birth of a Galaxy} series
all use the same initial conditions, which were calculated four years
ago.  As a note, all of our simulations started in the past two years
have used MUSIC exclusively.

\begin{referee}
7. Section 2.2, about Population III IMF.
"a Salpeter IMF that exponentially ...."
I believe the Salpeter IMF is rather specific, and so
I'd suggest to write "a power-law IMF that exponentially...".
\end{referee}

Changed.

\begin{referee}
8. Figure 2 is interesting in that the most massive halos
at z=8-9 actually cool by H/He rather than by metal
cooling. Is this because metal mixing is inefficient in
the large halos ? When I see Sutherland-Dopita's cooling
function, metal (Fe, Si etc) cooling is effective also at
T>10000K.
Can one think of some numerical artifact causing
inefficient mixing in the simulated galaxies ?
\end{referee}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figs/halo0-z.pdf}
\end{figure}

Most of the ISM has a temperature between 8,000 and 30,000 K, where
the Sutherland and Dopita cooling curve does not depend on metallicity
greatly, where the increased metal-line cooling occurs at higher
temperatures.  See the Figure for a density-temperature histogram of
the gas inside the most massive halo at $z = 7.3$.  Because cooling is
so efficient at $T > 10^5$ K, there is very little gas mass to
contribute to the total cooling rate of the halo, thus most of the
cooling comes from hydrogen transitions.

Inefficient mixing does not appear to be a significant problem in our
simulation.  See the right panel of the Figure to see the average
metallicity for a given density and temperature inside the most
massive halo at z = 7.3.  Here the metals are well mixed between all
of the three ISM phases.  There is some metal-free gas at low
densities in the outskirts of the halo ($r \sim r_{\rm vir}$), which
could be worth investigating in a later paper.

\begin{referee}
9. Halo mass function in Section 3.3.
This is the most inaccurate part of the paper from my
view point. To obtain the LF, the authors devise a correction
factor n_analytic/n_sim of haloes. If the correction is
actually small overall, I would not do any correction, because
the comparison of LFs shown in Figure 6 is only qualitative
anyway. If the correction factor is significant, I would not
do such rough correction either. In any case, I request the
authors to clarify if the main conclusions are affected
if they simply use the measured LF without the correction.
\end{referee}

Fortunately, there was a bug in the Press-Schetcher (Sheth-Tormen)
halo mass function code that we were using.  We have fixed this bug,
and the analytical halo mass function is consistent with the simulated
halo mass function now.  There is a slight deficiency of $\sim 5 \times
10^7 \Ms$ halos in the simulation.  There is an underproduction of
halos with masses $M < 4 \times 10^5 \Ms$ that is caused by limited
mass resolution effects, which does not affect the luminosity function
because galaxies do not form in such small halos.  We have updated
Figure 5 to reflect this change.

We have removed the correction factor to the luminosity function and
updated Figure 6.  The mean galaxy luminosity function at $M_{\rm UV}
> -12$ has changed by a factor of two at $z > 10$, and we have updated
the abstract and Table 2 with these uncorrected values.

\begin{referee}
10 Figure 8
Please explain the large jump at log M ~ 8.0 of the
solid line at z=7.3, if it has some physical meaning.
Or, in other words, what happened between z=8.0
and z=7.3 in such a short physical time ?
Maybe a diffuse UV background rapidly increases
its intensity ?
\end{referee}

This large jump occurs when a single halo with $M \sim 10^8 \Ms$
undergoes a strong star formation event with an escape fraction around
60 per cent at $z = 7.3$.  We have added the following text to the end
of the next to last paragraph in Section 3.4.2.

``The large jump at $M \sim 10^8 \Ms$ is caused a single halo
undergoing a strong star formation event with a $\textrm{sSFR} \simeq
30$ and $\fesc \simeq 0.6$ that produces 70 per cent of the ionising
photon budget in the simulation with the remaining 20 and 10 per cent
originating from more massive and less massive haloes.''

\begin{referee}
11. Section 3.5
It is unclear to me if the authors include intra-galactic
gas to calculate the clumping factor. Shouldn't one
include only clumping in the diffuse IGM ?
In other words, I couldn't get clear consistency between
clumping, f_esc and the photon production rate for
individual galaxies.
\end{referee}

Thank you for catching this point.  We indeed restrict the clumping
factor calculation to the IGM, where we use the definition of 20 times
the critical density as the IGM, which also excludes filaments.  We
have clarified by this oversight in a few places in Section 3.5 and
the caption of Figure 11.

\begin{referee}
12. Occupation fraction f_host, equation (16)
The functional form looks like nothing but a function.
Please explain if eq (16) has some physical meaning
except the limit to f0.
\end{referee}

This equation fits the simulated occupation fraction shown in Figure
3.  With the exception to the sound-crossing time, the functional form
has no physical basis except to fit the simulated data.  We have added
the following phrase after Equation 16 to clarify the equation's
motivation.

``which provides a functional fit to the simulated values of $f_{\rm
host}$ that are shown in Figure 3.''

\begin{referee}
13. Section 5.2
The observability by JWST is mentioned but remain
unclear. Figure 15 does not seem to help our
understanding. Please clarify which part of Figure 15
is indeed within reach of JWST ? (Or TMT, ELT etc)
\end{referee}

We have added the detection limits of the HUDF12 and Frontier Fields
campaigns and JWST for a $10^5$ second exposure to the figure.  We have
also added the ``robust'' sample of $z \ge 6.5$ galaxies from McLure et
al. (2013) to the figure and made the associated changes to the text
to reflect these additions.

\begin{referee}
This concludes my report.
\end{referee}

We again thank the referee for the insightful review that helped
improve our paper.

\end{document}

### 2019-07-22 referee.tex
Adding initial responses to referee report - with some Latex formatting problems....

\documentclass[11pt]{article}
%\renewcommand\refname{ }

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}

\input macros.tex

\definecolor{verbgray}{gray}{0.9}
\lstnewenvironment{referee}{%
  \lstset{backgroundcolor=\color{verbgray},
  frame=single,
  framerule=0pt,
  basicstyle=\ttfamily,
  columns=fullflexible}}{}

\begin{document}

\begin{center} 
\bfseries{
\begin{large}
  Response to referee report for manuscript ref. MN-19-2054-MJ
\end{large}
}
\end{center}

\begin{referee}
The paper presented here is very well written and offers important new insights. It studies the dependence of the halo mass for first star formation on a Lyman-Werner background in a large simulation, and goes beyond current literature work by the inclusion of self-shielding and studying the multiplicity of Pop III stars. I generally recommend if for publication after some concerns are addressed.
\end{referee}

\begin{referee}
Major comments:
1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo. This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo. This is very plausible. If several Pop III stars are found forming in the same halo at the same time, however, the employed star particle algorithm has a hard-coded length scale of 1pc in which only one star particle can be formed. I am wondering if this is an effect that is resolution dependent - do the same number of stars form if the resolution is increased and the maximum distance is decreased? Which is the motivation for the length scale of 1pc?
\end{referee}

-Resolution testing

\begin{referee}
2) The authors select their haloes by the halo finding algorithm Rockstar. They should add a bit of information on that code (is it fof or subfind-like?). Also, one of their main points is to compare their work to Machacek+01. Machacek+01, however, use a different halo definition (spherical around the halo centre going out to a radius of 200 times the mean density of the Universe). How do these different halo masses compare?
Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper. The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.
In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo.
The baryon fraction varies with redshift. Please give an estimate by how much this influences the halo masses used here.
\end{referee}

-address concern about Rockstar details, and Machacek halo definition
-exclusion of atomic cooling haloes - we excluded these because of a bug in our code... how to explain this without simply saying that?
-fraction of halos that halo Pop III stars forming outside the haloes: I'm not sure I will be able to tell exactly how many are not in halos. I need to look back at the data to see if I will be able to pick out which halos I artificially drew a halo around. 
-shall I look at the baryon fraction as a function of time to see how much it varies?

\begin{referee}
Minor comments:
The authors should state at one point in the paper for which properties they use comoving or physical units.
\end{referee}
-We use physical units throughout the whole paper, apart from when we discuss the boxsize. I will make this more clear.

\begin{referee}
Introduction:
The authors write that Pop III star formation is generally more massive. While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
\end{referee}
-I will look at and add these citations and detail to the introduction.

\begin{referee}
The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14). 
\end{referee}
-I will add this detail

\begin{referee}
The authors cite the well-known study from Machacek+01. However, a more recent result would be from the study by Visbal+14, giving a lower mass limit. Since the authors find a lower mass limit than Machacek+01, it would be interesting to see how this compares to the lower mass limit from the more modern paper.
\end{referee}
-I will check out Visbal+ 14 (I think I have looked at this paper, will double check)

\begin{referee}
Methods:
In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
\end{referee}
-I will look at that simulation again, if John could provide some insight here that would be nice.

\begin{referee}
The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
\end{referee}
-Personal question: why is this initialization late?

\begin{referee}
Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z_sol?
\end{referee}
-Simulation question

\begin{referee}
What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence? 
\end{referee}
-Simulation question

\begin{referee}
Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
\end{referee}
-Simulation question

\begin{referee}
Do the authors set fixed mass limits to the IMF and if yes, which are they? If not, which is the highest / lowest mass they find in their random sampling? And which fraction of the Pop III stars in the simulation end up as type II SNe / BHs / PISN?
\end{referee}
-We do set fixed mass limits, between 1 and 300 Msol. I will add this detail. 
-What is the best way to get this information? Shall I look at all the Pop III stars at the end of the simulation and look at their masses? I should be able to get a fraction of these endings from that, correct?

\begin{referee}
One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here. 
\end{referee}
-Will have to look at Hartwig+15.

\begin{referee}
In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
\end{referee}
-This is a good point, that is confusing. I will add this.

\begin{referee}
The analytic calculation of the shielding factor is a nice property of the paper. However, assuming a constant H2 fraction seems not appropriate. Please repeat this exercise for a more realistic halo profile, which could be found in the simulations or in the literature, eg by Machacek+01 themselves.
\end{referee}
-I will check out a more realistic H2 fraction for a halo and try to get a nice plot out of that.

\begin{referee}
Results:
Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction. In addition, the authors could provide a line or an arrow to show their halo mass resolution limit.
\end{referee}
-Figure 2 is empty. I will add a vertical line at 10^5 Msol to show our resolution limit. As far as the HMF of the earliest Pop III formation redshift, is this referring to the HMF at the time when Pop III stars first begin to form, so at about z=27, what is the HMF at that time and how does it compare with Sheth-Tormen? I will plot this up.

\begin{referee}
Figure 3 looks very nice. It would be helpful if an additional line that only provides the global LWBG (in units of J21) was included.
\end{referee}
-Woohoo! Figure 3 does look nice! I will add the global LWBG, hopefully it looks alright. I am fairly certain we did this and for some reason it all didn't seem to add up. I will try this again.

\begin{referee}
The authors find no correlation between the host halo mass and the Lyman-Werner background intensity. However, they only look at the LWBG flux at the time of Pop III formation - is there maybe a correlation between the time integrated LW flux?
\end{referee}
-Haven't thought about the time integrated LW flux. Would like some advice on this point.

\begin{referee}
Figures 7 and 8 show very nice histograms as an additional panel on the right. I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
\end{referee}
-I will add a histogram on the spread of the creation time in Figure 9.

\begin{referee}
Discussion:
The authors give three reasons for the halo mass spread. Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
\end{referee}
-It's not immediately obvious to me how we would be able to estimate this. I would have to look at these processes in more detail to see if there are some mass ranges correlated with them. Any insight from John?

\begin{referee}
One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
\end{referee}
-I will check out this paper, and see what can be added.

\begin{referee}
In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different symbol / colour.
\end{referee}
-I will adjust this symbol.

\begin{referee}
Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
\end{referee}
-I will check out these papers and add accordingly.

\begin{referee}
The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction). While they cite some older work, they however fail to compare to more recent work eg by Hirano+18 or Schauer+19 (who do perform a systematic study not only based on a few, single haloes).
\end{referee}
-I will check out these papers as well, and see if I can compare.

\end{document}

### 2019-08-05 paper.tex
Fixed some formatting. Added notes to referee report and fixed a few different things within the paper (all in bold).

@@
 In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.
+\textbf{Throughout the rest of the paper, all numbers are in physical units.}
 
@@
 This results in an exponential cutoff below M$_{\rm char}$ and a power-law IMF above.
-Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
+\textbf{The Pop III IMF mass ranges from $1 \leq M / M_{\odot} \leq 300$.
+}Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
 The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere.
@@
 The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s.
-}
+\textbf{Note that a shielding factor of 1 means that there is no shielding and a shielding factor of 0 means complete shielding.}}
     \label{fig:shield_mass}
@@
 The thick, black line is the analytic Sheth-Tormen mass function.
-The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where halos are captured by 50 particles.}
+The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where halos are captured by 50 particles.
+\textbf{The vertical blue line indicates our halo mass resolution limit of 10$^{5}$ M$_{\odot}$.}}
     \label{fig:hmf}
@@
 %====================================================================
- To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}.
+ To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar} \textbf{(standing for Robust Overdensity Calculation using K-Space Topologically Adaptive Refinement), a friends-of-friends like algorithm which adaptively refines in six phase-space dimensions and one time dimension}.
 The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$.

### 2019-08-05 referee.tex
Fixed some formatting. Added notes to referee report and fixed a few different things within the paper (all in bold).

@@
 The paper presented here is very well written and offers important new insights. 
-It studies the dependence of the halo mass for first star formation on a Lyman-Werner background in a large simulation, and goes beyond current literature work by the inclusion of self-shielding and studying the multiplicity of Pop III stars.
-I generally recommend if for publication after some concerns are addressed.
+It studies the dependence of the halo mass for first star formation on a 
+Lyman-Werner background in a large simulation, and goes beyond current literature
+ work by the inclusion of self-shielding and studying the multiplicity of Pop III 
+ stars. I generally recommend if for publication after some concerns are 
+ addressed.
 \end{referee}
@@
 Major comments:
-1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo.
-This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo.
-This is very plausible.
-If several Pop III stars are found forming in the same halo at the same time, however, the employed star particle algorithm has a hard-coded length scale of 1pc in which only one star particle can be formed.
-I am wondering if this is an effect that is resolution dependent - do the same number of stars form if the resolution is increased and the maximum distance is decreased?
-Which is the motivation for the length scale of 1pc?
+1) One of the main points of the paper is studying the multiplicity of Pop III 
+stars in a halo. This multiplicity might be due to the fact that Pop III stars 
+have collapsed to a BH after their lifetime and a second Pop III star could form
+ in the same halo. This is very plausible. If several Pop III stars are found 
+ forming in the same halo at the same time, however, the employed star particle 
+ algorithm has a hard-coded length scale of 1pc in which only one star particle 
+ can be formed. I am wondering if this is an effect that is resolution dependent 
+ - do the same number of stars form if the resolution is increased and the 
+ maximum distance is decreased? Which is the motivation for the length scale of 
+ 1pc?
 \end{referee}
@@
 -Resolution testing
+-Ran original sim to see if it worked, it did run, but only reached until z=22. The simulation stopped because of a stopping parameter, StopFirstTimeAtLevel.
 
 \begin{referee}
-2) The authors select their haloes by the halo finding algorithm Rockstar.
-They should add a bit of information on that code (is it fof or subfind-like?).
-Also, one of their main points is to compare their work to Machacek+01.
-Machacek+01, however, use a different halo definition (spherical around the halo centre going out to a radius of 200 times the mean density of the Universe).
-How do these different halo masses compare?
-Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper.
-The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.
-In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo.
-The baryon fraction varies with redshift. Please give an estimate by how much this influences the halo masses used here.
+2) The authors select their haloes by the halo finding algorithm Rockstar. They 
+should add a bit of information on that code (is it fof or subfind-like?). Also,
+ one of their main points is to compare their work to Machacek+01. Machacek+01, 
+ however, use a different halo definition (spherical around the halo centre 
+ going out to a radius of 200 times the mean density of the Universe). How do 
+ these different halo masses compare?
+
+Further, it is not entirely clear why atomic cooling haloes are excluded in this
+ analysis and if they are excluded throughout the whole paper. The exclusion of 
+ atomic cooling haloes artificially shifts the average halo mass to lower 
+ values.
+
+In addition, the authors should state the fraction of haloes that have Pop III 
+stars forming outside the halo. The baryon fraction varies with redshift. Please
+ give an estimate by how much this influences the halo masses used here.
 \end{referee}
 
--address concern about Rockstar details, and Machacek halo definition
--exclusion of atomic cooling haloes - we excluded these because of a bug in our code... how to explain this without simply saying that?
--fraction of halos that halo Pop III stars forming outside the haloes: I'm not sure I will be able to tell exactly how many are not in halos.
+-Added a bit about what Rockstar is. 
+-Machacek halo definition - how should I quantify this difference?
+
+-Exclusion of atomic cooling haloes - we excluded these because of a bug in our code... how to explain this without simply saying that?
+
+-Fraction of halos that halo Pop III stars forming outside the halos: I'm not sure I will be able to tell exactly how many are not in halos.
 I need to look back at the data to see if I will be able to pick out which halos I artificially drew a halo around.
--shall I look at the baryon fraction as a function of time to see how much it varies?
+-Shall I look at the baryon fraction as a function of time to see how much it varies?
 
@@
 Minor comments:
-The authors should state at one point in the paper for which properties they use comoving or physical units.
+The authors should state at one point in the paper for which properties they use
+ comoving or physical units.
 \end{referee}
--We use physical units throughout the whole paper, apart from when we discuss the boxsize. I will make this more clear.
+-Clarified this at the end of the second paragraph in the Simulation Setup section.
 
@@
 Introduction:
-The authors write that Pop III star formation is generally more massive.
-While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
+The authors write that Pop III star formation is generally more massive. While a
+ fraction of the community agrees with that, there is manifoldly cited work that
+  finds low-mass Pop III progenitors, and the authors should not let that 
+  unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
 \end{referee}
@@
 \begin{referee}
-The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14). 
+The authors name a few processes for suppressing Pop III star formation. For 
+completeness, they should also mention eg X-ray heating (citing eg Jeon+14). 
 \end{referee}
--I will add this detail
+-I will add this detail (https://arxiv.org/pdf/1310.7944.pdf)
+-Jeon+14 seems to show that X-ray heating does not affect star formation, but 
+the clumping factor is reduced, and thus makes it easier to keep the reionized 
+gas ionized.
 
 \begin{referee}
-The authors cite the well-known study from Machacek+01.
-However, a more recent result would be from the study by Visbal+14, giving a lower mass limit.
-Since the authors find a lower mass limit than Machacek+01, it would be interesting to see how this compares to the lower mass limit from the more modern paper.
+The authors cite the well-known study from Machacek+01. However, a more recent 
+result would be from the study by Visbal+14, giving a lower mass limit. Since 
+the authors find a lower mass limit than Machacek+01, it would be interesting to
+ see how this compares to the lower mass limit from the more modern paper.
 \end{referee}
--I will check out Visbal+ 14 (I think I have looked at this paper, will double check)
+-Visbal+14 provides an equation for Mcrit (eqn. 4), I have plotted this previously. This lines up fairly well with our data, with a bit of scatter.  (https://arxiv.org/pdf/1402.0882.pdf)
 
@@
 Methods:
-In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
+In Wise+12, three different environment regions are picked. Please provide more 
+description on the rare peak simulation here and discuss why this one is 
+appropriate in this context.
 \end{referee}
--I will look at that simulation again, if John could provide some insight here that would be nice.
+-RP stands for radiation pressure in Wise+12 (correct?), not rare peak.
+The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here.
+The differences are the inclusion of H2 self-shielding and updated cosmo parameters.
 
 \begin{referee}
-The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
+The initialization at z=130 is very late. I am aware that it is impossible to 
+repeat this simulation starting at an earlier redshift, but would advise for 
+future work.
 \end{referee}
@@
 \begin{referee}
-Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z_sol?
+Why do the authors pick a non-zero metalicity threshold for Pop III star 
+formation? How many Pop III stars form between Z=0 and Z=5e-6 Z_sol?
 \end{referee}
@@
 \begin{referee}
-What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence? 
+What is the physical motivation for a density threshold of 1.e6/cc? Is there 
+convergence? 
 \end{referee}
@@
 \begin{referee}
-Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
+Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass 
+fraction or a number fraction?) How many Pop III stars do not form because of 
+this threshold?
 \end{referee}
@@
 If not, which is the highest / lowest mass they find in their random sampling? 
-And which fraction of the Pop III stars in the simulation end up as type II SNe / BHs / PISN?
+And which fraction of the Pop III stars in the simulation end up as type II 
+SNe / BHs / PISN?
 \end{referee}
--We do set fixed mass limits, between 1 and 300 Msol. I will add this detail. 
+-We do set fixed mass limits, between 1 and 300 Msol. I added this detail. 
 -What is the best way to get this information?
@@
 \begin{referee}
-One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here. 
+One effect than can weaken the shielding is shifting out of the Lyman-Werner 
+resonance lines (see Hartwig+15). I am wondering how much this would affect the 
+study presented here. 
 \end{referee}
@@
 \begin{referee}
-In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
+In Figure 1, please mention in the caption or at the top / bottom of the left 
+axis that a shielding factor of 1 corresponds to no shielding and a shielding 
+factor of 0 corresponds to high shielding, as these nomenclatures are not 
+immediately understandable for the reader.
 \end{referee}
--This is a good point, that is confusing. I will add this.
+-This detail has been added.
 
 \begin{referee}
-The analytic calculation of the shielding factor is a nice property of the paper.
-However, assuming a constant H2 fraction seems not appropriate.
-Please repeat this exercise for a more realistic halo profile, which could be found in the simulations or in the literature, eg by Machacek+01 themselves.
+The analytic calculation of the shielding factor is a nice property of the 
+paper. However, assuming a constant H2 fraction seems not appropriate. Please 
+repeat this exercise for a more realistic halo profile, which could be found in 
+the simulations or in the literature, eg by Machacek+01 themselves.
 \end{referee}
 -I will check out a more realistic H2 fraction for a halo and try to get a nice plot out of that.
+-Any suggestions from John for a more realistic halo profile?
 
@@
 Results:
-Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction.
-In addition, the authors could provide a line or an arrow to show their halo mass resolution limit.
+Figure 2 is quite empty, it would be useful to include the halo mass function of
+ the earliest Pop III formation redshift with its analytic prediction. In 
+ addition, the authors could provide a line or an arrow to show their halo mass 
+ resolution limit.
 \end{referee}
--Figure 2 is empty.
-I will add a vertical line at 10^5 Msol to show our resolution limit.
-As far as the HMF of the earliest Pop III formation redshift, is this referring to the HMF at the time when Pop III stars first begin to form, so at about z=27, what is the HMF at that time and how does it compare with Sheth-Tormen?
+-As far as the HMF of the earliest Pop III formation redshift, is this referring to the HMF at the time when Pop III stars first begin to form, so at about z=27, what is the HMF at that time and how does it compare with Sheth-Tormen?
 I will plot this up.
 
-\begin{referee}
-Figure 3 looks very nice. It would be helpful if an additional line that only provides the global LWBG (in units of J21) was included.
-\end{referee}
--Woohoo! Figure 3 does look nice! I will add the global LWBG, hopefully it looks alright. I am fairly certain we did this and for some reason it all didn't seem to add up. I will try this again.
+-Added a vertical line at $10^5 M_{\odot}$. Detail also added to caption.
+-Tried plotting the HMF of the earliest Pop III formation redshift, but I need to collect the HMF of that dataset -- having troubles remembering how this was produced
 
 \begin{referee}
-The authors find no correlation between the host halo mass and the Lyman-Werner background intensity.
-However, they only look at the LWBG flux at the time of Pop III formation - is there maybe a correlation between the time integrated LW flux?
+Figure 3 looks very nice. It would be helpful if an additional line that only 
+provides the global LWBG (in units of J21) was included.
+\end{referee}
+-Woohoo! Figure 3 does look nice!
+-I tried adding the global LWBG, but this makes our results seem funny, because we are getting the average J21 weighted by cell mass lying below the global LWBG. Thoughts about this?
+
+\begin{referee}
+The authors find no correlation between the host halo mass and the Lyman-Werner 
+background intensity. However, they only look at the LWBG flux at the time of 
+Pop III formation - is there maybe a correlation between the time integrated LW 
+flux?
 \end{referee}
@@
 \begin{referee}
-Figures 7 and 8 show very nice histograms as an additional panel on the right. I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
+Figures 7 and 8 show very nice histograms as an additional panel on the right. 
+I suggest to include a histogram on the spread of the creation time in Figure 9 
+similar to Figures 7 and 8.
 \end{referee}
--I will add a histogram on the spread of the creation time in Figure 9.
+-Added the histogram to Figure 9.
 
@@
 Discussion:
-The authors give three reasons for the halo mass spread.
-Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
+The authors give three reasons for the halo mass spread. Can they estimate which
+ of the three processes (BH formation, dynamical heating and temporal LWBG 
+ fluctuations) is responsible for the spread by which fraction?
 \end{referee}
@@
 \begin{referee}
-One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
+One of the most extensive studies on over 1000 minihaloes was performed by 
+Hirano+15, who also include a Lyman-Werner background. Their work should be put 
+in comparison as well.
 \end{referee}
--I will check out this paper, and see what can be added.
+Hirano+15 is looking at the distribution of stellar masses to calculate the IMF of p3 stars, which is why we quote them in the introduction. 
+-Their Fig. 3 shows the number of halos versus virial mass that host primordial star-forming clouds. 
+-Using their eqn. 6 they find Mvir = $2.1 \times 10^5$ at z=30, and Mvir = $9.9 \times 10^5$ at z=10, which they say is in good agreement with their Fig. 3. 
+(https://arxiv.org/pdf/1501.01630.pdf)
 
 \begin{referee}
-In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different symbol / colour.
+In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different 
+symbol / colour.
 \end{referee}
--I will adjust this symbol.
+-Adjusted. Changed the symbol to a pentagon and the outline color black. Okay?
 
 \begin{referee}
-Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
+Since the authors study star formation in minihaloes, it would be appropriate to
+ also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions 
+ from minihaloes.
 \end{referee}
--I will check out these papers and add accordingly.
+-Kitayama+04: HII regions are governed by an initial slow and weak D-type ionization front followed by a rapid R-type front.
+For there to be complete ionization, the transition between the types is critical.
+They find that in small mass halos, less than $10^6 M_{\odot}$, this critical transition takes place fairly rapidly, allowing for high escape fractions of greater than 80\%.
+In larger mass halos, the ionization front remains as a D-type, and the escape fraction is essentially zero.
+They use a simulation to study these HII regions in similar mass halos as ours and within a similar redshift range.
+Their Fig.
+4 shows the ionizing and LW escape fractions as a function of halo mass for different stellar masses.
+(https://arxiv.org/pdf/astro-ph/0406280.pdf)
+
+-Schauer+15: They run simulations of LW escape fractions from P3 stars in $10^5 - 10^7 M_{\odot}$ halos.
+They find escape fractions from 0-85\%, and that H2 shielding by neutral hydrogen also decreases escape fractions compared to escape fractions predicted by only H2 self-shielding.
+Fig.3 shows escape fractions for different models and different P3 stellar masses.
+When H2 shielding by neutral hydrogen is not included, escape fractions are overpredicted.
+(https://arxiv.org/pdf/1506.04796.pdf)
 
 \begin{referee}
-The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction).
-While they cite some older work, they however fail to compare to more recent work eg by Hirano+18 or Schauer+19 (who do perform a systematic study not only based on a few, single haloes).
+The authors mention a few times that streaming velocities are another pathway of
+ suppressing Pop III formation (also in the introduction). While they cite some 
+ older work, they however fail to compare to more recent work eg by Hirano+18 or
+  Schauer+19 (who do perform a systematic study not only based on a few, single 
+  haloes).
 \end{referee}
--I will check out these papers as well, and see if I can compare.
+-Hirano+18: Investigate the collapse of primordial gas to form P3 stars when the energy transfer between baryon and dark matter fluids (due to non-gravitational scattering) is included.
 

### 2019-08-08 referee.tex
Referee response: Formatting changes. Adding intro sentences.

@@
 \usepackage{listings,color}
+\usepackage{mdframed}
 
@@
 
-\definecolor{verbgray}{gray}{0.9}
-\lstnewenvironment{referee}{%
-  \lstset{backgroundcolor=\color{verbgray},
-  frame=single,
-  framerule=0pt,
-  basicstyle=\ttfamily,
-  columns=fullflexible}}{}
+\definecolor{quotegray}{gray}{0.9}
+% \lstnewenvironment{referee}{%
+%   \lstset{backgroundcolor=\color{quotegray},
+%   frame=single,
+%   framerule=0pt,
+%   basicstyle=\ttfamily,
+%   columns=fullflexible}}{}
+
+% https://tex.stackexchange.com/questions/111065/quoting-styles-technical-an-appreciation-questions
+\mdfdefinestyle{myquotestyle}{
+  leftmargin=15pt,
+  rightmargin=15pt,
+  backgroundcolor=quotegray,
+  linewidth=0pt,
+  skipbelow=\topskip,
+  skipabove=\topskip
+}
+\newenvironment{referee}[1][]{%
+    \ignorespaces%
+    \begin{mdframed}[style=myquotestyle,#1]%
+}{%
+    \end{mdframed}%
+    \ignorespacesafterend%
+}%
+
+% \newenvironment{referee}[1][]{
+%   \ignorespaces%
+%   \begin{mdframed}[style=myquotestyle,#1]%
+% }{%
+%   \end{mdframed}%
+%   \ignorespaceafterend%
+% }%
 
@@
 
+We thank the referee for their insightful review.  Their review is directly quoted below in the gray boxes with our responses below.  Any changes to the manuscript has been \textbf{bold-faced}.
+
 \begin{referee}
 The paper presented here is very well written and offers important new insights.
-It studies the dependence of the halo mass for first star formation on a 
-Lyman-Werner background in a large simulation, and goes beyond current literature
- work by the inclusion of self-shielding and studying the multiplicity of Pop III 
- stars. I generally recommend if for publication after some concerns are 
- addressed.
+It studies the dependence of the halo mass for first star formation on a Lyman-Werner background in a large simulation, and goes beyond current literature work by the inclusion of self-shielding and studying the multiplicity of Pop III stars.
+I generally recommend if for publication after some concerns are addressed.
 \end{referee}
@@
 Major comments:
-1) One of the main points of the paper is studying the multiplicity of Pop III 
-stars in a halo. This multiplicity might be due to the fact that Pop III stars 
-have collapsed to a BH after their lifetime and a second Pop III star could form
- in the same halo. This is very plausible. If several Pop III stars are found 
- forming in the same halo at the same time, however, the employed star particle 
- algorithm has a hard-coded length scale of 1pc in which only one star particle 
- can be formed. I am wondering if this is an effect that is resolution dependent 
- - do the same number of stars form if the resolution is increased and the 
- maximum distance is decreased? Which is the motivation for the length scale of 
- 1pc?
+
+1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo.
+This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo.
+This is very plausible.
+If several Pop III stars are found forming in the same halo at the same time, however, the employed star particle algorithm has a hard-coded length scale of 1pc in which only one star particle can be formed.
+I am wondering if this is an effect that is resolution dependent - do the same number of stars form if the resolution is increased and the maximum distance is decreased?
+Which is the motivation for the length scale of 1pc?
 \end{referee}
@@
 \begin{referee}
-2) The authors select their haloes by the halo finding algorithm Rockstar. They 
-should add a bit of information on that code (is it fof or subfind-like?). Also,
- one of their main points is to compare their work to Machacek+01. Machacek+01, 
- however, use a different halo definition (spherical around the halo centre 
- going out to a radius of 200 times the mean density of the Universe). How do 
- these different halo masses compare?
+2) The authors select their haloes by the halo finding algorithm Rockstar.
+They should add a bit of information on that code (is it fof or subfind-like?).
+Also, one of their main points is to compare their work to Machacek+01.
+Machacek+01, however, use a different halo definition (spherical around the halo centre going out to a radius of 200 times the mean density of the Universe).
+How do these different halo masses compare?
 
-Further, it is not entirely clear why atomic cooling haloes are excluded in this
- analysis and if they are excluded throughout the whole paper. The exclusion of 
- atomic cooling haloes artificially shifts the average halo mass to lower 
- values.
+Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper.
+The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.
 
-In addition, the authors should state the fraction of haloes that have Pop III 
-stars forming outside the halo. The baryon fraction varies with redshift. Please
- give an estimate by how much this influences the halo masses used here.
+In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo.
+The baryon fraction varies with redshift.
+Please give an estimate by how much this influences the halo masses used here.
 \end{referee}
@@
 Minor comments:
-The authors should state at one point in the paper for which properties they use
- comoving or physical units.
+
+The authors should state at one point in the paper for which properties they use comoving or physical units.
 \end{referee}
@@
 Introduction:
-The authors write that Pop III star formation is generally more massive. While a
- fraction of the community agrees with that, there is manifoldly cited work that
-  finds low-mass Pop III progenitors, and the authors should not let that 
-  unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
+
+The authors write that Pop III star formation is generally more massive.
+While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
 \end{referee}
@@
 \begin{referee}
-The authors name a few processes for suppressing Pop III star formation. For 
-completeness, they should also mention eg X-ray heating (citing eg Jeon+14). 
+The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14).
 \end{referee}
@@
 \begin{referee}
-The authors cite the well-known study from Machacek+01. However, a more recent 
-result would be from the study by Visbal+14, giving a lower mass limit. Since 
-the authors find a lower mass limit than Machacek+01, it would be interesting to
- see how this compares to the lower mass limit from the more modern paper.
+The authors cite the well-known study from Machacek+01.
+However, a more recent result would be from the study by Visbal+14, giving a lower mass limit.
+Since the authors find a lower mass limit than Machacek+01, it would be interesting to see how this compares to the lower mass limit from the more modern paper.
 \end{referee}
@@
 Methods:
-In Wise+12, three different environment regions are picked. Please provide more 
-description on the rare peak simulation here and discuss why this one is 
-appropriate in this context.
+
+In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
 \end{referee}
@@
 \begin{referee}
-Why do the authors pick a non-zero metalicity threshold for Pop III star 
-formation? How many Pop III stars form between Z=0 and Z=5e-6 Z_sol?
+Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
 \end{referee}
@@
 \begin{referee}
-What is the physical motivation for a density threshold of 1.e6/cc? Is there 
-convergence? 
+What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
 \end{referee}
@@
 \begin{referee}
-Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass 
-fraction or a number fraction?) How many Pop III stars do not form because of 
-this threshold?
+Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
 \end{referee}
@@
 If not, which is the highest / lowest mass they find in their random sampling?
-And which fraction of the Pop III stars in the simulation end up as type II 
-SNe / BHs / PISN?
+And which fraction of the Pop III stars in the simulation end up as type II SNe / BHs / PISN?
 \end{referee}
@@
 \begin{referee}
-One effect than can weaken the shielding is shifting out of the Lyman-Werner 
-resonance lines (see Hartwig+15). I am wondering how much this would affect the 
-study presented here. 
+One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
 \end{referee}
@@
 \begin{referee}
-In Figure 1, please mention in the caption or at the top / bottom of the left 
-axis that a shielding factor of 1 corresponds to no shielding and a shielding 
-factor of 0 corresponds to high shielding, as these nomenclatures are not 
-immediately understandable for the reader.
+In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
 \end{referee}
@@
 \begin{referee}
-The analytic calculation of the shielding factor is a nice property of the 
-paper. However, assuming a constant H2 fraction seems not appropriate. Please 
-repeat this exercise for a more realistic halo profile, which could be found in 
-the simulations or in the literature, eg by Machacek+01 themselves.
+The analytic calculation of the shielding factor is a nice property of the paper.
+However, assuming a constant H2 fraction seems not appropriate.
+Please repeat this exercise for a more realistic halo profile, which could be found in the simulations or in the literature, eg by Machacek+01 themselves.
 \end{referee}
@@
 Results:
-Figure 2 is quite empty, it would be useful to include the halo mass function of
- the earliest Pop III formation redshift with its analytic prediction. In 
- addition, the authors could provide a line or an arrow to show their halo mass 
- resolution limit.
+
+Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction.
+In addition, the authors could provide a line or an arrow to show their halo mass resolution limit.
 \end{referee}
@@
 \begin{referee}
-The authors find no correlation between the host halo mass and the Lyman-Werner 
-background intensity. However, they only look at the LWBG flux at the time of 
-Pop III formation - is there maybe a correlation between the time integrated LW 
-flux?
+The authors find no correlation between the host halo mass and the Lyman-Werner background intensity.
+However, they only look at the LWBG flux at the time of Pop III formation - is there maybe a correlation between the time integrated LW flux?
 \end{referee}
@@
 \begin{referee}
-Figures 7 and 8 show very nice histograms as an additional panel on the right. 
-I suggest to include a histogram on the spread of the creation time in Figure 9 
-similar to Figures 7 and 8.
+Figures 7 and 8 show very nice histograms as an additional panel on the right.  I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
 \end{referee}
@@
 Discussion:
-The authors give three reasons for the halo mass spread. Can they estimate which
- of the three processes (BH formation, dynamical heating and temporal LWBG 
- fluctuations) is responsible for the spread by which fraction?
+
+The authors give three reasons for the halo mass spread.
+Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
 \end{referee}
@@
 \begin{referee}
-One of the most extensive studies on over 1000 minihaloes was performed by 
-Hirano+15, who also include a Lyman-Werner background. Their work should be put 
-in comparison as well.
+One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
 \end{referee}
@@
 \begin{referee}
-In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different 
-symbol / colour.
+In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different symbol / colour.
 \end{referee}
@@
 \begin{referee}
-Since the authors study star formation in minihaloes, it would be appropriate to
- also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions 
- from minihaloes.
+Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
 \end{referee}
@@
 \begin{referee}
-The authors mention a few times that streaming velocities are another pathway of
- suppressing Pop III formation (also in the introduction). While they cite some 
- older work, they however fail to compare to more recent work eg by Hirano+18 or
-  Schauer+19 (who do perform a systematic study not only based on a few, single 
-  haloes).
+The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction).
+While they cite some older work, they however fail to compare to more recent work eg by Hirano+18 or Schauer+19 (who do perform a systematic study not only based on a few, single haloes).
 \end{referee}

### 2019-08-08 referee.tex
Added some answers to simulation questions (not finished yet)

@@
 \begin{referee}
-The initialization at z=130 is very late. I am aware that it is impossible to 
-repeat this simulation starting at an earlier redshift, but would advise for 
-future work.
+The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
 \end{referee}
--Personal question: why is this initialization late?
+
+In hindsight, we agree that we initialized the simulation too late, even with 2nd order Lagrangian perturbation theory.
+The maximum baryon overdensity is 1.64$\bar{\rho}_{\rm b}$, and the maximum DM particle displacement is 2.5 $\times$ (cell width).
+In future studies, we will start at earlier times when the evolution is solidly in the linear regime.
+We thank the referee for pointing this out.
 
@@
 \end{referee}
--Simulation question
+
+We chose this metallicity threshold based on the work of Omukai et al.
+(2005), Schneider et al.
+(2006) and others, who found that dust cooling was efficient enough above this metallicity to induce low-mass star formation.
+Very few stars (\textbf{calculate percentage}) form with metallicities between zero and $5 \times 10^{-6} Z_\odot$ and doesn't affect our results greatly.
+Stars only obtain this extremely low (non-zero) metallicity when metal mixing is incomplete.
+This usually occurs when a blastwave is mixing into a nearby halo, and the core collapses before it can fully mix.
+Because of the randomness of the IMF sampling and errors from numerical diffusion and other solvers, we do not place great emphasis on stars in this metallicity range.
+It is unclear what would be the actual stellar metallicity when it reaches main sequence, given our 0.1 proper pc resolution.
+Thus we have not changed the manuscript on this topic.
 
@@
 \end{referee}
--Simulation question
+
+We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12.
+This density can be calculated as \textbf{(give calculation and density value at level 13)}.
 
@@
 \end{referee}
--Simulation question
 
@@
 -Added a vertical line at $10^5 M_{\odot}$. Detail also added to caption.
--Tried plotting the HMF of the earliest Pop III formation redshift, but I need to collect the HMF of that dataset -- having troubles remembering how this was produced
+2-Tried plotting the HMF of the earliest Pop III formation redshift, but I need to collect the HMF of that dataset -- having troubles remembering how this was produced
 

### 2019-08-09 paper.tex
Minor updates.

@@
 We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
-resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
+resolution and a dark matter paticle mass of 2001 M$_{\odot}$.
+It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.
+\jhw{Add refinement criteria.} The simulation is
 initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit 

### 2019-08-09 referee.tex
Minor updates.

@@
 We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12.
-This density can be calculated as \textbf{(give calculation and density value at level 13)}.
+At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.
+At $T=300$ K, the Jeans length is $L_{\rm J} = 0.17$~pc at $\rho = 10^6 m_{\rm H}$~g/cm$^3$.
+\textbf{JHW: finish this point.}
 

### 2019-08-12 paper.tex
Finishing answer to density threshold

--- 2019-08-05 paper.tex
@@
 \usepackage{mathtools}
-\usepackage{hyperref}
+%\usepackage[draft]{hyperref}
 %\usepackage{subcaption}
@@
 We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
-resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
-initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit 
-\citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 
-0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables 
-having their usual definitions.
+resolution and a dark matter paticle mass of 2001 M$_{\odot}$.
+It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.
+\textbf{We refine the cells one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.
+Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.} The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions.
 The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue.
@@
 \end{enumerate}
+%
+\textbf{Our chosen threshold density corresponds to a value similar to a density that would trigger another mesh refinement past level 12.
+At these scales, Jeans length refinement is the most common because of the cold temperatures in the cloud core.}
 
@@
 %====================================================================
-\subsection{\hh{} Self-Shielding}
+\subsection{\texorpdfstring{H$_2$} Self-Shielding}
 %====================================================================

### 2019-08-12 referee.tex
Finishing answer to density threshold

@@
 We thank the referee for pointing this out.
-
+q
 \begin{referee}
@@
 
-We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12.
+Our choice was motivated by our refinement strategy rather than convergence.
+We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12 (dx = 0.09 proper pc at $z=10$).
 At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.
-At $T=300$ K, the Jeans length is $L_{\rm J} = 0.17$~pc at $\rho = 10^6 m_{\rm H}$~g/cm$^3$.
-\textbf{JHW: finish this point.}
+Solving for the density in the Jeans length equation, given a typical temperature $T=300$~K with primordial cooling and a Jeans Length of $8 \times \textrm{dx}$, we obtain a number density $n = 5.7 \times 10^4 \cubecm$.
+This number density does not exactly match the chosen density criterion because some oversight when setting up the simulation.
+In the case where the density SF criterion is larger than $n$, the gas will continue to condense on a faster timescale than its surroundings.
+Thus we are confident that this slight mismatch does not affect our results.
+
+We have added the AMR refinement criteria to Section 2.1 and our motivation to this threshold to Section 2.2.1.
 

### 2019-08-12 paper.tex
Addressing H2 Pop III criterion question

@@
 
-	\item molecular hydrogen fraction, f$_{\rm H2}$ > 10$^{-3}$
+	\item molecular hydrogen \textbf{number} fraction, f$_{\rm H2}$ > 10$^{-3}$
 \end{enumerate}
-%
-\textbf{Our chosen threshold density corresponds to a value similar to a density that would trigger another mesh refinement past level 12.
-At these scales, Jeans length refinement is the most common because of the cold temperatures in the cloud core.}
+\textbf{Our chosen threshold density are consistent with values found in previous simulations of Pop III star formation \citep[e.g.][]{Hirano15} at our resolution limit.
+Additionally, it is similar to a density that would trigger another mesh refinement past level 12.
+At these scales, Jeans length refinement is the most common because of the cold temperatures in the cloud core.
+The molecular hydrogen criterion is also consistent with previous work in the ``loitering'' phase of molecule formation between $10^2$ and $10^8 \cubecm$ before three-body reactions become important \citep[e.g.][]{Omukai10}.}
 

### 2019-08-12 referee.tex
Addressing H2 Pop III criterion question

@@
 
-Our choice was motivated by our refinement strategy rather than convergence.
-We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12 (dx = 0.09 proper pc at $z=10$).
+Our choice was motivated by both previous work and our refinement strategy rather than convergence.
+Previous work (e.g.
+O'Shea et al.
+2007; Yoshida et al.
+2007) and later groups (e.g.
+Hirano et al.
+2015) have shown that the number density is $\sim 10^6 \cubecm$ at our resolution limit of $0.09$ proper pc at $z=10$.
+Secondly, we chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12 (dx = 0.09 proper pc at $z=10$).
 At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.
@@
 \end{referee}
+
+We chose this critical H$_2$ fraction to match with the values found in previous work (e.g.
+Yoshida et al.
+2007; Omukai et al.
+2010) at the density threshold of $10^6 \cubecm$.
+It is a number fraction.
+We have added a note in Section 2.2.1 to reflect this detail.
+
+In our original formulation (Abel et al.
+2007), we implemented this restriction to avoid spurious star particle formation in D-type ionization fronts that can meet all of the other criteria.
+But in the presence of an extremely strong Lyman-Werner flux from a nearby ($\sim$1 pc) star, star formation is unlikely to occur in the shell because it is irradiated and not self-gravitating.
+The last question is an interesting question, but it is difficult to determine because these conditions (high density but low H$_2$ fractions) are short-lived just after star formation.
+Thus we cannot give a definite answer to it, but from the original formulation, we would estimate that the number of Pop III stars would increase by a factor of several with multiple cells in the quasi-spherical ionization front triggering star particle formation.
+Because of these uncertainties, we have not added any of these details to the manuscript.
 

### 2019-08-12 paper.tex
very low metallicity P3 stars answer

@@
 \end{enumerate}
-\textbf{Our chosen threshold density are consistent with values found in previous simulations of Pop III star formation \citep[e.g.][]{Hirano15} at our resolution limit.
+\textbf{The critical metallicity marks where dust cooling becomes efficient enough to cause fragmentation at high densities \citep[e.g.][]{Schneider06_Frag}.
+In practice, we find about 10 per cent of Pop III star particles having a non-zero metallicity below this value.
+This scenario occurs when a halo is externally enriched by a nearby supernova.
+Because of uncertainties with turbulent mixing and collapse timescales, we choose not to predict the final metallicity at zero-age main sequence and assign the star particle the metallicity of the densest cell.
+The chosen threshold density are consistent with values found in previous simulations of Pop III star formation \citep[e.g.][]{Hirano15} at our resolution limit.
 Additionally, it is similar to a density that would trigger another mesh refinement past level 12.
@@
 %====================================================================
-\subsection{\texorpdfstring{H$_2$} Self-Shielding}
+\subsection{\texorpdfstring{H$_2$}{H2} Self-Shielding}
 %====================================================================

### 2019-08-12 referee.tex
very low metallicity P3 stars answer

@@
 (2005), Schneider et al.
-(2006) and others, who found that dust cooling was efficient enough above this metallicity to induce low-mass star formation.
-Very few stars (\textbf{calculate percentage}) form with metallicities between zero and $5 \times 10^{-6} Z_\odot$ and doesn't affect our results greatly.
+(2006), who found that dust cooling was efficient enough above this metallicity to induce low-mass star formation.
+About 10\% of Pop III stars form with metallicities between zero and $5 \times 10^{-6} Z_\odot$.
 Stars only obtain this extremely low (non-zero) metallicity when metal mixing is incomplete.
@@
 It is unclear what would be the actual stellar metallicity when it reaches main sequence, given our 0.1 proper pc resolution.
-Thus we have not changed the manuscript on this topic.
+We have made a note of this in Section 2.2.1.
 

### 2019-08-12 paper.tex
Final changes for now

@@
 12 of W12.
+\textbf{With our chosen IMF (Eq.
+\ref{IMF}), XX, XX, and XX per cent of Pop III stars produce Type II SN, black holes with no SN, and PISNe, respectively.} \jhw{Fill in percentages}
 
@@
 There are three main causes of this significant variation in mass.
-First, a fraction of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.
+First, a fraction \jhw{Give number} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.
 Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs.

### 2019-08-12 referee.tex
Final changes for now

@@
 \usepackage{mdframed}
+\parskip=10pt
 
@@
 We thank the referee for pointing this out.
-q
+
 \begin{referee}
@@
 \end{referee}
--It's not immediately obvious to me how we would be able to estimate this.
-I would have to look at these processes in more detail to see if there are some mass ranges correlated with them.
-Any insight from John?
+
+This is an interesting question, but it is outside the scope of this paper.
+It most likely depends on the large-scale environment, halo mass accretion history, and halo star formation history, but how these factors affect each other is unclear.
+In practice, it would be difficult to determine the relative importance of dynamical heating and temporal LWBG fluctuations because of the time variations in the heating rate and suppression of H$_2$ cooling.
+Because of these reasons, we do not give any estimates in the discussion.
+
+The occurrence of BH formation and no metal enrichment depends on the chosen Pop III IMF, and we have addressed in an earlier answer and made a note in Section 2.2.1.
 

### 2019-08-12 referee.tex
minor change

@@
 It is a number fraction.
-We have added a note in Section 2.2.1 to reflect this detail.
+We have added to Section 2.2.1 to reflect this detail.
 
@@
 
-The occurrence of BH formation and no metal enrichment depends on the chosen Pop III IMF, and we have addressed in an earlier answer and made a note in Section 2.2.1.
+The occurrence of BH formation and no metal enrichment depends on the chosen Pop III IMF, and we have addressed in an earlier answer and noted this fraction in the discussion.
 

### 2019-08-16 paper.tex
Adjusted comparison plot, and Figure 3. Added a few adjustments to the paper regarding some of the referees first notes.

@@
 Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today.
-These stars are, by definition, metal-free (Population III; Pop III) and are thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}.
-A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
+These stars are, by definition, metal-free (Population III; Pop III) and are \textbf{traditionally} thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}\textbf{, although recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}} A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
 The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.
@@
 Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12,OLeary12}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}.
+\textbf{X-ray heating from High-Mass X-ray Binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.}
 
@@
 %====================================================================
- To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar} \textbf{(standing for Robust Overdensity Calculation using K-Space Topologically Adaptive Refinement), a friends-of-friends like algorithm which adaptively refines in six phase-space dimensions and one time dimension}.
+ To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar} \textbf{, a friends-of-friends like algorithm which adaptively refines in six phase-space dimensions and one time dimension}.
 The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$.

### 2019-08-16 referee.tex
Adjusted comparison plot, and Figure 3. Added a few adjustments to the paper regarding some of the referees first notes.

@@
 -Resolution testing
--Ran original sim to see if it worked, it did run, but only reached until z=22. The simulation stopped because of a stopping parameter, StopFirstTimeAtLevel.
+-Need to update enzo to John's version with the bug fix.
+
+-Restart from DD0029 after pulling it back down. "enzo.exe -r output"
+-At the last output, check to see how many stars are in the halo. 
+-"our results are insensitive to the star combine radius"
 
@@
 -Added a bit about what Rockstar is. 
--Machacek halo definition - how should I quantify this difference?
+-Machacek halo definition comparison - I have plotted the rockstar mass versus the calculated mass, looks like a solid group of halos lie in a 1:1 relationship, and others are fairly close, apart from a group where the calculated mass is much smaller than the rockstar mass.
+Need to determine why this is.
 
@@
 
--Fraction of halos that halo Pop III stars forming outside the halos: I'm not sure I will be able to tell exactly how many are not in halos.
-I need to look back at the data to see if I will be able to pick out which halos I artificially drew a halo around.
--Shall I look at the baryon fraction as a function of time to see how much it varies?
+-Fraction of halos that halo Pop III stars forming outside the halos: Turns out I was not able to get this data as easily as I thought.
+I am going to quickly run through my script and find the P3 stars in each dataset which are not in halos.
+
+-I am waiting to get this data!
 
@@
 \end{referee}
--Visbal+14 provides an equation for Mcrit (eqn. 4), I have plotted this previously. This lines up fairly well with our data, with a bit of scatter.  (https://arxiv.org/pdf/1402.0882.pdf)
+-Visbal+14 provides an equation for Mcrit (eqn.
+4), I have plotted this previously.
+I have plotted this for z=20, and adjusted the trenti line for that redshift as well.
+May have to adjust the plot more.
+I will add detail about the line to the paper.
+(https://arxiv.org/pdf/1402.0882.pdf)
 
@@
 \end{referee}
--RP stands for radiation pressure in Wise+12 (correct?), not rare peak.
+-RP stands for radiation pressure in Wise+12, not rare peak.
 The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here.
@@
 -We do set fixed mass limits, between 1 and 300 Msol. I added this detail.
--What is the best way to get this information?
-Shall I look at all the Pop III stars at the end of the simulation and look at their masses?
-I should be able to get a fraction of these endings from that, correct?
+
+-Plot IMF of P3 stars, find the fractional between each mass range. Watch units, will have to divide by M. Need to figure out how to plot this still.
 
@@
 \end{referee}
--I will check out a more realistic H2 fraction for a halo and try to get a nice plot out of that.
--Any suggestions from John for a more realistic halo profile?
+-I have pulled data from O'Shea and Norman 07 from their Figure 14, where there is a LW background.
 
@@
 \end{referee}
--As far as the HMF of the earliest Pop III formation redshift, is this referring to the HMF at the time when Pop III stars first begin to form, so at about z=27, what is the HMF at that time and how does it compare with Sheth-Tormen?
-I will plot this up.
+-I have the data for the halo masses from the earliest dataset where star formation ahppens, but it does not line up well with the analytic formula....
 
@@
 -Woohoo! Figure 3 does look nice!
--I tried adding the global LWBG, but this makes our results seem funny, because we are getting the average J21 weighted by cell mass lying below the global LWBG. Thoughts about this?
+-I have added the background LW. I will add the detail that the JLW that is plotted for the whole plot is coming from only sources.
 
@@
 \end{referee}
--Haven't thought about the time integrated LW flux. Would like some advice on this point.
+This would be difficult to calculate. It would require constant tracking of halos through time to calculate the time integrated LW flux.
 

### 2019-08-20 paper.tex
Addressed more referee notes, including the shielding factor for a more appropriate halo profile, the LWBG on figure 3, and added a few citations and descriptions.

@@
 
-For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, a typical \hh{} fraction of $f_{\rm H2} = 10^{-4}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, and redshift.
+For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, redshift\textbf{, and for a given \hh{} fraction halo profile}.
 Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively.
 The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$.
-Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.
+\textbf{To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.119543 from \citet{oshea07a} Figure 13 panel d, where $J_{21}$ = 0.
+These profiles were approximated with a linear fit for simplicity.
+As the halo masses increase, the shielding factor increases, meaning there is less shielding occuring within that halo.
+This is because at larger radii, there is less \hh{} available, and therefore, shielding is decreased.} Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.
 At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum.
@@
 Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$.
-For these parameters, and assuming the Doppler broadening parameter equals the circular velocity, the shielding factor is below 1 percent.
+For these parameters, assuming the Doppler broadening parameter equals the circular velocity, \textbf{and assuming \hh{} fraction halo profiles from \citet{oshea07a}, }the shielding factor is below 1 percent.
 The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/JLW_xe_mass.pdf}
-    \caption{For the entire box, the average mass weighted LW background and the fraction of the volume ionized above 10\% versus time.
-Temperature projections are shown at the points indicated by the arrows.}
+	\includegraphics[width=\columnwidth]{images/JLW_xe_bg_mass_weight.pdf}
+    \caption{For the entire box, the average mass weighted LW background \textbf{from sources} shown in solid red and the fraction of the volume ionized above 10\% versus time shown in solid black.
+\textbf{The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}).}Temperature projections are shown at the points indicated by the arrows.}
     \label{fig:JLW_xe_mass}
@@
 Since we include \hh{} self-shielding, Pop III stars are allowed to form in smaller mass halos for a given LW background.
-\citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6.
+\textbf{\citet{Visbal14} used zero-dimensional one-zone models to study the gaseous centers of dark matter halos and how they react to a LW background.
+They use a particular parametrization of the central gas density, which then follows their analytic equation for critical mass (see their Equation 4) to withing a factor of two.
+This critical mass is plotted in our Figure \ref{fig:compare_JLW_mass} at a redshift of 20.
+At that redshift, almost all of our halos fall below their critical mass relationship, with only the highest mass halos rising above.
+\citet{Visbal14} also compare their results to three-dimensional hydrodynamical simulations, where they find similar threshold halo masses as \citet{Machacek01}.}\citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6.
 They found a minimum halo mass for hosting Pop III star formation, but with the caveat that they did not include \hh{} self-shielding.
@@
 Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
+\textbf{\citet{Hirano15} used cosmological simulations to study 1540 gas clouds in the early universe to derive the corresponding stellar mass distribution.
+They find that star forming halos of virial masses $M_{\rm vir} = 2.1 \times 10^5 M_{\odot}$ at z = 30 and $M_{\rm vir} = 9.9 \times 10^5 M_{\odot}$ at z = 10.
+These masses are fairly similar to our work, with our mean halo mass lying between these values.}
 
@@
     \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works.
-The black solid line is from M01, blue solid line from \citet{Trenti09_SFR}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.
+The black solid line is from M01 \textbf{given our LW background}, blue solid line from \citet{Trenti09_SFR} \textbf{at z=20, the purple solid line from \citet{Visbal14} at z=20,}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.
 J$_{LW}$ = 0 for the various sources is plotted here at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
@@
 In general, they find that the LW escape fractions in the far-field are higher than 75\%.
-Since we are not accounting for the reduced escape fraction within our halos, we are overestimatng the LW radiation coming from point sources in our simulation.
+\textbf{Their work was based on previous work, done by \citet{Schauer15}, where they study LW radiation coming from single Pop III stars, rather than stellar populations.
+They find similar results as \citet{Schauer17}, with the exception that H2 shielding by neutral hydrogen decreases escape fractions as compared to when only H2 shielding is considered.
+In their more recent work, they find that this difference in escape fractions between when H2 shielding by neutral hydrogen is included or not is negligible.
+\citet{kitayama04} investigated the transition between D-type and R-type ionization fronts within halos to determine the escape fractions of ionizing and photodissociating photons using a one-dimensional Lagrangian hydrodynamics code.
+They found that in halos with masses $< 10^6 M_{\odot}$, escape fractions are greater than 80 \%, and in larger mass halos, with masses $> 10^7 M_{\odot}$, the escape fractions are essentially zero.} Since we are not accounting for the reduced escape fraction within our halos, we are overestimating the LW radiation coming from point sources in our simulation.
 We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results as we find little dependence on LW intensity.

### 2019-08-20 referee.tex
Addressed more referee notes, including the shielding factor for a more appropriate halo profile, the LWBG on figure 3, and added a few citations and descriptions.

@@
 \end{referee}
--Clarified this at the end of the second paragraph in the Simulation Setup section.
+This has been clarified at the end of the second paragraph in the Simulation Setup section.
 
@@
 \end{referee}
--I will look at and add these citations and detail to the introduction.
+These studies have been mentioned and cited in the introcution.
 
@@
 \end{referee}
--I will add this detail (https://arxiv.org/pdf/1310.7944.pdf)
--Jeon+14 seems to show that X-ray heating does not affect star formation, but 
-the clumping factor is reduced, and thus makes it easier to keep the reionized 
-gas ionized.
+This study has been mentioned and cited in the introduction.
 
@@
 \end{referee}
+I have included the $M_{\rm crit}$ function that Visbal+14 use in their study (their Equation 4) for a redshift of 20.
+It appears the Visbal+14 find similar masses as Machacek+01, and when comparing the Machacek+01 for our LWBG and the relation from Visbal+14 at z=20, Visbal+14 find higher halo masses overall.
+
 -Visbal+14 provides an equation for Mcrit (eqn.
@@
 \end{referee}
--RP stands for radiation pressure in Wise+12, not rare peak.
+RP stands for radiation pressure in Wise+12, not rare peak.
 The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here.
@@
 \end{referee}
--This detail has been added.
+This is a tricky detail, and has been added to the caption of of Figure 1.
 
@@
 \end{referee}
--I have pulled data from O'Shea and Norman 07 from their Figure 14, where there is a LW background.
+This is a good point, and the plot has been adjusted accordingly.
+The halo profiles from O'Shea and Norman 2007 are now being used as the \hh{} fraction as a function of radius.
+The plot now shows that the shielding factor increases as a function of mass, since at larger radii, there is less \hh{}.
+The overall take away of the plot has not changed.
 
@@
 \end{referee}
--Woohoo! Figure 3 does look nice!
--I have added the background LW. I will add the detail that the JLW that is plotted for the whole plot is coming from only sources.
+Thank you for your comment. The global LWBG has been added as a red dashed line. Some more detail about the global LW background (solid red line) has also been added.
 
@@
 \end{referee}
-This would be difficult to calculate. It would require constant tracking of halos through time to calculate the time integrated LW flux.
+While the time integrated LW flux would be interesting to follow, and may provide some further insight to what we are exploring, this would be difficult to calculate.
+It would require constant tracking of halos through time to calculate the time integrated LW flux.
 
@@
 \end{referee}
--Added the histogram to Figure 9.
+The side histogram has been added to Figure 9.
 
@@
 (https://arxiv.org/pdf/1501.01630.pdf)
+-Should more be added?
 
@@
 \end{referee}
--Adjusted. Changed the symbol to a pentagon and the outline color black. Okay?
+This has been adjusted. The point from Yoshida+03 is now a pentagon and is outlined in black, and all symbols have had their edges increased.
 
@@
 \end{referee}
--Kitayama+04: HII regions are governed by an initial slow and weak D-type ionization front followed by a rapid R-type front.
-For there to be complete ionization, the transition between the types is critical.
-They find that in small mass halos, less than $10^6 M_{\odot}$, this critical transition takes place fairly rapidly, allowing for high escape fractions of greater than 80\%.
-In larger mass halos, the ionization front remains as a D-type, and the escape fraction is essentially zero.
-They use a simulation to study these HII regions in similar mass halos as ours and within a similar redshift range.
-Their Fig.
-4 shows the ionizing and LW escape fractions as a function of halo mass for different stellar masses.
-(https://arxiv.org/pdf/astro-ph/0406280.pdf)
-
--Schauer+15: They run simulations of LW escape fractions from P3 stars in $10^5 - 10^7 M_{\odot}$ halos.
-They find escape fractions from 0-85\%, and that H2 shielding by neutral hydrogen also decreases escape fractions compared to escape fractions predicted by only H2 self-shielding.
-Fig.3 shows escape fractions for different models and different P3 stellar masses.
-When H2 shielding by neutral hydrogen is not included, escape fractions are overpredicted.
-(https://arxiv.org/pdf/1506.04796.pdf)
+These papers have been added and referenced in the first paragraph of the caveats section.
 

### 2019-08-21 paper.tex
Edited comments to the referee report and corresponding changes in the paper. This includes the results that the merging resolution does not affect our results and that the Rockstar halo masses and Machacek halo masses are comparable. Most referee comments have been addressed.

@@
 
-If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.
-The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
+If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.\textbf{Our simulation is insensitive to the merging distance between Pop III stars.} The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
 \begin{equation} \label{IMF}
@@
 \textbf{With our chosen IMF (Eq.
-\ref{IMF}), XX, XX, and XX per cent of Pop III stars produce Type II SN, black holes with no SN, and PISNe, respectively.} \jhw{Fill in percentages}
+\ref{IMF}), 59, 36, and 5 per cent of Pop III stars produce Type II SN, black holes with no SN, and PISNe, respectively.}
 
@@
 There are three main causes of this significant variation in mass.
-First, a fraction \jhw{Give number} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.
+First, \textbf{36 per cent} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.
 Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs.
@@
 Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
-\textbf{\citet{Hirano15} used cosmological simulations to study 1540 gas clouds in the early universe to derive the corresponding stellar mass distribution.
+\textbf{\citet{Hirano15} used cosmological simulations to study 1540 gas clouds in the early universe to derive the corresponding primordial stellar mass distribution.
 They find that star forming halos of virial masses $M_{\rm vir} = 2.1 \times 10^5 M_{\odot}$ at z = 30 and $M_{\rm vir} = 9.9 \times 10^5 M_{\odot}$ at z = 10.
@@
 In the evolution of such a halo, it would have started to accumulate gas above these critical masses while also being irradiated by a LW background.
-Afterwards, the collapse will be controled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results.
+Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results.
+\textbf{\citet{Schauer19} quote minimum and average halo masses necessary for the center of the halo to have enough cold dense gas available for star formation for various streaming velocities to study star formation in minihalos and it's relation to the 21-cm absorption feature from the EDGES survey.
+Ranging from 0 $\rm v_{\rm bc}$ to 3.0 $\rm v_{\rm bc}$ in units of $\sigma_{\rm rms}$, they found that the minimum halo mass ranges from $5 \times 10^5 M_{\odot}$ to $10^7 M_{\odot}$, and the average halo mass ranges from about $2 \times 10^6 M_{\odot}$ to $4 \times 10^7 M_{\odot}$.
+Our halo masses generally fall within these ranges, confirming again that streaming velocities would likely not affect our results.}
 

### 2019-08-21 referee.tex
Edited comments to the referee report and corresponding changes in the paper. This includes the results that the merging resolution does not affect our results and that the Rockstar halo masses and Machacek halo masses are comparable. Most referee comments have been addressed.

@@
 
--Resolution testing
--Need to update enzo to John's version with the bug fix.
-
--Restart from DD0029 after pulling it back down. "enzo.exe -r output"
--At the last output, check to see how many stars are in the halo. 
--"our results are insensitive to the star combine radius"
+We have performed resolution tests to determine if our results are resolution dependent.
+The important simulation parameter to see how many stars form within a certain spatial range is called StarClusterCombineRadius.
+Within our original simulation, this parameter was set to 10 pc, meaning that all stars that would form within 10 pc are merged into a single star.
+To make sure that resolution does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc.
+We see the same number of Pop III stars form regardless of the chosen value for the merging parameter.
+Thus, our results are resolution independent.
+This detail has been added to section 2.2.1.
 
@@
 
--Added a bit about what Rockstar is. 
--Machacek halo definition comparison - I have plotted the rockstar mass versus the calculated mass, looks like a solid group of halos lie in a 1:1 relationship, and others are fairly close, apart from a group where the calculated mass is much smaller than the rockstar mass.
-Need to determine why this is.
+A short description of Rockstar has been added in section 3.1, where Rockstar is introduced.
+
+We have compared the mass calculations between Rockstar and Machacek+01 and have found the following results.
+Figure \ref{fig:compare_mass} shows how the Rockstar halo masses and the Machacek+01 method of calculating halo masses.
+To do this calculation, we calculated the virial mass around the center of each halo given by Rockstar by determining the sphere that contains an average overdensity of 200 $\rho_{c}$.
+We see that the halos generally fall on a 1:1 relation, ensuring that the two methods are comparable.
+The halos that have larger calculated masses compared to Rockstar masses are those that are sub-halos.
+This results in a larger radius at the point where the average overdensity of 200 $\rho_{c}$ falls off, and thus a larger calculated mass.
+Within our calculations, we do not consider sub-halos, and take the most massive halo the sub-halo falls within for our analysis.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{images/compare_halo_mass.pdf}
+    \label{fig:compare_mass}
+\end{figure}
 
@@
 I am going to quickly run through my script and find the P3 stars in each dataset which are not in halos.
-
--I am waiting to get this data!
 
@@
 \end{referee}
-I have included the $M_{\rm crit}$ function that Visbal+14 use in their study (their Equation 4) for a redshift of 20.
+We have included the $M_{\rm crit}$ function that Visbal+14 use in their study (their Equation 4) for a redshift of 20 as a solid purple line in Figure 10.
 It appears the Visbal+14 find similar masses as Machacek+01, and when comparing the Machacek+01 for our LWBG and the relation from Visbal+14 at z=20, Visbal+14 find higher halo masses overall.
-
--Visbal+14 provides an equation for Mcrit (eqn.
-4), I have plotted this previously.
-I have plotted this for z=20, and adjusted the trenti line for that redshift as well.
-May have to adjust the plot more.
-I will add detail about the line to the paper.
-(https://arxiv.org/pdf/1402.0882.pdf)
 
@@
 The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here.
-The differences are the inclusion of H2 self-shielding and updated cosmo parameters.
+The differences are the inclusion of H2 self-shielding and updated cosmological parameters.
 
@@
 \end{referee}
--We do set fixed mass limits, between 1 and 300 Msol. I added this detail.
+We do set fixed mass limits, between 1 and 300 $M_{\odot}$. We have added this detail in section 2.2.1.
 
--Plot IMF of P3 stars, find the fractional between each mass range. Watch units, will have to divide by M. Need to figure out how to plot this still.
+59, 36, and 5 per cent of Pop III stars become Type II SN, black holes with no SN, and PISNe respectively. This detail has been added in section 2.2.1.
 
@@
 \end{referee}
--Will have to look at Hartwig+15.
+-Would like to discuss this more in detail with John.
 
@@
 \end{referee}
-This is a tricky detail, and has been added to the caption of of Figure 1.
+This is a tricky detail, and has been added to the caption of Figure 1.
 
@@
 The halo profiles from O'Shea and Norman 2007 are now being used as the \hh{} fraction as a function of radius.
-The plot now shows that the shielding factor increases as a function of mass, since at larger radii, there is less \hh{}.
+The plot now shows that the shielding factor increases as a function of mass, since at larger radii, there is less \hh{}, resulting in a less effective \hh{} shield.
 The overall take away of the plot has not changed.
@@
 \end{referee}
--I have the data for the halo masses from the earliest dataset where star formation ahppens, but it does not line up well with the analytic formula....
+We have added a vertical line at $10^5 M_{\odot}$ to show our halo mass resolution limit. This detail has also been added to the caption.
 
--Added a vertical line at $10^5 M_{\odot}$. Detail also added to caption.
-2-Tried plotting the HMF of the earliest Pop III formation redshift, but I need to collect the HMF of that dataset -- having troubles remembering how this was produced
+-The HMF at z=20 is overshooting the analytic estimate. Need to get together with John to see why.
 
@@
 \end{referee}
-Thank you for your comment. The global LWBG has been added as a red dashed line. Some more detail about the global LW background (solid red line) has also been added.
+Thank you for your comment. The global LWBG has been added as a red dashed line. More detail about the LW background (solid red line) has also been added.
 
@@
 \end{referee}
-Hirano+15 is looking at the distribution of stellar masses to calculate the IMF of p3 stars, which is why we quote them in the introduction. 
--Their Fig. 3 shows the number of halos versus virial mass that host primordial star-forming clouds. 
--Using their eqn. 6 they find Mvir = $2.1 \times 10^5$ at z=30, and Mvir = $9.9 \times 10^5$ at z=10, which they say is in good agreement with their Fig. 3. 
-(https://arxiv.org/pdf/1501.01630.pdf)
+This study has been added and cited in the Comparison section.
 -Should more be added?
@@
 \end{referee}
-This has been adjusted. The point from Yoshida+03 is now a pentagon and is outlined in black, and all symbols have had their edges increased.
+This has been adjusted. The point from Yoshida+03 is now a pentagon and is outlined in black, and all symbols have had their edges increased for visibility.
 
@@
 \end{referee}
--Hirano+18: Investigate the collapse of primordial gas to form P3 stars when the energy transfer between baryon and dark matter fluids (due to non-gravitational scattering) is included.
+The Schauer+19 study has been added to the caveat section.
 

### 2019-08-22 referee.tex
Adjusted some referee responses.

@@
 
-We have performed resolution tests to determine if our results are resolution dependent.
-The important simulation parameter to see how many stars form within a certain spatial range is called StarClusterCombineRadius.
-Within our original simulation, this parameter was set to 10 pc, meaning that all stars that would form within 10 pc are merged into a single star.
-To make sure that resolution does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc.
+There was an error in the original draft of our paper, stating that "If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells." It should instead say "within 10 pc", not "within 1 pc".
+This error has been corrected.
+
+The 10 pc quoted above is a parameter called StarClusterCombineRadius, and controls how many stars form within a certain spatial range.
+Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star.
+To make sure that this value does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc.
+The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{7.7} M_{\odot}$ at the end of the run.
+The simulations run for a total of 10 Myr.
 We see the same number of Pop III stars form regardless of the chosen value for the merging parameter.
-Thus, our results are resolution independent.
+Thus, our results are independent of this value.
 This detail has been added to section 2.2.1.
@@
 We have compared the mass calculations between Rockstar and Machacek+01 and have found the following results.
-Figure \ref{fig:compare_mass} shows how the Rockstar halo masses and the Machacek+01 method of calculating halo masses.
+Figure \ref{fig:compare_mass} below shows how the Rockstar halo masses and the Machacek+01 method of calculating halo masses compare.
 To do this calculation, we calculated the virial mass around the center of each halo given by Rockstar by determining the sphere that contains an average overdensity of 200 $\rho_{c}$.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/compare_halo_mass.pdf}
+	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{images/compare_halo_mass.pdf}
     \label{fig:compare_mass}

### 2019-08-22 referee.tex
Adjusted referee responses.

@@
 \usepackage{mdframed}
+\usepackage{float}
 \parskip=10pt
@@
 
-1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo.
+A -- 1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo.
 This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo.
@@
 \begin{referee}
-2) The authors select their haloes by the halo finding algorithm Rockstar.
+B -- 2) The authors select their haloes by the halo finding algorithm Rockstar.
 They should add a bit of information on that code (is it fof or subfind-like?).
@@
 
-Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper.
+C -- Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper.
 The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.
 
-In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo.
+D -- In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo.
 The baryon fraction varies with redshift.
@@
 
-\begin{figure}
-	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{images/compare_halo_mass.pdf}
+\begin{figure}[H]
+	\centering
+	\includegraphics[keepaspectratio=true, scale=0.5]{images/compare_halo_mass.pdf}
     \label{fig:compare_mass}
@@
 
-The authors should state at one point in the paper for which properties they use comoving or physical units.
+E -- The authors should state at one point in the paper for which properties they use comoving or physical units.
 \end{referee}
@@
 
-The authors write that Pop III star formation is generally more massive.
+F -- The authors write that Pop III star formation is generally more massive.
 While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
@@
 \begin{referee}
-The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14).
+G -- The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14).
 \end{referee}
@@
 \begin{referee}
-The authors cite the well-known study from Machacek+01.
+H -- The authors cite the well-known study from Machacek+01.
 However, a more recent result would be from the study by Visbal+14, giving a lower mass limit.
@@
 
-In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
+I -- In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
 \end{referee}
@@
 \begin{referee}
-The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
+J -- The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
 \end{referee}
@@
 \begin{referee}
-Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
+K -- Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
 \end{referee}
@@
 \begin{referee}
-What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
+L -- What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
 \end{referee}
@@
 \begin{referee}
-Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
+M -- Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
 \end{referee}
@@
 \begin{referee}
-Do the authors set fixed mass limits to the IMF and if yes, which are they?
+N -- Do the authors set fixed mass limits to the IMF and if yes, which are they?
 If not, which is the highest / lowest mass they find in their random sampling?
@@
 \begin{referee}
-One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
+O -- One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
 \end{referee}
@@
 \begin{referee}
-In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
+P -- In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
 \end{referee}
@@
 \begin{referee}
-The analytic calculation of the shielding factor is a nice property of the paper.
+Q -- The analytic calculation of the shielding factor is a nice property of the paper.
 However, assuming a constant H2 fraction seems not appropriate.
@@
 
-Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction.
+R -- Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction.
 In addition, the authors could provide a line or an arrow to show their halo mass resolution limit.
@@
 \begin{referee}
-Figure 3 looks very nice. It would be helpful if an additional line that only 
+S -- Figure 3 looks very nice. It would be helpful if an additional line that only 
 provides the global LWBG (in units of J21) was included.
@@
 \begin{referee}
-The authors find no correlation between the host halo mass and the Lyman-Werner background intensity.
+T -- The authors find no correlation between the host halo mass and the Lyman-Werner background intensity.
 However, they only look at the LWBG flux at the time of Pop III formation - is there maybe a correlation between the time integrated LW flux?
@@
 \begin{referee}
-Figures 7 and 8 show very nice histograms as an additional panel on the right.  I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
+U -- Figures 7 and 8 show very nice histograms as an additional panel on the right.  I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
 \end{referee}
@@
 
-The authors give three reasons for the halo mass spread.
+V -- The authors give three reasons for the halo mass spread.
 Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
@@
 \begin{referee}
-One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
+W -- One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
 \end{referee}
@@
 \begin{referee}
-In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different symbol / colour.
+X -- In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different symbol / colour.
 \end{referee}
@@
 \begin{referee}
-Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
+Y -- Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
 \end{referee}
@@
 \begin{referee}
-The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction).
+Z -- The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction).
 While they cite some older work, they however fail to compare to more recent work eg by Hirano+18 or Schauer+19 (who do perform a systematic study not only based on a few, single haloes).

### 2019-08-27 referee.tex
Adding some comments and minor changes to the response

@@
 The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{7.7} M_{\odot}$ at the end of the run.
-The simulations run for a total of 10 Myr.
+\jhw{Double check the mass.
+Looking at the projections of the halo, its virial radius is about 100 pc, which corresponds to a halo mass around $10^6 M_\odot$.} The simulations run for a total of 10 Myr.
 We see the same number of Pop III stars form regardless of the chosen value for the merging parameter.
@@
 A short description of Rockstar has been added in section 3.1, where Rockstar is introduced.
+
+\jhw{The referee is asking how our halo mass calculation with $200\rho_c$ compares with the $200\rho_m$ definition in Machacek+01.
+I think a better figure would show the halo masses with these two definitions in each axis.
+To make the differences more clear, I would add a subpanel that shows the ratio between the two mass calculations.
+I would also calculate the mean ratio of the masses to see how it differs to the analytical expectation if we consider an isothermal sphere, whose mass enclosed $M_{\rm enc} \propto r$ and density $\rho \propto r^{-2}$, i.e.
+the virial radius will be larger in the $200\rho_m$ definition and thus the virial masses will be larger in Machacek+01.}
 
@@
 \end{referee}
-RP stands for radiation pressure in Wise+12, not rare peak.
+
+\jhw{This is good.}
+
+RP stands for radiation pressure in Wise+12, not rare peak of the Renaissance Simulations (Xu et al.
+2016).
 The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here.

### 2019-08-27 paper.tex
Added note about how many Pop III stars form outside of halos.
Addressing atomic cooling halo point

@@
 The total mass is subsequently used in our analysis.
-We also take the center and virial radius from the \rockstar{} halo catalog.
-A small percentage of Pop III stars do not form in a halo identified by \rockstar{}.
+\textbf{For stars that form in subhalos identified by \rockstar{}, we assign the parent halo mass as the host halo mass.
+There is one interesting case that we exclude from our analysis, where the parent halo is above the atomic cooling limit, because the radiative cooling physics are different in this regime and is not sensitive to a LW background.
+Here seven Pop III stars form in a pristine $10^6 \msun$ subhalo inside of a $3 \times 10^8 \msun$ atomic cooling parent halo.
+Because this object only contains 1 per cent of the Pop III stars, it only shifts our average halo masses by a similar amount.} We also take the center and virial radius from the \rockstar{} halo catalog.
+\textbf{About 1\%} of Pop III stars do not form in a halo identified by \rockstar{}.
 Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$.

### 2019-08-27 referee.tex
Addressing atomic cooling halo point

@@
 How do these different halo masses compare?
-
-C -- Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper.
-The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.
-
-D -- In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo.
-The baryon fraction varies with redshift.
-Please give an estimate by how much this influences the halo masses used here.
 \end{referee}
@@
 
-\jhw{The referee is asking how our halo mass calculation with $200\rho_c$ compares with the $200\rho_m$ definition in Machacek+01.
+\jhw{The referee is asking how our halo mass calculation with Rockstar (with the $\Omega_{\rm DM} / \Omega_{\rm M}$ correction) compares with the $200\rho_m$ definition in Machacek+01.
 I think a better figure would show the halo masses with these two definitions in each axis.
@@
 I would also calculate the mean ratio of the masses to see how it differs to the analytical expectation if we consider an isothermal sphere, whose mass enclosed $M_{\rm enc} \propto r$ and density $\rho \propto r^{-2}$, i.e.
-the virial radius will be larger in the $200\rho_m$ definition and thus the virial masses will be larger in Machacek+01.}
+the virial radius will be larger in the $200\rho_m$ definition than the $200\rho_c$ one, and thus the virial masses will be larger in Machacek+01.}
 
@@
 We see that the halos generally fall on a 1:1 relation, ensuring that the two methods are comparable.
-The halos that have larger calculated masses compared to Rockstar masses are those that are sub-halos.
+The halos that have larger calculated masses compared to Rockstar masses are those that are subhalos.
 This results in a larger radius at the point where the average overdensity of 200 $\rho_{c}$ falls off, and thus a larger calculated mass.
-Within our calculations, we do not consider sub-halos, and take the most massive halo the sub-halo falls within for our analysis.
+Within our calculations, we do not consider subhalos, and take the most massive halo the subhalo falls within for our analysis.
 
-\begin{figure}[H]
+\begin{figure}[ht!]
 	\centering
-	\includegraphics[keepaspectratio=true, scale=0.5]{images/compare_halo_mass.pdf}
-    \label{fig:compare_mass}
+	\includegraphics[keepaspectratio=true, scale=0.4]{images/compare_halo_mass.pdf}
+  \caption{\label{fig:compare_mass} \jhw{Include caption.}}
 \end{figure}
 
--Exclusion of atomic cooling haloes - we excluded these because of a bug in our code... how to explain this without simply saying that?
+\begin{referee}
+C -- Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper.
+The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.
+\end{referee}
+
+We apologize for not being more clear on this point.
+As seen in Figure \ref{fig:compare_mass}, there are seven stars that form in a halo with $M_{\rm halo} > 10^8 M_\odot$ but are actually hosted by a subhalo that hasn't been enriched yet.
+This is an interesting case within itself.
+We might follow up on this object in a later study because it's outside the scope of the paper.
+Because we take the parent halo mass as the host halo mass, we did not include these stars in the analysis because the parent halo mass is not representative of the cooling processes inside of the subhalo.
+Because this is a rare event in our simulation (7 out of 688 Pop III stars), it does not shift the average halo mass by a significant amount.
+We have added some clarifying text to the first paragraph of the Section 3.1.
+
+\begin{referee}
+D -- In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo.
+The baryon fraction varies with redshift.
+Please give an estimate by how much this influences the halo masses used here.
+\end{referee}
 
@@
 \end{referee}
-This has been clarified at the end of the second paragraph in the Simulation Setup section.
+We have clarified this point at the end of the second paragraph in the Simulation Setup section.
 
@@
 \end{referee}
-These studies have been mentioned and cited in the introcution.
+
+This is a good point about low-mass Pop III stars, and we have included these references in the introduction.
 
@@
 \end{referee}
-This study has been mentioned and cited in the introduction.
+
+We have mentioned X-ray heating in the introduction and cited Jeon+14.
 
@@
 
-RP stands for radiation pressure in Wise+12, not rare peak of the Renaissance Simulations (Xu et al.
-2016).
+RP stands for radiation pressure in Wise+12, not rare peak of the Renaissance Simulations (Xu+ 2016).
 The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here.
@@
 \end{referee}
-This has been adjusted. The point from Yoshida+03 is now a pentagon and is outlined in black, and all symbols have had their edges increased for visibility.
+We have modified Figure 10 to be more clear. The point from Yoshida+03 is now a pentagon and is outlined in black, and all symbols have had their edges increased for visibility.
 

### 2019-09-23 referee.tex
minor note
Adding some notes to the report (just to keep track of my thoughts)
adding changes to fix merge problem.

@@
 	\centering
-	\includegraphics[keepaspectratio=true, scale=0.4]{images/compare_halo_mass.pdf}
-  \caption{\label{fig:compare_mass} \jhw{Include caption.}}
+	\includegraphics[keepaspectratio=true, scale=0.4]{images/compare_mass_ratio.pdf}
+  \caption{\label{fig:compare_mass} The Rockstar mass multiplied by $\Omega_{\rm M} / \Omega_{\rm DM}$ versus the Machacek+01 method of calculating halo mass.
+The bottom panel is the ratio of the Rockstar mass to the calculated mass versus the calculated mass.
+The Rockstar mass tends to lie just above the 1:1 relation, implying that the halo masses are comparable.
+For the case where the calculated mass is much larger than the rockstar mass, this occurs when the halos are subhalos of a larger halo.}
 \end{figure}
@@
 
--Fraction of halos that halo Pop III stars forming outside the halos: Turns out I was not able to get this data as easily as I thought.
-I am going to quickly run through my script and find the P3 stars in each dataset which are not in halos.
+1\% of Pop III stars form outside the halo. This has been added to the Population III Host Halo Masses subsection.
+
+Figure \ref{fig:avg_baryon_fraction} show the average baryon fraction for each halo as a function of the halo mass. The cosmic baryon fraction is shown as a solid black line.
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[keepaspectratio=true, scale=0.4]{images/avg_baryon_fraction.pdf}
+  \caption{\label{fig:avg_baryon_fraction} Average baryon fraction within each halo versus the corresponding halo mass. The solid line indicates the cosmic baryon fraction of 0.154.}
+\end{figure}
 

### 2019-09-23 referee.tex
Fixed halo mass for resultion testing.

@@
 To make sure that this value does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc.
-The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{7.7} M_{\odot}$ at the end of the run.
-\jhw{Double check the mass.
-Looking at the projections of the halo, its virial radius is about 100 pc, which corresponds to a halo mass around $10^6 M_\odot$.} The simulations run for a total of 10 Myr.
+The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ at the end of the run.
+The simulations run for a total of 10 Myr.
 We see the same number of Pop III stars form regardless of the chosen value for the merging parameter.
@@
 A short description of Rockstar has been added in section 3.1, where Rockstar is introduced.
+
+\jhw{Readdress this point, using that $\rho_c = \rho_m$ at high redshifts.}
 
@@
 
+\jhw{I can answer this point.}
+
 \begin{referee}
@@
 -The HMF at z=20 is overshooting the analytic estimate. Need to get together with John to see why.
+
+\jhw{We are still investigating this issue. Calculate the matter power spectrum and compare with the analytic expectation to see if the simulation was initialized with some odd mode.}
 

### 2019-09-23 referee.tex
Added a note about the Hartwig+15 paper.

@@
 
+-From Tilmans paper, they find that Jcrit, which corresponds to the point where if a halo is exposed to a flux above that value then it provides conditions for supermassive star formation, is almost half as small as the jeans length approach to calculating Jcrit.
+They use the Wolcott-Green shielding factor that we use, but they use a different method for calculating the column density.
+Figure 5 shows the differences.
+But since they are finding that even more halos would be allowed to form star formation, then (if I'm getting this correctly), we would be underestimating the amount of potential star formation sites.
+
 \jhw{I can answer this point.}

### 2019-10-02 paper.tex
Adding response about Doppler shifting (Hartwigs paper), baryon fraction, and mass comparison.

@@
 This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding.
+\textbf{\citet{Hartwig15} use the same shielding factor equation from \citet{Wolcott11}, but implement an improved calculation of the column density to incorporate the relative gas velocities and geometries of the halo.
+This method takes into account the Doppler-shifting of spectral lines, which would affect \hh{} shielding.
+With the improved calculation of the column density, they find that the shielding factor is larger for gas at higher temperatures than when the shielding factor is calculated for an average column density for the halo, meaning that self-shielding is generally less efficient for higher temperatures.
+In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our halos are less massive, and at lower temperatures.
+Our calculation of the shielding factor is still valid for the temperature range of our halos, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.}
 

### 2019-10-02 referee.tex
Adding response about Doppler shifting (Hartwigs paper), baryon fraction, and mass comparison.

--- 2019-09-23 referee.tex
@@
 
-\jhw{Readdress this point, using that $\rho_c = \rho_m$ at high redshifts.}
-
-\jhw{The referee is asking how our halo mass calculation with Rockstar (with the $\Omega_{\rm DM} / \Omega_{\rm M}$ correction) compares with the $200\rho_m$ definition in Machacek+01.
-I think a better figure would show the halo masses with these two definitions in each axis.
-To make the differences more clear, I would add a subpanel that shows the ratio between the two mass calculations.
-I would also calculate the mean ratio of the masses to see how it differs to the analytical expectation if we consider an isothermal sphere, whose mass enclosed $M_{\rm enc} \propto r$ and density $\rho \propto r^{-2}$, i.e.
-the virial radius will be larger in the $200\rho_m$ definition than the $200\rho_c$ one, and thus the virial masses will be larger in Machacek+01.}
-
-We have compared the mass calculations between Rockstar and Machacek+01 and have found the following results.
-Figure \ref{fig:compare_mass} below shows how the Rockstar halo masses and the Machacek+01 method of calculating halo masses compare.
-To do this calculation, we calculated the virial mass around the center of each halo given by Rockstar by determining the sphere that contains an average overdensity of 200 $\rho_{c}$.
-We see that the halos generally fall on a 1:1 relation, ensuring that the two methods are comparable.
-The halos that have larger calculated masses compared to Rockstar masses are those that are subhalos.
-This results in a larger radius at the point where the average overdensity of 200 $\rho_{c}$ falls off, and thus a larger calculated mass.
-Within our calculations, we do not consider subhalos, and take the most massive halo the subhalo falls within for our analysis.
-
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[keepaspectratio=true, scale=0.4]{images/compare_mass_ratio.pdf}
-  \caption{\label{fig:compare_mass} The Rockstar mass multiplied by $\Omega_{\rm M} / \Omega_{\rm DM}$ versus the Machacek+01 method of calculating halo mass.
-The bottom panel is the ratio of the Rockstar mass to the calculated mass versus the calculated mass.
-The Rockstar mass tends to lie just above the 1:1 relation, implying that the halo masses are comparable.
-For the case where the calculated mass is much larger than the rockstar mass, this occurs when the halos are subhalos of a larger halo.}
-\end{figure}
+We have compared the mass calculations between Rockstar and Machacek+01 and have found that the masses are comparable.
+The difference between Rockstar halo masses and the Machacek+01 halo mass definition varies by a few percent.
+At high redshifts, when Pop III stars are forming, $\rho_c = \rho_m$, so our calculations are not affected by this difference, and allows the two mass definitions to be directly compared.
 
@@
 
-1\% of Pop III stars form outside the halo. This has been added to the Population III Host Halo Masses subsection.
+1\% of Pop III stars form in a halo not identified by Rockstar.
+This has been added to the Population III Host Halo Masses subsection.
+To be clear, Pop III stars should not be forming outside of halos.
+This small percentage of Pop III stars are forming in halos, but in halos not identified by Rockstar.
 
-Figure \ref{fig:avg_baryon_fraction} show the average baryon fraction for each halo as a function of the halo mass. The cosmic baryon fraction is shown as a solid black line.
+Figure \ref{fig:avg_baryon_fraction} shows the average baryon fraction for each halo as a function of the halo mass. The cosmic baryon fraction is shown as a solid black line.
+
+The baryon fraction varies with time at the lowest mass scales, just above the cosmological jeans mass, around $10^{4} M_{\odot}$.
+In our work, we are looking at halos above that value by about a factor of 20.
+At this point, the halos have had time to collect baryons.
+In general, the baryon fraction is dependent on redshift in our work due to feedback, not cosmological effects.
+This results in a range of average baryon fractions for halo masses throughout our simulation.
+In Figure \ref{fig:avg_baryon_fraction}, the halos with smaller masses tend to have low average baryon fractions due to resolution effects and feedback.
 
@@
 \end{referee}
--Would like to discuss this more in detail with John.
 
-\jhw{I can answer this point.}
+In Hartwig+15, they take into account the Doppler-shifting of spectral lines with an improved calculation of the column densities, but use the same shielding factor as we do.
+They find that shielding is generally less efficient at higher temperatures.
+In our work, because our halos are less massive, the temperatures are typically $10^{3}$ K, which looking at the Figure 5, lies close to the 1:1 line.
+The shielding factor as calculated in our work will therefore not vary significantly compared to the full treatment of the column density, so we do not expect this to be a problem.
+
+A brief desription of this has been added to the \hh{} Self-Shielding section.
 

### 2019-10-07 referee.tex
Adjusted some comments - but finalized my comments to the referee.

@@
 
-There was an error in the original draft of our paper, stating that "If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells." It should instead say "within 10 pc", not "within 1 pc".
+There was an error in the original draft of our paper, stating that ``If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells." It should instead say ``within 10 pc", not ``within 1 pc".
 This error has been corrected.
@@
 This detail has been added to section 2.2.1.
+
+--May still need to answer the questions ``Which is the motivation for the length scale of 1 pc?''
 
@@
 We apologize for not being more clear on this point.
-As seen in Figure \ref{fig:compare_mass}, there are seven stars that form in a halo with $M_{\rm halo} > 10^8 M_\odot$ but are actually hosted by a subhalo that hasn't been enriched yet.
-This is an interesting case within itself.
+\textbf{As seen in Figure \ref{fig:compare_mass}, there are seven stars that form in a halo with $M_{\rm halo} > 10^8 M_\odot$ but are actually hosted by a subhalo that hasn't been enriched yet.
+\textit{DS -- this figure was removed for simplicity}} This is an interesting case within itself.
 We might follow up on this object in a later study because it's outside the scope of the paper.
@@
 \end{referee}
-
-\jhw{This is good.}
 
@@
 They find that shielding is generally less efficient at higher temperatures.
-In our work, because our halos are less massive, the temperatures are typically $10^{3}$ K, which looking at the Figure 5, lies close to the 1:1 line.
+In our work, because our halos are less massive, the temperatures are typically $10^{3}$ K, which looking at their Figure 5, lies close to the 1:1 line.
 The shielding factor as calculated in our work will therefore not vary significantly compared to the full treatment of the column density, so we do not expect this to be a problem.
@@
 This study has been added and cited in the Comparison section.
--Should more be added?
+\textbf{-Should more be added?}
 

### 2019-10-09 paper.tex
Adding response to HMF comment and added a line in the paper.

@@
 After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box.
-These stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
+\textbf{At this time, $z = 27$, there are only 6 halos that are above our mass resolution limit.} These \textbf{Pop III} stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
 Metal-enriched star formation begins to take place as soon as enough metals are present within a halo.

### 2019-10-09 referee.tex
Adding response to HMF comment and added a line in the paper.

@@
 
--The HMF at z=20 is overshooting the analytic estimate. Need to get together with John to see why.
-
-\jhw{We are still investigating this issue. Calculate the matter power spectrum and compare with the analytic expectation to see if the simulation was initialized with some odd mode.}
+At the time of the first star formation, our simulation only marginally resolves the smallest main halos, there is only a total of 6 halos above our resolution limit of $10^{5} M_{\odot}$.
+Because of this, there are not enough halos to accurately represent the HMF at that time, which is why we have not added that to Figure 2.
+We have added this detail to the first paragraph of the Results section.
 

### 2019-10-21 referee.tex
Revising response to the first issue

@@
 
-The 10 pc quoted above is a parameter called StarClusterCombineRadius, and controls how many stars form within a certain spatial range.
-Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star.
-To make sure that this value does not affect our results, we have run simulations for a range of this parameter, namely from 0.625 pc to the original 10 pc.
-The simulations are a 1 comoving Mpc$^3$ box, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ at the end of the run.
-The simulations run for a total of 10 Myr.
+The 10 pc quoted above is a parameter called \texttt{StarClusterCombineRadius}, and controls whether newly formed star particles will be merged within a certain radius.
+Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star particle.
+The 10 kyr timescale originates from the approximate protostellar timescale when the ionizing luminosity is linearly increased to its ZAMS value.
+We chose a value of 10 pc because it corresponds to the approximate radius where H$_2$ formation allows the gas to cool from the halo's virial temperature (e.g.
+Yoshida et al.
+2006).
+
+To ensure that this value does not affect our results, we have run a suite of test simulations for a range of this parameter, namely from 0.625 pc, increasing by a factor of two up to the original 10 pc.
+The simulations are a 1 comoving Mpc$^3$ box with the same mass and spatial resolution and physics set, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ at the end of the run.
+The simulations run for a total of 10 Myr after the first star forms.
 We see the same number of Pop III stars form regardless of the chosen value for the merging parameter.
-Thus, our results are independent of this value.
-This detail has been added to section 2.2.1.
-
---May still need to answer the questions ``Which is the motivation for the length scale of 1 pc?''
+Thus, we conclude that our results are independent of this value.
+We have added these details to Section 2.2.1.
 

### 2019-10-21 referee.tex
Revised response B

@@
 The 10 pc quoted above is a parameter called \texttt{StarClusterCombineRadius}, and controls whether newly formed star particles will be merged within a certain radius.
-Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star particle.
+Within the presented simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star particle.
 The 10 kyr timescale originates from the approximate protostellar timescale when the ionizing luminosity is linearly increased to its ZAMS value.
@@
 
-To ensure that this value does not affect our results, we have run a suite of test simulations for a range of this parameter, namely from 0.625 pc, increasing by a factor of two up to the original 10 pc.
-The simulations are a 1 comoving Mpc$^3$ box with the same mass and spatial resolution and physics set, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ at the end of the run.
-The simulations run for a total of 10 Myr after the first star forms.
-We see the same number of Pop III stars form regardless of the chosen value for the merging parameter.
+To ensure that this value does not affect our results, we have run a set of simulations that tests the robustness of our results on this parameter.
+Specifically, we have varied it from 0.625 pc to the original 10 pc, increasing the radius by a factor of two in each simulation.
+The simulations have the same boxsize of 1 comoving Mpc$^3$ with the same mass/spatial resolution and physics set, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ that collapses at $z = 22$.
+We run the  simulations for a total of 10 Myr after the first star forms.
+We see the same number of Pop III star particles form regardless of the chosen value for the merging parameter.
 Thus, we conclude that our results are independent of this value.
@@
 
-A short description of Rockstar has been added in section 3.1, where Rockstar is introduced.
+We have added a short description of Rockstar to Section 3.1, where it is introduced.
 
-We have compared the mass calculations between Rockstar and Machacek+01 and have found that the masses are comparable.
-The difference between Rockstar halo masses and the Machacek+01 halo mass definition varies by a few percent.
-At high redshifts, when Pop III stars are forming, $\rho_c = \rho_m$, so our calculations are not affected by this difference, and allows the two mass definitions to be directly compared.
+We have also compared the mass calculations between Rockstar and Machacek et al.
+(2001) and have found that the masses are comparable.
+The difference between Rockstar halo masses and the Machacek et al.
+halo mass definition varies by a few percent.
+At very high redshifts when Pop III stars are forming, the mass density is equivalent to the critical density ($\rho_c = \rho_m$), so our calculations are not affected by this difference, and allows the two mass definitions to be directly compared.
 

### 2019-10-21 referee.tex
Revising points C and D

@@
 We apologize for not being more clear on this point.
-\textbf{As seen in Figure \ref{fig:compare_mass}, there are seven stars that form in a halo with $M_{\rm halo} > 10^8 M_\odot$ but are actually hosted by a subhalo that hasn't been enriched yet.
-\textit{DS -- this figure was removed for simplicity}} This is an interesting case within itself.
+There are seven stars that form in an atomic cooling halo but are actually hosted by a subhalo that hasn't been enriched yet.
+This is an interesting case within itself.
 We might follow up on this object in a later study because it's outside the scope of the paper.
@@
 
-1\% of Pop III stars form in a halo not identified by Rockstar.
-This has been added to the Population III Host Halo Masses subsection.
+There are 1\% of Pop III stars that form in a halo not identified by Rockstar.
 To be clear, Pop III stars should not be forming outside of halos.
-This small percentage of Pop III stars are forming in halos, but in halos not identified by Rockstar.
+This small percentage of Pop III stars are forming in halos but in halos not identified by Rockstar.
+We have added these details to the ``Population III Host Halo Masses" subsection.
 
-Figure \ref{fig:avg_baryon_fraction} shows the average baryon fraction for each halo as a function of the halo mass. The cosmic baryon fraction is shown as a solid black line.
+\jhw{Need to double-check baryon fraction figure.}
 
-The baryon fraction varies with time at the lowest mass scales, just above the cosmological jeans mass, around $10^{4} M_{\odot}$.
-In our work, we are looking at halos above that value by about a factor of 20.
-At this point, the halos have had time to collect baryons.
-In general, the baryon fraction is dependent on redshift in our work due to feedback, not cosmological effects.
+Figure \ref{fig:avg_baryon_fraction} shows the average baryon fraction for each halo as a function of the halo mass.
+The cosmic baryon fraction is shown as a solid black line.
+The baryon fraction only should smoothly increase with time as it grows from the cosmological Jeans mass, around $10^{4} M_{\odot}$.
+Our simulations do not resolve this mass scale, but the baryon fraction will be slightly lower than the cosmic value ($\Omega_b/\Omega_m$) in the smallest resolved halos ($2 \times 10^5 M_\odot$ are sampled with 100 particles).
+However above this mass scale, the baryon fraction will greatly vary with time due to feedback, not cosmological effects.
 This results in a range of average baryon fractions for halo masses throughout our simulation.
-In Figure \ref{fig:avg_baryon_fraction}, the halos with smaller masses tend to have low average baryon fractions due to resolution effects and feedback.
+In Figure \ref{fig:avg_baryon_fraction}, the halos with smaller masses tend to have low average baryon fractions due to resolution at the very low-mass end and feedback once they have hosted star formation.
 

### 2019-10-21 referee.tex
Addressing method points in the referee response

@@
 
-Figure \ref{fig:avg_baryon_fraction} shows the average baryon fraction for each halo as a function of the halo mass.
+Figure \ref{fig:avg_baryon_fraction} shows the average baryon fraction for each halo as a function of the halo mass at the final redshift.
 The cosmic baryon fraction is shown as a solid black line.
@@
   \includegraphics[keepaspectratio=true, scale=0.4]{images/avg_baryon_fraction.pdf}
-  \caption{\label{fig:avg_baryon_fraction} Average baryon fraction within each halo versus the corresponding halo mass. The solid line indicates the cosmic baryon fraction of 0.154.}
+  \caption{\label{fig:avg_baryon_fraction} Average baryon fraction within each halo versus the corresponding halo mass at the final redshift.
+The solid line indicates the cosmic baryon fraction of $\Omega_b / \Omega_m = 0.154$.}
 \end{figure}
@@
 
-We have mentioned X-ray heating in the introduction and cited Jeon+14.
+We now include X-ray heating in the introduction and cited Jeon et al. (2014).
 
@@
 \end{referee}
-We have included the $M_{\rm crit}$ function that Visbal+14 use in their study (their Equation 4) for a redshift of 20 as a solid purple line in Figure 10.
-It appears the Visbal+14 find similar masses as Machacek+01, and when comparing the Machacek+01 for our LWBG and the relation from Visbal+14 at z=20, Visbal+14 find higher halo masses overall.
+
+We have included the $M_{\rm crit}$ function that Visbal et al.
+(2014) use in their study (their Equation 4) for $z=20$ as a solid purple line in Figure 10.
+The Visbal et al.
+relation give similar masses as Machacek et al.
+(2001).
+But when we input the LW background utilized in our study, the Visbal et al.
+relation give higher halo masses overall when compared to Machacek et al.
 
@@
 
-RP stands for radiation pressure in Wise+12, not rare peak of the Renaissance Simulations (Xu+ 2016).
+RP stands for the ``radiation pressure" simulation from Wise et al.
+(2012), not rare peak of the Renaissance Simulations (Xu et al.
+2016).
 The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here.
@@
 At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.
-Solving for the density in the Jeans length equation, given a typical temperature $T=300$~K with primordial cooling and a Jeans Length of $8 \times \textrm{dx}$, we obtain a number density $n = 5.7 \times 10^4 \cubecm$.
+Solving for the density in the Jeans length equation, given a typical temperature $T=300$~K with primordial cooling and a Jeans Length of $8 \times \textrm{dx}$, we obtain a number density $n = 5.7 \times 10^4~\cubecm$.
 This number density does not exactly match the chosen density criterion because some oversight when setting up the simulation.
@@
 2007; Omukai et al.
-2010) at the density threshold of $10^6 \cubecm$.
+2010) at the density threshold of $10^6~\cubecm$.
 It is a number fraction.
-We have added to Section 2.2.1 to reflect this detail.
+We have added this detail to Section 2.2.1 to reflect this detail.
 
@@
 But in the presence of an extremely strong Lyman-Werner flux from a nearby ($\sim$1 pc) star, star formation is unlikely to occur in the shell because it is irradiated and not self-gravitating.
+
 The last question is an interesting question, but it is difficult to determine because these conditions (high density but low H$_2$ fractions) are short-lived just after star formation.
@@
 \end{referee}
-We do set fixed mass limits, between 1 and 300 $M_{\odot}$. We have added this detail in section 2.2.1.
 
-59, 36, and 5 per cent of Pop III stars become Type II SN, black holes with no SN, and PISNe respectively. This detail has been added in section 2.2.1.
+In our simulation, we consider a fixed mass limit between 1 and 300 $M_{\odot}$ of the IMF.
+We have added this detail in section 2.2.1.
+Given this IMF, 59, 36, and 5 per cent of Pop III stars become Type II SN, black holes with no SN, and PISNe, respectively.
+We have added this detail to Section 2.2.1.
 
@@
 
-In Hartwig+15, they take into account the Doppler-shifting of spectral lines with an improved calculation of the column densities, but use the same shielding factor as we do.
+Hartwig et al.
+(2015) take into account the Doppler-shifting of spectral lines with an improved calculation of the column densities but use the same shielding factor as we do.
 They find that shielding is generally less efficient at higher temperatures.
-In our work, because our halos are less massive, the temperatures are typically $10^{3}$ K, which looking at their Figure 5, lies close to the 1:1 line.
+In our work, because our halos are less massive, the temperatures are typically around $10^{3}$ K, which looking at their Figure 5, lies close to the 1:1 line.
 The shielding factor as calculated in our work will therefore not vary significantly compared to the full treatment of the column density, so we do not expect this to be a problem.
-
-A brief desription of this has been added to the \hh{} Self-Shielding section.
+We have added a brief desription of this effect to the \hh{} Self-Shielding section.
 
@@
 \end{referee}
-This is a tricky detail, and has been added to the caption of Figure 1.
+
+We thank the referee for pointing out this tricky detail, and we have added it to the caption of Figure 1.
 
@@
 \end{referee}
+
 This is a good point, and the plot has been adjusted accordingly.
-The halo profiles from O'Shea and Norman 2007 are now being used as the \hh{} fraction as a function of radius.
+We chose to use the \hh{} radial profiles from O'Shea and Norman (2007) because of the variety of halos and high resolution.
 The plot now shows that the shielding factor increases as a function of mass, since at larger radii, there is less \hh{}, resulting in a less effective \hh{} shield.
-The overall take away of the plot has not changed.
+The overall takeaway of the plot has not changed.
 

### 2019-10-21 referee.tex
Addressed results responses

@@
 
-At the time of the first star formation, our simulation only marginally resolves the smallest main halos, there is only a total of 6 halos above our resolution limit of $10^{5} M_{\odot}$.
-Because of this, there are not enough halos to accurately represent the HMF at that time, which is why we have not added that to Figure 2.
-We have added this detail to the first paragraph of the Results section.
+At the time of the first star formation, our simulation only marginally resolves (with 50 particles) the smallest minihalos that can host Pop III star formation.
+Thus there is only a total of 6 halos above our resolution limit of $10^{5} M_{\odot}$.
+Because of this lack of data, there are not enough halos to accurately represent the halo mass function at that time, which is why we have not added that to Figure 2.
+However we have added some details about the number of halos and the redshift of the first star formation with the analytical expectation (one $10^5~M_\odot$ halo per comoving Mpc$^3$) to the first paragraph of the Results section.
 
@@
 \end{referee}
-Thank you for your comment. The global LWBG has been added as a red dashed line. More detail about the LW background (solid red line) has also been added.
+Thank you for your comment. We have added the global LW background as a red dashed line. We have also added more details about the LW background (solid red line) to the text.
 
@@
 \end{referee}
-While the time integrated LW flux would be interesting to follow, and may provide some further insight to what we are exploring, this would be difficult to calculate.
+While the time integrated LW flux would be interesting to follow, and may provide some further insight to what we are exploring, this would be difficult to calculate in post-processing with the information contained in the datasets.
 It would require constant tracking of halos through time to calculate the time integrated LW flux.
@@
 \end{referee}
-The side histogram has been added to Figure 9.
+We agree that this addition is useful and have added a side histogram to Figure 9.
 

### 2019-10-21 referee.tex
Finished revising responses

@@
 \end{referee}
-
 This is an interesting question, but it is outside the scope of this paper.
@@
 \end{referee}
-This study has been added and cited in the Comparison section.
-\textbf{-Should more be added?}
+We have added the results from Hirano et al. (2015) to our comparison to other work in the discussion.
 
@@
 \end{referee}
-These papers have been added and referenced in the first paragraph of the caveats section.
+We have added and cited these papers in the first paragraph of the caveats subsection.
 
@@
 \end{referee}
-The Schauer+19 study has been added to the caveat section.
+We have also added the Schauer et al. (2019) study to the caveats subsection.
 

### 2019-10-21 referee.tex
Formatting change (no indents in first para)

@@
 \end{referee}
-
 There was an error in the original draft of our paper, stating that ``If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells." It should instead say ``within 10 pc", not ``within 1 pc".
@@
 \end{referee}
-
 We have added a short description of Rockstar to Section 3.1, where it is introduced.
@@
 \end{referee}
-
 We apologize for not being more clear on this point.
@@
 \end{referee}
-
 There are 1\% of Pop III stars that form in a halo not identified by Rockstar.
@@
 \end{referee}
-
 This is a good point about low-mass Pop III stars, and we have included these references in the introduction.
@@
 \end{referee}
-
 We now include X-ray heating in the introduction and cited Jeon et al. (2014).
@@
 \end{referee}
-
 We have included the $M_{\rm crit}$ function that Visbal et al.
@@
 \end{referee}
-
 RP stands for the ``radiation pressure" simulation from Wise et al.
@@
 \end{referee}
-
 In hindsight, we agree that we initialized the simulation too late, even with 2nd order Lagrangian perturbation theory.
@@
 \end{referee}
-
 We chose this metallicity threshold based on the work of Omukai et al.
@@
 \end{referee}
-
 Our choice was motivated by both previous work and our refinement strategy rather than convergence.
@@
 \end{referee}
-
 We chose this critical H$_2$ fraction to match with the values found in previous work (e.g.
@@
 \end{referee}
-
 In our simulation, we consider a fixed mass limit between 1 and 300 $M_{\odot}$ of the IMF.
@@
 \end{referee}
-
 Hartwig et al.
@@
 \end{referee}
-
 We thank the referee for pointing out this tricky detail, and we have added it to the caption of Figure 1.
@@
 \end{referee}
-
 This is a good point, and the plot has been adjusted accordingly.

### 2019-10-21 paper.tex
changing case of figure filename
Minor revisions to intro/methods sections

--- 2019-08-27 paper.tex
@@
 Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today.
-These stars are, by definition, metal-free (Population III; Pop III) and are \textbf{traditionally} thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}\textbf{, although recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}} A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
+These stars are, by definition, metal-free (Population III; Pop III) and are \textbf{traditionally} thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}\textbf{, although more recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}} A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
 The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.
@@
 Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12,OLeary12}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}.
-\textbf{X-ray heating from High-Mass X-ray Binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.}
+\textbf{X-ray heating from high-mass X-ray binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.}
 
@@
 
-If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.\textbf{Our simulation is insensitive to the merging distance between Pop III stars.} The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
+If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.\textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.} The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
 \begin{equation} \label{IMF}
@@
 This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding.
+\textbf{\citet{Hartwig15} use the same shielding factor equation from \citet{Wolcott11} but implement an improved calculation of the column density to incorporate the relative gas velocities and geometries of the halo.
+This method takes into account the Doppler-shifting of spectral lines, which can affect \hh{} shielding.
+With the improved calculation of the column density, they find that the shielding factor is larger for gas at higher temperatures near $10^4$~K than when the shielding factor is calculated for an average column density for the halo, meaning that self-shielding is generally less efficient for higher temperatures.
+In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our halos are less massive and contain gas at lower temperatures.
+Our calculation of the shielding factor is still valid for the temperature range of our halos, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.}
 
@@
 The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$.
-\textbf{To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.119543 from \citet{oshea07a} Figure 13 panel d, where $J_{21}$ = 0.
-These profiles were approximated with a linear fit for simplicity.
+\textbf{To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{oshea07a} (their Figure 13d) with $J_{21}$ = 0.
+These profiles were approximated with a piecewise power-law for simplicity.
 As the halo masses increase, the shielding factor increases, meaning there is less shielding occuring within that halo.
-This is because at larger radii, there is less \hh{} available, and therefore, shielding is decreased.} Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.
+This behavior occurs because at larger radii, there is less \hh{} available, and therefore, the effects of shielding are decreased.} Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.
 At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum.
@@
 The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s.
-\textbf{Note that a shielding factor of 1 means that there is no shielding and a shielding factor of 0 means complete shielding.}}
+\textbf{Note that a shielding factor of 1 (0) corresponds to no (complete) shielding.}}
     \label{fig:shield_mass}
@@
 After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box.
-These stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
+\textbf{When the first Pop III star forms in our simulation at $z = 27$, there are only 6 halos that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}.} These \textbf{Pop III} stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
 Metal-enriched star formation begins to take place as soon as enough metals are present within a halo.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{images/JLW_xe_bg_mass_weight.pdf}
+	\includegraphics[width=\columnwidth]{images/jlw_xe_bg_mass_weight.pdf}
     \caption{For the entire box, the average mass weighted LW background \textbf{from sources} shown in solid red and the fraction of the volume ionized above 10\% versus time shown in solid black.

### 2019-10-21 paper.tex
Final revisions to paper

@@
 %====================================================================
- To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar} \textbf{, a friends-of-friends like algorithm which adaptively refines in six phase-space dimensions and one time dimension}.
-The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$.
+ To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, \textbf{an algorithm that adaptively refines halos found with a friends-of-friends method in position and velocity phase-space and also temporally.} The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$.
 The total mass is subsequently used in our analysis.
@@
 Here seven Pop III stars form in a pristine $10^6 \msun$ subhalo inside of a $3 \times 10^8 \msun$ atomic cooling parent halo.
-Because this object only contains 1 per cent of the Pop III stars, it only shifts our average halo masses by a similar amount.} We also take the center and virial radius from the \rockstar{} halo catalog.
+Because this object only contains 1 per cent of the number of Pop III stars, it only affects our average halo masses by a similar amount.} We also take the center and virial radius from the \rockstar{} halo catalog.
 \textbf{About 1\%} of Pop III stars do not form in a halo identified by \rockstar{}.
@@
 There are three main causes of this significant variation in mass.
-First, \textbf{36 per cent} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.
+First \textbf{given our assumed IMF (Equation \ref{IMF}), 36 per cent} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.
 Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs.
@@
 Since we include \hh{} self-shielding, Pop III stars are allowed to form in smaller mass halos for a given LW background.
-\textbf{\citet{Visbal14} used zero-dimensional one-zone models to study the gaseous centers of dark matter halos and how they react to a LW background.
-They use a particular parametrization of the central gas density, which then follows their analytic equation for critical mass (see their Equation 4) to withing a factor of two.
-This critical mass is plotted in our Figure \ref{fig:compare_JLW_mass} at a redshift of 20.
-At that redshift, almost all of our halos fall below their critical mass relationship, with only the highest mass halos rising above.
-\citet{Visbal14} also compare their results to three-dimensional hydrodynamical simulations, where they find similar threshold halo masses as \citet{Machacek01}.}\citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6.
+\textbf{\citet{Visbal14} used one-zone models to study the gaseous centers of dark matter halos and how they react to a LW background.
+They use a particular parametrization of the central gas density, which then follows their analytic equation for critical mass (see their Equation 4) to within a factor of two.
+This critical mass is plotted in our Figure \ref{fig:compare_JLW_mass} at redshift 20.
+Here almost all of our halos fall below their critical mass relationship, with only the highest mass halos rising above.
+\citeauthor{Visbal14} also compare their results to three-dimensional hydrodynamical simulations, where they find similar threshold halo masses as \citet{Machacek01}.} \citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6.
 They found a minimum halo mass for hosting Pop III star formation, but with the caveat that they did not include \hh{} self-shielding.
@@
 Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
-\textbf{\citet{Hirano15} used cosmological simulations to study 1540 gas clouds in the early universe to derive the corresponding primordial stellar mass distribution.
-They find that star forming halos of virial masses $M_{\rm vir} = 2.1 \times 10^5 M_{\odot}$ at z = 30 and $M_{\rm vir} = 9.9 \times 10^5 M_{\odot}$ at z = 10.
-These masses are fairly similar to our work, with our mean halo mass lying between these values.}
+\textbf{\citet{Hirano15} used cosmological simulations to study 1540 collapsing metal-free gas clouds in the early universe to derive the corresponding primordial stellar mass distribution.
+They find that stars form in halos above virial masses $M_{\rm vir} = 2.1 \times 10^5 M_{\odot}$ at $z = 30$ and $M_{\rm vir} = 9.9 \times 10^5 M_{\odot}$ at $z = 10$.
+These masses are consistent with our results with our mean halo mass lying between these values.}
 
@@
     \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works.
-The black solid line is from M01 \textbf{given our LW background}, blue solid line from \citet{Trenti09_SFR} \textbf{at z=20, the purple solid line from \citet{Visbal14} at z=20,}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.
+The black solid line is from M01 \textbf{given our LW background}, blue solid line from \citet{Trenti09_SFR} \textbf{at $z=20$, the purple solid line from \citet{Visbal14} at $z=20$}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.
 J$_{LW}$ = 0 for the various sources is plotted here at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
@@
 \textbf{Their work was based on previous work, done by \citet{Schauer15}, where they study LW radiation coming from single Pop III stars, rather than stellar populations.
-They find similar results as \citet{Schauer17}, with the exception that H2 shielding by neutral hydrogen decreases escape fractions as compared to when only H2 shielding is considered.
-In their more recent work, they find that this difference in escape fractions between when H2 shielding by neutral hydrogen is included or not is negligible.
+They find similar results as \citet{Schauer17}, with the exception that \hh{} shielding by neutral hydrogen decreases LW escape fractions as compared to when only \hh{} shielding is considered.
+In their more recent work, they find that this difference in LW escape fractions between when \hh{} shielding by neutral hydrogen is included or not is negligible.
 \citet{kitayama04} investigated the transition between D-type and R-type ionization fronts within halos to determine the escape fractions of ionizing and photodissociating photons using a one-dimensional Lagrangian hydrodynamics code.
@@
 Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results.
-\textbf{\citet{Schauer19} quote minimum and average halo masses necessary for the center of the halo to have enough cold dense gas available for star formation for various streaming velocities to study star formation in minihalos and it's relation to the 21-cm absorption feature from the EDGES survey.
+\textbf{\citet{Schauer19} give minimum and average halo masses necessary for enough cold dense gas to form in halo centers to support star formation for various streaming velocities in their study of star formation in minihalos and its relation to the EDGES 21-cm absorption feature \citep{EDGES}.
 Ranging from 0 $\rm v_{\rm bc}$ to 3.0 $\rm v_{\rm bc}$ in units of $\sigma_{\rm rms}$, they found that the minimum halo mass ranges from $5 \times 10^5 M_{\odot}$ to $10^7 M_{\odot}$, and the average halo mass ranges from about $2 \times 10^6 M_{\odot}$ to $4 \times 10^7 M_{\odot}$.
-Our halo masses generally fall within these ranges, confirming again that streaming velocities would likely not affect our results.}
+Our halo masses generally fall within these ranges, confirming again that only the rarest and strongest of the streaming velocities would affect our results.}
 
@@
 
-JHW is supported by National Science Foundation grants AST-1614333 and OAC-1835213, NASA grant NNX17AG23G, and Hubble theory grant
-HST-AR-14326.  We thank the support staff at Georgia Tech's PACE,
-where we ran this simulation.  The freely available plotting library
-{\sc matplotlib} \citep{matplotlib} was used to construct numerous
-plots within this paper. Computations and analysis described in this
-work were performed using the publicly-available \enzo{} and \yt{}
-codes, which is the product of a collaborative effort of many
-independent scientists from numerous institutions around the world.
+JHW is supported by National Science Foundation grants AST-1614333 and OAC-1835213, and NASA grant NNX17AG23G.
+The freely available plotting library {\sc matplotlib} \citep{matplotlib} was used to construct numerous plots within this paper.
+Computations and analysis described in this work were performed using the publicly-available \enzo{} and \yt{} codes, which is the product of a collaborative effort of many independent scientists from numerous institutions around the world.
 

### 2019-10-21 paper.tex
Adding new acknowledgments

@@
 
-JHW is supported by National Science Foundation grants AST-1614333 and OAC-1835213, and NASA grant NNX17AG23G.
+JHW is supported by National Science Foundation grants AST-1614333 and OAC-1835213, and NASA grant NNX17AG23G.  The simulation was performed on Blue
+Waters operated by the National Center for Supercomputing Applications (NCSA) with PRAC allocation support by the NSF (awards ACI-1514580 and OAC-1810584).
+The subsequent analysis was performed with NSF's XSEDE allocation AST-120046 on the Comet resource and also on the Georgia Tech PACE compute system.
+This research is part of the Blue Waters sustained-petascale computing project, which is supported by the NSF (awards OCI-0725070, ACI-1238993) and the state of Illinois.
+Blue Waters is a joint effort of the University of Illinois at Urbana-Champaign and its NCSA.
 The freely available plotting library {\sc matplotlib} \citep{matplotlib} was used to construct numerous plots within this paper.

### 2019-10-21 paper.tex
spell checking

@@
 These profiles were approximated with a piecewise power-law for simplicity.
-As the halo masses increase, the shielding factor increases, meaning there is less shielding occuring within that halo.
+As the halo masses increase, the shielding factor increases, meaning there is less shielding occurring within that halo.
 This behavior occurs because at larger radii, there is less \hh{} available, and therefore, the effects of shielding are decreased.} Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.
@@
 Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity.
-However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the mininum.
+However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the minimum.
 We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation.
@@
 Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}.
-This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situtation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}.
+This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}.
 Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool.
-While this may only be a small effect in some halos where the local LW radiation flucutations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.
+While this may only be a small effect in some halos where the local LW radiation fluctuations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.
 In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.
@@
 Their J$_{\rm LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
-\citet{OShea08} used cosmological simulations to investivate Pop III star formation in various LW backgrounds.
+\citet{OShea08} used cosmological simulations to investigate Pop III star formation in various LW backgrounds.
 They found that due to an increased LW background, there is a delay in star formation, and thus there is an increase in the halo masses at collapse.
@@
 %====================================================================
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 %====================================================================

### 2019-10-21 paper.tex
Fixing minor errors, fixing baryon fraction plot and caption.

@@
 It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.
-\textbf{We refine the cells one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.
+\textbf{We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.
 Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.} The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions.
@@
 
-If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.\textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.} The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
+If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.
+\textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.} The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
 \begin{equation} \label{IMF}

### 2019-10-21 referee.tex
spell checking
Fixing minor errors, fixing baryon fraction plot and caption.

@@
 
-\jhw{Need to double-check baryon fraction figure.}
-
 Figure \ref{fig:avg_baryon_fraction} shows the average baryon fraction for each halo as a function of the halo mass at the final redshift.
@@
   \caption{\label{fig:avg_baryon_fraction} Average baryon fraction within each halo versus the corresponding halo mass at the final redshift.
-The solid line indicates the cosmic baryon fraction of $\Omega_b / \Omega_m = 0.154$.}
+The solid line indicates the cosmic baryon fraction of $\Omega_b / \Omega_m = 0.154$.
+Halos with an average baryon fraction less than or equal to $10^{-3}$ are all set at $10^{-3}$.}
 \end{figure}
@@
 The shielding factor as calculated in our work will therefore not vary significantly compared to the full treatment of the column density, so we do not expect this to be a problem.
-We have added a brief desription of this effect to the \hh{} Self-Shielding section.
+We have added a brief description of this effect to the \hh{} Self-Shielding section.
 

### 2019-10-21 referee.tex
Removing alphabet letters in referee response.

@@
 
-A -- 1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo.
+1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo.
 This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo.
@@
 \begin{referee}
-B -- 2) The authors select their haloes by the halo finding algorithm Rockstar.
+2) The authors select their haloes by the halo finding algorithm Rockstar.
 They should add a bit of information on that code (is it fof or subfind-like?).
@@
 \begin{referee}
-C -- Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper.
+Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper.
 The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.
@@
 \begin{referee}
-D -- In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo.
+In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo.
 The baryon fraction varies with redshift.
@@
 
-E -- The authors should state at one point in the paper for which properties they use comoving or physical units.
+The authors should state at one point in the paper for which properties they use comoving or physical units.
 \end{referee}
@@
 
-F -- The authors write that Pop III star formation is generally more massive.
+The authors write that Pop III star formation is generally more massive.
 While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
@@
 \begin{referee}
-G -- The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14).
+The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14).
 \end{referee}
@@
 \begin{referee}
-H -- The authors cite the well-known study from Machacek+01.
+The authors cite the well-known study from Machacek+01.
 However, a more recent result would be from the study by Visbal+14, giving a lower mass limit.
@@
 
-I -- In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
+In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
 \end{referee}
@@
 \begin{referee}
-J -- The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
+The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
 \end{referee}
@@
 \begin{referee}
-K -- Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
+Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
 \end{referee}
@@
 \begin{referee}
-L -- What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
+What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
 \end{referee}
@@
 \begin{referee}
-M -- Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
+Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
 \end{referee}
@@
 \begin{referee}
-N -- Do the authors set fixed mass limits to the IMF and if yes, which are they?
+Do the authors set fixed mass limits to the IMF and if yes, which are they?
 If not, which is the highest / lowest mass they find in their random sampling?
@@
 \begin{referee}
-O -- One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
+One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
 \end{referee}
@@
 \begin{referee}
-P -- In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
+In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
 \end{referee}
@@
 \begin{referee}
-Q -- The analytic calculation of the shielding factor is a nice property of the paper.
+The analytic calculation of the shielding factor is a nice property of the paper.
 However, assuming a constant H2 fraction seems not appropriate.
@@
 
-R -- Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction.
+Figure 2 is quite empty, it would be useful to include the halo mass function of the earliest Pop III formation redshift with its analytic prediction.
 In addition, the authors could provide a line or an arrow to show their halo mass resolution limit.
@@
 \begin{referee}
-S -- Figure 3 looks very nice. It would be helpful if an additional line that only 
+Figure 3 looks very nice. It would be helpful if an additional line that only 
 provides the global LWBG (in units of J21) was included.
@@
 \begin{referee}
-T -- The authors find no correlation between the host halo mass and the Lyman-Werner background intensity.
+The authors find no correlation between the host halo mass and the Lyman-Werner background intensity.
 However, they only look at the LWBG flux at the time of Pop III formation - is there maybe a correlation between the time integrated LW flux?
@@
 \begin{referee}
-U -- Figures 7 and 8 show very nice histograms as an additional panel on the right.  I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
+Figures 7 and 8 show very nice histograms as an additional panel on the right.  I suggest to include a histogram on the spread of the creation time in Figure 9 similar to Figures 7 and 8.
 \end{referee}
@@
 
-V -- The authors give three reasons for the halo mass spread.
+The authors give three reasons for the halo mass spread.
 Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
@@
 \begin{referee}
-W -- One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
+One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
 \end{referee}
@@
 \begin{referee}
-X -- In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different symbol / colour.
+In Figure 10, the result from Yoshida+03 is hard to see, maybe use a different symbol / colour.
 \end{referee}
@@
 \begin{referee}
-Y -- Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
+Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
 \end{referee}
@@
 \begin{referee}
-Z -- The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction).
+The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction).
 While they cite some older work, they however fail to compare to more recent work eg by Hirano+18 or Schauer+19 (who do perform a systematic study not only based on a few, single haloes).

### 2019-10-22 paper.tex
Fixing small error

@@
 % out the following line
-\usepackage{newtxtext,newtxmath}
+%\usepackage{newtxtext,newtxmath}
 % Depending on your LaTeX fonts installation, you might get better results with 
@@
 Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today.
-These stars are, by definition, metal-free (Population III; Pop III) and are \textbf{traditionally} thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}\textbf{, although more recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}} A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
+These stars are, by definition, metal-free (Population III; Pop III) and are \textbf{traditionally} thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}\textbf{, although more recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}.} A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
 The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.

### 2019-11-15 paper.tex
Adding referee_2.tex to begin to respond. I have adjusted the paper according to some of their first comments. I have indicated which ones in the .tex file.

@@
 If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.
-\textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.} The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
+\textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.
+We found that even when this number was decreased to 0.065 pc, the number of stars which formed was unchanged.} The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
 \begin{equation} \label{IMF}
@@
 Interestingly, a full radiation hydrodynamics simulation, such as ours, does not produce identical results as M01 predicts.
+
 Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[e.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
@@
 Since we include \hh{} self-shielding, Pop III stars are allowed to form in smaller mass halos for a given LW background.
+
 \textbf{\citet{Visbal14} used one-zone models to study the gaseous centers of dark matter halos and how they react to a LW background.
@@
 The results from \citet{Trenti09} and \citet{Mebane18} have higher halo masses in comparison with M01, although this more closely matches results from simulations \citep[see][]{Wise07_UVB, OShea08}.
+
 It should be noted that because our box is fairly small, we cannot capture the cosmic variance of rare halos and galaxies.
@@
 While our halos never experience a LW intensity as low as 0.01 J$_{21}$, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}).
+
 \citet{Wise07_UVB} used cosmological simulations to investigate \hh{} cooling in a LW background.
@@
 Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results.
+
 \textbf{\citet{Schauer19} give minimum and average halo masses necessary for enough cold dense gas to form in halo centers to support star formation for various streaming velocities in their study of star formation in minihalos and its relation to the EDGES 21-cm absorption feature \citep{EDGES}.

### 2019-11-15 referee_2.tex
Adding referee_2.tex to begin to respond. I have adjusted the paper according to some of their first comments. I have indicated which ones in the .tex file.

\documentclass[11pt]{article}
%\renewcommand\refname{ }

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}
\usepackage{mdframed}
\usepackage{float}
\parskip=10pt

\input macros.tex

\definecolor{quotegray}{gray}{0.9}
% \lstnewenvironment{referee}{%
%   \lstset{backgroundcolor=\color{quotegray},
%   frame=single,
%   framerule=0pt,
%   basicstyle=\ttfamily,
%   columns=fullflexible}}{}

% https://tex.stackexchange.com/questions/111065/quoting-styles-technical-an-appreciation-questions
\mdfdefinestyle{myquotestyle}{
  leftmargin=15pt,
  rightmargin=15pt,
  backgroundcolor=quotegray,
  linewidth=0pt,
  skipbelow=\topskip,
  skipabove=\topskip
}
\newenvironment{referee}[1][]{%
    \ignorespaces%
    \begin{mdframed}[style=myquotestyle,#1]%
}{%
    \end{mdframed}%
    \ignorespacesafterend%
}%

% \newenvironment{referee}[1][]{
%   \ignorespaces%
%   \begin{mdframed}[style=myquotestyle,#1]%
% }{%
%   \end{mdframed}%
%   \ignorespaceafterend%
% }%

\begin{document}

\begin{center} 
\bfseries{
\begin{large}
  Response to referee report for manuscript ref. MN-19-2054-MJ.R1
\end{large}
}
\end{center}

We thank the referee for their response to our recent revision. Their review is directly quoted below in the gray boxes with our responses below.  Any changes to the manuscript, as well as changes made previously, have been \textbf{bold-faced}.

\begin{referee}
    The authors have clarified most of the open questions in the revised manuscript. A few points need further discussion, they are listed below: 
\end{referee}

\begin{referee}
    A -- In this paper, some very long paragraphs can be found, especially in Sections 3 and 4. Please break these long paragraphs down in smaller ones to increase the read flow. 
\end{referee}
    These paragraphs have been broken down.

\begin{referee}
    To Major comment number 1)

    B -- The convergence study is a great addition to the paper. However, the lowest limit explored here (0.625pc) is a factor of roughly 100 larger than the scale on which fragmentation can be seen (compare eg the 1000AU regions, in which several Pop III stars form in work by Stacy+16). I recommend to explicitly state down to which resolution the convergence was tested in Section 2.2.1 and adding these limitations to the "Caveats" section. Instead of single Pop III stars, this paper is a study of the multiplicity of Pop III star formation regions. Please make this clear in the paper. 
\end{referee}
    The lowest limit has been added to section 2.2.1.

    --need to add to Caveats
    --adjust some wording about Pop III star formation regions?

\begin{referee}
    Minor points:

    C -- - Is the SFRD really in physical (and not comoving) units (Figure 4 / Section 3)? Please provide values for the comparison papers (Xu+13, Magg+16) and include a comparison to Jaacks+19. 
\end{referee}

\begin{referee}
    D -- - The initialization at z=130 should be mentioned as a caveat. 
\end{referee}

\begin{referee}
    E -- - The analytic calculation of the self-shielding of the halo now takes into account a realistic halo profile. However, there are three issues: 
    E.1 -- -- In the first paragraph of Section 2.4, it still reads "with a constant H2 fraction". Please correct this. 
    E.2 -- -- For completeness, please provide the readers with the H2 radial fit to the O'Shea & Normal 07 paper that was performed. 
    E.3 -- -- Compared to the previous version with a constant profile, the shielding factor increases for higher halo masses (in the previous version of the paper, there was a slight decrease): leading to less shielding. I do not understand where this is coming from, a more massive halo has a larger overall gas mass, and therefore more H2 and more shielding. Maybe it has to do with the scaling of the H2 fraction?  It is important to know how the authors scale the H2 fraction as a function of radius for different halo masses (see point above). If this is not the reason, please explain what else is causing more massive haloes to be worse at self-shielding.  
\end{referee}

\begin{referee}
    F -- - Thank you for adding the global LWBG as a dashed line in Figure 3. Please also mention at some point in the text or add a legend that this is again given in units of J21. 
\end{referee}

\begin{referee}
    G -- - I see that retrospectively calculating the time-averaged LWBG is not possible without repeating the study. However, please mention the possibility for a correlation between the time-integrated LWBG and the host halo mass in Section 3.2 and summary and be more explicit that this is the LWBG at star formation (eg in the introduction and in Section 3.2 and in the second bullet point of the Conclusions).  
\end{referee}

\begin{referee}
    H -- - The authors put their work in comparison to Schauer+19, ApJL 877, 5 who match the star formation efficiency in minihaloes to the observed 21cm signal. They should rather compare to Schauer+19 MNRAS, 484, 3510 who performed cosmological hydrodynamical simulations for the minimum and average halo mass in different streaming velocity regions. Please include their limits in your Figure 10, as done with the Naoz+13 results, and a short comparison to Hirano+18 (their Science paper). Please include these references also in the introduction. Also the sentence "Often in the literature, streaming velocities are only studied for a few haloes" seems outdated.
\end{referee}

\end{referee}

### 2019-11-15 paper.tex
Responding to referee_2. Made corresponding changes to paper. Need to finish responding to B, D, and H.

@@
 
-In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background, augmenting results from prior work.
+In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background \textbf{at the instance of star formation}, augmenting results from prior work.
 We aim to provide further insight into the host halos of Pop III stars.
@@
 In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.
-\textbf{Throughout the rest of the paper, all numbers are in physical units.}
+\textbf{Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.}
 
@@
 %====================================================================
-To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a constant \hh{} fraction, and use Equation \ref{shield} to calculate the shielding factor.
+To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a \textbf{realistic \hh{} halo profile}, and use Equation \ref{shield} to calculate the shielding factor.
 The \hh{} molecule number density within the halo is given by
@@
 The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$.
-\textbf{To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{oshea07a} (their Figure 13d) with $J_{21}$ = 0.
+\textbf{To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{OShea08} (their Figure 13d) with $J_{21}$ = 0, which was extracted directly from their plot.
 These profiles were approximated with a piecewise power-law for simplicity.
@@
 In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place.
-By the end of the simulation, 20\% of the box has an ionized fraction greater than 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.
+By the end of the simulation, 20\% of the box has an ionized fraction greater than 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from sources} as a function of time, \textbf{the LW background given by equation \ref{LWbg} in units of J$_{21}$,} and temperature projections of the box at certain points in time.
 
@@
     \caption{For the entire box, the average mass weighted LW background \textbf{from sources} shown in solid red and the fraction of the volume ionized above 10\% versus time shown in solid black.
-\textbf{The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}).}Temperature projections are shown at the points indicated by the arrows.}
+\textbf{The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}).
+The solid red line in the legend refers to both the solid and dashed lines in the figure.}Temperature projections are shown at the points indicated by the arrows.}
     \label{fig:JLW_xe_mass}
@@
 In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39.
-The corresponding star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4} \ \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 21.3$ and slowly decreases.
+The corresponding \textbf{comoving} star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4} \ \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 21.3$ and slowly decreases.
 The SFRD sharply declines near the end of the simulation but does not drop to zero.
@@
 In particular, it decreases at $z \le 11$ when the most massive galaxy undergoes an extended period of star formation, boosting the local LW radiation field as shown in Figure \ref{fig:JLW_xe_mass}.
-The rates are consistent with other studies \citep[e.g.][]{Xu13, Magg16}, but it is likely to change depending on the particular modes captured by the initial conditions.
+\textbf{\citet{Xu13} and \citet{Magg16} see a SFRD of $~10^{-4} \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 15$ and $z = 20$ respectively.
+\citet{Jaacks19} find a SFRD of $~10^{4.5} \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 20$, which flattens out to $10^{-3} \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ by $z =7$.} \textbf{Our} SFRD rates are consistent with \textbf{these} other studies, but it is likely to change depending on the particular modes captured by the initial conditions.
 
@@
 	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
-    \caption{The star formation rate density of Pop III stars.
+    \caption{The \textbf{comoving} star formation rate density of Pop III stars.
 The SFRD peaks at a redshift of 20, and slowly falls off.
@@
 
-The LW background intensity versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}.
+The LW background intensity \textbf{at the instance of Pop III star formation} versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}.
 Because the LW background only varies by a factor of five as Pop III stars form, most points lie within a small intensity range, just below $1~J_{21}$.
@@
 Given that the background intensity only varies by a factor of five, previous work suggested that most halos should have formed stars around or above the M01 relationship.
-However, we see a large spread in host halo masses, over an order of magnitude, and no clear relationship between the LW intensity and the host halo mass.
+However, we see a large spread in host halo masses, over an order of magnitude, and no clear relationship between the \textbf{instantaneous} LW intensity and the host halo mass.
 This behavior suggests that the LW intensity is not the primary indicator of the mass at which a metal-free halo collapses.
 \hh{} self-shielding is the main cause behind this conclusion because the internal dynamics and chemo-thermal evolution are now isolated from its large-scale environment and mostly depends on the local conditions within the halo.
+\textbf{Alternatively, it is possible that there could be a correlation between the time-integrated LW background and the host halo mass.
+These calculations are outside the scope of this paper and require further study.}
 
@@
 	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.
-Self-shielding creates a disconnect between the LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
+Self-shielding creates a disconnect between the \textbf{instantaneous}LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
 	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
@@
 While we do not see any relationship between the LW intensity and Pop III host halo mass,  in order to determine exactly how the LW intensity influences the host halo mass, a more systematic approach needs to be taken.
+\textbf{The time-integrated LW background leading up to the formation of a Pop III star would be an interesting calculation to follow up with, and may result in a correlation with the host halo mass.}
 

### 2019-11-15 referee_2.tex
Responding to referee_2. Made corresponding changes to paper. Need to finish responding to B, D, and H.

@@
 
+    Upon review of these calculations, you are correct in questioning the units of the SFRD.
+The SFRD is in comoving units.
+This correction has been added to the caption of the SFRD and to the description above the plot.
+
+    These comparison values have been added to the beginning of the results section.
+
 \begin{referee}
@@
     E.1 -- -- In the first paragraph of Section 2.4, it still reads "with a constant H2 fraction". Please correct this. 
+\end{referee}
+    This has been corrected.
+
+\begin{referee}
     E.2 -- -- For completeness, please provide the readers with the H2 radial fit to the O'Shea & Normal 07 paper that was performed. 
+\end{referee}
+    The citation previously written was referencing their first paper in their series of Pop III star formation. It should have referenced their second paper in the series. This has been corrected.
+
+    O'Shea and Norman 2008 do not provide an analytic fit for the H2 radial profile.
+The profile used in our calculations were taken from their figure 13 panel d.
+This detail has been added in the description of the H2 radial profiles.
+
+\begin{referee}
     E.3 -- -- Compared to the previous version with a constant profile, the shielding factor increases for higher halo masses (in the previous version of the paper, there was a slight decrease): leading to less shielding.
@@
 \end{referee}
+    The shielding factor increases for more massive halos because these halos have larger virial radii, at which point there is significantly less \hh{} compared to smaller radii.
+So halos with smaller masses, and thus smaller virial radii, have more \hh{} built up at the edges compared to their larger counterparts, resulting in a more effective shield at the virial radius.
 
@@
 \end{referee}
+    The solid red line in the legend refers to both the solid and the dashed red lines. This detail has been added to the caption and to the text.
 
@@
 \end{referee}
+    The possible correlation between the LW background and the host halo mass has been added to the requested sections.
+
+    We have also added the detail about how we are investigating the LWBG at the instance of star formation to the requested sections.
 
@@
 \end{referee}
-
-\end{referee}

### 2019-11-18 paper.tex
Addressing z_init and fragmentation points

@@
 Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.} The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions.
-The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue.
+\textbf{We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.} The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue.
 At this point, about 20\% of the volume is over 10\% ionized.
@@
 \textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.
-We found that even when this number was decreased to 0.065 pc, the number of stars which formed was unchanged.} The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
+We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.
+Our density threshold for star particle formation is equivalent to a molecular core.
+Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU \citep[e.g.][]{Turk09, Stacy11} with molecular cores, therefore our results on multiplicity should be considered as lower limits.}
+
+The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
 \begin{equation} \label{IMF}
@@
 In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}.
-We are only tracking massive Pop III star formation.
+\textbf{Again, we are only tracking the formation of metal-free molecular cores, which form either a single or multiple massive Pop III stars and perhaps several more low mass stars.}
 
@@
 We now inspect the number of Pop III stars and the total mass of Pop III stars per halo.
-Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses $<1 M_{\odot}$.
-The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation.
+Again, we are only tracking \textbf{star-forming regions where the star particles form at densities equivalent to molecular cores that may form multiple massive stars.
+Furthermore, we are not modeling the formation of low-mass stars ($<1 M_{\odot}$) that may form out of fragmented gas at higher densities and smaller scales.
+Thus our results in this section should be considered as lower limits to the number of Pop III stars.}  The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation.
 The histogram of the number of Pop III stars for all masses is projected on the right hand side.

### 2019-11-18 referee_2.tex
Minor changes to make Second response compilable
Addressing z_init and fragmentation points

@@
 
+    \jhw{I've add some wording in Sections 2.2.1 and 3.3 about fragmentation and our study being a lower limit on the multiplicity but nothing to the caveats section.
+I think with these statements, we can argue in the response that changes throughout the text are not needed.}
+
 \begin{referee}
@@
 \end{referee}
+We have added the following text to Section 2.1 after stating the initialization redshift, ``We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.''
 
@@
 \begin{referee}
-    E.2 -- -- For completeness, please provide the readers with the H2 radial fit to the O'Shea & Normal 07 paper that was performed. 
+    E.2 -- -- For completeness, please provide the readers with the H2 radial fit to the O'Shea \& Normal 07 paper that was performed. 
 \end{referee}
@@
 
-    O'Shea and Norman 2008 do not provide an analytic fit for the H2 radial profile.
+    O'Shea and Norman 2008 do not provide an analytic fit for the H$_2$ radial profile.
 The profile used in our calculations were taken from their figure 13 panel d.
-This detail has been added in the description of the H2 radial profiles.
+This detail has been added in the description of the H$_2$ radial profiles.
+
+    \jhw{You should give the exact fitting formula in the text.}
 
@@
 So halos with smaller masses, and thus smaller virial radii, have more \hh{} built up at the edges compared to their larger counterparts, resulting in a more effective shield at the virial radius.
+We have clarified this point in the text.
 
@@
 \end{referee}
+
+\end{document}

### 2019-11-20 paper.tex
Removed previous bold text. Responded to all referee comments and have made adjustments to the paper. Still have a few questions and things to finish up leftover regarding the last comment.

@@
 Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today.
-These stars are, by definition, metal-free (Population III; Pop III) and are \textbf{traditionally} thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}\textbf{, although more recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}.} A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
+These stars are, by definition, metal-free (Population III; Pop III) and are traditionally thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}, although more recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}.
+A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}.
 The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.
@@
 Halos with an \hh{} column density of N$_{\rm H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars.
-Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12,OLeary12}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}.
-\textbf{X-ray heating from high-mass X-ray binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.}
+Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19,Hirano17_Science}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}.
+X-ray heating from high-mass X-ray binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.
 
@@
 In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.
-\textbf{Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.}
+Throughout the rest of the paper, all numbers are in physical units\textbf{, unless otherwise specified}.
 
@@
 
-	\item molecular hydrogen \textbf{number} fraction, f$_{\rm H2}$ > 10$^{-3}$
+	\item molecular hydrogen number fraction, f$_{\rm H2}$ > 10$^{-3}$
 \end{enumerate}
-\textbf{The critical metallicity marks where dust cooling becomes efficient enough to cause fragmentation at high densities \citep[e.g.][]{Schneider06_Frag}.
+The critical metallicity marks where dust cooling becomes efficient enough to cause fragmentation at high densities \citep[e.g.][]{Schneider06_Frag}.
 In practice, we find about 10 per cent of Pop III star particles having a non-zero metallicity below this value.
@@
 At these scales, Jeans length refinement is the most common because of the cold temperatures in the cloud core.
-The molecular hydrogen criterion is also consistent with previous work in the ``loitering'' phase of molecule formation between $10^2$ and $10^8 \cubecm$ before three-body reactions become important \citep[e.g.][]{Omukai10}.}
+The molecular hydrogen criterion is also consistent with previous work in the ``loitering'' phase of molecule formation between $10^2$ and $10^8 \cubecm$ before three-body reactions become important \citep[e.g.][]{Omukai10}.
 
 If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.
-\textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.
-We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.
+In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.
+\textbf{We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.
 Our density threshold for star particle formation is equivalent to a molecular core.
@@
 12 of W12.
-\textbf{With our chosen IMF (Eq.
-\ref{IMF}), 59, 36, and 5 per cent of Pop III stars produce Type II SN, black holes with no SN, and PISNe, respectively.}
+With our chosen IMF (Eq.
+\ref{IMF}), 59, 36, and 5 per cent of Pop III stars produce Type II SN, black holes with no SN, and PISNe, respectively.
 
@@
 This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding.
-\textbf{\citet{Hartwig15} use the same shielding factor equation from \citet{Wolcott11} but implement an improved calculation of the column density to incorporate the relative gas velocities and geometries of the halo.
+\citet{Hartwig15} use the same shielding factor equation from \citet{Wolcott11} but implement an improved calculation of the column density to incorporate the relative gas velocities and geometries of the halo.
 This method takes into account the Doppler-shifting of spectral lines, which can affect \hh{} shielding.
@@
 In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our halos are less massive and contain gas at lower temperatures.
-Our calculation of the shielding factor is still valid for the temperature range of our halos, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.}
+Our calculation of the shielding factor is still valid for the temperature range of our halos, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.
 
@@
 
-For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, redshift\textbf{, and for a given \hh{} fraction halo profile}.
+For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, redshift, and for a given \hh{} fraction halo profile.
 Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively.
 The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$.
-\textbf{To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{OShea08} (their Figure 13d) with $J_{21}$ = 0, which was extracted directly from their plot.
-These profiles were approximated with a piecewise power-law for simplicity.
+To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{OShea08} (their Figure 13d) with $J_{21}$ = 0, which was extracted directly from their plot.
+These profiles were approximated with a piecewise power-law for simplicity \textbf{given by Equation \ref{h2fitting}}.
+\begin{equation} \label{h2fitting}
+	log_{10}(f_{\rm H2}) = -0.482 \times log_{10}(R_{\rm vir}) - 4.714
+\end{equation}
 As the halo masses increase, the shielding factor increases, meaning there is less shielding occurring within that halo.
-This behavior occurs because at larger radii, there is less \hh{} available, and therefore, the effects of shielding are decreased.} Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.
+This behavior occurs because at larger radii, there is less \hh{} available, and therefore, the effects of shielding are decreased.
+Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.
 At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum.
@@
 Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$.
-For these parameters, assuming the Doppler broadening parameter equals the circular velocity, \textbf{and assuming \hh{} fraction halo profiles from \citet{oshea07a}, }the shielding factor is below 1 percent.
+For these parameters, assuming the Doppler broadening parameter equals the circular velocity, and assuming \hh{} fraction halo profiles from \citet{oshea07a}, the shielding factor is below 1 percent.
 The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s.
-\textbf{Note that a shielding factor of 1 (0) corresponds to no (complete) shielding.}}
+Note that a shielding factor of 1 (0) corresponds to no (complete) shielding.}
     \label{fig:shield_mass}
@@
 After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box.
-\textbf{When the first Pop III star forms in our simulation at $z = 27$, there are only 6 halos that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}.} These \textbf{Pop III} stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
+When the first Pop III star forms in our simulation at $z = 27$, there are only 6 halos that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}.
+These Pop III stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
 Metal-enriched star formation begins to take place as soon as enough metals are present within a halo.
@@
 The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where halos are captured by 50 particles.
-\textbf{The vertical blue line indicates our halo mass resolution limit of 10$^{5}$ M$_{\odot}$.}}
+The vertical blue line indicates our halo mass resolution limit of 10$^{5}$ M$_{\odot}$.}
     \label{fig:hmf}
@@
 	\includegraphics[width=\columnwidth]{images/jlw_xe_bg_mass_weight.pdf}
-    \caption{For the entire box, the average mass weighted LW background \textbf{from sources} shown in solid red and the fraction of the volume ionized above 10\% versus time shown in solid black.
-\textbf{The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}).
-The solid red line in the legend refers to both the solid and dashed lines in the figure.}Temperature projections are shown at the points indicated by the arrows.}
+    \caption{For the entire box, the average mass weighted LW background from sources shown in solid red and the fraction of the volume ionized above 10\% versus time shown in solid black.
+The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}).
+\textbf{The solid red line in the legend refers to both the solid and dashed lines in the figure.}Temperature projections are shown at the points indicated by the arrows.}
     \label{fig:JLW_xe_mass}
@@
 %====================================================================
- To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, \textbf{an algorithm that adaptively refines halos found with a friends-of-friends method in position and velocity phase-space and also temporally.} The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$.
+ To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, an algorithm that adaptively refines halos found with a friends-of-friends method in position and velocity phase-space and also temporally.
+The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$.
 The total mass is subsequently used in our analysis.
-\textbf{For stars that form in subhalos identified by \rockstar{}, we assign the parent halo mass as the host halo mass.
+For stars that form in subhalos identified by \rockstar{}, we assign the parent halo mass as the host halo mass.
 There is one interesting case that we exclude from our analysis, where the parent halo is above the atomic cooling limit, because the radiative cooling physics are different in this regime and is not sensitive to a LW background.
 Here seven Pop III stars form in a pristine $10^6 \msun$ subhalo inside of a $3 \times 10^8 \msun$ atomic cooling parent halo.
-Because this object only contains 1 per cent of the number of Pop III stars, it only affects our average halo masses by a similar amount.} We also take the center and virial radius from the \rockstar{} halo catalog.
-\textbf{About 1\%} of Pop III stars do not form in a halo identified by \rockstar{}.
+Because this object only contains 1 per cent of the number of Pop III stars, it only affects our average halo masses by a similar amount.
+We also take the center and virial radius from the \rockstar{} halo catalog.
+About 1\% of Pop III stars do not form in a halo identified by \rockstar{}.
 Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$.
@@
 There are three main causes of this significant variation in mass.
-First \textbf{given our assumed IMF (Equation \ref{IMF}), 36 per cent} of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.
+First given our assumed IMF (Equation \ref{IMF}), 36 per cent of metal-free stars directly form a black hole without metal ejecta \citep{Heger03}, leaving the halo chemically pristine.
 Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs.
@@
 
-\textbf{\citet{Visbal14} used one-zone models to study the gaseous centers of dark matter halos and how they react to a LW background.
+\citet{Visbal14} used one-zone models to study the gaseous centers of dark matter halos and how they react to a LW background.
 They use a particular parametrization of the central gas density, which then follows their analytic equation for critical mass (see their Equation 4) to within a factor of two.
@@
 Here almost all of our halos fall below their critical mass relationship, with only the highest mass halos rising above.
-\citeauthor{Visbal14} also compare their results to three-dimensional hydrodynamical simulations, where they find similar threshold halo masses as \citet{Machacek01}.} \citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6.
+\citeauthor{Visbal14} also compare their results to three-dimensional hydrodynamical simulations, where they find similar threshold halo masses as \citet{Machacek01}.
+\citet{Mebane18} used a semi-analytic model of star formation, including feedback properties such as a LW background, photoionization due to Pop III stars, supernovae of Pop III stars and metal-enriched stars, and chemical enrichment, to determine for how long Pop III stars will survive for and found that Pop III stars can continue to form until z $\approx$ 6.
 They found a minimum halo mass for hosting Pop III star formation, but with the caveat that they did not include \hh{} self-shielding.
@@
 Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
-\textbf{\citet{Hirano15} used cosmological simulations to study 1540 collapsing metal-free gas clouds in the early universe to derive the corresponding primordial stellar mass distribution.
+\citet{Hirano15} used cosmological simulations to study 1540 collapsing metal-free gas clouds in the early universe to derive the corresponding primordial stellar mass distribution.
 They find that stars form in halos above virial masses $M_{\rm vir} = 2.1 \times 10^5 M_{\odot}$ at $z = 30$ and $M_{\rm vir} = 9.9 \times 10^5 M_{\odot}$ at $z = 10$.
-These masses are consistent with our results with our mean halo mass lying between these values.}
+These masses are consistent with our results with our mean halo mass lying between these values.
 
@@
     \caption{The halo mass versus the average LW intensity normalized by J21 versus for this work and a variety of other works.
-The black solid line is from M01 \textbf{given our LW background}, blue solid line from \citet{Trenti09_SFR} \textbf{at $z=20$, the purple solid line from \citet{Visbal14} at $z=20$}, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.
+The black solid line is from M01 given our LW background, blue solid line from \citet{Trenti09_SFR} at $z=20$, the purple solid line from \citet{Visbal14} at $z=20$, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.
 J$_{LW}$ = 0 for the various sources is plotted here at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
@@
 For each band, the maximum halo mass occurs at $z = 15$.
-For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$, the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.}
+For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$, the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.
+\textbf{The minimum halo mass hosting cold dense gas for different streaming velocities in units of km/s from \citet{Schauer19} are shown as horizontal black lines with different linestyles.}}
     \label{fig:compare_JLW_mass}
@@
 There are a few minor shortcomings to this work that should be noted.
+\textbf{As discussed in section 2.2.1, the number of Pop III stars that form is insensitive down to distances of 0.625 pc.
+Since this value is larger than fragmentation scales, it's possible that the location of the Pop III stars formed in our simulation are sites for multiple Pop III star formation.
+With this in mind, our results are only strengthened by the possibility of having more Pop III stars forming at these locations.}
+
 \citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo.
@@
 In general, they find that the LW escape fractions in the far-field are higher than 75\%.
-\textbf{Their work was based on previous work, done by \citet{Schauer15}, where they study LW radiation coming from single Pop III stars, rather than stellar populations.
+Their work was based on previous work, done by \citet{Schauer15}, where they study LW radiation coming from single Pop III stars, rather than stellar populations.
 They find similar results as \citet{Schauer17}, with the exception that \hh{} shielding by neutral hydrogen decreases LW escape fractions as compared to when only \hh{} shielding is considered.
@@
 \citet{kitayama04} investigated the transition between D-type and R-type ionization fronts within halos to determine the escape fractions of ionizing and photodissociating photons using a one-dimensional Lagrangian hydrodynamics code.
-They found that in halos with masses $< 10^6 M_{\odot}$, escape fractions are greater than 80 \%, and in larger mass halos, with masses $> 10^7 M_{\odot}$, the escape fractions are essentially zero.} Since we are not accounting for the reduced escape fraction within our halos, we are overestimating the LW radiation coming from point sources in our simulation.
+They found that in halos with masses $< 10^6 M_{\odot}$, escape fractions are greater than 80 \%, and in larger mass halos, with masses $> 10^7 M_{\odot}$, the escape fractions are essentially zero.
+Since we are not accounting for the reduced escape fraction within our halos, we are overestimating the LW radiation coming from point sources in our simulation.
 We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results as we find little dependence on LW intensity.
 
-We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12}.
+We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19}.
 Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with time.
@@
 The streaming velocities will generally result in lower gas densities within halos as well as an offset of the peak density from the center of the halo \citep{OLeary12}.
-Often in the literature, streaming velocities are only studied for a few halos.
-But \citet{Naoz13} estimated the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be seen in Figure \ref{fig:compare_JLW_mass} (see shaded bands).
+\citet{Naoz13} estimated the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be seen in Figure \ref{fig:compare_JLW_mass} (see shaded bands).
 These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the star forming halos in our simulation.
 \citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass halos.
-Our results indicate that halos collapse at larger masses that are not as affected by typical streaming velocities ($<1\sigma_{\rm vbc}$).
+\textbf{A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within halos for varying streaming velocities, showed that high streaming velocities restrict first star formation to atomic cooling halos.
+Their minimum halo masses which host cold dense gas for various streaming velocities are shown as black horizontal lines with different linestyles in Figure \ref{fig:compare_JLW_mass}.} Our results indicate that halos collapse at larger masses that are not as affected by typical streaming velocities ($<1\sigma_{\rm vbc}$).
 In the evolution of such a halo, it would have started to accumulate gas above these critical masses while also being irradiated by a LW background.
 Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results.
-
-\textbf{\citet{Schauer19} give minimum and average halo masses necessary for enough cold dense gas to form in halo centers to support star formation for various streaming velocities in their study of star formation in minihalos and its relation to the EDGES 21-cm absorption feature \citep{EDGES}.
-Ranging from 0 $\rm v_{\rm bc}$ to 3.0 $\rm v_{\rm bc}$ in units of $\sigma_{\rm rms}$, they found that the minimum halo mass ranges from $5 \times 10^5 M_{\odot}$ to $10^7 M_{\odot}$, and the average halo mass ranges from about $2 \times 10^6 M_{\odot}$ to $4 \times 10^7 M_{\odot}$.
-Our halo masses generally fall within these ranges, confirming again that only the rarest and strongest of the streaming velocities would affect our results.}
 
@@
 	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.
-Self-shielding creates a disconnect between the \textbf{instantaneous}LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
+Self-shielding creates a disconnect between the \textbf{instantaneous} LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
 	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.

### 2019-11-20 referee_2.tex
Adding a note in the response
Removed previous bold text. Responded to all referee comments and have made adjustments to the paper. Still have a few questions and things to finish up leftover regarding the last comment.

@@
 Their review is directly quoted below in the gray boxes with our responses below.
-Any changes to the manuscript, as well as changes made previously, have been \textbf{bold-faced}.
+Any changes to the manuscript, have been \textbf{bold-faced}.
 
@@
 
-    --need to add to Caveats
-    --adjust some wording about Pop III star formation regions?
+    --Added to the caveats
 
     \jhw{I've add some wording in Sections 2.2.1 and 3.3 about fragmentation and our study being a lower limit on the multiplicity but nothing to the caveats section.
-I think with these statements, we can argue in the response that changes throughout the text are not needed.}
+I think with these statements, we can argue in the response that changes throughout the text are not needed.
+Make the changes to the caveats section, and I'll write the rebuttal here.}
 
@@
 
-    O'Shea and Norman 2008 do not provide an analytic fit for the H$_2$ radial profile.
-The profile used in our calculations were taken from their figure 13 panel d.
-This detail has been added in the description of the H$_2$ radial profiles.
-
-    \jhw{You should give the exact fitting formula in the text.}
+    Our fitting formula has been added to the text where their H2 profiles are discussed.
 
@@
 \end{referee}
+	The limits from Schauer+19 have been added to Figure 10, and the previous description regarding the 21cm signal has been removed. 
+	--conclusions from this?
+	--weird to me how the units of the streaming velocities are different. Change this?
+	--unbolded addition to citation in caveat section
+
+	--need to add the Hirano+18 science paper to caveats section
+
+	Schauer+19 and Hirano+18 have been added to the introduction (unbolded -- fix this?).
+
+	The sentence "Often in the literature, streaming velocities are only studied for a few haloes" has been removed.
 

### 2019-11-25 paper.tex
Adding final revisions to paper and responses to referee.

@@
 Halos with an \hh{} column density of N$_{\rm H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars.
-Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19,Hirano17_Science}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}.
+Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19, Hirano17_Science}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}.
 X-ray heating from high-mass X-ray binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.
@@
 To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{OShea08} (their Figure 13d) with $J_{21}$ = 0, which was extracted directly from their plot.
-These profiles were approximated with a piecewise power-law for simplicity \textbf{given by Equation \ref{h2fitting}}.
-\begin{equation} \label{h2fitting}
-	log_{10}(f_{\rm H2}) = -0.482 \times log_{10}(R_{\rm vir}) - 4.714
-\end{equation}
+These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.482 \times \log_{10}(R_{\rm vir}) - 4.714$}.
 As the halo masses increase, the shielding factor increases, meaning there is less shielding occurring within that halo.
@@
 J$_{LW}$ = 0 for the various sources is plotted here at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
-The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
+\textbf{The left panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}.}The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
 For each band, the maximum halo mass occurs at $z = 15$.
 For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$, the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.
-\textbf{The minimum halo mass hosting cold dense gas for different streaming velocities in units of km/s from \citet{Schauer19} are shown as horizontal black lines with different linestyles.}}
+\textbf{The minimum halo mass hosting cold dense gas for different streaming velocities from \citet{Schauer19} are shown as horizontal black lines.}}
     \label{fig:compare_JLW_mass}
@@
 
-We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19}.
+We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19, Hirano17_Science}.
 Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with time.
@@
 \citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass halos.
+
 \textbf{A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within halos for varying streaming velocities, showed that high streaming velocities restrict first star formation to atomic cooling halos.
-Their minimum halo masses which host cold dense gas for various streaming velocities are shown as black horizontal lines with different linestyles in Figure \ref{fig:compare_JLW_mass}.} Our results indicate that halos collapse at larger masses that are not as affected by typical streaming velocities ($<1\sigma_{\rm vbc}$).
-In the evolution of such a halo, it would have started to accumulate gas above these critical masses while also being irradiated by a LW background.
+Their minimum halo masses which host cold dense gas for various streaming velocities are shown as black horizontal lines with different linestyles in Figure \ref{fig:compare_JLW_mass}.
+\citet{Hirano17_Science} investigated the effect that streaming velocities have on black hole formation in the early universe and find that in regions with high streaming velocities and for z $> 30$, first generation star formation can be suppressed in minihalos up to the atomic cooling limit, and may produce massive black hole seeds.}
+
+Our results indicate that halos collapse at larger masses that are not as affected by typical streaming velocities ($<1\sigma_{\rm vbc}$).
+\textbf{We also find that Pop III stars begin to form at much later times than the halos found in \citet{Hirano17_Science}.} In the evolution of such a halo, it would have started to accumulate gas above these critical masses while also being irradiated by a LW background.
 Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results.

### 2019-11-25 referee_2.tex
Adding final revisions to paper and responses to referee.

@@
 \begin{referee}
-    A -- In this paper, some very long paragraphs can be found, especially in Sections 3 and 4. Please break these long paragraphs down in smaller ones to increase the read flow. 
+    In this paper, some very long paragraphs can be found, especially in Sections 3 and 4. Please break these long paragraphs down in smaller ones to increase the read flow. 
 \end{referee}
@@
 
-    B -- The convergence study is a great addition to the paper.
+    The convergence study is a great addition to the paper.
 However, the lowest limit explored here (0.625pc) is a factor of roughly 100 larger than the scale on which fragmentation can be seen (compare eg the 1000AU regions, in which several Pop III stars form in work by Stacy+16).
@@
 
-    C -- - Is the SFRD really in physical (and not comoving) units (Figure 4 / Section 3)? Please provide values for the comparison papers (Xu+13, Magg+16) and include a comparison to Jaacks+19. 
+    - Is the SFRD really in physical (and not comoving) units (Figure 4 / Section 3)? Please provide values for the comparison papers (Xu+13, Magg+16) and include a comparison to Jaacks+19. 
 \end{referee}
@@
 \begin{referee}
-    D -- - The initialization at z=130 should be mentioned as a caveat. 
+    - The initialization at z=130 should be mentioned as a caveat. 
 \end{referee}
@@
 \begin{referee}
-    E -- - The analytic calculation of the self-shielding of the halo now takes into account a realistic halo profile. However, there are three issues: 
-    E.1 -- -- In the first paragraph of Section 2.4, it still reads "with a constant H2 fraction". Please correct this. 
+    - The analytic calculation of the self-shielding of the halo now takes into account a realistic halo profile. However, there are three issues: 
+    -- In the first paragraph of Section 2.4, it still reads "with a constant H2 fraction". Please correct this. 
 \end{referee}
@@
 \begin{referee}
-    E.2 -- -- For completeness, please provide the readers with the H2 radial fit to the O'Shea \& Normal 07 paper that was performed. 
+    -- For completeness, please provide the readers with the H2 radial fit to the O'Shea \& Normal 07 paper that was performed. 
 \end{referee}
@@
 \begin{referee}
-    E.3 -- -- Compared to the previous version with a constant profile, the shielding factor increases for higher halo masses (in the previous version of the paper, there was a slight decrease): leading to less shielding.
+    -- Compared to the previous version with a constant profile, the shielding factor increases for higher halo masses (in the previous version of the paper, there was a slight decrease): leading to less shielding.
 I do not understand where this is coming from, a more massive halo has a larger overall gas mass, and therefore more H2 and more shielding.
@@
 \begin{referee}
-    F -- - Thank you for adding the global LWBG as a dashed line in Figure 3. Please also mention at some point in the text or add a legend that this is again given in units of J21. 
+    - Thank you for adding the global LWBG as a dashed line in Figure 3. Please also mention at some point in the text or add a legend that this is again given in units of J21. 
 \end{referee}
@@
 \begin{referee}
-    G -- - I see that retrospectively calculating the time-averaged LWBG is not possible without repeating the study.
+    - I see that retrospectively calculating the time-averaged LWBG is not possible without repeating the study.
 However, please mention the possibility for a correlation between the time-integrated LWBG and the host halo mass in Section 3.2 and summary and be more explicit that this is the LWBG at star formation (eg in the introduction and in Section 3.2 and in the second bullet point of the Conclusions).
@@
 \begin{referee}
-    H -- - The authors put their work in comparison to Schauer+19, ApJL 877, 5 who match the star formation efficiency in minihaloes to the observed 21cm signal.
+    - The authors put their work in comparison to Schauer+19, ApJL 877, 5 who match the star formation efficiency in minihaloes to the observed 21cm signal.
 They should rather compare to Schauer+19 MNRAS, 484, 3510 who performed cosmological hydrodynamical simulations for the minimum and average halo mass in different streaming velocity regions.
@@
 \end{referee}
-	The limits from Schauer+19 have been added to Figure 10, and the previous description regarding the 21cm signal has been removed. 
-	--conclusions from this?
-	--weird to me how the units of the streaming velocities are different. Change this?
-	--unbolded addition to citation in caveat section
+    We have added a panel to the left of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minimums related to streaming velocitys.
 
-	--need to add the Hirano+18 science paper to caveats section
+    The limits from Schauer+19 have been added to the left panel of Figure 10, and the previous description regarding the 21cm signal has been removed.
+Their citation has been added to the list of citations investigating streaming velocities.
 
-	Schauer+19 and Hirano+18 have been added to the introduction (unbolded -- fix this?).
+    We have added a short compariosn to Hirano+18 and have also added their citation to the list of citations mentioned previously.
+
+    These citations have also been added to the introduction.
 

### 2019-11-25 referee_2.tex
Adding response to major comment 1

@@
 \end{referee}
-    The lowest limit has been added to section 2.2.1.
+    In Section 2.2, we have expanded our description of the convergence study to include the smallest resolution and pointed out that the overdensity formation criterion is similar to a molecular core.
+We explicitly state that our results are lower limits on the number of Pop III stars, massive and low-mass, in this section.
+Furthermore, we remind the reader about this lower limit in Section 3.3, where we present our results on the stellar multiplicity.
+Lastly, we have added a paragraph in the Caveats section (S4.3) about our simulation not resolving fragment below 0.625 pc and emphasize that our work strengthens the case for multiple Pop III stars in each halo, especially considering this limitation.
 
-    --Added to the caveats
-
-    \jhw{I've add some wording in Sections 2.2.1 and 3.3 about fragmentation and our study being a lower limit on the multiplicity but nothing to the caveats section.
-I think with these statements, we can argue in the response that changes throughout the text are not needed.
-Make the changes to the caveats section, and I'll write the rebuttal here.}
+    That being said, we decided to refer to these star forming regions as ``stars'' throughout the paper because the phrase ``star forming regions'' or something similar would have been too wordy because it is mentioned many times throughout the manuscript and in the figures.
+We feel that emphasizing that our results are lower limits on the number of massive Pop III stars is a good compromise.
 

### 2019-11-25 paper.tex
Updating shielding factor -- piecewise power law

@@
 To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{OShea08} (their Figure 13d) with $J_{21}$ = 0, which was extracted directly from their plot.
-These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.482 \times \log_{10}(R_{\rm vir}) - 4.714$}.
+These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.199 \times \log_{10}(R) - 3.646$ for $R < 10$ pc and $\log_{10}(f_{\rm H2}) = -0.696 \times \log_{10}(R) - 4.939$ for $R >= 10$ pc}.
 As the halo masses increase, the shielding factor increases, meaning there is less shielding occurring within that halo.

### 2019-11-25 referee_2.tex

@@
 \parskip=10pt
+\setlength\parindent{0pt}
 
@@
 Furthermore, we remind the reader about this lower limit in Section 3.3, where we present our results on the stellar multiplicity.
-Lastly, we have added a paragraph in the Caveats section (S4.3) about our simulation not resolving fragment below 0.625 pc and emphasize that our work strengthens the case for multiple Pop III stars in each halo, especially considering this limitation.
+Lastly, we have added a paragraph in the Caveats section (S4.3) about our simulation not resolving fragmentation below 0.625 pc and conclude that our work strengthens the case for multiple Pop III stars in each halo, especially considering this limitation.
 
-    That being said, we decided to refer to these star forming regions as ``stars'' throughout the paper because the phrase ``star forming regions'' or something similar would have been too wordy because it is mentioned many times throughout the manuscript and in the figures.
-We feel that emphasizing that our results are lower limits on the number of massive Pop III stars is a good compromise.
+    That being said, we decided to retain the naming of these star forming regions as ``stars'' throughout the paper because the phrase ``star forming regions'' or something similar would have been too wordy as it is mentioned many times throughout the manuscript and in the figures.
+We feel that emphasizing that our results are lower limits on the number of massive Pop III stars throughout the paper is a good compromise.
 
@@
 \end{referee}
-
     Upon review of these calculations, you are correct in questioning the units of the SFRD.
@@
 \end{referee}
-    The shielding factor increases for more massive halos because these halos have larger virial radii, at which point there is significantly less \hh{} compared to smaller radii.
-So halos with smaller masses, and thus smaller virial radii, have more \hh{} built up at the edges compared to their larger counterparts, resulting in a more effective shield at the virial radius.
-We have clarified this point in the text.
+    The shielding factor increases for more massive halos because these halos have larger virial radii, at which point there is significantly less \hh{} compared to the halo's interior.
+So halos with smaller masses, and thus smaller virial radii, have a higher \hh{} fraction in their outer regions compared to their larger counterparts, resulting in a more effective H2 shield.
+
+    \jhw{Possibly revise after using piecewise fitting function.}
 
@@
 \end{referee}
-    We have added a panel to the left of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minimums related to streaming velocitys.
+    We have added a panel to the left of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minimums related to streaming velocities.
 
@@
 
-    We have added a short compariosn to Hirano+18 and have also added their citation to the list of citations mentioned previously.
+    We have added a short comparison to Hirano+17 (Science) and have also added their citation to the list of citations mentioned previously.
 

### 2019-11-27 paper.tex
Fixing shielding factor plot. Text has been added to the paper to reflect the now decreasing shielding factor, and a response has been added to referee_2.tex.

--- 2019-11-25 paper.tex
@@
 To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{OShea08} (their Figure 13d) with $J_{21}$ = 0, which was extracted directly from their plot.
-These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.482 \times \log_{10}(R_{\rm vir}) - 4.714$}.
-As the halo masses increase, the shielding factor increases, meaning there is less shielding occurring within that halo.
-This behavior occurs because at larger radii, there is less \hh{} available, and therefore, the effects of shielding are decreased.
+These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.192 \times \log_{10}(R) - 3.039$ for $R < 3.5$ pc and $\log_{10}(f_{\rm H2}) = -0.745 \times \log_{10}(R) - 2.737$ for $R > 3.5$ pc}.
+As the halo masses increase, the shielding factor \textbf{decreases}, meaning there is \textbf{more} shielding occurring within that halo.
+This behavior occurs \textbf{because as halo masses increase, more \hh{} is being added to the calculation of the column density.
+The more \hh{} present within a halo, the smaller the shielding factor will become}.
 Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.

### 2019-11-27 referee_2.tex
Fixing shielding factor plot. Text has been added to the paper to reflect the now decreasing shielding factor, and a response has been added to referee_2.tex.

@@
 \end{referee}
-    The shielding factor increases for more massive halos because these halos have larger virial radii, at which point there is significantly less \hh{} compared to the halo's interior.
-So halos with smaller masses, and thus smaller virial radii, have a higher \hh{} fraction in their outer regions compared to their larger counterparts, resulting in a more effective H2 shield.
-
-    \jhw{Possibly revise after using piecewise fitting function.}
+    We thank the reader for asking these questions.
+They have caused us to go back to our calculations to try to find the source of the increase in the shielding factor for larger halo masses.
+It turned out that there was an error in our calculations stemming from when we assumed a constant H2 fraction.
+This has been fixed, as well as an incorrect decimal place in our core radius calculations, and we now see decreased shielding factors (more effective shielding) for increased halo masses, as expected.
+We would like to remind the referee that the dashed lines indicate a smaller core radius, and thus, the shielding factor is even more effective for this core radius since more H2 is being added to the column density.
 

### 2019-12-05 paper.tex
Changes after my 1st proofread

@@
 In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.
-\textbf{We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.
-Our density threshold for star particle formation is equivalent to a molecular core.
+\textbf{We ran another 1~Mpc$^3$ simulation with the same setup as the main simulation with the exception that it was a zoom-in simulation focusing on a single minihalo of mass $5 \times 10^5~\Ms$ collapsing at $z \simeq 23$.
+Starting from 1~Myr before the collapse, we followed Pop III star formation in this one halo with a merging distance of 10, 5, 2.5, 1.25, and 0.625~pc.
+We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.
+We note that our density threshold for star particle formation is equivalent to a molecular core.
 Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU \citep[e.g.][]{Turk09, Stacy11} with molecular cores, therefore our results on multiplicity should be considered as lower limits.}
@@
 The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}).
-\textbf{The solid red line in the legend refers to both the solid and dashed lines in the figure.}Temperature projections are shown at the points indicated by the arrows.}
+\textbf{The solid red line in the legend refers to both the solid and dashed lines in the figure.} Temperature projections are shown at the points indicated by the arrows.}
     \label{fig:JLW_xe_mass}
@@
 In particular, it decreases at $z \le 11$ when the most massive galaxy undergoes an extended period of star formation, boosting the local LW radiation field as shown in Figure \ref{fig:JLW_xe_mass}.
-\textbf{\citet{Xu13} and \citet{Magg16} see a SFRD of $~10^{-4} \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 15$ and $z = 20$ respectively.
-\citet{Jaacks19} find a SFRD of $~10^{4.5} \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 20$, which flattens out to $10^{-3} \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ by $z =7$.} \textbf{Our} SFRD rates are consistent with \textbf{these} other studies, but it is likely to change depending on the particular modes captured by the initial conditions.
+\textbf{\citet{Xu13} and \citet{Magg16} see a SFRD of $~10^{-4}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 15$ and $z = 20$ respectively.
+\citet{Jaacks19} find a SFRD of $~10^{4.5}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 20$, which flattens out to $10^{-3}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ by $z =7$.} \textbf{Our} SFRD rates are consistent with \textbf{these} other studies, but it is likely to change depending on the particular modes captured by the initial conditions.
 
@@
 We now inspect the number of Pop III stars and the total mass of Pop III stars per halo.
-Again, we are only tracking \textbf{star-forming regions where the star particles form at densities equivalent to molecular cores that may form multiple massive stars.
+We are only tracking \textbf{star-forming regions where the star particles form at densities equivalent to molecular cores that may form multiple massive stars.
 Furthermore, we are not modeling the formation of low-mass stars ($<1 M_{\odot}$) that may form out of fragmented gas at higher densities and smaller scales.
@@
 J$_{LW}$ = 0 for the various sources is plotted here at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
-\textbf{The left panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}.}The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
+\textbf{The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}} The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
 For each band, the maximum halo mass occurs at $z = 15$.
-For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$, the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.
-\textbf{The minimum halo mass hosting cold dense gas for different streaming velocities from \citet{Schauer19} are shown as horizontal black lines.}}
+For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$ (5.8 km/s at $z=199$), the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.
+\textbf{The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=199$, from \citet{Schauer19} are shown as horizontal black lines.}}
     \label{fig:compare_JLW_mass}
@@
 There are a few minor shortcomings to this work that should be noted.
-\textbf{As discussed in section 2.2.1, the number of Pop III stars that form is insensitive down to distances of 0.625 pc.
-Since this value is larger than fragmentation scales, it's possible that the location of the Pop III stars formed in our simulation are sites for multiple Pop III star formation.
-With this in mind, our results are only strengthened by the possibility of having more Pop III stars forming at these locations.}
+\textbf{As discussed in \S2.2.1, the number of Pop III stars that form is insensitive down to distances of 0.625 pc.
+Since this value is larger than fragmentation scales, it is possible that the location of the Pop III star particles formed in our simulation are sites for multiple Pop III star formation.
+With this in mind, our multiplicity results are only strengthened by the possibility of having more Pop III stars forming at these locations.}
 
@@
 We also do not include streaming velocities between baryons and dark matter within our simulation \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19, Hirano17_Science}.
-Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease with time.
+Streaming velocities can suppress star formation at very high ($z \ga 20$) redshifts only, because the streaming velocities decrease inversely with the scale factor.
 Pop III star formation is delayed by an average of $\delta z = 4$ by increasing the halo mass needed to overcome the bulk velocity by about a factor of three \citep{Greif11_Delay}.
@@
 \citet{Naoz13} estimated the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be seen in Figure \ref{fig:compare_JLW_mass} (see shaded bands).
-These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc}$, which is smaller than the star forming halos in our simulation.
+These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc} = 3$ km/s at $z=99$, which is smaller than the star forming halos in our simulation.
 \citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass halos.
 
-\textbf{A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within halos for varying streaming velocities, showed that high streaming velocities restrict first star formation to atomic cooling halos.
-Their minimum halo masses which host cold dense gas for various streaming velocities are shown as black horizontal lines with different linestyles in Figure \ref{fig:compare_JLW_mass}.
-\citet{Hirano17_Science} investigated the effect that streaming velocities have on black hole formation in the early universe and find that in regions with high streaming velocities and for z $> 30$, first generation star formation can be suppressed in minihalos up to the atomic cooling limit, and may produce massive black hole seeds.}
+\textbf{A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within halos for varying streaming velocities, showed that high streaming velocities could restrict first star formation to atomic cooling halos in the most extreme cases.
+Their minimum halo masses which host cold dense gas for various streaming velocities are shown as black horizontal lines in Figure \ref{fig:compare_JLW_mass}.
+\citet{Hirano17_Science} investigated the effect that streaming velocities have on massive black hole seed formation and find that in regions with high streaming velocities and for z $> 30$, first generation star formation can be suppressed in minihalos up to the atomic cooling limit.}
 
-Our results indicate that halos collapse at larger masses that are not as affected by typical streaming velocities ($<1\sigma_{\rm vbc}$).
-\textbf{We also find that Pop III stars begin to form at much later times than the halos found in \citet{Hirano17_Science}.} In the evolution of such a halo, it would have started to accumulate gas above these critical masses while also being irradiated by a LW background.
-Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our results.
+\textbf{The results of \citet{Naoz13} and \citep{Schauer19} in Figure \ref{fig:compare_JLW_mass} show that typical streaming velocities ($\le 1\sigma_{\rm vbc} = 5.8$~km/s at $z=199$) would affect halos below $10^6~\Ms$, especially at redshifts $z>20$ when streaming velocities are the strongest.
+Our results sample minihalos that experience such streaming velocities primarily at $z < 20$, whereas \citet{Hirano17_Science} studied much earlier structure formation.
+In the evolution of a halo affected by streaming velocities, it would have started to accumulate gas once above these critical masses while also being irradiated by a LW background.
+Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our main conclusion that \hh{} plays an important role in Pop III star formation.}
 

### 2019-12-05 paper.tex
Changes after 2nd proofreading

@@
 It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.
-\textbf{We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.
-Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.} The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions.
+We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.
+Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.
+The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions.
 \textbf{We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.} The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue.
@@
 In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.
-Throughout the rest of the paper, all numbers are in physical units\textbf{, unless otherwise specified}.
+Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.
 
@@
 We note that our density threshold for star particle formation is equivalent to a molecular core.
-Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU \citep[e.g.][]{Turk09, Stacy11} with molecular cores, therefore our results on multiplicity should be considered as lower limits.}
+Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU within molecular cores \citep[e.g.][]{Turk09, Stacy11}, therefore our results on multiplicity should be considered as lower limits.}
 
@@
 \end{equation}
-Here, x $\equiv$ N$_{\rm H2}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter.
+Here, $x \equiv N_{\rm H2}/5 \times 10^{14}$ cm$^{-2}$, $b_{5} \equiv b/10^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter.
 This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding.
@@
 The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$.
-To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at z = 24.1 from \citet{OShea08} (their Figure 13d) with $J_{21}$ = 0, which was extracted directly from their plot.
-These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.192 \times \log_{10}(R) - 3.039$ for $R < 3.5$ pc and $\log_{10}(f_{\rm H2}) = -0.745 \times \log_{10}(R) - 2.737$ for $R > 3.5$ pc}.
+To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at $z = 24.1$ from \citet{OShea08} (their Figure 13d) with $J_{21} = 0$, which was extracted directly from their plot.
+These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.192 \times \log_{10}(r) - 3.039$ for $r < 3.5$ pc and $\log_{10}(f_{\rm H2}) = -0.745 \times \log_{10}(r) - 2.737$ for $r > 3.5$ pc}.
 As the halo masses increase, the shielding factor \textbf{decreases}, meaning there is \textbf{more} shielding occurring within that halo.
@@
 The more \hh{} present within a halo, the smaller the shielding factor will become}.
-Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s.
+Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a Doppler broadening parameter $ b = 10 \kms$.
 At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum.
-The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background.
-Smaller mass halos can then form Pop III stars since \hh{} will survive in the halo for a longer amount of time.
-We also see that for column densities at just under $10^{17} \rm cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} in relatively low halo masses.
+Self-shielding will then significantly decrease the dissociation rate of \hh{} in the halo core, allowing for the presence of a significant \hh{} fraction even in a strong LW background.
 
@@
 Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$.
-For these parameters, assuming the Doppler broadening parameter equals the circular velocity, and assuming \hh{} fraction halo profiles from \citet{oshea07a}, the shielding factor is below 1 percent.
-The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s.
+For these parameters, assuming the Doppler broadening parameter $b$ equals the circular velocity, and assuming \hh{} fraction halo profiles from \citet{oshea07a}, the shielding factor is below 1 percent.
+The green line shows the shielding factor as a function of \hh{} column density for $b = 10 \kms$.
 Note that a shielding factor of 1 (0) corresponds to no (complete) shielding.}
@@
 In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place.
-By the end of the simulation, 20\% of the box has an ionized fraction greater than 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from sources} as a function of time, \textbf{the LW background given by equation \ref{LWbg} in units of J$_{21}$,} and temperature projections of the box at certain points in time.
+By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from stars within the simulation} as a function of time, \textbf{the LW background given by Equation \ref{LWbg} in units of J$_{21}$,} and temperature projections of the box at certain points in time.
 
@@
 	\includegraphics[width=\columnwidth]{images/jlw_xe_bg_mass_weight.pdf}
-    \caption{For the entire box, the average mass weighted LW background from sources shown in solid red and the fraction of the volume ionized above 10\% versus time shown in solid black.
+    \caption{For the entire box, the mass-weighted average LW intensity from stars within the simulation is shown in solid red, and the fraction of the volume ionized above 10 per cent versus time is shown in solid black.
 The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}).
@@
 \ref{LWbg}).
-In this work, we only analyze halos below the atomic cooling limit.
 
@@
 We are only tracking \textbf{star-forming regions where the star particles form at densities equivalent to molecular cores that may form multiple massive stars.
-Furthermore, we are not modeling the formation of low-mass stars ($<1 M_{\odot}$) that may form out of fragmented gas at higher densities and smaller scales.
-Thus our results in this section should be considered as lower limits to the number of Pop III stars.}  The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation.
+Furthermore, we are not modeling the formation of low-mass stars ($<1~\Ms$) that may form out of fragmented gas at higher densities and smaller scales.
+Thus our results in this section should be considered as lower limits to the number of Pop III stars.}
+
+The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation.
 The histogram of the number of Pop III stars for all masses is projected on the right hand side.
@@
 We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation.
+
 There are three main causes of this significant variation in mass.
@@
 Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.
+
 Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}.
 This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}.
+
 Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool.
@@
 There are a few minor shortcomings to this work that should be noted.
-\textbf{As discussed in \S2.2.1, the number of Pop III stars that form is insensitive down to distances of 0.625 pc.
-Since this value is larger than fragmentation scales, it is possible that the location of the Pop III star particles formed in our simulation are sites for multiple Pop III star formation.
+\textbf{As discussed in \S2.2.1, the number of Pop III star particles that form is insensitive to merging distances in our formation algorithm down to 0.625 pc.
+Since this value is larger than fragmentation scales within molecular cores, it is possible that our Pop III star particles are sites for multiple Pop III star formation.
 With this in mind, our multiplicity results are only strengthened by the possibility of having more Pop III stars forming at these locations.}
@@
 In their more recent work, they find that this difference in LW escape fractions between when \hh{} shielding by neutral hydrogen is included or not is negligible.
+
 \citet{kitayama04} investigated the transition between D-type and R-type ionization fronts within halos to determine the escape fractions of ionizing and photodissociating photons using a one-dimensional Lagrangian hydrodynamics code.

### 2019-12-05 paper.tex
Minor typos

@@
 \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
-They fit a simple analytic expression for the mass threshold of halos given a particular LW intensity J$_{\rm LW}$:
+They fit a simple analytic expression for the mass threshold of halos given a particular LW intensity $J_{\rm LW}$:
 \begin{equation} \label{mthresh}
@@
 We will compare our results with this relation in future sections.
-\citet{Yoshida03} also found that cooling is inefficient in halos with a LW background > 0.01 J$_{\rm 21}$, where J$_{\rm 21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation.
-In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 J$_{21}$.
+\citet{Yoshida03} also found that cooling is inefficient in halos with a LW background > 0.01 $J_{\rm 21}$, where $J_{\rm 21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation.
+In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 $J_{21}$.
 They find that \hh{} cooling is always a dominant process, even in large LW background fluxes.
@@
 In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place.
-By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from stars within the simulation} as a function of time, \textbf{the LW background given by Equation \ref{LWbg} in units of J$_{21}$,} and temperature projections of the box at certain points in time.
+By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from stars within the simulation} as a function of time, \textbf{the LW background given by Equation \ref{LWbg} in units of $J_{21}$,} and temperature projections of the box at certain points in time.
 
@@
 We see again that almost all halos form Pop III stars below the M01 threshold.
-There are also a few halos that form Pop III stars in very high J$_{\rm LW}$, below the relation.
+There are also a few halos that form Pop III stars in very high $J_{\rm LW}$, below the relation.
 This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 100 pc of each other.
 Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation.
-The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs at about the same time, star formation will not be suppressed, so long as they are a suitable distance away from each other.
+The high $J_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs at about the same time, star formation will not be suppressed, so long as they are a suitable distance away from each other.
 As there are only a few data points in this region, this situation is rare.
 It should be noted that there are duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation.
-The grouped points in the higher end of J$_{\rm LW}$ are representative of such halos.
+The grouped points in the higher end of $J_{\rm LW}$ are representative of such halos.
 
@@
 In a series of simulations, they found a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12).
-They found that in the presence of a LW background of 0.01 J$_{21}$, the minimum halo mass is $7 \times 10^{5} M_{\odot}$.
+They found that in the presence of a LW background of 0.01 $J_{21}$, the minimum halo mass is $7 \times 10^{5} M_{\odot}$.
 When \hh{} self-shielding is taken into account along with a LW background, their minimum halo mass decreases to $4.5 \times 10^{5} M_{\odot}$.
@@
 In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses, ranging from $2.8 \times 10^{5}$ M$_{\odot}$ to $1.4 \times 10^{7}$ M$_{\odot}$.
-While our halos never experience a LW intensity as low as 0.01 J$_{21}$, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}).
+While our halos never experience a LW intensity as low as 0.01 $J_{21}$, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}).
 
@@
 They did not include self-shielding and subsequently found halo masses at their collapse that lie well above the M01 relation (see red open triangles in Figure \ref{fig:compare_JLW_mass}).
-Their J$_{\rm LW}$ = 0 control is plotted in Figure \ref{fig:compare_JLW_mass} at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
+Their $J_{\rm LW} = 0$ control is plotted in Figure \ref{fig:compare_JLW_mass} at $J_{\rm LW}/J_{21} = 10^{-4}$.
 \citet{OShea08} used cosmological simulations to investigate Pop III star formation in various LW backgrounds.
@@
 Their halo masses are similar to the results of \citet{Wise07_UVB}.
-Their control of J$_{21}$ = 0 control is plotted at J$_{LW}$/J$_{21}$ = 10$^{-4}$.
+Their control of $J_{21}$ = 0 control is plotted at $J_{\rm LW}/J_{21} = 10^{-4}$.
 \citet{Hirano15} used cosmological simulations to study 1540 collapsing metal-free gas clouds in the early universe to derive the corresponding primordial stellar mass distribution.
@@
 The black solid line is from M01 given our LW background, blue solid line from \citet{Trenti09_SFR} at $z=20$, the purple solid line from \citet{Visbal14} at $z=20$, blue open circle from \citet{Yoshida03}, green open squares from \citet{OShea08}, and red open triangles from \citet{Wise07_UVB}.
-J$_{LW}$ = 0 for the various sources is plotted here at J$_{\rm LW}$/J$_{21}$ = 10$^{-4}$.
+$J_{LW}$ = 0 for the various sources is plotted here at $J_{\rm LW}$/$J_{21}$ = 10$^{-4}$.
 \textbf{The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}} The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
 For each band, the maximum halo mass occurs at $z = 15$.
-For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$ (5.8 km/s at $z=199$), the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.
+For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$ (5.8 \kms{} at $z=199$), the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.
 \textbf{The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=199$, from \citet{Schauer19} are shown as horizontal black lines.}}
@@
 \citet{Naoz13} estimated the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be seen in Figure \ref{fig:compare_JLW_mass} (see shaded bands).
-These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc} = 3$ km/s at $z=99$, which is smaller than the star forming halos in our simulation.
+These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc} = 3 \kms$ at $z=99$, which is smaller than the star forming halos in our simulation.
 \citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass halos.
@@
 
-\textbf{The results of \citet{Naoz13} and \citep{Schauer19} in Figure \ref{fig:compare_JLW_mass} show that typical streaming velocities ($\le 1\sigma_{\rm vbc} = 5.8$~km/s at $z=199$) would affect halos below $10^6~\Ms$, especially at redshifts $z>20$ when streaming velocities are the strongest.
+\textbf{The results of \citet{Naoz13} and \citep{Schauer19} in Figure \ref{fig:compare_JLW_mass} show that typical streaming velocities ($\le 1\sigma_{\rm vbc} = 5.8\kms$ at $z=199$) would affect halos below $10^6~\Ms$, especially at redshifts $z>20$ when streaming velocities are the strongest.
 Our results sample minihalos that experience such streaming velocities primarily at $z < 20$, whereas \citet{Hirano17_Science} studied much earlier structure formation.

### 2019-12-05 paper.tex
Spell checking (also halos -> haloes)

@@
 One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, that destroys \hh{}, a necessary coolant in the creation of Pop III stars.
-Self-shielding can alleviate the effect the LW background has on the \hh{} within halos.
+Self-shielding can alleviate the effect the LW background has on the \hh{} within haloes.
 In this work, we perform a cosmological simulation to study the birthplaces of Pop III stars, using the adaptive mesh refinement code \textsc{Enzo}.
 We investigate the distribution of host halo masses and its relationship to the LW background intensity.
-Compared to previous work, halos form Pop III stars at much lower masses, up to a factor of a few, due to the inclusion of \hh{} self-shielding.
+Compared to previous work, haloes form Pop III stars at much lower masses, up to a factor of a few, due to the inclusion of \hh{} self-shielding.
 We see no relationship between the LW intensity and host halo mass.
-Most halos form multiple Pop III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation.
+Most haloes form multiple Pop III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation.
 Our results suggest that Pop III star formation may be less affected by LW radiation feedback than previously thought and that Pop III multiple systems are common.
@@
 This marks the end of metal-free star formation in that pregalactic object.
-Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation.
-Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep{Wise08_Gal, Greif10, Smith15}.
-Stars will continue to form in halos, but with an increased metal abundance.
+Understanding the mixing of metals into the environment of these haloes is necessary to constrain the reach of these metals and the effects they have for future star formation.
+Numerical studies have shown that turbulence within haloes can mix metals well down to their resolution limit \citep{Wise08_Gal, Greif10, Smith15}.
+Stars will continue to form in haloes, but with an increased metal abundance.
 These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and can survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18, Ezzeddine19}.
@@
 Diffuse gas is optically thin to LW radiation, thus a background builds over time and can suppress \hh{} formation, delaying Pop III star formation.
-Furthermore, nearby sources of LW radiation can boost the intensity above the background value which facilitates further \hh{} dissociation in minihalos.
+Furthermore, nearby sources of LW radiation can boost the intensity above the background value which facilitates further \hh{} dissociation in minihaloes.
 This process can be counteracted with a sufficient amount of \hh{} already present within a halo, via \hh{} self-shielding.
 Halos with an \hh{} column density of N$_{\rm H2}$ $\geq$ 10$^{14}$ cm$^{-2}$ can suppress the photodissociation of \hh{} by LW photons \citep{Draine96}, giving the halo a chance to form Pop III stars.
-Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19, Hirano17_Science}, arising from recombination, and dynamical heating, occurring during the virialization of halos \citep{Yoshida03, Fernandez14}.
+Other sources of the suppression of Pop III star formation are streaming baryonic velocities \citep{Tselia11, Greif11_Delay, Naoz12, OLeary12, Schauer19, Hirano17_Science}, arising from recombination, and dynamical heating, occurring during the virialization of haloes \citep{Yoshida03, Fernandez14}.
 X-ray heating from high-mass X-ray binaries also has the potential to suppress Pop III star formation \citep{Jeon14}.
 
-Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos.
-But in which halos do these first generations of stars form?
+Given the paradigm of hierarchical structure formation, haloes grow through smooth accretion and successive mergers of smaller haloes.
+But in which haloes do these first generations of stars form?
 Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization.
-Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars.
-\citet{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15.
-In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time.
+Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which haloes can host Pop III stars.
+\citet{Tegmark97} discovered that haloes can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15.
+In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  haloes can cool in a Hubble time.
 \citet{Visbal18} devised a semi-analytic model for the formation of Pop III stars and the transition to metal-enriched stars.
@@
 Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation.
-\citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos.
-They fit a simple analytic expression for the mass threshold of halos given a particular LW intensity $J_{\rm LW}$:
+\citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass haloes.
+They fit a simple analytic expression for the mass threshold of haloes given a particular LW intensity $J_{\rm LW}$:
 \begin{equation} \label{mthresh}
@@
 We will compare our results with this relation in future sections.
-\citet{Yoshida03} also found that cooling is inefficient in halos with a LW background > 0.01 $J_{\rm 21}$, where $J_{\rm 21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation.
+\citet{Yoshida03} also found that cooling is inefficient in haloes with a LW background > 0.01 $J_{\rm 21}$, where $J_{\rm 21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$, although with sufficient \hh{} shielding, haloes are able to cool in the given LW background radiation.
 In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 $J_{21}$.
@@
 In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background \textbf{at the instance of star formation}, augmenting results from prior work.
-We aim to provide further insight into the host halos of Pop III stars.
+We aim to provide further insight into the host haloes of Pop III stars.
 In \S 2 the methods of the simulation, implementation of star formation, feedback, and \hh{} self-shielding are described.
@@
 We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
-resolution and a dark matter paticle mass of 2001 M$_{\odot}$.
+resolution and a dark matter particle mass of 2001 M$_{\odot}$.
 It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.
@@
 With the improved calculation of the column density, they find that the shielding factor is larger for gas at higher temperatures near $10^4$~K than when the shielding factor is calculated for an average column density for the halo, meaning that self-shielding is generally less efficient for higher temperatures.
-In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our halos are less massive and contain gas at lower temperatures.
-Our calculation of the shielding factor is still valid for the temperature range of our halos, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.
+In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our haloes are less massive and contain gas at lower temperatures.
+Our calculation of the shielding factor is still valid for the temperature range of our haloes, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.
 
@@
 Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a Doppler broadening parameter $ b = 10 \kms$.
-At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum.
+At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these haloes is almost at a maximum.
 Self-shielding will then significantly decrease the dissociation rate of \hh{} in the halo core, allowing for the presence of a significant \hh{} fraction even in a strong LW background.
@@
 To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$.
-The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles.
+The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ haloes that contain $\approx$ 50 particles.
 After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box.
-When the first Pop III star forms in our simulation at $z = 27$, there are only 6 halos that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}.
+When the first Pop III star forms in our simulation at $z = 27$, there are only 6 haloes that are above $10^5~\Ms$, which are resolved by 50 DM particles, consistent with analytical expectations from an ellipsoidal variant of Press-Schechter formalism \citep{PS74,Sheth01}.
 These Pop III stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings.
 Metal-enriched star formation begins to take place as soon as enough metals are present within a halo.
-In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place.
+In the meantime, haloes form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place.
 By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from stars within the simulation} as a function of time, \textbf{the LW background given by Equation \ref{LWbg} in units of $J_{21}$,} and temperature projections of the box at certain points in time.
@@
 The thick, black line is the analytic Sheth-Tormen mass function.
-The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where halos are captured by 50 particles.
+The distribution of halo masses matches well with analytical expectations above 10$^{5}$ M$_{\odot}$, where haloes are captured by 50 particles.
 The vertical blue line indicates our halo mass resolution limit of 10$^{5}$ M$_{\odot}$.}
@@
 %====================================================================
- To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, an algorithm that adaptively refines halos found with a friends-of-friends method in position and velocity phase-space and also temporally.
-The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$.
+ To determine the host haloes of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}, an algorithm that adaptively refines haloes found with a friends-of-friends method in position and velocity phase-space and also temporally.
+The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the haloes, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$.
 The total mass is subsequently used in our analysis.
-For stars that form in subhalos identified by \rockstar{}, we assign the parent halo mass as the host halo mass.
+For stars that form in subhaloes identified by \rockstar{}, we assign the parent halo mass as the host halo mass.
 There is one interesting case that we exclude from our analysis, where the parent halo is above the atomic cooling limit, because the radiative cooling physics are different in this regime and is not sensitive to a LW background.
@@
 About 1\% of Pop III stars do not form in a halo identified by \rockstar{}.
-Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$.
+Assuming that Pop III stars must form in collapsed haloes, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$.
 We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo.
@@
 The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation.
-\hh{} shielding allows for halos to cool at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times.
+\hh{} shielding allows for haloes to cool at much lower masses, and therefore, Pop III stars are forming in these haloes at earlier times.
 In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times.
@@
 
-Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[e.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
-As can be seen by the red solid line in Figure \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation.
+Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass haloes collapse in the presence of a LW background radiation \citep[e.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}.
+As can be seen by the red solid line in Figure \ref{fig:mean_mass}, nearly 100\% of the haloes hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation.
 The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times.
@@
 	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
-    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus time.
+    \caption{For haloes hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus time.
 The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass.
 The error bars indicate the 15.9 and 84.1 percentiles.
-The right hand side shows the percentage of halos that fall below the M01 mass threshold as a function of redshift.
+The right hand side shows the percentage of haloes that fall below the M01 mass threshold as a function of redshift.
 The M01 mass threshold (Eq.
@@
 \ref{LWbg}.
-Almost all halos fall below the M01 relation, until $\approx$ 380 Myr, when the mean halo mass rises above the relation.}
+Almost all haloes fall below the M01 relation, until $\approx$ 380 Myr, when the mean halo mass rises above the relation.}
     \label{fig:mean_mass}
@@
 \ref{LWbg}) is the solid black line.
-We see again that almost all halos form Pop III stars below the M01 threshold.
-There are also a few halos that form Pop III stars in very high $J_{\rm LW}$, below the relation.
+We see again that almost all haloes form Pop III stars below the M01 threshold.
+There are also a few haloes that form Pop III stars in very high $J_{\rm LW}$, below the relation.
 This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 100 pc of each other.
 Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation.
-The high $J_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs at about the same time, star formation will not be suppressed, so long as they are a suitable distance away from each other.
+The high $J_{\rm LW}$ is generally an indicator that the haloes will likely have their star formation suppressed, but in cases where Pop III star formation occurs at about the same time, star formation will not be suppressed, so long as they are a suitable distance away from each other.
 As there are only a few data points in this region, this situation is rare.
-It should be noted that there are duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation.
-The grouped points in the higher end of $J_{\rm LW}$ are representative of such halos.
+It should be noted that there are duplicate haloes within this plot, since haloes are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation.
+The grouped points in the higher end of $J_{\rm LW}$ are representative of such haloes.
 
-We find that a total of 84\% of the halos forming Pop III stars lie below the M01 mass threshold over the entire simulation redshift range.
-Given that the background intensity only varies by a factor of five, previous work suggested that most halos should have formed stars around or above the M01 relationship.
+We find that a total of 84\% of the haloes forming Pop III stars lie below the M01 mass threshold over the entire simulation redshift range.
+Given that the background intensity only varies by a factor of five, previous work suggested that most haloes should have formed stars around or above the M01 relationship.
 However, we see a large spread in host halo masses, over an order of magnitude, and no clear relationship between the \textbf{instantaneous} LW intensity and the host halo mass.
@@
 	\includegraphics[width=\columnwidth]{images/jlw_mass_machacek_total.pdf}
-	\caption{The average LW background for host halos of new Pop III stars is plotted versus the host halo mass, colored by redshift.
+	\caption{The average LW background for host haloes of new Pop III stars is plotted versus the host halo mass, colored by redshift.
 The Machacek et al.
@@
 \ref{LWbg}.
-Almost all halos fall below the relation, across a range of redshifts.
-There are extreme cases where Pop III stars form in small halos located in a very intense LW radiation field or large halos in relatively weak radiation fields.}
+Almost all haloes fall below the relation, across a range of redshifts.
+There are extreme cases where Pop III stars form in small haloes located in a very intense LW radiation field or large haloes in relatively weak radiation fields.}
     \label{fig:jlw_mass_machacek}
@@
 Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo.
-Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars, similar to the radiation hydrodynamic simulations of \citet{Susa13, Susa14}.
-It should be noted that these halos are not necessarily forming all of the Pop III stars at once.
+Out of the haloes forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars, similar to the radiation hydrodynamic simulations of \citet{Susa13, Susa14}.
+It should be noted that these haloes are not necessarily forming all of the Pop III stars at once.
 For example, a halo can form stars again if it did not host a supernova.
 The number of Pop III stars that form within a halo is indicative of the star formation history of that halo.
-Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side.
+Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all haloes is projected on the right hand side.
 Lines of constant star formation efficiency are overplotted.
 We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$.
-The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$.
+The mean total mass of Pop III stars for all haloes is 195 M$_{\odot}$.
 Note that the mass of the Pop III stars depends on the chosen IMF.
 
-At the end of the simulation, the right panel of Figure \ref{fig:num_p3} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star.
+At the end of the simulation, the right panel of Figure \ref{fig:num_p3} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all haloes in the simulation that host either a living or a remnant Pop III star.
 The red line shows the median number of Pop III stars for each halo mass bin.
 At low masses, the number of Pop III stars per halo sits around 2 Pop III stars, and quickly rises once the halo mass reaches $10^{7} M_{\odot}$.
-\citet{Xu13} found that at $z = 15$, halos with masses at about $10^{7} M_{\odot}$ will contain between 10 and 100 Pop III stellar remnants, similar to our results.
+\citet{Xu13} found that at $z = 15$, haloes with masses at about $10^{7} M_{\odot}$ will contain between 10 and 100 Pop III stellar remnants, similar to our results.
 We can also look at the spread in creation times of these Pop III stars per halo, shown in Figure \ref{fig:p3spread_mass}.
-The halos that have a zero spread in their Pop III creation time, meaning the Pop III stars formed at the same time, lie at $10^{-2}$ Myr.
+The haloes that have a zero spread in their Pop III creation time, meaning the Pop III stars formed at the same time, lie at $10^{-2}$ Myr.
 The red line indicates the median spread in creation times for each halo mass bin.
 There are two groups within this plot.
-The first group contains halos that form their Pop III stars in a spread of < 10 Myr, with a median spread of about 0.1 Myr.
-The second group contains halos that form their Pop III stars in a spread of > 10 Myr, with a median spread of about 100 Myr.
-The second group represents typically larger mass halos that have acquired older Pop III stars by the end of the simulation through their long merger history.
-These halos have acquired these Pop III stars from outside halos, accounting for the large spread in Pop III creation time as well as the increased number of Pop III stars, as seen in the right panel of Figure \ref{fig:num_p3}.
+The first group contains haloes that form their Pop III stars in a spread of < 10 Myr, with a median spread of about 0.1 Myr.
+The second group contains haloes that form their Pop III stars in a spread of > 10 Myr, with a median spread of about 100 Myr.
+The second group represents typically larger mass haloes that have acquired older Pop III stars by the end of the simulation through their long merger history.
+These haloes have acquired these Pop III stars from outside haloes, accounting for the large spread in Pop III creation time as well as the increased number of Pop III stars, as seen in the right panel of Figure \ref{fig:num_p3}.
 
@@
 On the right, the red line indicates the median number of Pop III stars in each halo mass bin.
-By the end of the simulation, high mass halos contain a large number of Pop III stars due to their long merger history with smaller halos hosting Pop III stars.}
+By the end of the simulation, high mass haloes contain a large number of Pop III stars due to their long merger history with smaller haloes hosting Pop III stars.}
   \label{fig:num_p3}
@@
 	\includegraphics[width=\columnwidth]{images/totp3mass_halomass_sidehist.pdf}
-    \caption{Total mass of Pop III stars in halos hosting new Pop III stars versus halo mass.
+    \caption{Total mass of Pop III stars in haloes hosting new Pop III stars versus halo mass.
 Lines of constant star formation efficiencies are overplotted.
-Most halos form Pop III stars at efficiencies between 10$^{-3}$ and 10$^{-4}$.}
+Most haloes form Pop III stars at efficiencies between 10$^{-3}$ and 10$^{-4}$.}
     \label{fig:totp3mass_halomass_sidehist}
@@
 The red line indicates the median spread in creation times for each halo mass bin.
-There are two groups that appear in this plot, halos that have a spread of less than 10 Myr, representing halos that form Pop III stars quickly, and halos that have a spread of greater than 10 Myr, representing larger mass halos that acquire old Pop III stars through mergers.}
+There are two groups that appear in this plot, haloes that have a spread of less than 10 Myr, representing haloes that form Pop III stars quickly, and haloes that have a spread of greater than 10 Myr, representing larger mass haloes that acquire old Pop III stars through mergers.}
     \label{fig:p3spread_mass}
@@
 Previous studies have focused on the minimum halo mass of Pop III hosts as a function of LW intensity.
-However, they have also found that Pop III stars often form in halos up to an order of magnitude greater than the minimum.
+However, they have also found that Pop III stars often form in haloes up to an order of magnitude greater than the minimum.
 We also have found that Pop III star formation occurs in a similar range of host halo masses throughout our simulation.
@@
 Second-generation stars forming later in that halo could still be metal-free if no external enrichment occurs.
-Thus they would form in halos substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.
+Thus they would form in haloes substantially larger than the minimum, as it takes tens of millions of years for the halo to recover its gas after radiative feedback \citep{Muratov13, Jeon14_Recovery}.
 
 Second, dynamical heating from mergers and accretion provide a heating source inside the growing halo, preventing the gas from efficiently cooling via \hh{}.
-This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situation but otherwise forms in halos more massive than the minimum \citep{Yoshida03, Wise19}.
+This turbulent stirring can delay star formation that could cool through \hh{} in an ideal situation but otherwise forms in haloes more massive than the minimum \citep{Yoshida03, Wise19}.
 
 Finally, temporal fluctuations in the local LW radiation field can greatly affect the amount of \hh{} within a halo and thus, how efficiently the halo can cool.
-While this may only be a small effect in some halos where the local LW radiation fluctuations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in halos that are close to active star formation sites.
+While this may only be a small effect in some haloes where the local LW radiation fluctuations are relatively small and star formation is distant, Pop III star formation may be significantly delayed or completely prevented in haloes that are close to active star formation sites.
 In summary, the timing of Pop III star formation depends on both local -- halo histories of star formation and growth -- and environmental properties.
-The combination of these three processes determines which halos will be able to form Pop III stars, and thus results in a wide range of host halo masses.
+The combination of these three processes determines which haloes will be able to form Pop III stars, and thus results in a wide range of host halo masses.
 
@@
 At $z = 15$, this minimum halo mass is $10^{6} M_{\odot}$.
-\citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and found that metal-free halos can exist until z $\approx$ 6 using cosmological simulations and an analytical model for metal enrichment.
-They also provide some insight into whether or not Pop III supernova rates are high enough within these metal-free halos to allow for the LSST to see these regions of the universe.
+\citet{Trenti09} uses a similar argument as \citet{Tegmark97}, and found that metal-free haloes can exist until z $\approx$ 6 using cosmological simulations and an analytical model for metal enrichment.
+They also provide some insight into whether or not Pop III supernova rates are high enough within these metal-free haloes to allow for the LSST to see these regions of the universe.
 They used the minimum halo mass capable of cooling via \hh{} from \citet{Trenti09_SFR} as one part of their halo mass model (see the blue solid line in Figure \ref{fig:compare_JLW_mass}, given our LW background).
 Neither \citet{Trenti09} nor \citet{Tegmark97} included the effects of \hh{} self-shielding, which can explain the discrepancy between our data and their mass threshold relationship (Figure \ref{fig:compare_JLW_mass}).
-For a LW background of $J_{\rm LW} / J_{21} = 0.2$, we see halos hosting Pop III stars down to $4 \times 10^{5}$ M$_{\odot}$, while the relation from \citet{Trenti09_SFR} would expect to see minimum halo masses capable of cooling, and thus capable of hosting Pop III stars, at $10^7$ M$_{\odot}$, almost two orders of magnitude larger.
-Since we include \hh{} self-shielding, Pop III stars are allowed to form in smaller mass halos for a given LW background.
+For a LW background of $J_{\rm LW} / J_{21} = 0.2$, we see haloes hosting Pop III stars down to $4 \times 10^{5}$ M$_{\odot}$, while the relation from \citet{Trenti09_SFR} would expect to see minimum halo masses capable of cooling, and thus capable of hosting Pop III stars, at $10^7$ M$_{\odot}$, almost two orders of magnitude larger.
+Since we include \hh{} self-shielding, Pop III stars are allowed to form in smaller mass haloes for a given LW background.
 
-\citet{Visbal14} used one-zone models to study the gaseous centers of dark matter halos and how they react to a LW background.
+\citet{Visbal14} used one-zone models to study the gaseous centers of dark matter haloes and how they react to a LW background.
 They use a particular parametrization of the central gas density, which then follows their analytic equation for critical mass (see their Equation 4) to within a factor of two.
 This critical mass is plotted in our Figure \ref{fig:compare_JLW_mass} at redshift 20.
-Here almost all of our halos fall below their critical mass relationship, with only the highest mass halos rising above.
+Here almost all of our haloes fall below their critical mass relationship, with only the highest mass haloes rising above.
 \citeauthor{Visbal14} also compare their results to three-dimensional hydrodynamical simulations, where they find similar threshold halo masses as \citet{Machacek01}.
@@
 
-It should be noted that because our box is fairly small, we cannot capture the cosmic variance of rare halos and galaxies.
+It should be noted that because our box is fairly small, we cannot capture the cosmic variance of rare haloes and galaxies.
 For example, at late times, a single galaxy dominates the LW radiation field, and drives up the host halo masses.
@@
 They followed the growth of structure to find where gas cools and condenses which would form the first stars, and how the effects of LW radiation may affect these gas clouds.
-Importantly, they included \hh{} self-shielding within halos.
-In a series of simulations, they found a minimum halo mass for those halos hosting gas clouds which may result in active star formation (see their Figure 12).
+Importantly, they included \hh{} self-shielding within haloes.
+In a series of simulations, they found a minimum halo mass for those haloes hosting gas clouds which may result in active star formation (see their Figure 12).
 They found that in the presence of a LW background of 0.01 $J_{21}$, the minimum halo mass is $7 \times 10^{5} M_{\odot}$.
@@
 In comparison with our work, we find similar minimum halo masses for each redshift, although we do see a wider range of halo masses, ranging from $2.8 \times 10^{5}$ M$_{\odot}$ to $1.4 \times 10^{7}$ M$_{\odot}$.
-While our halos never experience a LW intensity as low as 0.01 $J_{21}$, we find that their minimum mass for this LW intensity lies in the same mass range as our halos (see blue open circle in Figure \ref{fig:compare_JLW_mass}).
+While our haloes never experience a LW intensity as low as 0.01 $J_{21}$, we find that their minimum mass for this LW intensity lies in the same mass range as our haloes (see blue open circle in Figure \ref{fig:compare_JLW_mass}).
 
@@
 \citet{Hirano15} used cosmological simulations to study 1540 collapsing metal-free gas clouds in the early universe to derive the corresponding primordial stellar mass distribution.
-They find that stars form in halos above virial masses $M_{\rm vir} = 2.1 \times 10^5 M_{\odot}$ at $z = 30$ and $M_{\rm vir} = 9.9 \times 10^5 M_{\odot}$ at $z = 10$.
+They find that stars form in haloes above virial masses $M_{\rm vir} = 2.1 \times 10^5 M_{\odot}$ at $z = 30$ and $M_{\rm vir} = 9.9 \times 10^5 M_{\odot}$ at $z = 10$.
 These masses are consistent with our results with our mean halo mass lying between these values.
@@
 $J_{LW}$ = 0 for the various sources is plotted here at $J_{\rm LW}$/$J_{21}$ = 10$^{-4}$.
-\textbf{The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}} The solid bands of halo masses correspond to the characteristic masses of halos to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
+\textbf{The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}} The solid bands of halo masses correspond to the characteristic masses of haloes to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
 For each band, the maximum halo mass occurs at $z = 15$.
@@
 
-\citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling halos can vary significantly depending on the ionisation front within the halo.
+\citet{Schauer17} investigated the escape fraction of LW photons in the near and far-field and found that the LW escape fraction of atomic cooling haloes can vary significantly depending on the ionisation front within the halo.
 In the near-field with an ionisation front breaking out of a halo, they find that the LW escape fraction is greater than 95\%.
@@
 
-\citet{kitayama04} investigated the transition between D-type and R-type ionization fronts within halos to determine the escape fractions of ionizing and photodissociating photons using a one-dimensional Lagrangian hydrodynamics code.
-They found that in halos with masses $< 10^6 M_{\odot}$, escape fractions are greater than 80 \%, and in larger mass halos, with masses $> 10^7 M_{\odot}$, the escape fractions are essentially zero.
-Since we are not accounting for the reduced escape fraction within our halos, we are overestimating the LW radiation coming from point sources in our simulation.
+\citet{kitayama04} investigated the transition between D-type and R-type ionization fronts within haloes to determine the escape fractions of ionizing and photodissociating photons using a one-dimensional Lagrangian hydrodynamics code.
+They found that in haloes with masses $< 10^6 M_{\odot}$, escape fractions are greater than 80 \%, and in larger mass haloes, with masses $> 10^7 M_{\odot}$, the escape fractions are essentially zero.
+Since we are not accounting for the reduced escape fraction within our haloes, we are overestimating the LW radiation coming from point sources in our simulation.
 We could account for this by decreasing the intensity of the stars, since the overall LW radiation would be reduced, although this should not significantly affect our results as we find little dependence on LW intensity.
@@
 Pop III star formation is delayed by an average of $\delta z = 4$ by increasing the halo mass needed to overcome the bulk velocity by about a factor of three \citep{Greif11_Delay}.
-The streaming velocities will generally result in lower gas densities within halos as well as an offset of the peak density from the center of the halo \citep{OLeary12}.
+The streaming velocities will generally result in lower gas densities within haloes as well as an offset of the peak density from the center of the halo \citep{OLeary12}.
 \citet{Naoz13} estimated the minimum mass needed to retain the bulk of the baryons within the dark matter halo using a series of cosmological simulations, the results of which can be seen in Figure \ref{fig:compare_JLW_mass} (see shaded bands).
-These halos only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc} = 3 \kms$ at $z=99$, which is smaller than the star forming halos in our simulation.
-\citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass halos.
+These haloes only reach up to about $2 - 3 \times 10^5 M_\odot$ when the streaming velocity is about $1\sigma_{\rm vbc} = 3 \kms$ at $z=99$, which is smaller than the star forming haloes in our simulation.
+\citet{Naoz13} mention that at the largest streaming velocity, their simulations do not match expected values due to a small sample size of high mass haloes.
 
-\textbf{A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within halos for varying streaming velocities, showed that high streaming velocities could restrict first star formation to atomic cooling halos in the most extreme cases.
+\textbf{A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within haloes for varying streaming velocities, showed that high streaming velocities could restrict first star formation to atomic cooling haloes in the most extreme cases.
 Their minimum halo masses which host cold dense gas for various streaming velocities are shown as black horizontal lines in Figure \ref{fig:compare_JLW_mass}.
-\citet{Hirano17_Science} investigated the effect that streaming velocities have on massive black hole seed formation and find that in regions with high streaming velocities and for z $> 30$, first generation star formation can be suppressed in minihalos up to the atomic cooling limit.}
+\citet{Hirano17_Science} investigated the effect that streaming velocities have on massive black hole seed formation and find that in regions with high streaming velocities and for z $> 30$, first generation star formation can be suppressed in minihaloes up to the atomic cooling limit.}
 
-\textbf{The results of \citet{Naoz13} and \citep{Schauer19} in Figure \ref{fig:compare_JLW_mass} show that typical streaming velocities ($\le 1\sigma_{\rm vbc} = 5.8\kms$ at $z=199$) would affect halos below $10^6~\Ms$, especially at redshifts $z>20$ when streaming velocities are the strongest.
-Our results sample minihalos that experience such streaming velocities primarily at $z < 20$, whereas \citet{Hirano17_Science} studied much earlier structure formation.
+\textbf{The results of \citet{Naoz13} and \citep{Schauer19} in Figure \ref{fig:compare_JLW_mass} show that typical streaming velocities ($\le 1\sigma_{\rm vbc} = 5.8\kms$ at $z=199$) would affect haloes below $10^6~\Ms$, especially at redshifts $z>20$ when streaming velocities are the strongest.
+Our results sample minihaloes that experience such streaming velocities primarily at $z < 20$, whereas \citet{Hirano17_Science} studied much earlier structure formation.
 In the evolution of a halo affected by streaming velocities, it would have started to accumulate gas once above these critical masses while also being irradiated by a LW background.
@@
 \begin{itemize}
-	\item We find that Pop III stars are forming in halos with a mean mass below $10^{6}$ M$_{\odot}$, which falls well below the M01 relation, until $z=15$, at which point the mean halo mass rises above the M01 relation to a mean value of $3 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
-	\item \hh{} self-shielding allows halos below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.
-Self-shielding creates a disconnect between the \textbf{instantaneous} LW background and the collapse, resulting in a broad mass distribution of metal-free star forming halos and no strict correlation between the two quantities.
+	\item We find that Pop III stars are forming in haloes with a mean mass below $10^{6}$ M$_{\odot}$, which falls well below the M01 relation, until $z=15$, at which point the mean halo mass rises above the M01 relation to a mean value of $3 \times 10^{6}$ M$_{\odot}$ due to the domination of LW radiation produced by metal-enriched stars in the most massive galaxy in the simulation box.
+	\item \hh{} self-shielding allows haloes below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.
+Self-shielding creates a disconnect between the \textbf{instantaneous} LW background and the collapse, resulting in a broad mass distribution of metal-free star forming haloes and no strict correlation between the two quantities.
 	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
-	\item By the end of the simulation, halos with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass halos, resulting in galaxies with young and old metal-free stars.
+	\item By the end of the simulation, haloes with masses $>10^{7} M_{\odot}$ acquire multiple Pop III stars due to mergers with smaller mass haloes, resulting in galaxies with young and old metal-free stars.
 \end{itemize}
@@
 Our results provide another piece of the Pop III puzzle.
-With the inclusion of \hh{} self-shielding, we find Pop III stars forming in smaller mass halos than previously predicted.
-These smaller mass halos provide earlier and additional sites for Pop III star formation, and therefore, more metal-enrichment within halos.
+With the inclusion of \hh{} self-shielding, we find Pop III stars forming in smaller mass haloes than previously predicted.
+These smaller mass haloes provide earlier and additional sites for Pop III star formation, and therefore, more metal-enrichment within haloes.
 We also find that Pop III stars do not necessarily have to form in isolation, in fact, they are more likely to form in a halo that has already formed multiple other Pop III stars.
@@
 The assumptions often made about the formation of Pop III stars, like how they will only form in isolation and how the LW background mainly determines the collapse mass, appear to break down when self-shielding is taken into account and restrictions about their formation are lifted.
-Further work needs to be done to determine why some halos form Pop III stars and others do not, to provide insight about the formation process of these stars and thus how they will affect their surrounding pre-galactic environment.
+Further work needs to be done to determine why some haloes form Pop III stars and others do not, to provide insight about the formation process of these stars and thus how they will affect their surrounding pre-galactic environment.
 The effect of the LW intensity on host halo mass should be systematically investigated with \hh{} self-shielding to determine whether or not this background radiation really has a profound effect on Pop III formation or not.

### 2019-12-05 referee_2.tex
Fixing typo in response v2

@@
 Furthermore, we remind the reader about this lower limit in Section 3.3, where we present our results on the stellar multiplicity.
-Lastly, we have added a paragraph in the Caveats section (S4.3) about our simulation not resolving fragmentation below 0.625 pc and conclude that our work strengthens the case for multiple Pop III stars in each halo, especially considering this limitation.
+Lastly, we have added a paragraph in the Caveats section (\S4.3) about our simulation not resolving fragmentation below 0.625 pc and conclude that our work strengthens the case for multiple Pop III stars in each halo, especially considering this limitation.
 
@@
 \end{referee}
-    We have added a panel to the left of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minimums related to streaming velocities.
+    We have added a panel to the left of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minima related to streaming velocities.
 
@@
 
-    We have added a short comparison to Hirano+17 (Science) and have also added their citation to the list of citations mentioned previously.
+    We have added a short comparison to Hirano+17 (Science) and Schauer+19 have also added their citation to the list of citations mentioned previously.
 

### 2019-12-06 referee_2.tex
Fixing minor errors. Added statement about fixing Figure 7. Final versions to be submitted.

@@
 \end{referee}
-    We thank the reader for asking these questions.
+    We thank the referee for asking these questions.
 They have caused us to go back to our calculations to try to find the source of the increase in the shielding factor for larger halo masses.
@@
 \end{referee}
-    We have added a panel to the left of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minima related to streaming velocities.
+    We have added a panel to the right of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minima related to streaming velocities.
 
-    The limits from Schauer+19 have been added to the left panel of Figure 10, and the previous description regarding the 21cm signal has been removed.
+    The limits from Schauer+19 have been added to the right panel of Figure 10, and the previous description regarding the 21cm signal has been removed.
 Their citation has been added to the list of citations investigating streaming velocities.
 
-    We have added a short comparison to Hirano+17 (Science) and Schauer+19 have also added their citation to the list of citations mentioned previously.
+    We have added a short comparison to Hirano+17 (Science) and Schauer+19. We have also added the Hirano+17 citation to the list of citations mentioned previously.
 
@@
 
-	The sentence "Often in the literature, streaming velocities are only studied for a few haloes" has been removed.
+	The sentence ``Often in the literature, streaming velocities are only studied for a few haloes" has been removed.
 
+    We also want to point out that the right panel of Figure 7 has been adjusted to represent the data in a clearer way.
+The y-axis bins have been centered on integers, and the median red line is now centered on those bins.
 \end{document}

### 2020-01-10 paper.tex
Fixing minor errors. Added statement about fixing Figure 7. Final versions to be submitted.
Removing bolded text from .tex file for next revision.

@@
 
-In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background \textbf{at the instance of star formation}, augmenting results from prior work.
+In this paper, we focus on the distribution of host halo masses, not just the minimum, and its dependence on redshift and the LW background at the instance of star formation, augmenting results from prior work.
 We aim to provide further insight into the host haloes of Pop III stars.
@@
 The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions.
-\textbf{We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.} The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue.
+We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.
+The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue.
 At this point, about 20\% of the volume is over 10\% ionized.
@@
 
-If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.
+If within 10 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells.
 In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance.
-\textbf{We ran another 1~Mpc$^3$ simulation with the same setup as the main simulation with the exception that it was a zoom-in simulation focusing on a single minihalo of mass $5 \times 10^5~\Ms$ collapsing at $z \simeq 23$.
+We ran another 1~Mpc$^3$ simulation with the same setup as the main simulation with the exception that it was a zoom-in simulation focusing on a single minihalo of mass $5 \times 10^5~\Ms$ collapsing at $z \simeq 23$.
 Starting from 1~Myr before the collapse, we followed Pop III star formation in this one halo with a merging distance of 10, 5, 2.5, 1.25, and 0.625~pc.
-We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.
+We found that even when this number was decreased to 0.625 pc, the number of star particles that formed was unchanged.
 We note that our density threshold for star particle formation is equivalent to a molecular core.
-Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU within molecular cores \citep[e.g.][]{Turk09, Stacy11}, therefore our results on multiplicity should be considered as lower limits.}
+Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU within molecular cores \citep[e.g.][]{Turk09, Stacy11}, therefore our results on multiplicity should be considered as lower limits.
 
@@
 This results in an exponential cutoff below M$_{\rm char}$ and a power-law IMF above.
-\textbf{The Pop III IMF mass ranges from $1 \leq M / M_{\odot} \leq 300$.
-}Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
+The Pop III IMF mass ranges from $1 \leq M / M_{\odot} \leq 300$.
+Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle.
 The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere.
 In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}.
-\textbf{Again, we are only tracking the formation of metal-free molecular cores, which form either a single or multiple massive Pop III stars and perhaps several more low mass stars.}
+Again, we are only tracking the formation of metal-free molecular cores, which form either a single or multiple massive Pop III stars and perhaps several more low mass stars.
 
@@
 %====================================================================
-To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a \textbf{realistic \hh{} halo profile}, and use Equation \ref{shield} to calculate the shielding factor.
+To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a realistic \hh{} halo profile, and use Equation \ref{shield} to calculate the shielding factor.
 The \hh{} molecule number density within the halo is given by
@@
 To have an accurate depiction of the shielding factor for a given halo radius, the \hh{} fraction is given by the \hh{} fraction halo profiles at $z = 24.1$ from \citet{OShea08} (their Figure 13d) with $J_{21} = 0$, which was extracted directly from their plot.
-These profiles were approximated with a piecewise power-law for simplicity \textbf{given by $\log_{10}(f_{\rm H2}) = -0.192 \times \log_{10}(r) - 3.039$ for $r < 3.5$ pc and $\log_{10}(f_{\rm H2}) = -0.745 \times \log_{10}(r) - 2.737$ for $r > 3.5$ pc}.
-As the halo masses increase, the shielding factor \textbf{decreases}, meaning there is \textbf{more} shielding occurring within that halo.
-This behavior occurs \textbf{because as halo masses increase, more \hh{} is being added to the calculation of the column density.
-The more \hh{} present within a halo, the smaller the shielding factor will become}.
+These profiles were approximated with a piecewise power-law for simplicity given by $\log_{10}(f_{\rm H2}) = -0.192 \times \log_{10}(r) - 3.039$ for $r < 3.5$ pc and $\log_{10}(f_{\rm H2}) = -0.745 \times \log_{10}(r) - 2.737$ for $r > 3.5$ pc.
+As the halo masses increase, the shielding factor decreases, meaning there is more shielding occurring within that halo.
+This behavior occurs because as halo masses increase, more \hh{} is being added to the calculation of the column density.
+The more \hh{} present within a halo, the smaller the shielding factor will become.
 Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a Doppler broadening parameter $ b = 10 \kms$.
@@
 In the meantime, haloes form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place.
-By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity \textbf{coming from stars within the simulation} as a function of time, \textbf{the LW background given by Equation \ref{LWbg} in units of $J_{21}$,} and temperature projections of the box at certain points in time.
+By the end of the simulation, 20\% of the box has an ionized fraction greater than 10 per cent, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity coming from stars within the simulation as a function of time, the LW background given by Equation \ref{LWbg} in units of $J_{21}$, and temperature projections of the box at certain points in time.
 
@@
 The red dashed line represents the LW background implemented in the simulation (see Equation \ref{LWbg}).
-\textbf{The solid red line in the legend refers to both the solid and dashed lines in the figure.} Temperature projections are shown at the points indicated by the arrows.}
+The solid red line in the legend refers to both the solid and dashed lines in the figure.
+Temperature projections are shown at the points indicated by the arrows.}
     \label{fig:JLW_xe_mass}
@@
 In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39.
-The corresponding \textbf{comoving} star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4} \ \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 21.3$ and slowly decreases.
+The corresponding comoving star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4} \ \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 21.3$ and slowly decreases.
 The SFRD sharply declines near the end of the simulation but does not drop to zero.
@@
 In particular, it decreases at $z \le 11$ when the most massive galaxy undergoes an extended period of star formation, boosting the local LW radiation field as shown in Figure \ref{fig:JLW_xe_mass}.
-\textbf{\citet{Xu13} and \citet{Magg16} see a SFRD of $~10^{-4}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 15$ and $z = 20$ respectively.
-\citet{Jaacks19} find a SFRD of $~10^{4.5}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 20$, which flattens out to $10^{-3}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ by $z =7$.} \textbf{Our} SFRD rates are consistent with \textbf{these} other studies, but it is likely to change depending on the particular modes captured by the initial conditions.
+\citet{Xu13} and \citet{Magg16} see a SFRD of $~10^{-4}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 15$ and $z = 20$ respectively.
+\citet{Jaacks19} find a SFRD of $~10^{4.5}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 20$, which flattens out to $10^{-3}~\rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ by $z =7$.
+Our SFRD rates are consistent with these other studies, but it is likely to change depending on the particular modes captured by the initial conditions.
 
@@
 	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
-    \caption{The \textbf{comoving} star formation rate density of Pop III stars.
+    \caption{The comoving star formation rate density of Pop III stars.
 The SFRD peaks at a redshift of 20, and slowly falls off.
@@
 
-The LW background intensity \textbf{at the instance of Pop III star formation} versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}.
+The LW background intensity at the instance of Pop III star formation versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}.
 Because the LW background only varies by a factor of five as Pop III stars form, most points lie within a small intensity range, just below $1~J_{21}$.
@@
 Given that the background intensity only varies by a factor of five, previous work suggested that most haloes should have formed stars around or above the M01 relationship.
-However, we see a large spread in host halo masses, over an order of magnitude, and no clear relationship between the \textbf{instantaneous} LW intensity and the host halo mass.
+However, we see a large spread in host halo masses, over an order of magnitude, and no clear relationship between the instantaneous LW intensity and the host halo mass.
 This behavior suggests that the LW intensity is not the primary indicator of the mass at which a metal-free halo collapses.
 \hh{} self-shielding is the main cause behind this conclusion because the internal dynamics and chemo-thermal evolution are now isolated from its large-scale environment and mostly depends on the local conditions within the halo.
-\textbf{Alternatively, it is possible that there could be a correlation between the time-integrated LW background and the host halo mass.
-These calculations are outside the scope of this paper and require further study.}
+Alternatively, it is possible that there could be a correlation between the time-integrated LW background and the host halo mass.
+These calculations are outside the scope of this paper and require further study.
 
@@
 We now inspect the number of Pop III stars and the total mass of Pop III stars per halo.
-We are only tracking \textbf{star-forming regions where the star particles form at densities equivalent to molecular cores that may form multiple massive stars.
+We are only tracking star-forming regions where the star particles form at densities equivalent to molecular cores that may form multiple massive stars.
 Furthermore, we are not modeling the formation of low-mass stars ($<1~\Ms$) that may form out of fragmented gas at higher densities and smaller scales.
-Thus our results in this section should be considered as lower limits to the number of Pop III stars.}
+Thus our results in this section should be considered as lower limits to the number of Pop III stars.
 
@@
 $J_{LW}$ = 0 for the various sources is plotted here at $J_{\rm LW}$/$J_{21}$ = 10$^{-4}$.
-\textbf{The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}} The solid bands of halo masses correspond to the characteristic masses of haloes to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
+The right panel represents halo masses corresponding to different streaming velocities from \citet{Naoz13} and \citet{Schauer19}.
+The solid bands of halo masses correspond to the characteristic masses of haloes to contain a baryon fraction that is half of the cosmic mean for various redshifts and for the shown streaming velocities from \citet{Naoz13}.
 For each band, the maximum halo mass occurs at $z = 15$.
 For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$ (5.8 \kms{} at $z=199$), the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.
-\textbf{The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=199$, from \citet{Schauer19} are shown as horizontal black lines.}}
+The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=199$, from \citet{Schauer19} are shown as horizontal black lines.}
     \label{fig:compare_JLW_mass}
@@
 There are a few minor shortcomings to this work that should be noted.
-\textbf{As discussed in \S2.2.1, the number of Pop III star particles that form is insensitive to merging distances in our formation algorithm down to 0.625 pc.
+As discussed in \S2.2.1, the number of Pop III star particles that form is insensitive to merging distances in our formation algorithm down to 0.625 pc.
 Since this value is larger than fragmentation scales within molecular cores, it is possible that our Pop III star particles are sites for multiple Pop III star formation.
-With this in mind, our multiplicity results are only strengthened by the possibility of having more Pop III stars forming at these locations.}
+With this in mind, our multiplicity results are only strengthened by the possibility of having more Pop III stars forming at these locations.
 
@@
 
-\textbf{A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within haloes for varying streaming velocities, showed that high streaming velocities could restrict first star formation to atomic cooling haloes in the most extreme cases.
+A more recent study by \citet{Schauer19}, who used cosmological simulations to study cold gas content within haloes for varying streaming velocities, showed that high streaming velocities could restrict first star formation to atomic cooling haloes in the most extreme cases.
 Their minimum halo masses which host cold dense gas for various streaming velocities are shown as black horizontal lines in Figure \ref{fig:compare_JLW_mass}.
-\citet{Hirano17_Science} investigated the effect that streaming velocities have on massive black hole seed formation and find that in regions with high streaming velocities and for z $> 30$, first generation star formation can be suppressed in minihaloes up to the atomic cooling limit.}
+\citet{Hirano17_Science} investigated the effect that streaming velocities have on massive black hole seed formation and find that in regions with high streaming velocities and for z $> 30$, first generation star formation can be suppressed in minihaloes up to the atomic cooling limit.
 
-\textbf{The results of \citet{Naoz13} and \citep{Schauer19} in Figure \ref{fig:compare_JLW_mass} show that typical streaming velocities ($\le 1\sigma_{\rm vbc} = 5.8\kms$ at $z=199$) would affect haloes below $10^6~\Ms$, especially at redshifts $z>20$ when streaming velocities are the strongest.
+The results of \citet{Naoz13} and \citep{Schauer19} in Figure \ref{fig:compare_JLW_mass} show that typical streaming velocities ($\le 1\sigma_{\rm vbc} = 5.8\kms$ at $z=199$) would affect haloes below $10^6~\Ms$, especially at redshifts $z>20$ when streaming velocities are the strongest.
 Our results sample minihaloes that experience such streaming velocities primarily at $z < 20$, whereas \citet{Hirano17_Science} studied much earlier structure formation.
 In the evolution of a halo affected by streaming velocities, it would have started to accumulate gas once above these critical masses while also being irradiated by a LW background.
-Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our main conclusion that \hh{} plays an important role in Pop III star formation.}
+Afterwards, the collapse will be controlled by the processes discussed in Section \ref{sec:variations}, and thus streaming velocities would likely not affect our main conclusion that \hh{} plays an important role in Pop III star formation.
 
@@
 	\item \hh{} self-shielding allows haloes below the M01 mass relation, as small as half as previously thought, to cool and form Pop III stars.
-Self-shielding creates a disconnect between the \textbf{instantaneous} LW background and the collapse, resulting in a broad mass distribution of metal-free star forming haloes and no strict correlation between the two quantities.
+Self-shielding creates a disconnect between the instantaneous LW background and the collapse, resulting in a broad mass distribution of metal-free star forming haloes and no strict correlation between the two quantities.
 	\item Halos are likely to form multiple Pop III stars. At the instance of Pop III star formation, a halo will have formed a median number of four Pop III stars, up to a maximum of 16.
@@
 While we do not see any relationship between the LW intensity and Pop III host halo mass,  in order to determine exactly how the LW intensity influences the host halo mass, a more systematic approach needs to be taken.
-\textbf{The time-integrated LW background leading up to the formation of a Pop III star would be an interesting calculation to follow up with, and may result in a correlation with the host halo mass.}
+The time-integrated LW background leading up to the formation of a Pop III star would be an interesting calculation to follow up with, and may result in a correlation with the host halo mass.
 

### 2020-01-10 paper.tex
Fixing Schauer units in Figure 10

@@
 For streaming velocities of $3.4 \sigma_{\rm vbc}$, $1.7 \sigma_{\rm vbc}$, and $1 \sigma_{\rm vbc}$ (5.8 \kms{} at $z=199$), the minimum halo mass occurs at $z = 17, 22, \rm{and} \ 27$, respectively.
-The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=199$, from \citet{Schauer19} are shown as horizontal black lines.}
+The minimum halo mass hosting cold dense gas for different streaming velocities, given at their starting redshift $z=200$, from \citet{Schauer19} are shown as horizontal black lines.}
     \label{fig:compare_JLW_mass}
